### 2015-10-13 latex/article.tex
initial latex commit

\documentclass{llncs}
\usepackage{enumerate}% http://ctan.org/pkg/enumerate
\usepackage{multirow}
\usepackage{amsmath,amssymb}
\usepackage{url}
\usepackage{overpic}
\usepackage{enumerate}
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage{tikz}        % standard LaTeX graphics tool
\usetikzlibrary{arrows}
\usetikzlibrary{quotes,angles}
\usepackage{subfigure}                                 % authors: subfigures
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}   % authors: last version of algorithm display
\usepackage{todonotes}

\newcommand{\ie}{\emph{i.e.} }
\newcommand{\eg}{\emph{e.g.} }
\newcommand{\wnlog}{w.l.o.g. }
\newcommand{\Zr}{\ensuremath{\mathbb{Z}[\rho]}}
\newcommand{\C}{\ensuremath{\mathbb{C}}}
\newcommand{\E}{\ensuremath{\mathcal{E}}}

\title{Interactive Curvature Tensor  Visualization on Digital Surfaces\thanks{This work has been mainly funded by
   XXXXXXX  research
    grants.}}

\author{xxx}

 \institute{ CNRS,  LIRIS, UMR5205, F-69621, France\\
   %\email{david.coeurjolly@liris.cnrs.fr}
}
\graphicspath{{./Figs/}}
\input{macros}
\begin{document}
\maketitle

\begin{abstract}\sloppy

\keywords{isosurface visualization, Digital Geometry, Curvature estimation}
\end{abstract}

\section{Introduction}
\label{sec:introduction}

\textbf{Contributions}

\section{Preliminaries}
\label{sec:preliminaries}

\subsection{Curvature Tensor Estimation}
\label{sec:curv-tens-estim}

\subsection{Isosurface Extraction on GPU}
\label{sec:isos-extr-gpu}

\section{Interactive Visualization on GPU}
\label{sec:inter-visu-gpu}

\section{Conclusion and Discussion}
\label{sec:discussion}

\bibliographystyle{splncs03}
\bibliography{ictv}
\end{document}

### 2015-10-14 latex/CGI_Transvoxels/cgi2015_latex/template_CGIconf.tex
Vizo_light, Work In Progress Added the sources for the Transvoxels CGI paper

\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
\smartqed  % flush right qed marks, e.g. at end of proof
\usepackage{graphicx}
\journalname{CGI2015} % The correct name will be entered by the editor
\begin{document}

\title{Insert your title here}
\subtitle{Insert your subtitle here, otherwise leave blank}
\author{First Author \and Second Author}
\institute{F. Author \at first adress \and S. Author \at second address}
\date{ }% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
[Insert your abstract here] Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec imperdiet tincidunt nibh quis dictum. Pellentesque eget tellus nunc. Donec semper blandit metus vel rhoncus. Nullam tincidunt enim nibh, suscipit volutpat neque. Ut eget ipsum dolor, ac semper sapien. Nunc nec rutrum nulla. Vivamus sodales auctor orci, vel bibendum leo pretium at. Fusce placerat lectus mi. 
\keywords{First keyword \and Second keyword \and More}
\end{abstract}

\section{Section1}
\label{sec:1}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec imperdiet tincidunt nibh quis dictum. Pellentesque eget tellus nunc. Donec semper blandit metus vel rhoncus. Nullam tincidunt enim nibh, suscipit volutpat neque. Ut eget ipsum dolor, ac semper sapien. Nunc nec rutrum nulla. Vivamus sodales auctor orci, vel bibendum leo pretium at. Fusce placerat lectus mi.

\section{Section2}
\label{sec:2}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec imperdiet tincidunt nibh quis dictum. Pellentesque eget tellus nunc. Donec semper blandit metus vel rhoncus. Nullam tincidunt enim nibh, suscipit volutpat neque. Ut eget ipsum dolor, ac semper sapien. Nunc nec rutrum nulla. Vivamus sodales auctor orci, vel bibendum leo pretium at. Fusce placerat lectus mi.

\section{Section3}
\label{sec:3}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec imperdiet tincidunt nibh quis dictum. Pellentesque eget tellus nunc. Donec semper blandit metus vel rhoncus. Nullam tincidunt enim nibh, suscipit volutpat neque. Ut eget ipsum dolor, ac semper sapien. Nunc nec rutrum nulla. Vivamus sodales auctor orci, vel bibendum leo pretium at. Fusce placerat lectus mi.

\begin{figure}
	\begin{center}
			\includegraphics[width=0.9\columnwidth]{./bwgrid.jpg}
	\end{center}
	\caption{A Sample Image}
	\label{fig:1}
\end{figure}

\begin{thebibliography}{}
\bibitem{RefA}
Author, Article title, Journal, Volume, page numbers (year)
\bibitem{RefB}
Author, Book title, page numbers. Publisher, place (year)
\end{thebibliography}

\end{document}

### 2015-10-14 latex/CGI_Transvoxels/conclusion.tex
Vizo_light, Work In Progress Added the sources for the Transvoxels CGI paper

\section{Conclusion}

\paragraph{}
We presented a new tool for real-time visualisation of volumetric data.
Our method runs entirely and efficiently on the GPU.
We also triangulate the surface on the fly and therefore are able to visualize dynamic scenes such as moving metaballs.
Furthermore, with a LoD criterion that is based on the cells projected size, we prevent geometrical aliasing artefacts during rasterization.

\paragraph{}
One of the main characteristics of our solution is that it is based on MC.
Thus, it does a geometrical sampling of the object.
This implies that we can only render objects that can be sampled, \textit{i.e.} it prevents the rendering of frequencies that exceed by far the Nyquist limit.
To render such objects, ray casting based method are usually used.
Furthermore, the constant re-meshing of the object may also create popping artefacts, that could be fixed with vertex interpolation.

\paragraph{}
The choice of the LoD criterion could also improve this solution.
The actual one is based solely on the projected size of the cell. 
By combining it with the curvature of the object, we could limit the geometrical sampling issues.
However, this requires to be able to measure the curvature without pre process and with a data parallel algorithm.

### 2015-10-14 latex/CGI_Transvoxels/introduction.tex
Vizo_light, Work In Progress Added the sources for the Transvoxels CGI paper

\section{Introduction}

\paragraph{} %Intro générale
Volumetric objects are being more and more used in computer graphics.
They represent a volume by a function that associate a density to each point in world space.
This function can be defined analytically or with a dataset.
Since this representation does not contain topological information, volumetric objects are easy to manipulate.
They are hence a good candidate for procedural generation \cite{peytavie2009arches}.
They can be also be found in medical applications, considering they are the output of acquisition scanners.
Finally, this representation is widely used in gas and fluids simulation \cite{bridson2007fluid}.

\paragraph{} %Nos conditions pour assurer cette visualisation correcte
Visualising such objects is a crucial issue.
However, it imposes several constraints.
For interactive applications, it must be done in real-time.
We must also be able to render dynamic datasets such as fluids, as well as changing on the fly the data parameters.
Furthermore, visualising the results should be done as fast as possible to leave computational time for simulation purposes.
A solution would be to have a full GPU implementation that runs asynchronously from the CPU.
To sum up, an ideal method would fulfill those conditions:
\begin{itemize}
	\item Able to visualise volumetric objects in real-time.
	\item Able to handle dynamic datasets.
	\item Implemented entirely on the GPU.
\end{itemize}

\paragraph{}
There are two families of solutions to visualise volumetric data in real-time : ray casting and rasterization.
Ray casting  \cite{hadwiger2005real} accounts easily for lighting effects.
It also renders easily transparent surfaces, which can be useful when visualising medical datasets.
However, it does not fit the GPU pipeline and is thus slower than rasterization based solutions.

\paragraph{}
Our goal is to implement a solution that runs as fast as possible by taking full advantage of the GPU hardware. 
We thus choose to use rasterization.
This implies that a triangulated surface needs to be extracted from the data.
A very popular algorithm to do this triangulation is Marching Cubes (MC) \cite{lorensen1987marching}. 
It is data parallel so a GPU implementation of this method is very efficient \cite{tatarchuk2007real}.
During the rasterization process, each pixel of the framebuffer samples a unique triangle.
As a result, when several triangles project onto the same pixel, aliasing artefacts appear due to under-sampling (Figure \ref{lod}). 
To avoid such artefacts, the surface extraction must be adaptive to maintain a good sampling rate.

%\begin{figure}
%\includegraphics[height=0.125\textheight]{alias_close}
%\hfill
%\includegraphics[height=0.125\textheight]{alias_far}
%\hfill
%\includegraphics[height=0.125\textheight]{groundtruth}
%\caption{This model has a different color for each of its triangles. When close (Left), every triangle projects onto more than a pixel so the visualisation is fine. When viewed from distance (Middle), several triangles projects onto a single pixel and aliasing artefacts occur. (Right) is the same object visualised with 1024 samples per pixel.}
%\label{aliasing}
%\end{figure}

\paragraph{} %Situation par rapport au STAR
We are thus facing a problem of adaptive surface extraction, which is an extensively studied topic.
Many solutions have been developed in computational geometry \cite{shu1995adaptive,schaefer2004dual}.
However, they focus on the topology of the resulting mesh, whereas we focus on correct visualisation.
Real-time solutions have been developed using Level of Details (LoD). 
These methods dynamically refine the extracted triangulation using both the curvature of the object and its distance to the camera.
But since they rely on a preprocessing phase, they do not support visualising fully dynamic data in real-time.

\paragraph{}
Most of those LoD solutions were developed for heightfields visualisation \cite{duchaineau1997roaming}.
Yet, there are solutions that triangulate true volumetric data by applying MC on a hierarchical partition of space.
Since MC is not adaptive, the resulting hierarchical triangulation may carry cracks at resolution changes.
To avoid this, complex structures \cite{scholz2014real,schaefer2004dual} may be used or more triangles may be generated to stitch the holes \cite{lengyel2010voxel}.
Such adaptive methods run in real-time but they require both CPU and GPU time.
Furthermore, for performance purposes, some of them cache parts of the triangulation, which prevents the use of fully dynamic data.
Finally, none of the aforementioned solutions ensure a minimal triangle size, and are thus subject to aliasing issues.

\paragraph{} %What we do
The method developed by Lengyel \textit{et al.} \cite{lengyel2010voxel} is the best suited to our needs.
However, it was preferably developed to visualise in real-time static or near static data and present a complex CPU implementation.
In this paper we propose a GPU pipeline inspired from this method.
It leaves the CPU free for other tasks and avoids synchronisation with the GPU.
Our high framerate also allows this method to run in real-time on fully dynamic data. 
The triangulation is controlled by a GPU LoD criterion that ensures that triangles project onto more than one pixel, thus removing geometrical aliasing.

\paragraph{}
In the next section, we present the main algorithms on which our work is based \cite{lengyel2010voxel,dupuy2014quadtrees}. 
Then, we present our GPU implementation, followed by our results and performances.
Finally, we end up by concluding on the limitations and perspectives of our approach.

### 2015-10-14 latex/CGI_Transvoxels/introduction_GPUImplTransvo.tex
Vizo_light, Work In Progress Added the sources for the Transvoxels CGI paper

\section{Introduction}

\paragraph{}
The need of immersion and realism in video games is increasing.
Developing a game makes the use of an already existing engine mandatory.
The C4Engine is one of them.
Amongst other features, it presents a solution for real time visualisation of volumetric data.
This algorithm, developed by Lengyel \cite{lengyel2010voxel}, will be reffered as Transvoxel in the rest of the paper.

\paragraph{}
Transvoxel renders volumetric data through rasterization.
It is based on Marching Cubes (MC) \cite{lorensen1987marching} to convert the dataset into a triangulated surface.
However, where MC is not adaptive, Lengyel's method adapts the resolution of the triangulation depending on the distance to the camera.
This adaptivity is handled by applying a modified MC on an octree structure.

\paragraph{}
Therefor Lengyel's method is based on modified MC and an octree.
MC is data parallel and thus can be implemented efficiently on a GPU.
However, the octree is an recursive structure and is then handled on the CPU.
Transvoxels is finally a rendering method that runs partly on the CPU and partly on the GPU.

\paragraph{}
It would be interesting to make this solution GPU only.
This would lead to a great speed up as GPUs are very efficient when running data parallel algorithms.
Furthermore, the implementation would be simplified, as the GPU and CPU would run asynchroneously.
Finally, this would leave the CPU free for other computational tasks.

\paragraph{}
To make this algorithm GPU only, the octree need to be linearised.
This non recursive representation have been developped by Gargantini \cite{gargantini1982effective} and efficiently GPU implemented by Dupuy \cite{dupuy2014quadtrees}.
By combining those linear octrees with Transvoxels, we obtain a method to render volumetric data entirely on the GPU.

\paragraph{}
Rasterizing this surface can only be done if all triangles projects onto more than a pixel.
Otherwise, aliasing artefacts appear.
Therefor we add a LoD criteria based on the triangles projected size.
This leads to a method that is 
\begin{itemize}
	\item Real time
	\item Keeping the triangles always bigger than a pixel
	\item GPU only to free the CPU
\end{itemize}

### 2015-10-14 latex/CGI_Transvoxels/ourmethod.tex
Vizo_light, Work In Progress Added the sources for the Transvoxels CGI paper

\section{Data parallel real-time visualisation}

\begin{figure*} [t!]
  \centering
  \includegraphics[width=0.9\textwidth]{pipeline}
  \caption{ This figure summarizes our GPU pipeline. Data buffers are represented in green and computations in red. Each computation retrieves data from a buffer and fills a new one. }
  \label{fig_pipeline} 
\end{figure*}

\paragraph{}
We present a new tool for isosurfaces visualisation that is adapted to rasterization issues and runs in real-time.
It is based on the adaptive triangulation of Lengyel \textit{et al}. \cite{lengyel2010voxel}, the linear quadtrees  of Gargantini \cite{gargantini1982effective}, and the LoD criterion of Dupuy \textit{et al.} \cite{dupuy2014quadtrees}.

\paragraph{}
Our pipeline is divided in 3 parts.
\begin{itemize}
\item The first step consists in updating a linear octree that maintains the active front of cells.
\item The second step performs both a culling on the octree cells, and creates the transition cells required for a crack-free MC triangulation.
\item The last step re-subdivides and triangulates the remaining cells.
\end{itemize}
This whole process is illustrated in Figure \ref{fig_pipeline}.
In the following sections, we present each step of our solution.

\subsection{Maintaining the linear octree}

Our method triangulates a set of cells.
Therefore, the first step of our pipeline evaluates a LoD criterion on each cell to determine if it is kept, split or merged.
In this section, we present the GPU representation for those trees, as well as the criterion we use to evaluate the new partition.

\subsubsection*{Linear octree on the GPU}

\begin{figure}
\centering
\includegraphics[height=0.2\textheight]{subdivision}
\caption{The octree at frame $t$ is stored as a list of Morton codes in a buffer. 
To update the tree, we fill a new buffer representing its state at frame $t+1$. 
On the GPU, each code of the first buffer is processed in parallel. 
If the cell is to be subdivided, it writes the codes of its children in the new buffer. 
If it merges, it writes either nothing, or the code of its parent (if it is the first child).
If it is kept, it just re-writes its own code. }
\label{subdivision}
\end{figure}

\paragraph{}
Dupuy \textit{et al}. \cite{dupuy2014quadtrees} proposed an implementation to handle efficiently quadtrees on the GPU.
Here, we want to manipulate an octree, hence, we generalize their solution to the third dimension.

\paragraph{}
To represent the cells, we use Morton codes.
Those codes are a succession of locations relatively to the root node.
In three dimensions, there are $2^3 = 8$ possible locations for a node so 3 bits are required to encode one subdivision.
Thus, if we keep the codes on 32 bits as in \cite{dupuy2014quadtrees}, we will be limited to a maximal subdivision depth of 9.
This is too coarse to do a correct triangulation of the surface.
Therefore, we used 64 bits for the encoding. 
This doubles the memory size of the front but, by using 5 bits for the depth of the cell and the other 59 bits for the code, we can subdivide 19 times.

\paragraph{}
At each frame we have the active front of the previous frame, $t$, and we want to update it to get the front at frame $t+1$.
To do so, we evaluate the LoD criterion given in equation (\ref{lod_criterion}) on every cell at frame $t$.
We then test the equations (\ref{split_test}) and (\ref{merge_test}) to determine if the cell should split or merge.
If a cell splits, it emits the codes of its children.
If a cell is kept it re-emits its own code.
If a cell merges, there are two possibilities.
If it is the first child (with the lowest Morton code), it emits the code of its parent.
Otherwise, it does nothing. 
This ensures that the merging operation produce only one cell.
The new cells are written into a new buffer that represents the active front at frame $t+1$.
This is illustrated Figure \ref{subdivision}.

\subsubsection*{Improved LoD criterion}

\paragraph{}
Dupuy \textit{et al.} manipulated quadtrees, a two dimensional structure, which contained a reasonable amount of cells in their active front.
This amount is greater when using an octree as those structures are in three dimensions.
We thus extended the LoD criterion determining the partition to minimize the size of the front.
Note that our extended criterion could still be used in two dimensions.

\paragraph{}
Here, we use the criterion given equation (\ref{lod_criterion}).
Its evaluation is data parallel and controls the projected size of the cells.
However, it is based on the Euclidean distance between a cell and the camera. 
Since this distance is absolute, cells behind the camera are highly subdivided even though they do not contribute to the final image.
Therefore, we combine this Euclidean distance with a radial angle to the camera's forward direction.
Cells behind the camera are then less subdivided, which reduces the number of cells in the octree.
The new criterion is given equation \ref{improved_lod_criterion} and illustrated Figure \ref{fig_lod_octree}.
\\
\begin{equation}
z'= z +
\begin{cases}
    w \cdot z \cdot (\theta - \alpha) 	& \text{if } \theta \geq \alpha\\
    0	              		    			& \text{else.}
\end{cases}
\label{improved_lod_criterion}
\end{equation}

\begin{figure}
  	\includegraphics[width=0.4\linewidth]{viewlod1_small}
  	\hfill
  	\includegraphics[width=0.4\linewidth]{viewlod2_small}
  \caption{ Adaptive triangulation of a plane. The camera is located in the center and looks up. (Left) uses the criterion in \cite{dupuy2014quadtrees} and (Right) uses our criterion.
  The total number of cells is (Left) 1037114 and (Right) 210323.}
  \label{fig_lod_octree} 
\end{figure}

\paragraph{}
In this equation, $z$ is the Euclidean distance between the center of the cell and the camera, $\theta$ is the angle and $\alpha$ is the fovy, both expressed in radians.
The parameter $w$ controls the importance of the radial distance over the Euclidean distance.
Its value has to be chosen carefully.
If it is too high, the difference of levels between the cells on both side of the frustum becomes very important, which might break the octree consistency. 
Empirically, we found that using $w \leq 6 $ prevents artefacts.

\paragraph{}
With this new $z'$, the criterion evaluated is now $s(z')$ instead of $s(z)$.
Note that we may lose the guarantee of maintaining a restricted octree outside the frustum.
However, as those cells are not triangulated, the visualisation is not impacted.

\subsection{Culling and transitions determination}

\paragraph{}
Once the active front has been updated, it contains the list of the cells to triangulate.
We then apply frustum culling to remove the nodes that are outside the view frustum.
We also remove empty cells; a cell that is fully inside or outside the object will not generate triangles and therefore should not be triangulated.
The remaining cells are stored in a new buffer that is used as input for triangulation.

\paragraph{}
If those cells are directly triangulated, cracks will appear at resolution changes.
As, Lengyel \textit{et al.} \cite{lengyel2010voxel}, we solve this issue by inserting and triangulating transition cells.
At each frame, we identify the level changes in the octree to create the corresponding transitions.
We do so by checking if a cell has a neighbour of higher resolution than itself.
%The difficulty is to do this with a data parallel method.
In our implementation, the chosen LoD criterion is fully data parallel and allows to determine if a cell has been split or merged.
Therefore, we can determine the transitions by evaluating this criterion on the neighbours of a cell.

\paragraph{}
Our LoD criterion is based on the projected size of a cell.
We thus need the position of the neighbours of the current cell.
This is easy to compute as we know the position of the cell and its size.
We then test each of them to determine if it has been split, using equation (\ref{split_test}).
If this test is verified, we emit a transition cell.
Note that each cell can then emit a maximum of 3 transitions, one for each axis.
We finally have two buffers containing the octree and transition cells.

\subsection{Triangulation and further subdivision}

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{tessellation}
  \caption{The upper configuration represents a cell with 4 more subdivided neighbours and a transition cell (red).
  This is what is returned by the update and culling steps.
  All those cells are subdivided, leading to the configuration presented on the bottom picture.
  Each cell has become a tile of $(2^N)$ cells on each dimension.
  Except for the transition cells, as their width do not change. }
  \label{tessellation} 
\end{figure}

\paragraph{}
We added a subdivision pass to increase the resolution of the extracted triangulation while staying real-time. 
When triangulating cells that are in the lowest levels of the octree, the resulting mesh is more precise. 
However, with a deeper octree, the update and culling steps are slowed down by the high number of cells to process.
We aim here at keeping the triangulation precise but with a coarser octree.

\paragraph{}
Therefore, a subdivision pass is added between the culling and the triangulation. 
It applies on every octree cell and on every transition cell.
Each octree cell is turned into a regular grid of smaller cells with a resolution of $(2^N)^3$, $N$ being a positive integer controlling the new level of subdivision.
The transition cells have a fixed width so they become a regular grid with a resolution of $(2^N)^2$ (Figure \ref{tessellation}).
This subdivision happens before the triangulation but after the LoD and culling.
This way, those first two steps run on a coarser octree, keeping their efficiency, while the triangulation is done on smaller cells, leading to a more precise mesh.

\paragraph{}
However, no culling is done on the new smaller cells.
Therefore, they will all be triangulated even if they are empty or outside the frustum. 
There is then a $N$ for which it is more interesting to cull a deeper tree than to subdivide the cells. 
Our experiments showed that the best $N$ is 2.

\paragraph{}
The last step is then to apply MC with the modified tables given by Lengyel \textit{et al.} to triangulate the cells and render our surface.

### 2015-10-14 latex/CGI_Transvoxels/preliminaries.tex
Vizo_light, Work In Progress Added the sources for the Transvoxels CGI paper

\section{Background}

The solution of Lengyel \textit{et al.} \cite{lengyel2010voxel} is based on extracting an adaptive triangulated surface by applying MC on an octree.
However, due to its recursive nature, the octree is not suited for the GPU pipeline.
Hence, to take full advantage ofthe GPU, we must convert this tree to a non recursive structure.
Such representations were first introduced by Gargantini \cite{gargantini1982effective} and are known as linear quadtrees.
They have been implemented on the GPU by Dupuy \textit{et al.} \cite{dupuy2014quadtrees}.
Along with this implementation, they presented a LoD criterion that bounds the projected size of the tree cells.

\subsection{Adaptive surface extraction}

\begin{figure}
\centering
\includegraphics[width=0.8\linewidth]{transition_cell}
\caption{ Triangulating a hierarchical grid with MC creates cracks at level changes.
To fix those, Lengyel \textit{et al}. inserts transition cells (bold).
Those cells are more subdivided on one side to patch the change of resolution.}
\label{transition_cell}
\end{figure}

\paragraph{}
Lengyel \textit{et al}. \cite{lengyel2010voxel} developed a solution to visualise volumetric data in real-time.
They start by subdividing the space with an octree.
At each frame, they select a set of cells within this tree, called the active front, that partitions the space.
The resolution of the partition varies along the space, depending on the chosen cells.
This idea is illustrated for quadtrees in the Figure \ref{fig_quadtree_partitionning}.
Whether a cell is part of this active front is determined by evaluating a LoD criterion.
The selected cells can finally be triangulated using a method similar to MC.

\paragraph{}
When two cells of different resolution meet, T-Junctions appear.
They are due to some vertices in the high resolution cells that have no match in the low resolution cell.
The problem is that when using a MC algorithm, those inconsistencies create cracks in the final triangulation.
To fix this, Lengyel \textit{et al.} inserts transition cells (Figure \ref{transition_cell}) where two cells of different level meet.
Those cells are more subdivided one on side than on the other to patch the difference of resolution.
They are then triangulated with a modified MC, producing a crack-free surface for visualisation.
However, it requires having triangulation tables adapted to the unusual structure of the transitions.
It also demands the use of a restricted octree, since the transitions only allow a single level of difference between neighbouring cells.
As the triangulation is based on modified MC, it is data parallel.

\paragraph{}
The adaptivity of the final triangulation is controlled by a LoD criterion.
Lengyel \textit{et al}. use a measure based on the distance between the cell and the camera, which must therefore be re-evaluated every time the camera moves.

\paragraph{}
On the GPU, recomputing the whole active front from the root node would be too expensive.
Instead, we update the tree by merging or splitting the cells.
If this operation could be done on the GPU, it would be possible to extract the adaptive triangulation entirely on the GPU.
This requires a non recursive representation for the tree, as well as data parallel update operations.
The LoD must also be evaluable during a data parallel process as it controls the partition.
Those properties can be found using linear trees \cite{dupuy2014quadtrees}.

\subsection{Linear Quadtrees}

\begin{figure}
\centering
\includegraphics[height=0.17\textheight]{partitioning.pdf}
\hfill
\includegraphics[height=0.17\textheight]{quadtree_activefront}
\caption{In \cite{dupuy2014quadtrees}, a linear quadtree is used to maintain a 2D hierarchical partitioning of space.
(Left) presents such a partitioning.
A cell is more or less subdivided depending on its distance to the camera.
They are also encoded with morton code, that identifies each cell with its position relatively to its parent.
(Right) shows the corresponding active front in the full tree.
This partition is entirely represented by storing the list of codes of the gray cells. }
\label{fig_quadtree_partitionning}
\end{figure}

\paragraph{}
Linear quadtrees were presented by Gargantini \cite{gargantini1982effective} as a non recursive representation for quadtrees.
Such structures were reused by Dupuy \textit{et al.} \cite{dupuy2014quadtrees} who presented a solution to handle them efficiently on the GPU.

\paragraph{}
Linear quadtrees associate a code to each cell, identifying it by its path to the root node.
The full tree is thus entirely represented by the list of its leaves' codes, which removes the recursivity.
In their implementation, Dupuy \textit{et al.} used Morton codes (Figure \ref{fig_quadtree_partitionning}).
Those codes store a spatial position, encoding the location of the cell relatively to its parent.
The final code of a cell is thus the succession of locations between the cell and the root node.
Therefore, the maximal depth of the tree depends on the number of quadrants that can be encoded.
In a quadtree, a cell is divided into $2^2$ quadrants, so encoding one subdivision requires two bits.
Dupuy \textit{et al.} store for each cell its Morton code and its depth within the tree.
Therefore, with a code stored on 32 bits, using 28 bits for the locations and 4 bits for the depth, the tree is limited to 14 levels.

\paragraph{}
Dupuy \textit{et al}. used those quadtrees to maintain a 2D hierarchical space partition.
They thus encode a front of cells within this tree (Figure \ref{fig_quadtree_partitionning}).
To determine if a cell is part of the front, they evaluate on each of them a LoD criterion.
The criterion they chose is view dependent and thus must be evaluated quickly on the GPU.

\paragraph{}
During an update, there a three possible operations on a cell: it can be kept, merged or split.
A merge operation removes the codes of the children's cells from the list and replaces them with the code of the parent cell.
A split operation removes the code of a cell replacing it by the codes of its children.
Therefore, an efficient GPU implementation relies on the fact that those operations can be done independently on each cell.
This is true as long as the LoD criterion is also evaluable independently on each cell.

\paragraph{}
With this implementation of linear tree, it is possible to maintain a quadtree on the GPU.
By generalizing this to the octree, it could be used with the triangulation presented by Lengyel \textit{et al.} to develop a fully data parallel pipeline.
There is however three conditions on the LoD criterion.
It must ensure that the extracted triangles will project onto more than one pixel, to ensure a good rasterization sampling.
The tree must also stay restricted at all times as the transition cells of Lengyel \textit{et al.} only patch cells with a single change in resolution.
Finally, this criterion must allow to detect if the neighbour of a cell is more subdivided than the cell itself in a data parallel manner.
This is mandatory to determine where the transition cells should be inserted.

\subsection{LoD on projected size}

\paragraph{}
When rasterizing a triangulated surface, to ensure a good sampling, all triangles must project onto more than one pixel.
When using a MC algorithm, the size of the generated triangles is bounded by the size of the cell.
Therefore, the cells must all project onto more than one pixel.

\paragraph{}
Dupuy \textit{et al.} \cite{dupuy2014quadtrees} addressed this issue.
They use linear quadtrees to achieve adaptive tessellation.
The subdivision of their quadtree's cells is controlled by a LoD criterion that is evaluable on the GPU and that is based on the cells projected size.
This ensures that all cells project onto more than a pixel.
This criterion is given in equation (\ref{lod_criterion}).
\\
\begin{equation}
s(z) = z \cdot \tan(\alpha)
\label{lod_criterion}
\end{equation}

\paragraph{}
Here, $2 \cdot s(z)$ is the projected screen size at a distance $z$ from the camera, and $2\cdot\alpha$ is the horizontal viewing angle (the fovy). 
To determine if a cell should be merged/split, the ratio $$\frac{\mathrm{cell\_size}}{2 \cdot s(z)}$$ is evaluated.
This ratio is compared to a factor $k$ that controls the density of the triangulation.\\
\begin{equation}
\mathrm{If} \hspace{15pt} \frac{\mathrm{cell\_size}}{2 \cdot s(z)} \geq k \hspace{15pt} \mathrm{then} \hspace{3pt} \mathrm{split}
\label{split_test}
\end{equation}
\begin{equation}
\mathrm{Else} \hspace{3pt} \mathrm{if} \hspace{15pt} \frac{\mathrm{parent\_cell\_size}}{2 \cdot s(z_{\mathrm{parent}})} \leq k \hspace{15pt} \mathrm{then} \hspace{3pt} \mathrm{merge}
\label{merge_test}
\end{equation}
\begin{equation*}
\mathrm{Else} \hspace{3pt} \mathrm{keep}
\end{equation*}
\paragraph{}
Evaluating (\ref{split_test}) splits a cell if its project size exceeds a certain amount.
Equation \ref{merge_test} determines if a cell should merge by testing if the parent of this cell should be split.
This guarantees that all the children of a cell will merge at the same time, since they will all evaluate the criterion on the same parent.
This criterion also maintains a restricted quadtree while the condition $$\frac{\mathrm{cell\_size}}{2 \cdot s(z)} < 2 \cdot k $$ is always verified.
For $k = 2$ , this is ensured as long as the horizontal viewing angle doesn't exceed $142^o$.
We prove this in Appendix 1.

\paragraph{}
This LoD criterion has the four characteristics that we need:
\begin{itemize}
	\item It is data parallel.
	\item It can ensure that the cells project onto more than one pixel.
	\item It maintains a restricted tree.
	\item Its evaluation returns if a cell should split or merge.
\end{itemize}
Therefore, by generalizing it to the octree, we could use it with Lengyel \textit{et al.} triangulation method to implement an adaptive visualisation pipeline on the GPU.

### 2015-10-14 latex/CGI_Transvoxels/results.tex
Vizo_light, Work In Progress Added the sources for the Transvoxels CGI paper

\section{Results}

We tested our method with an Intel Pentium 3550M processor and a NVIDIA GeForce GTX 850M GPU. 
We implemented it with C++ and GLSL. 
The pipeline runs with geometry shaders, combined with transform feedbacks.

\paragraph{}
We ran our method on different volumetric datasets.
The first one is a stack-based representation of a terrain, called Moria, created with the ARCHES framework \cite{peytavie2009arches}.
It contains $512^3$ voxels, which we uploaded on the GPU using a 3D texture.
We also used two other datasets to further illustrate the performances of our method.
We first visualised a set of metaballs.
Those implicit surfaces are defined analytically to be evaluated on the GPU and are updated at every frame.
This scene creates objects that goes through high geometrical changes and thus cannot be precomputed.
We also visualised an animated ocean.
This object is again defined analytically and evaluated on the GPU. 
All those scenes are illustrated in Figure \ref{final_outputs} and in the accompanying video.

\paragraph{}
In all our experiments, we used the LoD criterion given in equation (\ref{improved_lod_criterion}).
This criterion is data parallel and is based on the projected size of the cells.
It thus prevents rasterization under-sampling and can be efficiently used on the GPU (Figure \ref{lod})

\begin{figure}
\centering
\includegraphics[height=0.2\textheight]{alias}
\hfill
\includegraphics[height=0.2\textheight]{filtered}
\caption{Each extracted triangle has a different color. (Right) presents the result of rasterizing an object visualised with a regular grid. (Left) presents the result of rasterizing an object visualised with our LoD criterion. It can be seen that the aliasing artefacts present on (Right) disappeared on (Left).}
\label{lod}
\end{figure}

\subsection{Stack-based terrain}

\paragraph{}
We ran our method on the Moria scene \cite{peytavie2009arches}, enhanced with a noise function to add high resolution geometric details.
We present the average execution times for each step of the pipeline, as well as the number of cells in input (Table \ref{table_step}).

\begin{table}[tb]
\centering
\begin{tabular}{|l|c|c|c|}
\hline
Step           & Time (ms) & \#Cells & Memory (MB) \\ \hline
Update         & 1.13      & 219295  & 1.67        \\
Culling        & 3.3       & 219295  & 1.67        \\
Triangulation  & 0.94      & 5570    & 0.04        \\ \hline
Total GPU time & \multicolumn{3}{c|}{5.4}           \\ 
Total CPU Time & \multicolumn{3}{c|}{2.3}          \\ \hline
\end{tabular}
\caption{Average execution time for each step of the pipeline during a flythrough of the Moria scene.
The first column gives the average execution time, 
the second contains the number of cells in input, and
the last gives the memory size of the buffer used.
Since each cell is coded on 64 bits, the memory footprint of a buffer is $\mathrm{buffer\_size} * 64$ bits.}
\label{table_step}
\end{table}

\paragraph{}
We can note that updating the octree is very fast (less than 2 ms) whereas the culling step is slower (by roughly 300\%).
This is due to the fact that this pass runs tests on the whole partition, which can be computationally expensive.
Nonetheless, this efficient culling allows the triangulation to run on a very small amount of cells, thus reaching very good performances.
Finally, the total GPU time needed to update and triangulate the new frame is under 6 ms (180 FPS), for a memory consumption of only 4 MB.
Furthermore, as every computation is done on the GPU, the CPU is only active for 2 ms to initiate the shaders.

\subsection{Animated metaballs}

\paragraph{}
The cells inside the frustum are re-triangulated at each frame.
Therefore, it is possible to visualise fully dynamic data without any performance loss.
We tested this while visualising animated metaballs.
When running our experiments, the animation was stopped between the frames 5000 and 10000.
We can then show that our framerate is not affected by the changes in the scene.
The camera was static during the whole experiment to remove all variability that would have been induced if the number of cells to evaluate was changing.
The resulting graph is shown in Figure \ref{metaballs_graph}.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{l_importance_d_etre_constant}
\caption{Rendering time for an animated scene. 
The average rendering time is about 3 ms even though the object is re-triangulated on each frame.
Those timings do not include the shading.
The blue box identifies the frames during which the object was static.
As can be seen, the fact that the object is or not animated has no impact whatsoever on the rendering time.}
\label{metaballs_graph}
\end{figure}

\paragraph{}
As can be seen on this graph, the triangulation timings are constant.
The only variability that can be measured is induced by the task scheduling on the GPU.

\subsection{Comparison}

%\paragraph{}
%Our goal in this work is to get a correct visualisation as fast as possible.
%The surface is triangulated for rasterization purposes and is not kept in memory.
%This differs from other methods that focuses on the topology of the mesh and return a full mesh.
%Furthermore, we gave ourselves the constraint that this method should be completely data parallel.
%This condition allows us to present a full GPU implementation with very high framerates.
%From those, we can afford to re-triangulate the whole object on the fly and still do a real-time visualisation.
%This differentiate our solution from most methods that achieve real-time through pre-process and data caching.

\paragraph{}
As developed during the introduction, there are several kind of methods on the state of the art.
The first category focuses on extracting a complete mesh from the data and are thus slower than methods that aim only at visualisation.
Amongst the visualisation solutions, the real-time is mostly achieved with data caching and pre-processing.
Here, we constrained ourselves to run in real-time without this data-caching and pre-processing, by taking full advantage of the GPU.
The solutions developed by other methods are thus quite different from ours.

\paragraph{}
We present a completely data parallel implementation based on the method of Lengyel \textit{et al}. \cite{lengyel2010voxel}.
Therefore, a pertinent comparison to prove our solution would be to compare both algorithms.
Since the method of Lengyel \textit{et al}. is part of a commercial game engine, it is not freely accessible.
We used instead a free implementation, independently developed by Lanner \cite{lanner}.
This implementation is based on data-caching.
The volumetric object is pre-triangulated at every level of detail during a preprocess.
Therefore during rendering, the only task left is to identify the cells of the octree's active front and to send their pre-computed triangulation to the GPU.
This increases the rendering speed but the preprocessing time can be prohibitive.
Furthermore, it is memory intensive.
Still, this implementation is very fast and allows localized modifications of the data.

\paragraph{}
We ran both methods on a static voxel based scene, adapting the LoD criteria to have a similar behaviour.
The dataset has a resolution of $256^3$.
The results are given in Figure \ref{cpu_gpu}.
It can be seen on this graph that even though we re-triangulate the cells at each frame, we are still running faster than a CPU implementation.
Furthermore, there is no transfer between the CPU and the GPU in our implementation.
This give us a speed up over CPU implementations that are constantly transferring data to the GPU.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{cpu_gpu}
\caption{Comparison between our GPU solution and Lanner's implementation \cite{lanner}.
This graph presents the execution time in ms for each frame.
}
\label{cpu_gpu}
\end{figure}

\begin{figure*}
\centering
\includegraphics[height=0.17\textheight]{metaballs}
\hfill
\includegraphics[height=0.17\textheight]{ocean}
\hfill
\includegraphics[height=0.17\textheight]{moria2}
\caption{This shows some outputs of our program. (Left) is an example of moving metaballs. (Middle) is an animated ocean. (Right) is a stack based terrain from the ARCHES plateform \cite{peytavie2009arches} }
\label{final_outputs}
\end{figure*}

### 2015-10-14 latex/CGI_Transvoxels/template_CGIconf.tex
Vizo_light, Work In Progress Added the sources for the Transvoxels CGI paper

\RequirePackage{fix-cm}

%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{cgi2015_latex/svjour3}          % twocolumn
\smartqed  % flush right qed marks, e.g. at end of proof
\usepackage{graphicx}
\usepackage{amsmath, amssymb}
\journalname{CGI2015} % The correct name will be entered by the editor

\graphicspath{{figures/}}

\begin{document}

\title{Real-time visualisation of volumetric data on the GPU}
\subtitle{}
\author{H. Perrier \and J. Dupuy \and J.-C. Iehl \and J.-P. Farrugia}
\institute{H. Perrier \at helene.perrier@liris.cnrs.fr \and J. Dupuy \at jonathan.dupuy@liris.cnrs.fr \and J.-C. Iehl \at jean-claude.iehl@liris.cnrs.fr \and J.-P. Farrugia \at jean-philippe.farrugia@liris.cnrs.fr}
\date{ }% The correct dates will be entered by the editor

\maketitle

\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{octree}
\includegraphics[width=0.7\linewidth]{mesh_muti_res}
\includegraphics[width=0.7\linewidth]{terrain_potential}
\caption{Our method is based on Lengyel's algorithm \cite{lengyel2010voxel} combined with a linear restricted octree (top) which allows us to create adaptive meshes (middle) from volumetric data in real-time (bottom).}
\end{figure}

\begin{abstract}
We present a tool to visualise volumetric data in real-time by extracting an adaptive triangulated surface from the object.
We extend an existing adaptive marching cubes solution and increase its execution speed by developing a pipeline that is fully data parallel and implemented on the GPU.
This lets us visualise in real-time static scenes as well as fully dynamic data.
Furthermore, we propose a criterion to control the adaptivity of the triangulation that adds control over the projected size of triangles.
This allow us to remove geometric aliasing in the resulting rendering.
\keywords{GPU, Real-time, Level of Details, Volumetric Datasets}
\end{abstract}

\input{introduction}
%p1 : pourquoi volumes cools et important de les visu
%p2 : nos contraintes et pk celles là
%p3 : les methodes actuelles ac leurs objectifs !=
%p4 : ce qu'on fait
%p5 : plan

\input{preliminaries} %previous work
\input{ourmethod} %how/why it works
\input{results} %how awesome it is
\input{conclusion} %how it could be more awesome

\bibliographystyle{alpha}
\bibliography{bibtex}

\appendix

\section{Ensuring a restricted octree}

\paragraph{}
To partition the space, Dupuy \textit{et al}. use the criterion given in equation (\ref{lod_criterion}).
They then test the size of the cell over this criterion.
If equation (\ref{ratio_division}) is verified, it means that the cell will be twice more subdivided than its neighbour.
To maintain a restricted tree, we need to ensure that it never happens.\\
\begin{equation}
\frac{\mathrm{cell\_size}}{2 \cdot s(z)} < 2k
\label{ratio_division}
\end{equation}

\paragraph{}
We illustrate this limit case Figure \ref{proof_constraint}.
Because the only variable is $\alpha$, we need to bound it.
From Thales, we can deduce:
$$
\frac{2k \cdot s(z)}{s(z)} = \frac{z + s(z)}{z}
$$
From this, we can express $z$ in terms of $s(z)$:
$$
z = \frac{s(z)}{2k - 1}
$$
Finally, trigonometry gives us:
$$
tan(\alpha) = 2k - 1
$$
As $\alpha$ is half the horizontal viewing angle, the octree is constraint as long as $\alpha < 2\arctan(2k - 1)$
For $k = 2$, this implies that the fovy must not exceed $142^o$.

\begin{figure} [h]
\centering
\includegraphics[height=0.2\textheight]{proof1}
\caption{If this situation happens, the LoD criterion no longer ensures to maintain a restricted tree.
The parameter $\alpha$ is thus bounded. Over a certain value, a cell can have two level of differences with its neighbours.
This figure is willingly wrongly scaled for readability purposes.}
\label{proof_constraint}
\end{figure}

\end{document}

### 2015-10-14 src/cpp/vizo_light/DataLoader.cpp

@@ -5,11 +5,12 @@
 #include <cstring>
 
 const GLenum MIN_FILT = GL_LINEAR_MIPMAP_LINEAR;
-const GLenum MAG_FILT = GL_LINEAR;
+//const GLenum MAG_FILT = GL_LINEAR;
 //const GLenum MIN_FILT = GL_NEAREST_MIPMAP_NEAREST;
-//const GLenum MAG_FILT = GL_NEAREST;
+const GLenum MAG_FILT = GL_NEAREST;
 
 bool mymipmap = false;
+bool novolumenomoments = false;
 
 void DataLoader::loadData32BGpu()
 {
@@ -22,7 +23,7 @@ void DataLoader::loadData32BGpu()
 	glTexParameteri(GL_TEXTURE_3D, GL_TEXTURE_WRAP_T, GL_CLAMP_TO_EDGE);
 	glTexParameteri(GL_TEXTURE_3D, GL_TEXTURE_WRAP_R, GL_CLAMP_TO_EDGE);
 	
-	glTexImage3D(GL_TEXTURE_3D, 0, GL_R16F, sizex, sizey, sizez, 0, GL_RED, GL_FLOAT, data);
+	glTexImage3D(GL_TEXTURE_3D, 0, GL_R32F, sizex, sizey, sizez, 0, GL_RED, GL_FLOAT, data);
         glGenerateMipmap(GL_TEXTURE_3D);
 	
 	glBindTexture(GL_TEXTURE_3D, 0);
@@ -86,9 +87,16 @@ void DataLoader::loadx2y2z2()
 		float norm_j = j;
 		float norm_k = k;
 		
-		mmt[nb*3] = norm_i*norm_i*data[nb];
-		mmt[nb*3 + 1] = norm_j*norm_j*data[nb];
-		mmt[nb*3 + 2] = norm_k*norm_k*data[nb];
+		mmt[nb*3] = norm_i*norm_i;
+		mmt[nb*3 + 1] = norm_j*norm_j;
+		mmt[nb*3 + 2] = norm_k*norm_k;
+		
+		if (novolumenomoments)
+		{
+			mmt[nb*3] = data[nb];
+			mmt[nb*3 + 1] = data[nb];
+			mmt[nb*3 + 2] = data[nb];
+		}
 		nb++;
 	}
 	
@@ -102,7 +110,7 @@ void DataLoader::loadx2y2z2()
[…]

### 2015-10-14 src/cpp/vizo_light/main.cpp

@@ -459,9 +459,9 @@ public:
 		if (Parameters::getInstance()->g_draw_triangles)
 		{
 			m_time_shading->begin();
-			glEnable(GL_RASTERIZER_DISCARD);
+			//glEnable(GL_RASTERIZER_DISCARD);
 			curver.run(queryResult_regular, queryResult_transition, &triangles_regular, &triangles_transition, &sync_count_triangles);
-			glDisable(GL_RASTERIZER_DISCARD);
+			//glDisable(GL_RASTERIZER_DISCARD);
 			m_time_shading->end();
 			
 			static int nb_export = 0;
@@ -638,7 +638,7 @@ public:
 			}
 		}
 		
-		shadator.run(triangles_regular+triangles_transition);
+		//shadator.run(triangles_regular+triangles_transition);
 		
 		//fprintf(stdout, "%lf %lf %lf -- ", Parameters::getInstance()->g_camera.pos[0], Parameters::getInstance()->g_camera.pos[1], Parameters::getInstance()->g_camera.pos[2]);
 		//fprintf(stdout, "[Cells] Total %d Regular %d Transition %d // [Triangles] Regular %d Transition %d ...\r", 

### 2015-10-14 latex/article.tex
abstract

@@
 
-\author{xxx}
+\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1}\and  David Coeurjolly\inst{1}\and  Jonathan
+  Dupuy\inst{1}\inst{2}\and   Jean-Philippe Farrugia\inst{1}\and Jean-Claude Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{3} }
 
- \institute{ CNRS,  LIRIS, UMR5205, F-69621, France\\
-   %\email{david.coeurjolly@liris.cnrs.fr}
+%\address[liris]{Universit\'e de Lyon, CNRS, INSA-Lyon, LIRIS, UMR5205, F-69621, France}
+%\address[lama]{Universit\'e de Savoie, CNRS, LAMA, UMR 5127, F-73776, France}
+
+ \institute{ Universit\'e de Lyon, CNRS\\
+   INSA-Lyon, LIRIS, UMR5205, F-69621, France
+%   \email{\{david.coeurjolly,jeremy.levallois\}@liris.cnrs.fr}
+   \and
+ Universit\'ee de Montr\'eeal\\
+LIGUM, Dept. I.R.O., Canada\\
+\and
+Universit\'e de Savoie, CNRS\\
+LAMA, UMR5127, F-73776, France\\
+%\email{jacques-olivier.lachaud@univ-savoie.fr}
 }
+
 \graphicspath{{./Figs/}}
@@
 \begin{abstract}\sloppy
+  Interactive visualization is a very convenient tool to explore
+  complex scientific data or to explore different parameter settings
+  for a given processing algorithm. In article, we present a tool to
+  efficiently explore the curvature tensor on the boundary of
+  potentially large digital object. More precisely, we combine a fully
+  parallel pipeline on GPU to extract an adaptive triangulated
+  iso-surface of the digital object, with a curvature tensor
+  estimation at each surface point based on integral invariants. Integral
+  invariants being parametrized by a given ball radius, our proposal
+  allows us to explore interactively different radii and thus select
+  the appropriate scale to perform the computations (mean and gaussian
+  curvature, principal curvatures, principal directions and normal
+  vector field).
 

### 2015-10-14 src/cpp/vizo_light/Curvature.cpp
Removed mmts in vizo_light TODO: FIX THE AWFUL BUG THAT CRASHES MY COMPUTEEEEEEEER

@@ -10,6 +10,7 @@
 #include "ImageIO.h"
 #include "Image.h"
 
+
 void configure_curv(GLuint program, GLuint first_loc)
 {
 	/*
@@ -385,14 +386,7 @@ void Curvature::loadBuffers()
 {
 	int res = (int)Parameters::getInstance()->g_tessel;
 	long long int nb_cells = 300000*res*res*res;
-	int export_data = 4; //vec3 pos
-	//export_data += 3; //vec2 k1k2
-	//export_data += 3; //vec3 min_dir;
-	//export_data += 3; //vec3 max_dir;
-	//export_data += 3; //vec3 normale;
-	/*export_data += 3; //vec3 eigenvalues
-	export_data += 3; //vec3 covmatup
-	export_data += 3; //vec3 covmatdiag*/
+	int export_data = 4;
 	
 	glGenBuffers (1, &Parameters::getInstance()->g_buffers[BUFFER_EXPORT_TGL]);
 		glBindBuffer (GL_ARRAY_BUFFER, Parameters::getInstance()->g_buffers[BUFFER_EXPORT_TGL]);
@@ -403,19 +397,6 @@ void Curvature::loadBuffers()
 				GL_DYNAMIC_COPY
 		);
 	glBindBuffer (GL_ARRAY_BUFFER, 0);
-	
-	/*
-	export_data = 4;
-	glGenBuffers (1, &Parameters::getInstance()->g_buffers[BUFFER_EXPORT_K1K2]);
-		glBindBuffer (GL_ARRAY_BUFFER, Parameters::getInstance()->g_buffers[BUFFER_EXPORT_K1K2]);
-		glBufferData (
-				GL_ARRAY_BUFFER,
-				nb_cells*12*export_data*sizeof(float), //12 triangles max for each cell, each made of 3 vec3
-				NULL,
-				GL_DYNAMIC_COPY
-		);
-	glBindBuffer (GL_ARRAY_BUFFER, 0);
-	*/
 	
 	export_data = 4;
 	glGenBuffers (1, &Parameters::getInstance()->g_buffers[BUFFER_EXPORT_DIRMIN]);

### 2015-10-14 src/cpp/vizo_light/DataLoader.cpp

@@ -5,12 +5,12 @@
 #include <cstring>
 
 const GLenum MIN_FILT = GL_LINEAR_MIPMAP_LINEAR;
-//const GLenum MAG_FILT = GL_LINEAR;
+const GLenum MAG_FILT = GL_LINEAR;
 //const GLenum MIN_FILT = GL_NEAREST_MIPMAP_NEAREST;
-const GLenum MAG_FILT = GL_NEAREST;
+//const GLenum MAG_FILT = GL_NEAREST;
 
 bool mymipmap = false;
-bool novolumenomoments = false;
+bool novolumenomoments = true;
 
 void DataLoader::loadData32BGpu()
 {
@@ -93,9 +93,9 @@ void DataLoader::loadx2y2z2()
 		
 		if (novolumenomoments)
 		{
-			mmt[nb*3] = data[nb];
-			mmt[nb*3 + 1] = data[nb];
-			mmt[nb*3 + 2] = data[nb];
+			mmt[nb*3] *= data[nb];
+			mmt[nb*3 + 1] *= data[nb];
+			mmt[nb*3 + 2] *= data[nb];
 		}
 		nb++;
 	}
@@ -160,9 +160,9 @@ void DataLoader::loadxyyzxz()
 		
 		if (novolumenomoments)
 		{
-			mmt[nb*3] = data[nb];
-			mmt[nb*3 + 1] = data[nb];
-			mmt[nb*3 + 2] = data[nb];
+			mmt[nb*3] *= data[nb];
+			mmt[nb*3 + 1] *= data[nb];
+			mmt[nb*3 + 2] *= data[nb];
 		}
 		nb++;
 	}
@@ -228,9 +228,9 @@ void DataLoader::loadxyz()
 		
 		if (novolumenomoments)
 		{
-			mmt[nb*3] = data[nb];
-			mmt[nb*3 + 1] = data[nb];
-			mmt[nb*3 + 2] = data[nb];
+			mmt[nb*3] *= data[nb];
+			mmt[nb*3 + 1] *= data[nb];
+			mmt[nb*3 + 2] *= data[nb];
 		}
 		
 		nb++;

### 2015-10-14 src/cpp/vizo_light/Parameters.cpp

@@ -54,7 +54,7 @@ Parameters::Parameters()
     g_regular = false;
     g_radius_show = true;
 
-	g_curvradius = 5.0;
+	g_curvradius = 25.0;
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 

### 2015-10-14 src/cpp/vizo_light/main.cpp

@@ -19,12 +19,13 @@
 
 #include <cmath>
 #include <string>
-#include <boost/concept_check.hpp>
 
 #define CAM_SPEED 20
 #define CAM_SPEED_MAX Parameters::getInstance()->g_geometry.scale[0] / 5.0
 #define CAM_ROTATE 0.1f
 #define CAM_ROTATE_MAX 1.0f
+
+//#define MMTS
 
 void updateMatricesAndFrustum()
 {
@@ -93,12 +94,14 @@ void activateTextures()
 	glActiveTexture(GL_TEXTURE0 + TEXTURE_DENSITY);
 	glBindTexture(GL_TEXTURE_3D, Parameters::getInstance()->g_textures[TEXTURE_DENSITY]);
 
+#ifdef MMTS
 	glActiveTexture(GL_TEXTURE0 + TEXTURE_X2Y2Z2);
 	glBindTexture(GL_TEXTURE_3D, Parameters::getInstance()->g_textures[TEXTURE_X2Y2Z2]);
 	glActiveTexture(GL_TEXTURE0 + TEXTURE_XY_YZ_XZ);
 	glBindTexture(GL_TEXTURE_3D, Parameters::getInstance()->g_textures[TEXTURE_XY_YZ_XZ]);
 	glActiveTexture(GL_TEXTURE0 + TEXTURE_XYZ);
 	glBindTexture(GL_TEXTURE_3D, Parameters::getInstance()->g_textures[TEXTURE_XYZ]);
+#endif
 	
 	glActiveTexture(GL_TEXTURE0 + TEXTURE_CODE_CLASS);
 	glBindTexture(GL_TEXTURE_1D, Parameters::getInstance()->g_textures[TEXTURE_CODE_CLASS]);
@@ -273,9 +276,12 @@ public:
 		}
 		dl->loadFile(argv[1]);
 		dl->loadData32BGpu();
+	
+#ifdef MMTS
 		dl->loadx2y2z2();
 		dl->loadxyyzxz();
 		dl->loadxyz();
+#endif
 		
 		lodManager.init();
 		extractor.init();
@@ -459,9 +465,9 @@ public:
 		if (Parameters::getInstance()->g_draw_triangles)
 		{
 			m_time_shading->begin();
-			//glEnable(GL_RASTERIZER_DISCARD);
+			glEnable(GL_RASTERIZER_DISCARD);
 			curver.run(queryResult_regular, queryResult_transition, &triangles_regular, &triangles_transition, &sync_count_triangles);
[…]

### 2015-10-14 latex/article.tex
abstract

@@
   complex scientific data or to explore different parameter settings
-  for a given processing algorithm. In article, we present a tool to
-  efficiently explore the curvature tensor on the boundary of
-  potentially large digital object. More precisely, we combine a fully
-  parallel pipeline on GPU to extract an adaptive triangulated
+  for a given processing algorithm. In this article, we present a tool
+  to efficiently explore the curvature tensor on the boundary of
+  potentially large digital objects. More precisely, we combine a
+  fully parallel pipeline on GPU to extract an adaptive triangulated
   iso-surface of the digital object, with a curvature tensor
-  estimation at each surface point based on integral invariants. Integral
-  invariants being parametrized by a given ball radius, our proposal
-  allows us to explore interactively different radii and thus select
-  the appropriate scale to perform the computations (mean and gaussian
-  curvature, principal curvatures, principal directions and normal
-  vector field).
+  estimation at each surface point based on integral
+  invariants. Integral invariants being parametrized by a given ball
+  radius, our proposal allows us to explore interactively different
+  radii and thus select the appropriate scale to which the computation
+  is performed and visualized (mean and gaussian curvature, principal
+  curvatures, principal directions and normal vector field).
 

### 2015-10-15 tests/hierarchy.c
Enhance approximation.

@@ -14,6 +14,7 @@ typedef float Value;
 // Useful basic functions
 Value square_int( int x );
 Value square( Value x );
+Value cube( Value x );
 Value distance2( int x1, int y1, int z1, int x2, int y2, int z2 );
 Value distance( int x1, int y1, int z1, int x2, int y2, int z2 );
 
@@ -87,6 +88,10 @@ Value square_int( int x )
 Value square( Value x )
 {
   return x*x;
+}
+Value cube( Value x )
+{
+  return x*x*x;
 }
 
 Value distance2( int x1, int y1, int z1, int x2, int y2, int z2 )
@@ -474,7 +479,7 @@ Value computeApproximateHierarchy( MipMap* M, int x0, int y0, int z0, Value r, i
 
   It should be noted that 2^min_h should be smaller than r.
 
-  Curiously, does not behave better than computeApproximateHierarchy.
+  Last version behaves slightly better than computeApproximateHierarchy.
 */
 Value computeApproximateHierarchy2( MipMap* M, int x0, int y0, int z0, Value r, int min_h )
 {
@@ -539,11 +544,17 @@ Value computeApproximateHierarchy2( MipMap* M, int x0, int y0, int z0, Value r, 
           else 
             { // Compute proportion inside.
               // double prop = 1.0 - (d2-upper2) / (4.0*r*diag[ k ]); // Without sqrt
-              double prop = ( ( r + diag[ k ] ) - sqrt( d2 ) ) / (2.56158 * diag[ k ] ); // with sqrt
+              // double prop = ( ( r + diag[ k ] ) - sqrt( d2 ) ) / (2.56158 * diag[ k ] ); // with sqrt
               // constant is two times int( sqrt(1+y^2+z^2) dy dz ) / 4.0
+              // double prop = ( 1.0 + cube( ( r - sqrt( d2 ) ) / ( 0.73946*diag[ k ] ) ) ) / 2.0; // with sqrt
+              
+              // Works best.
+              // 1.7320508/diag[k] = sqt(3)/diag(k) = 1 / h is the half-size of the cell edge.
+              double prop = cube( ( r - sqrt( d2 ) ) * 1.7320508 / diag[ k ] ); // in [-1,1]
+              prop = (1.0+prop) / 2.0; // in [0,1].
+              //printf("[%d] %d %d %d prop=%f\n", k, xyzk[ 0 ], xyzk[ 1 ], xyzk[ 2 ], prop );
[…]

### 2015-10-15 src/cpp/vizo/Parameters.cpp
Vizo charge les données en 32F comme vizo light Harmonisation en général des paramètres entre les deux appli Ajout d'une limite explicite pour vizo_light uniquement pour garantir que la boucle do while dans l'eigendecomposition ne deviendra pas une boucle infinie

@@ -54,7 +54,7 @@ Parameters::Parameters()
     g_regular = false;
     g_radius_show = true;
 
-	g_curvradius = 5.0;
+	g_curvradius = 10.0;
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 

### 2015-10-15 src/cpp/vizo_light/Parameters.cpp

@@ -54,7 +54,7 @@ Parameters::Parameters()
     g_regular = false;
     g_radius_show = true;
 
-	g_curvradius = 25.0;
+	g_curvradius = 10.0;
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 

### 2015-10-15 src/cpp/vizo_light/main.cpp

@@ -227,6 +227,7 @@ private:
 	int last_color;
 	
 	int min_lvl;
+	int max_lvl;
 	
 public:
 	Vizo(int _argc, char** _argv) : gk::App()
@@ -318,6 +319,7 @@ public:
 		
 		min_lvl = (int)floor(log2(Parameters::getInstance()->g_curvradius));
 		Parameters::getInstance()->g_lvl = min_lvl;
+		max_lvl = 0;
 		
 		last_radius = Parameters::getInstance()->g_curvradius;
 		last_lvl = Parameters::getInstance()->g_lvl;
@@ -358,8 +360,9 @@ public:
 			{
 				Parameters::getInstance()->g_lvl =  min_lvl;
 				Parameters::getInstance()->g_compute_min_max = true;
+				max_lvl = 0;
 			}
-			else if (Parameters::getInstance()->g_auto_refine && fps > 30 && Parameters::getInstance()->g_lvl > 0)
+			else if (Parameters::getInstance()->g_lvl > 0 && Parameters::getInstance()->g_lvl > max_lvl)
 			{
 				Parameters::getInstance()->g_lvl -= 1;
 				Parameters::getInstance()->g_compute_min_max = true;
@@ -1062,6 +1065,12 @@ public:
 	
 				cpu_time
 			);
+		}
+		
+		if (Parameters::getInstance()->g_auto_refine && Parameters::getInstance()->g_lvl < min_lvl && fps < 10)
+		{
+			Parameters::getInstance()->g_lvl+=1;
+			max_lvl = Parameters::getInstance()->g_lvl;
 		}
 		
 		return 1;

### 2015-10-15 latex/article.tex

@@
 
-\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1}\and  David Coeurjolly\inst{1}\and  Jonathan
-  Dupuy\inst{1}\inst{2}\and   Jean-Philippe Farrugia\inst{1}\and Jean-Claude Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{3} }
+\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1}\and  David Coeurjolly\inst{1}\and   Jean-Philippe Farrugia\inst{1}\and Jean-Claude Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{2} }
 
@@
  \institute{ Universit\'e de Lyon, CNRS\\
-   INSA-Lyon, LIRIS, UMR5205, F-69621, France
+   LIRIS, UMR5205, F-69621, France
 %   \email{\{david.coeurjolly,jeremy.levallois\}@liris.cnrs.fr}
-   \and
- Universit\'ee de Montr\'eeal\\
-LIGUM, Dept. I.R.O., Canada\\
    \and
@@
 
-\keywords{isosurface visualization, Digital Geometry, Curvature estimation}
+\keywords{Isosurface Visualization, Digital Geometry, Curvature
+  Estimation, GPU.}
 \end{abstract}

### 2015-10-15 latex/article.tex
moving files

@@
 \usepackage{tikz}        % standard LaTeX graphics tool
-\usetikzlibrary{arrows}
-\usetikzlibrary{quotes,angles}
+%\usetikzlibrary{arrows}
+%\usetikzlibrary{quotes,angles}
 \usepackage{subfigure}                                 % authors: subfigures
@@
 
-\title{Interactive Curvature Tensor  Visualization on Digital Surfaces\thanks{This work has been mainly funded by
-   XXXXXXX  research
-    grants.}}
+\title{Interactive Curvature Tensor Visualization on Digital
+Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}}
 
-\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1}\and  David Coeurjolly\inst{1}\and   Jean-Philippe Farrugia\inst{1}\and Jean-Claude Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{2} }
+\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1,2}\and David
+Coeurjolly\inst{1}\and Jean-Philippe Farrugia\inst{1}\and Jean-Claude
+Iehl\inst{1}\and Jacques-Olivier Lachaud\inst{2} }
 

### 2015-10-15 tools/comparison/main.cpp
adding some comparive tools (still in development)

@@ -1,0 +1,167 @@
+#include <iostream>
+#include <cstdlib>
+#include <boost/algorithm/string.hpp>
+#include <map>
+#include <vector>
+#include <fstream>
+#include <cmath>
+
+#define NBDATA 6 /// x y z H k1 k2
+
+typedef unsigned int uint;
+typedef float Value;
+
+struct Curvatures
+{
+  Value mean;
+  Value k1;
+  Value k2;
+};
+class Position
+{
+public:
+  int x;
+  int y;
+  int z;
+
+public:
+  Position(){ x=0; y=0; z=0; }
+  Position(int _x, int _y, int _z){ x=_x; y=_y; z=_z; }
+
+  bool operator< (const Position& p) const
+  {
+    if ( x != p.x )
+    {
+      return x < p.x;
+    }
+    if ( y != p.y )
+    {
+      return y < p.y;
+    }
+    if ( z != p.z )
+    {
+      return z < p.z;
+    }
+    return false;
+  }
+  bool operator> (const Position& p) const
+  {
+    if( *this == p)
+    {
+      return false;
+    }
+    return !(*this < p);
+  }
+  bool operator== (const Position& p) const
+  {
+    return x == p.x && y == p.y && z == p.y;
+  }
+  bool operator!= (const Position& p) const
+  {
+    return !(*this == p);
+  }
+};
+
+struct convertGPUtoKhalimsky : std::unary_function <unsigned int, double>
+{
+  inline
+  unsigned int operator() (const double& v) const
+  { return std::floor(2.0*v); }
+};
+
+struct convertCPUtoKhalimsky : std::unary_function <unsigned int, double>
+{
+  inline
+  unsigned int operator() (const double& v) const
+  { return std::floor(v); }
+};
+
+template< typename Predicate >
+bool loadFile(  const std::string& filename, std::map<Position,
+                Curvatures>& results, const Predicate& predicate)
+{
+  std::ifstream file( filename.c_str() );
+  std::string line;
+
+  if( file.is_open())
+  {
+    std::cout << "Collecting data from file ..." << filename << std::endl;
+    while( getline(file,line) )
+    {
+      /// Skip if the line contains a # char or N
+      if(line[0] == '#' || line[0] == 'N')
+      {
+        continue;
+      }
+
+      std::vector<std::string> words;
+      boost::split(words, line, boost::is_any_of(" \t"), boost::token_compress_on);
+      if(words.size() < NBDATA)
+      {
[…]

### 2015-10-15 latex/article.tex
Add hierarchical algorithm (approx)

@@
 
+A {\em cell} $(k,x,y,z)$ is a region of the space of size $2^k \times
+2^k \times 2^k$, characterized by its integer coordinates $x,y,z$,
+with $0 \le x < 2^k$, $0 \le y < 2^k$, $0 \le z < 2^k$. Cells forms an
+octree decomposition of a cubic space. We use functions Up, Down and
+Next to navigate between cells.
+
+\begin{algorithm}
+\KwIn{Integers $p,q,r$ \tcp*{the moment orders, with $0 \le p+q+r \le 2$}}
+\KwIn{Integer $k$ \tcp*{$(2^k)^3$ is the size of the digital shape image}}
+\KwIn{Mipmap $V$ \tcp*{array of $k+1$ images of sizes $(2^k)^3,  (2^{k-1})^3, \ldots,  1^3$}}
+\KwIn{Integers $x_0,y_0,z_0$, Real $r$ \tcp*{Ball radius $r$ and center $(x_0,y_0,z_0)$}}
+\KwOut{Real $m$ \tcp*{estimation of the $p,q,r$-moment of $X \cap B_r(x_0,y_0,z_0)$}}
+\KwData{Cell $c :=  (k,0,0,0)$ \tcp*{Starts from biggest cell}}
+\KwData{Integer $n := 2^k$ \tcp*{Size of each cell}}
+\KwData{Real $d,\delta,l$ \tcp*{variables for intermediate computations}}
+\Begin{
+    m := 0 \;
+    \Repeat{$c[0] = k$}{
+      \tcp{Distance between cell and ball centers}
+      $d := \frac{1}{2}\| 2^k(2c[1]+1,2c[2]+1,2c[3]+1) - (2x_0+1,2y_0+1,2z_0+1) \|_2$\;
+      $\delta := \frac{\sqrt{3}}{2}2^{c[0]}$ \tcp*{half-length of cell diagonal}
+      \If(\tcp*[f]{Is it a smallest cell ?}){$c[0] = 0$}{
+        \If(\tcp*[f]{Is cell inside ball ?}){$d^2 \le r^2$}{
+          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$
+        }
+        $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
+      } \Else{
+        $l := \max(r-\delta,0)$\;
+        \If(\tcp*[f]{Is cell completely inside ball ?}){$d^2 < l^2$}{
+          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$
+          $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
+        }\ElseIf(\tcp*[f]{Is cell outside ball ?}){$d^2 > (r+\delta)^2$}{
+          $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
+        }\lElse(\tcp*[f]{Go to a finer cell}){$c := \textsc{Down}(c)$}
+      }
+    }
+    \Return{m}\;
+  }
+  \caption{Derecursified hierarchical algorithm for computing the
+    $p,q,r$-moment of set $X \cap B_r(x_0,y_0,z_0)$, given a mipmap
+    $V$ that represents the volume of a shape $X$ in each cell, and
+    ball parameters $x_0,y_0,z_0,r$.}
+\end{algorithm}
+
+\begin{function}
+  \caption{Up( Cell $c$ ) : Cell}
+  \Return{Cell( $c[0]+1$, $c[1]/2$, $c[2]/2$, $c[3]/2$ )}
+\end{function}
+\begin{function}
+  \caption{Down( Cell $c$ ) : Cell}
+  \Return{Cell( $c[0]-1$, $c[1]*2$, $c[2]*2$, $c[3]*2$ )}
+\end{function}
+\begin{function}
+  \caption{Next( Cell $c$ ) : Cell}
+  \lWhile{$\mathrm{Odd}(c[1])$ and $\mathrm{Odd}(c[2])$ and $\mathrm{Odd}(c[3])$}{$c := \mathrm{Up}(c)$}
+  \lIf{$\mathrm{Even}(c[1])$}{$c[1] := c[1]+1$}
+  \Else{$c[1] := c[1] - 1$\;
+    \lIf{$\mathrm{Even}(c[2])$}{$c[2] := c[2]+1$}
+    \Else{$c[2] := c[2] - 1$\;
+      $c[3] := c[3]+1$}
+  }
+  \Return{c}
+\end{function}
+
 \subsection{Isosurface Extraction on GPU}

### 2015-10-16 src/cpp/vizo/Definitions.h
Minor modifications to visualize animated datasets (Vizo, 01 only => SOULD BE GT)

@@ -219,6 +219,7 @@ enum {
 	LOCATION_GTCURV_CURVVAL,
 	LOCATION_GTCURV_LVL,
 	LOCATION_GTCURV_K1K2NORMALS,
+	LOCATION_GTCURV_TIME,
 	
 	LOCATION_HIERARCHCURV_SIZE,
 	LOCATION_HIERARCHCURV_DENSITY,
@@ -239,6 +240,7 @@ enum {
 	LOCATION_HIERARCHCURV_CURVVAL,
 	LOCATION_HIERARCHCURV_LVL,
 	LOCATION_HIERARCHCURV_K1K2NORMALS,
+	LOCATION_HIERARCHCURV_TIME,
 	
 	LOCATION_APPROXCURV_SIZE,
 	LOCATION_APPROXCURV_DENSITY,
@@ -259,6 +261,7 @@ enum {
 	LOCATION_APPROXCURV_CURVVAL,
 	LOCATION_APPROXCURV_LVL,
 	LOCATION_APPROXCURV_K1K2NORMALS,
+	LOCATION_APPROXCURV_TIME,
 
 	LOCATION_SPHEREDRAW_SCENE_SIZE,
 	LOCATION_SPHEREDRAW_CURVRADIUS,

### 2015-10-16 latex/article.tex

@@
 
-A {\em cell} $(k,x,y,z)$ is a region of the space of size $2^k \times
+A {\em cell} is a tuple $(k,x,y,z)$, which represents a region of the space of size $2^k \times
 2^k \times 2^k$, characterized by its integer coordinates $x,y,z$,
@@
       $\delta := \frac{\sqrt{3}}{2}2^{c[0]}$ \tcp*{half-length of cell diagonal}
-      \If(\tcp*[f]{Is it a smallest cell ?}){$c[0] = 0$}{
-        \If(\tcp*[f]{Is cell inside ball ?}){$d^2 \le r^2$}{
-          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$
+      \If(\tcp*[f]{Is it a unit cell ?}){$c[0] = 0$}{
+        \If(\tcp*[f]{Is cell center inside ball ?}){$d^2 \le r^2$}{
+          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$ \;
         }
@@
         \If(\tcp*[f]{Is cell completely inside ball ?}){$d^2 < l^2$}{
-          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$
+          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$\;
           $c := \textsc{Next}(c)$ \tcp*{Go to next cell}

### 2015-10-16 tools/comparison/main.cpp
Should working now. There is a bug with input file.

@@ -5,11 +5,12 @@
 #include <vector>
 #include <fstream>
 #include <cmath>
+#include <limits>
 
 #define NBDATA 6 /// x y z H k1 k2
 
 typedef unsigned int uint;
-typedef float Value;
+typedef double Value;
 
 struct Curvatures
 {
@@ -82,10 +83,11 @@ struct convertCPUtoKhalimsky : std::unary_function <unsigned int, double>
 };
 
 template< typename Predicate >
-bool loadFile(  const std::string& filename, std::map<Position,
-                Curvatures*>& results, const Predicate& predicate)
+bool loadFile(  const std::string& filename,
+                std::vector< std::pair<Position*, Curvatures*> >& results,
+                const Predicate& predicate )
 {
-  std::ifstream file( filename.c_str() );
+  std::ifstream file( filename.c_str(), std::ifstream::in );
   std::string line;
 
   if( file.is_open())
@@ -103,135 +105,208 @@ bool loadFile(  const std::string& filename, std::map<Position,
       boost::split(words, line, boost::is_any_of(" \t"), boost::token_compress_on);
       if(words.size() < NBDATA)
       {
-        std::cout << "I've got a wrong number of data on this line..." << std::endl;
+        std::cout << "ERROR: I've got a wrong number of data on this line..." << std::endl;
         std::cout << "        ";
         for( uint i_word = 0; i_word < words.size(); ++i_word )
         {
             std::cout << words[i_word] << " ##### ";
         }
         std::cout << std::endl;
+        std::cout << "Leaving now..." << std::endl;
         return false;
       }
 
-      Position p;
-      p.x = predicate( std::atof(words[0].c_str()));
-      p.y = predicate( std::atof(words[1].c_str()));
-      p.z = predicate( std::atof(words[2].c_str()));
+      Position *p = new Position();
+      p->x = predicate( std::atof(words[0].c_str()));
+      p->y = predicate( std::atof(words[1].c_str()));
+      p->z = predicate( std::atof(words[2].c_str()));
 
       Curvatures *c = new Curvatures();
       c->mean = std::atof(words[3].c_str());
       c->k1   = std::atof(words[4].c_str());
       c->k2   = std::atof(words[5].c_str());
 
[…]

### 2015-10-16 latex/CGI_Transvoxels/preliminaries.tex

@@
 
-The solution of Lengyel \textit{et al.} \cite{lengyel2010voxel} is based on extracting an adaptive triangulated surface by applying MC on an octree.
-However, due to its recursive nature, the octree is not suited for the GPU pipeline.
-Hence, to take full advantage ofthe GPU, we must convert this tree to a non recursive structure.
-Such representations were first introduced by Gargantini \cite{gargantini1982effective} and are known as linear quadtrees.
-They have been implemented on the GPU by Dupuy \textit{et al.} \cite{dupuy2014quadtrees}.
-Along with this implementation, they presented a LoD criterion that bounds the projected size of the tree cells.
+The solution of Lengyel \textit{et al.} \cite{lengyel2010voxel} is
+based on extracting an adaptive triangulated surface by applying MC on
+an octree.  However, due to its recursive nature, the octree is not
+suited for the GPU pipeline.  Hence, to take full advantage ofthe GPU,
+we must convert this tree to a non recursive structure.  Such
+representations were first introduced by Gargantini
+\cite{gargantini1982effective} and are known as linear quadtrees.
+They have been implemented on the GPU by Dupuy \textit{et al.}
+\cite{dupuy2014quadtrees}.  Along with this implementation, they
+presented a LoD criterion that bounds the projected size of the tree
+cells.
 

### 2015-10-16 latex/article.tex

@@
   fully parallel pipeline on GPU to extract an adaptive triangulated
-  iso-surface of the digital object, with a curvature tensor
+  isosurface of the digital object, with a curvature tensor
   estimation at each surface point based on integral
@@
 
-\section{Preliminaries}
-\label{sec:preliminaries}
+\section{Curvature Tensor Estimation}
+\label{sec:curv-tens-estim}
 
-\subsection{Curvature Tensor Estimation}
-\label{sec:curv-tens-estim}
+\section{Isosurface Extraction on GPU}
+\label{sec:isos-extr-gpu}
+
+In this section, we detail the adaptive isosurface extraction
+algorithm. The proposed approach is based on an octree representation
+of the volumetric object on which an efficient adaptive triangulation
+of the isosurface is constructed on GPU. Such approach is motivated by
+the fact that the hierarchical representation of the object allows us
+to handle large datasets and to locally adapt the level of details
+with respect to the geometry or camera position. We first present the
+octree representation and then the isosurface extraction from
+hierarchical octree cells.
+
+\subsection{Linear Octree Representation}
+
+\begin{figure}
+  \begin{center}
+    \subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
+    \subfigure{}{\includegraphics[height=0.17\textheight]{figs/quadtree_activefront}}
+  \end{center}
+\caption{In \cite{dupuy2014quadtrees}, a linear quadtree is used to
+  maintain a 2D hierarchical partitioning of space.  (Left) presents
+  such a partitioning.  A cell is more or less subdivided depending on
+  its distance to the camera.  They are also encoded with morton code,
+  that identifies each cell with its position relatively to its
+  parent.  (Right) shows the corresponding active front in the full
+  tree.  This partition is entirely represented by storing the list of
+  codes of the gray cells. }
+\label{fig_quadtree_partitionning}
+\end{figure}
+
+Linear quadtrees or octrees are non-recursive spatial data structure
+to represent classical quadtree/octreee trees (see for instance
+Gargantini \cite{gargantini1982effective}).  Such structures were
+reused by Dupuy \textit{et al.}  \cite{dupuy2014quadtrees} who
+presented a solution to handle them efficiently on the GPU.  Linear
+quadtrees associate a code to each cell, identifying it by its path to
+the root node.  The full tree is thus entirely represented by the list
+of its leaves' codes, which removes the recursivity.  In their
+implementation, Dupuy \textit{et al.} used Morton codes (Figure
+\ref{fig_quadtree_partitionning}).  Those codes store a spatial
+position, encoding the location of the cell relatively to its parent.
+The final code of a cell is thus the succession of locations between
+the cell and the root node.  Therefore, the maximal depth of the tree
+depends on the number of quadrants that can be encoded.  In a
+quadtree, a cell is divided into $2^2$ quadrants, so encoding one
+subdivision requires two bits.  Dupuy \textit{et al.} store for each
+cell its Morton code and its depth within the tree.  Therefore, with a
+code stored on 32 bits, using 28 bits for the locations and 4 bits for
+the depth, the tree is limited to 14 levels.
+
+Dupuy \textit{et al}. used those quadtrees to maintain a 2D
+hierarchical space partition.  They thus encode a front of cells
+within this tree (Figure \ref{fig_quadtree_partitionning}).  To
+determine if a cell is part of the front, they evaluate on each of
+them a LoD criterion.  The criterion they chose is view dependent and
+thus must be evaluated quickly on the GPU.
+
+During an update, there a three possible operations on a cell: it can
+be kept, merged or split.  A merge operation removes the codes of the
+children's cells from the list and replaces them with the code of the
+parent cell.  A split operation removes the code of a cell replacing
+it by the codes of its children.  Therefore, an efficient GPU
+implementation relies on the fact that those operations can be done
+independently on each cell.  This is true as long as the LoD criterion
+is also evaluable independently on each cell.
+
+With this implementation of linear tree, it is possible to maintain a
+quadtree on the GPU.  By generalizing this to the octree, it could be
+used with the triangulation presented by Lengyel \textit{et al.} to
+develop a fully data parallel pipeline.  There is however three
+conditions on the LoD criterion.  It must ensure that the extracted
+triangles will project onto more than one pixel, to ensure a good
+rasterization sampling.  The tree must also stay restricted at all
+times as the transition cells of Lengyel \textit{et al.} only patch
+cells with a single change in resolution.  Finally, this criterion
+must allow to detect if the neighbour of a cell is more subdivided
+than the cell itself in a data parallel manner.  This is mandatory to
+determine where the transition cells should be inserted.
+
+\todo[inline]{work in progress, cleanup needed}
+
+\subsection{Data parallel and adaptive mesh generation}
+
+\begin{figure}[!htbp]
+\centering
+\subfigure{}{\includegraphics[width=0.4\linewidth]{mesh_muti_res}}
+\subfigure{}{\includegraphics[width=0.4\linewidth]{octree}}
+\caption{Isosurface extraction $(a)$ from a  a linear restricted octree
+  $(b)$ of a volumetric data.\label{fig:isoexample}}
+\end{figure}
+
+\begin{figure}[!htbp]
+  \centering
+  \includegraphics[width=0.9\textwidth]{figs/pipeline}
+  \caption{ This figure summarizes our GPU pipeline. Data buffers are
+    represented in green and computations in red. Each computation
+    retrieves data from a buffer and fills a new one. }
+  \label{fig_pipeline} 
+\end{figure}
+
+\section{Interactive Computation on GPU}
+\label{sec:inter-visu-gpu}
 
@@
 
-\subsection{Isosurface Extraction on GPU}
-\label{sec:isos-extr-gpu}
-
-\section{Interactive Visualization on GPU}
-\label{sec:inter-visu-gpu}
+\section{Experiments}
+\label{sec:experiments}
 

### 2015-10-19 latex/article.tex
figs

@@
 algorithm. The proposed approach is based on an octree representation
-of the volumetric object on which an efficient adaptive triangulation
+of the domain and object on which an efficient adaptive triangulation
 of the isosurface is constructed on GPU. Such approach is motivated by
@@
   \begin{center}
-    \subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
-    \subfigure{}{\includegraphics[height=0.17\textheight]{figs/quadtree_activefront}}
+    \subfigure{}{\includegraphics[width=\textwidth]{figs/morton}}
+    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
+    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/quadtree_activefront}}
   \end{center}
-\caption{In \cite{dupuy2014quadtrees}, a linear quadtree is used to
-  maintain a 2D hierarchical partitioning of space.  (Left) presents
-  such a partitioning.  A cell is more or less subdivided depending on
-  its distance to the camera.  They are also encoded with morton code,
-  that identifies each cell with its position relatively to its
-  parent.  (Right) shows the corresponding active front in the full
-  tree.  This partition is entirely represented by storing the list of
-  codes of the gray cells. }
+\caption{Morton codes associated to cells of a linear quatree. Each
+  children cell morton code is obtained by adding a suffix to its
+  parent code \emph{(left)}. The adpative representation consists of
+  quadtree cells whose depth is view point dependent \emph{(right)}.}
 \label{fig_quadtree_partitionning}

### 2015-10-19 src/cpp/vizo/Parameters.cpp
vizo données 512^3 dans 4go RAM GPU

@@ -34,7 +34,7 @@ Parameters::Parameters()
 
     g_mouse = MOUSE_GEOMETRY;
     
-    g_draw_cells = true;
+    g_draw_cells = false;
     g_draw_triangles = true;
     g_culling = true;
     g_fromtexture = true;
@@ -58,7 +58,7 @@ Parameters::Parameters()
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 
-    g_scale = 2;
+    g_scale = 5;
     g_tessel = 1.0;
     g_isosurface = 0;
 	

### 2015-10-19 src/cpp/vizo_light/GpuOctree.cpp

@@ -65,7 +65,7 @@ void GPUOctree::loadBuffers()
         //const size_t cap = 1 << 28;
 		
 		size_t full_tree = 1;
-		unsigned long int side = pow(2, 8);
+		unsigned long int side = pow(2, 9);
 		full_tree += side*side*side;
 		
 		size_t full_tree_cap = full_tree * sizeof(float) * 2.0; //1 vec2 for each
@@ -248,8 +248,6 @@ void GPUOctree::loadVertexArrays()
 		glBindBuffer (GL_ARRAY_BUFFER, Parameters::getInstance()->g_buffers[BUFFER_VERTEX_CUBE]);
 		glVertexAttribPointer (1, 3, GL_FLOAT, 0, 0, 0);
 		glBindBuffer (GL_ELEMENT_ARRAY_BUFFER, Parameters::getInstance()->g_buffers[BUFFER_INDEX_CUBE]);
-		glBindBuffer (GL_ARRAY_BUFFER, Parameters::getInstance()->g_buffers[BUFFER_VERTEX_CUBE]);
-		glVertexAttribPointer (1, 3, GL_FLOAT, 0, 0, 0);
 	glBindVertexArray(0);
 	
 	glGenVertexArrays (1, Parameters::getInstance()->g_vertex_arrays + VERTEX_ARRAY_OCTREE_RENDER2);

### 2015-10-19 src/cpp/vizo_light/RegularTriangulation.cpp

@@ -200,7 +200,7 @@ void list_indices(std::vector<unsigned int>& id_list)
 void RegularTriangulation::loadBuffers()
 {
 	int res = (int)Parameters::getInstance()->g_tessel;
-	long long int nb_cells = 1500000*res*res*res;
+	long long int nb_cells = 3000000*res*res*res;
 	
 	glGenBuffers (1, &Parameters::getInstance()->g_buffers[BUFFER_INDIRECT_DRAWS]);
 	glBindBuffer (GL_ARRAY_BUFFER, Parameters::getInstance()->g_buffers[BUFFER_INDIRECT_DRAWS]);

### 2015-10-19 latex/article.tex
octree ok

--- 2015-10-16 latex/article.tex
@@
 
-\section{Preliminaries}
-\label{sec:preliminaries}
+\section{Curvature Tensor Estimation}
+\label{sec:curv-tens-estim}
 
-\subsection{Curvature Tensor Estimation}
-\label{sec:curv-tens-estim}
+\section{Isosurface Extraction on GPU}
+\label{sec:isos-extr-gpu}
+
+In this section, we detail the adaptive isosurface extraction
+algorithm. The proposed approach is based on an octree representation
+of the input object on which an efficient adaptive triangulation
+of the isosurface is constructed on GPU. Such approach is motivated by
+the fact that the hierarchical representation of the object allows us
+to handle large datasets and to locally adapt the level of details
+with respect to the geometry or camera position. We first present the
+octree representation and then the isosurface extraction from
+hierarchical octree cells.
+
+\subsection{Linear Octree Representation}
+
+\begin{figure}[!htbp]
+  \begin{center}
+    \subfigure{}{\includegraphics[width=\textwidth]{figs/morton}}
+    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
+    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/quadtree_activefront}}
+  \end{center}
+\caption{Morton codes associated to cells of a linear quatree. Each
+   morton code of a child cell is obtained by adding a suffix to its
+  parent code \emph{(left)}. The adaptive representation consists of
+  quadtree cells whose depth is view point dependent
+  \emph{(middle)}. Finally, adaptive Marching-Cubes is used to
+  generate the triangulation \emph{(right)}.}
+\label{fig_quadtree_partitionning}
+\end{figure}
+
+Representing a hierachical structure on GPU is usually challenging
+since the GPU memory is limited and non consistent \todo{fix coherent/aligned/coalesced?}
+memory access (\emph{e.g.} tree traversal using pointer dereferencing)
+may lead to huge payload from cache misses.  Efficient spatial tree
+encoding can be achieved using pointerless strictures. We use here
+linear quadtrees or octrees to represent classical quadtree/octreee
+trees, see for instance Gargantini
+\cite{gargantini1982effective}. This structure consists in indexing
+each cell by a \emph{Morton code}: the code of children cells are
+defined by the code of the parent suffixed by two bits (in dimension
+2, three bits in dimension 3) (see Figure
+\ref{fig_quadtree_partitionning}-\emph{left}). For a given cell, its
+code encodes its position with respect to its parent cell and its
+complete path to the tree root. Hence, whatever their depth, all cell
+codes are simply stored in a linear vector on memory. Furthermore,
+cell operations such as subdivision, merging, neighbors access can be
+efficiently implemented using bitwise operations on the Morton code.
+In the following, we use the GPU implementation proposed by Dupuy
+\textit{et al.}  \cite{dupuy2014quadtrees}. In such approach, Morton
+codes and bitwise operations are optimized to match with GPU hardware
+requirements.
+
+\subsection{Data parallel and adaptive mesh generation}
+
+Using this spatial datastructure, triangulated mesh can be constructed
+from a Marching-Cubes approach \cite{lorensen1987marching} (MC for short): the
+triangulation is generated from local triangle patches computed on
+local cell configurations. Since triangle patches are locally
+computed, such approach is fully parallel and easy to implement on GPU
+hardwares. However, since adjacent cells may not have the same depth
+on the octree, original Lorensen and Cline's rules need to be
+updated (see Figure~\ref{fig_quadtree_partitionning}-\emph{right}). Many authors have addressed this problem both for primal and
+dual meshes
+\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.
+
+In the following, we use the extension of MC configurations to handle
+adaptive structures proposed by Lengyel \emph{et al.}
+\cite{lengyel2010voxel}. First this approach constrains the octree
+structure in order to make sure that the depth difference between any
+two adjacent cells is at most one. Then, Lengyel \emph{et al.} propose
+specific MC configurations for such transition cells,  leading to a
+crack-free triangulation.
+
+Similarly to original MC algorithm, this approach is perfectly adapted
+to GPU hardwares: Given a set of cells (a vector of morton codes),
+each triangle patch can be constructed in parallel (done by 
+in the \emph{geometry shader} in the GPU graphic pipeline).
+
+\subsection{LoD Criteria and Temporal Updates}
+
+\begin{figure}[!htbp]
+  \centering
+  \includegraphics[width=0.9\textwidth]{figs/pipeline}
+  \caption{ This figure summarizes our GPU pipeline. Data buffers are
+    represented in green and computations in red. Each computation
+    retrieves data from a buffer and fills a new one. }
+  \label{fig_pipeline} 
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[height=0.2\textheight]{subdivision}
+\caption{The octree at frame $t$ is stored as a list of Morton codes in a buffer. 
+To update the tree, we fill a new buffer representing its state at frame $t+1$. 
+On the GPU, each code of the first buffer is processed in parallel. 
+If the cell is to be subdivided, it writes the codes of its children in the new buffer. 
+If it merges, it writes either nothing, or the code of its parent (if it is the first child).
+If it is kept, it just re-writes its own code. }
+\label{subdivision}
+\end{figure}
+
+\section{Interactive Computation on GPU}
+\label{sec:inter-visu-gpu}
 

### 2015-10-19 latex/article.tex
wip

@@
 
+As illustrated in Figure
+\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
+dependent criterion to decide if a cell needs to be refined: the
+closer we are to the camera, the finer the cells are. In addition to
+the distance criterion, we define an angular criterion to only
+subdivide cells within the field of view.
+
 \begin{figure}[!htbp]

### 2015-10-19 latex/article.tex
latex editing

@@
 
-\subsection{LoD Criteria and Temporal Updates}
+\subsection{Level of Details Criteria and Temporal Updates}
 
@@
 closer we are to the camera, the finer the cells are. In addition to
-the distance criterion, we define an angular criterion to only
-subdivide cells within the field of view.
+the distance criterion, we define an angular criterion to refine cells
+within the camera frustrum. When rendering a mesh, a key stage is the
+rasterization one which digitizes triangles projected onto the
+screen. As a consequence, having several triangles whose projections
+lie inside the same pixel is something we should prevent. Hence,
+distance criterion can be set in order to both control the geometrical
+approximation and to ensure that cells project onto more than one
+pixel. Figure \ref{fig_lod_octree} illustrates the level of details
+(LoD for short criterion) we use.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.4\linewidth]{viewlod2_small}  
+  \end{center}
+  \caption{Adaptive meshing in dimension 2 using the LoD distance and
+    angular criterion.}
+  \label{fig_lod_octree} 
+\end{figure}
 

### 2015-10-19 latex/article.tex
figs

@@
 pixel. Figure \ref{fig_lod_octree} illustrates the level of details
-(LoD for short criterion) we use.
-
-\begin{figure}
+(LoD for short criterion) we use. More precisely, in dimension 2, if
+$\alpha$ denotes the viewing angle, an object at distance $d$ from the
+camera with diameter greater than $2\cdot d\cdot\tan(\alpha)$ is
+projected into more than one pixel (see
+Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance criterion is based
+on the ratio (\emph{visibility ratio} in the following)between the
+cell diameter $l(c)$ (power of 2 depending on the depth), and $2\cdot
+d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell
+center and the camera. For a given cell $c$, split and merge decision
+are based on this visibility ratio:
+\begin{itemize}
+\item $c$ is split if its children cells have a visibility ratio
+  greater than  constant $k$\,;
+\item $c$ and its sibling cells are merged if their parent cell $c'$
+  have av visibility ration lower than $k$\;
+\item otherwise, the cell $c$ stays.
+\end{itemize}
+%
+\begin{figure}[!h]
   \begin{center}
-    \includegraphics[width=0.4\linewidth]{viewlod2_small}  
+    \begin{overpic}[width=4cm]{figs/criterion}
+      \put(33,40){$\alpha$}
+      \put(50,45){$d_c$}
+      \put(95,65){$l(c)$}
+    \end{overpic}~~~~~
+    \includegraphics[width=4cm]{viewlod2_small}~~~~~
+    \includegraphics[width=3.5cm]{subdivision}
   \end{center}
-  \caption{Adaptive meshing in dimension 2 using the LoD distance and
-    angular criterion.}
+  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and
+    angular criterion \emph{(middle)}. Based on LoD criterion
+    evaluation, the cell buffer is
+  updated between each frame \emph{(right)}.}
   \label{fig_lod_octree} 
 \end{figure}
+%
+In addition to the distance criterion, we add an angular term in order
+to prevent subdivision of cells far from the camera frustrum (see
+Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
+details but please not that stay, split and merge decisions of all cells are computed in
+parallel from all cell morton codes.
+
+Once decisions have been made, a new set of cells are sent to the mesh
+generation step described above. Updating the cell buffer can be
+efficiently implemented on GPU hardware as illustrated in
+Figure~\ref{fig_lod_octree}-\emph{rigth}.
+
+Finally, before constructing the triangulation from remaining cells
+and transition cells, geometrical culling is performed in order to
+skip the triangle patch construction which are not visible. Figure
+\ref{fig_pipeline} illustrates the overall fully data parallel
+pipeline.
 
@@
   \includegraphics[width=0.9\textwidth]{figs/pipeline}
-  \caption{ This figure summarizes our GPU pipeline. Data buffers are
+  \caption{ Summary our GPU pipeline. Data buffers are
     represented in green and computations in red. Each computation
@@
   \label{fig_pipeline} 
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[height=0.2\textheight]{subdivision}
-\caption{The octree at frame $t$ is stored as a list of Morton codes in a buffer. 
-To update the tree, we fill a new buffer representing its state at frame $t+1$. 
-On the GPU, each code of the first buffer is processed in parallel. 
-If the cell is to be subdivided, it writes the codes of its children in the new buffer. 
-If it merges, it writes either nothing, or the code of its parent (if it is the first child).
-If it is kept, it just re-writes its own code. }
-\label{subdivision}
 \end{figure}

### 2015-10-19 latex/article.tex
figs
Minor modification on abstract.

@@
   radii and thus select the appropriate scale to which the computation
-  is performed and visualized (mean and gaussian curvature, principal
-  curvatures, principal directions and normal vector field).
+  is performed and visualized. Mean and gaussian curvature, principal
+  curvatures, principal directions and normal vector field may be interactively
+  visualized with our technique.
 
@@
 efficiently implemented on GPU hardware as illustrated in
-Figure~\ref{fig_lod_octree}-\emph{rigth}.
+Figure~\ref{fig_lod_octree}-\emph{right}.
 

### 2015-10-19 src/cpp/vizo/Curvature.cpp
moving sinus cardinal

@@ -203,6 +203,7 @@ void Curvature::loadProgram()
 
         fprintf (stderr, "loading O(1) curv program... "); fflush (stderr);
         gk::GLCompiler& c = gk::loadProgram( SHADER_PATH("curvature.glsl"));
+		c.include(SHADER_PATH("potential.glsl") );
         c.include(SHADER_PATH("o1_include.glsl") );
 		c.include(SHADER_PATH("eigendecomposition.glsl"));
         GLProgram* tmp = c.make();
@@ -221,6 +222,7 @@ void Curvature::loadProgram()
 
         fprintf (stderr, "loading GT curv program... "); fflush (stderr);
         gk::GLCompiler& c = gk::loadProgram( SHADER_PATH("curvature.glsl"));
+		c.include(SHADER_PATH("potential.glsl") );
         c.include(SHADER_PATH("gt_include.glsl") );
 		c.include(SHADER_PATH("eigendecomposition.glsl"));
         GLProgram* tmp = c.make();
@@ -239,6 +241,7 @@ void Curvature::loadProgram()
 
         fprintf (stderr, "loading hierarchic curv program... "); fflush (stderr);
         gk::GLCompiler& c = gk::loadProgram( SHADER_PATH("curvature.glsl"));
+		c.include(SHADER_PATH("potential.glsl") );
         c.include(SHADER_PATH("hierarch_include.glsl") );
 		c.include(SHADER_PATH("eigendecomposition.glsl"));
         GLProgram* tmp = c.make();

### 2015-10-19 src/cpp/vizo/GpuOctree.cpp

@@ -388,6 +388,7 @@ void GPUOctree::loadPrograms()
 	
         gk::GLCompiler& c = gk::loadProgram( SHADER_PATH("octree_lod.glsl"));
 	   c.include(SHADER_PATH("noise.glsl") );
+	   c.include(SHADER_PATH("potential.glsl") );
 	   c.include(SHADER_PATH("octree_common.glsl") );
 	   c.include(SHADER_PATH("ltree.glsl") );
 
@@ -431,6 +432,7 @@ void GPUOctree::loadPrograms()
         fprintf (stderr, "Loading octree cull program... "); fflush (stderr);
         gk::GLCompiler& c = gk::loadProgram( SHADER_PATH("octree_cull.glsl") );
     	c.include(SHADER_PATH("noise.glsl") );
+		c.include(SHADER_PATH("potential.glsl") );
     	c.include(SHADER_PATH("octree_common.glsl") );
     	c.include(SHADER_PATH("ltree.glsl") );
 
@@ -475,6 +477,7 @@ void GPUOctree::loadPrograms()
 	   fprintf (stderr, "Loading cell draw program... "); fflush (stderr);
         gk::GLCompiler& c = gk::loadProgram( SHADER_PATH("cell_draw.glsl"));
     	c.include(SHADER_PATH("noise.glsl") );
+		c.include(SHADER_PATH("potential.glsl") );
     	c.include(SHADER_PATH("octree_common.glsl") );
     	c.include(SHADER_PATH("ltree.glsl") );
         GLProgram* tmp = c.make();

### 2015-10-19 src/cpp/vizo/PrimitiveDraw.cpp

@@ -26,6 +26,7 @@ void SphereDraw::loadProgram()
     
     fprintf (stderr, "loading sphere drawing program... "); fflush (stderr);
     gk::GLCompiler& c = gk::loadProgram( SHADER_PATH("drawsphere.glsl"));
+	c.include(SHADER_PATH("potential.glsl"));
     c.include(SHADER_PATH("noise.glsl") );
     c.include(SHADER_PATH("octree_common.glsl") );
     c.include(SHADER_PATH("ltree.glsl") );

### 2015-10-19 src/cpp/vizo/RegularTriangulation.cpp

@@ -136,6 +136,7 @@ void RegularTriangulation::loadPrograms()
 	fprintf (stderr, "Loading regular draw program... "); fflush (stderr);
 	gk::GLCompiler& c = gk::loadProgram( SHADER_PATH("regular_render.glsl"));
 	c.include(SHADER_PATH("noise.glsl") );
+	c.include(SHADER_PATH("potential.glsl") );
 	c.include(SHADER_PATH("octree_common.glsl") );
 	c.include(SHADER_PATH("ltree.glsl") );
 

### 2015-10-19 src/cpp/vizo/TransitionTriangulation.cpp

@@ -136,9 +136,10 @@ void TransitionTriangulation::loadPrograms()
 	gk::GLCompiler& c = gk::loadProgram( SHADER_PATH("transition_render.glsl") );
 
 	c.include(SHADER_PATH("noise.glsl") );
+	c.include(SHADER_PATH("potential.glsl") );
 	c.include(SHADER_PATH("octree_common.glsl") );
 	c.include(SHADER_PATH("ltree.glsl") );
-
+	
 	GLProgram* tmp = c.make();
 	if (tmp->errors)
 		exit(-1);

### 2015-10-19 src/cpp/vizo/main.cpp

@@ -722,6 +722,7 @@ public:
 			extractor.loadPrograms();
 			curver.loadProgram();
 			radiusShower.loadProgram();
+			shadator.loadProgram();
 			gk::reloadPrograms();
 			key('r')= 0;
 		}

### 2015-10-19 latex/article.tex
moving sinus cardinal
typo

--- 2015-10-19 latex/article.tex
@@
 approximation and to ensure that cells project onto more than one
-pixel. Figure \ref{fig_lod_octree} illustrates the level of details
-(LoD for short criterion) we use. More precisely, in dimension 2, if
-$\alpha$ denotes the viewing angle, an object at distance $d$ from the
-camera with diameter greater than $2\cdot d\cdot\tan(\alpha)$ is
-projected into more than one pixel (see
-Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance criterion is based
-on the ratio (\emph{visibility ratio} in the following)between the
-cell diameter $l(c)$ (power of 2 depending on the depth), and $2\cdot
-d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell
-center and the camera. For a given cell $c$, split and merge decision
-are based on this visibility ratio:
+pixel. This does not prevent all triangles within such cells to be
+projected into more than one pixel but gives us a fast criterion to
+decide if a cell should be split or not.  Figure \ref{fig_lod_octree}
+illustrates the level of details (LoD for short criterion) we
+use. More precisely, in dimension 2, if $\alpha$ denotes the viewing
+angle, an object at distance $d$ from the camera with diameter greater
+than $2\cdot d\cdot\tan(\alpha)$ is projected into more than one pixel
+(see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance
+criterion is based on the ratio (\emph{visibility ratio} in the
+following)between the cell diameter $l(c)$ (power of 2 depending on
+the depth), and $2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the
+distance between the cell center and the camera. For a given cell $c$,
+split and merge decision are based on this visibility ratio:
 \begin{itemize}
@@
 \item $c$ and its sibling cells are merged if their parent cell $c'$
-  have av visibility ration lower than $k$\;
-\item otherwise, the cell $c$ stays.
+  have av visibility ratio lower than $k$\;
+\item otherwise, the cell $c$ stays for the next frame.
 \end{itemize}

### 2015-10-19 tools/comparison/comparison.cpp
adding some tools

@@ -176,18 +176,18 @@ bool normalizeCPU( const std::vector< std::pair<Position*, Curvatures*> >& mapCP
       std::cout << "Leaving now..." << std::endl;
       return false;
     }
-    if( minimal_distance != 0 )
-    {
-      std::cout << "ERROR: The distance between {" << elemGPU.first->x << ","
-                                            << elemGPU.first->y << ","
-                                            << elemGPU.first->z << "} and {"
-                                            << minimal_position->x << ","
-                                            << minimal_position->y << ","
-                                            << minimal_position->z
-                << "} is greater than 1 (exactly " << std::sqrt(minimal_distance) << ")." << std::endl;
-      std::cout << "Leaving now..." << std::endl;
-      return false;
-    }
+    // if( minimal_distance > 1 )
+    // {
+    //   std::cout << "ERROR: The distance between {" << elemGPU.first->x << ","
+    //                                         << elemGPU.first->y << ","
+    //                                         << elemGPU.first->z << "} and {"
+    //                                         << minimal_position->x << ","
+    //                                         << minimal_position->y << ","
+    //                                         << minimal_position->z
+    //             << "} is greater than 1 (exactly " << std::sqrt(minimal_distance) << ")." << std::endl;
+    //   //std::cout << "Leaving now..." << std::endl;
+    //   //return false;
+    // }
 
     Position *copy_pos = new Position();
     Curvatures *copy_curv = new Curvatures();
@@ -204,7 +204,7 @@ bool normalizeCPU( const std::vector< std::pair<Position*, Curvatures*> >& mapCP
 
 bool computeDifference( const std::vector< std::pair<Position*, Curvatures*> >& mapGPU,
                         const std::vector< std::pair<Position*, Curvatures*> >& mapCPUnormalized,
-                        const uint errorType,
[…]

### 2015-10-19 tools/comparison/joinFiles.cpp

@@ -1,0 +1,263 @@
+#include <iostream>
+#include <cstdlib>
+#include <boost/algorithm/string.hpp>
+#include <map>
+#include <vector>
+#include <fstream>
+#include <cmath>
+#include <limits>
+
+#define NBDATA 4 /// x y z H k1 k2
+
+typedef unsigned int uint;
+typedef double Value;
+
+struct Curvatures
+{
+  Value mean;
+  Value k1;
+  Value k2;
+};
+class Position
+{
+public:
+  int x;
+  int y;
+  int z;
+
+public:
+  Position(){ x=0; y=0; z=0; }
+  Position(int _x, int _y, int _z){ x=_x; y=_y; z=_z; }
+
+  bool operator< (const Position& p) const
+  {
+    if ( x != p.x )
+    {
+      return x < p.x;
+    }
+    if ( y != p.y )
+    {
+      return y < p.y;
+    }
+    if ( z != p.z )
+    {
+      return z < p.z;
+    }
+    return false;
+  }
+  bool operator> (const Position& p) const
+  {
+    if( *this == p)
+    {
+      return false;
+    }
+    return !(*this < p);
+  }
+  bool operator== (const Position& p) const
+  {
+    return x == p.x && y == p.y && z == p.y;
+  }
+  bool operator!= (const Position& p) const
+  {
+    return !(*this == p);
+  }
+
+  Position operator-( const Position& p) const
+  {
+    return Position(x-p.x, y-p.y, z-p.z);
+  }
+};
+
+struct convertGPUtoKhalimsky : std::unary_function <unsigned int, double>
+{
+  inline
+  unsigned int operator() (const double& v) const
+  { return std::floor(2.0*v); }
+};
+
+struct convertCPUtoKhalimsky : std::unary_function <unsigned int, double>
+{
+  inline
+  unsigned int operator() (const double& v) const
+  { return std::floor(v); }
+};
+
+template< typename Predicate >
+bool loadFile(  const std::string& filename,
+                std::vector< std::pair<Position*, Value> >& results,
+                const Predicate& predicate )
+{
+  std::ifstream file( filename.c_str(), std::ifstream::in );
+  std::string line;
+
+  if( file.is_open())
+  {
+    std::cout << "Collecting data from file " << filename << " ..."<< std::endl;
+    while( getline(file,line) )
+    {
+      /// Skip if the line contains a # char, or N, or any line too small (avoid the new line a end of file)
[…]

### 2015-10-19 tools/comparison/cmake/src/cpp11/auto.cpp
moving to CMake

@@ -1,0 +1,34 @@
+/**
+ *  This program is free software: you can redistribute it and/or modify
+ *  it under the terms of the GNU Lesser General Public License as
+ *  published by the Free Software Foundation, either version 3 of the
+ *  License, or  (at your option) any later version.
+ *
+ *  This program is distributed in the hope that it will be useful,
+ *  but WITHOUT ANY WARRANTY; without even the implied warranty of
+ *  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ *  GNU General Public License for more details.
+ *
+ *  You should have received a copy of the GNU General Public License
+ *  along with this program.  If not, see <http://www.gnu.org/licenses/>.
+ *
+ **/
+
+#include <iostream>
+#include <vector>
+
+using namespace std;
+
+
+int main()
+{
+  auto x = 7;
+  auto s= "blam";
+
+  std::vector<int> t(20);
+
+  for (auto p = t.begin(); p!=t.end(); ++p) 
+    std::cout << *p << "\n";
+  
+  return 1;
+}

### 2015-10-19 latex/article.tex

@@
 may lead to huge payload from cache misses.  Efficient spatial tree
-encoding can be achieved using pointerless strictures. We use here
+encoding can be achieved using pointerless structures. We use
 linear quadtrees or octrees to represent classical quadtree/octreee
@@
 2, three bits in dimension 3) (see Figure
-\ref{fig_quadtree_partitionning}-\emph{left}). For a given cell, its
-code encodes its position with respect to its parent cell and its
+\ref{fig_quadtree_partitionning}-\emph{left}). A cell's code encodes
+ its position with respect to its parent cell and its
 complete path to the tree root. Hence, whatever their depth, all cell
@@
 In the following, we use the GPU implementation proposed by Dupuy
-\textit{et al.}  \cite{dupuy2014quadtrees}. In such approach, Morton
+\textit{et al.}  \cite{dupuy2014quadtrees}. By using their approach, Morton
 codes and bitwise operations are optimized to match with GPU hardware
@@
 within the camera frustrum. When rendering a mesh, a key stage is the
-rasterization one which digitizes triangles projected onto the
+rasterization which digitizes triangles projected onto the
 screen. As a consequence, having several triangles whose projections
@@
 use. More precisely, in dimension 2, if $\alpha$ denotes the viewing
-angle, an object at distance $d$ from the camera with diameter greater
-than $2\cdot d\cdot\tan(\alpha)$ is projected into more than one pixel
+angle, an object at distance $d$ from the camera with diameter greater than
+\todo{Extract formulas from text with dots list} $2\cdot d\cdot\tan(\alpha)$
+ is projected into more than one pixel
 (see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance
@@
 following)between the cell diameter $l(c)$ (power of 2 depending on
-the depth), and $2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the
-distance between the cell center and the camera. For a given cell $c$,
+the depth), and 
+$2\cdot d_c\cdot\tan(\alpha)$ \todo{idem}
+,$d_c$ being the distance between the cell center and the camera. For a given cell $c$,
 split and merge decision are based on this visibility ratio:
@@
 Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
-details but please not that stay, split and merge decisions of all cells are computed in
+details but please note that stay, split and merge decisions of all cells are computed in
 parallel from all cell morton codes.

### 2015-10-19 latex/article.tex
intro minor edits

@@
 
-\graphicspath{{./Figs/}}
+\graphicspath{{./figs/}}
 \input{macros}
@@
   to efficiently explore the curvature tensor on the boundary of
-  potentially large digital objects. More precisely, we combine a
-  fully parallel pipeline on GPU to extract an adaptive triangulated
-  isosurface of the digital object, with a curvature tensor
-  estimation at each surface point based on integral
-  invariants. Integral invariants being parametrized by a given ball
-  radius, our proposal allows us to explore interactively different
-  radii and thus select the appropriate scale to which the computation
-  is performed and visualized. Mean and gaussian curvature, principal
-  curvatures, principal directions and normal vector field may be interactively
-  visualized with our technique.
+  potentially large and dynamic digital objects (mean and gaussian curvature,
+  principal curvatures, principal directions and normal vector
+  field). More precisely, we combine a fully parallel pipeline on GPU
+  to extract an adaptive triangulated isosurface of the digital
+  object, with a curvature tensor estimation at each surface point
+  based on integral invariants. Integral invariants being parametrized
+  by a given ball radius, our proposal allows us to explore
+  interactively different radii and thus select the appropriate scale
+  to which the computation is performed and visualized.
 

### 2015-10-19 latex/article.tex
hierachical probes -> appendix
adding II part (in progress)

@@
 \label{sec:curv-tens-estim}
+
+In our context, we consider digital shapes (any subset of $\Z^d$) and boundaries
+of digital shapes. We denote by $\DSh$ the Gauss digitization of
+$\Shape$ in a $d-$dimensional grid with grid step $h$, \emph{i.e.}
+$\DSh = \Shape \cap (h\Z)^d$. For such digitized set $\DigShape$,
+$\Body{\DigShape}{h}$ denotes its topological boundary, seen as a cellular Cartesian
+complex (See Fig. \ref{fig:notations}-b). It is thus composed of $0$-cells and
+$1$-cells (resp. \emph{pointels} and \emph{linels}), and, for $d=3$, with
+$2$-cells ({\em surfels}), embedded in the digital grid.
+
+\begin{figure}[t]{\small
+    \begin{center}
+      \subfigure[]{\begin{overpic}[width=5cm]{figs/integral2D_2}
+          \put(42,28){$\times$}
+          \put(46,31){$\vx$}
+          \put(55,45){$B_R(\vx)$}
+          \put(1,10){$\dS$}
+          \put(20,10){$\Shape$}
+      \end{overpic}}
+      \subfigure[]{\begin{overpic}[width=5cm]{figs/notation_2}
+          \put(44.5,25){$\vp$}
+          \put(42,28.5){$\times$}
+          \put(45,32.5){$\vx$}
+          \put(45,16.5){$h$}
+          %\put(88,39){$\Proj(p)$}
+          \put(3,11){$\partial \Shape$}
+          \put(15,7){$\Body{\DigShape}{h}$}
+      \end{overpic}}
+      \vspace{-0.4cm}
+    \end{center}}
+    \caption{Integral invariant computation $(a)$ and
+      notations $(b)$ in dimension 2 \cite{CVIU2014}.\label{fig:notations}}
+\end{figure}
+
+% We define the volumetric integral as follow:
+% \begin{Definition}
+%   %
+%   Given $\Shape \in \Shapes$ and a radius $R \in \R^{+*}$, the volumetric
+%   integral $V_R(\vx)$ at $\vx \in \dS$ is given by:
+%   %
+%   \begin{equation}
+%     V_R(\vx) \EqDef \int_{B_R(\vx)} \chi(\vp) d\vp \,,
+%   \end{equation}
+%   %
+%   where $B_R(\vx)$ is the Euclidean ball of radius $R$ centered on $\vx$, and $\chi(\cdot)$ the characteristic function of $\Shape$. In dimension 2, we denote $A_R(\vx)$ such quantity.
+%   %
+% \end{Definition}
+
+In \cite{DGCI2013}, we have defined the 2D digital curvature estimator
+$\CurvH{R}$ and the 3D digital mean curvature estimator $\MeanCurvH{R}$ based on
+the digital volumetric integral $V_{R_d}$ (or $A_{R_d}$ in dimension 2) of the
+intersection between the shape $\Shape$ and a ball of digital radius $R_d$:
+
+\begin{Definition}
+  %
+  Given $\DigShape \subset \Z^2$ (or $\Z^3$ for 3D mean curvature estimator) and
+  $h$ a gridstep, {\em digital curvature estimators} are defined for any pointel
+  $\vp \in \Body{\DigShape}{h}$ as:
+  %
+  \begin{align}
+   \CurvH{R}(\DigShape,\vp) &\EqDef \frac{1}{h} \left( \frac{3 \pi}{2 R_d} - \frac{3 A_{R_d}(\vp)}{{R_d}^3} \right),\label{eq:dig-curvature-estimator-k}\\
+   \MeanCurvH{R}(\DigShape,\vp) &\EqDef \frac{1}{h} \left( \frac{8}{3 R_d} - \frac{4V_{R_d}(\vp)}{{\pi R_d}^4} \right),\label{eq:dig-curvature-estimator-H}
+  %  \\
+  %  \hat{\kappa}^{1}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_2 - 3\hat{\lambda}_1)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),\label{eq:dig-curvature-estimator-k1}\\
+  %  \hat{\kappa}^{2}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_1 - 3\hat{\lambda}_2)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),
+  %  \label{eq:dig-curvature-estimator-k2}
+  \end{align}
+  %
+  where $R_d = \frac{R}{h}$ is the digitized radius of the ball, and
+  $A_{R_d}(p)$ and $V_{R_d}(p)$ are the number of digital points in the
+  intersection between $\DigShape$ and the ball.
+  % Similarly, $\hat{\lambda}_1$
+  % and $\hat{\lambda}_2$ are the two greatest eigenvalues of the covariance
+  % matrix of the digital points in the intersection between $Z$ and the ball.
+  %
+\end{Definition}
+
+We have proved that estimating the 2D curvature and 3D mean curvature on digital
+objets with volumetric integral information achieve to the multigrid convergence
+property (setting $R = kh^\frac{1}{3}$ on convex shapes with at least
+$C^3$-boundary and bounded curvature). For short, when the digital objet become
+finer and finer, \ie when the digitization step $h$ tends to zero, the estimate
+quantity on $\DSh$ should converge (theoretically and experimentally) to the associated one on $\Shape$.
+
+\begin{align}
+  \CurvH{R}(\DSh,\vx,h) &= \Curv(\Shape,\vx) + O(h^{\frac{1}{3}}),\\
+  \MeanCurvH{R}(\DSh,\vx,h) &= \MeanCurv(\Shape,\vx) + O(h^{\frac{1}{3}}) \,.
+\end{align}
+
+In \cite{CVIU2014}
+the 3D digital principal curvature estimators $\kappa^1_{R}$ and $\kappa^2_{R}$
+on $Z\subset\Z^3$
+
+\begin{Definition}
+  %
+  Given $\DigShape \subset \Z^3$ and
+  $h$ a gridstep, {\em 3D digital principal curvature estimators} are defined for any pointel
+  $\vp \in \Body{\DigShape}{h}$ as:
+  %
+  \begin{align}
+    \hat{\kappa}^{1}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_2 - 3\hat{\lambda}_1)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),\label{eq:dig-curvature-estimator-k1}\\
+    \hat{\kappa}^{2}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_1 - 3\hat{\lambda}_2)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),
+    \label{eq:dig-curvature-estimator-k2}
+  \end{align}
+  %
+  where $R_d = \frac{R}{h}$ is the digitized radius of the ball, and
+  $\hat{\lambda}_1$ and $\hat{\lambda}_2$ are the two greatest eigenvalues of the covariance matrix of the digital points in the intersection between $Z$ and the ball.
+  %
+\end{Definition}
+
+% When dealing with digital data in a multigrid framework, we must pay
+% attention to on how quantities expend where decreasing the grid step
+% $h$. For example, if you fixed $R$, the digital radius will be $R_d
+% = \frac{5}{h}$ and increase when $h$ tends to zero.
+Authors of \cite{CVIU2014} have proved the convergence of these
+estimators when setting the ball radius dependent on the
+grid step $h$: $R = kh^\frac{1}{3}$, where $k$ is a constant related
+to the maximal curvature of the shape. More formally, we get:
+\begin{align}
+  \hat{\kappa}^1_{R}(\DigF{\Shape}{h},p) &= \kappa^1(X,x) + O(h^{\frac{1}{3}}),\\
+  \hat{\kappa}^2_{R}(\DigF{\Shape}{h},p) &= \kappa^2(X,x) + O(h^{\frac{1}{3}}),
+\end{align}
+when the ball radius is $R = kh^\frac{1}{3}$.
 
@@
 
+\section{Experiments}
+\label{sec:experiments}
+
+\section{Conclusion and Discussion}
+\label{sec:discussion}
+
+\appendix
+\section{Hierarchical Probing Algorithm}
+
 A {\em cell} is a tuple $(k,x,y,z)$, which represents a region of the space of size $2^k \times
@@
 
-\section{Experiments}
-\label{sec:experiments}
-
-\section{Conclusion and Discussion}
-\label{sec:discussion}
-
 \bibliographystyle{splncs03}

### 2015-10-20 latex/article.tex
minor

@@
 angle, an object at distance $d$ from the camera with diameter greater than
-\todo{Extract formulas from text with dots list} $2\cdot d\cdot\tan(\alpha)$
+\todo{Extract formulas from text with dots list}\todo{DC: I don't
+  understand what you mean} $2\cdot d\cdot\tan(\alpha)$
  is projected into more than one pixel

### 2015-10-20 latex/article.tex
minor

@@
 
-In our context, we consider digital shapes (any subset of $\Z^d$) and boundaries
-of digital shapes. We denote by $\DSh$ the Gauss digitization of
-$\Shape$ in a $d-$dimensional grid with grid step $h$, \emph{i.e.}
-$\DSh = \Shape \cap (h\Z)^d$. For such digitized set $\DigShape$,
-$\Body{\DigShape}{h}$ denotes its topological boundary, seen as a cellular Cartesian
-complex (See Fig. \ref{fig:notations}-b). It is thus composed of $0$-cells and
-$1$-cells (resp. \emph{pointels} and \emph{linels}), and, for $d=3$, with
-$2$-cells ({\em surfels}), embedded in the digital grid.
+In our context, we consider digital shapes (any subset of $\Z^d$) and
+boundaries of digital shapes. We denote by $\DSh$ the Gauss
+digitization of $\Shape$ in a $d-$dimensional grid with grid step $h$,
+\emph{i.e.}  $\DSh = \Shape \cap (h\Z)^d$. For such digitized set
+$\DigShape$, $\Body{\DigShape}{h}$ \todo{DC: $\partial\Body{.}{h}$,
+  pas $\Body{.}{h}$, c'est pas un bord fait de i-cell} denotes its
+topological boundary, seen as a cellular Cartesian complex (See
+Fig. \ref{fig:notations}-b). It is thus composed of $0$-cells and
+$1$-cells (resp. \emph{pointels} and \emph{linels}), and, for $d=3$,
+with $2$-cells ({\em surfels}), embedded in the digital grid.
 
@@
 We have proved that estimating the 2D curvature and 3D mean curvature on digital
-objets with volumetric integral information achieve to the multigrid convergence
+objets with volumetric integral information have the multigrid convergence
 property (setting $R = kh^\frac{1}{3}$ on convex shapes with at least
-$C^3$-boundary and bounded curvature). For short, when the digital objet become
-finer and finer, \ie when the digitization step $h$ tends to zero, the estimate
-quantity on $\DSh$ should converge (theoretically and experimentally) to the associated one on $\Shape$.
+$C^3$-boundary and bounded curvature) \cite{CVIU2014}. For short, when the digital objet becomes
+finer and finer, \ie when the digitization step $h$ tends to zero, the estimated
+quantity on $\DSh$  converges (theoretically and experimentally) to
+the associated one on $\partial\Shape$. More precisely, we have:
 
@@
 
-In \cite{CVIU2014}
-the 3D digital principal curvature estimators $\kappa^1_{R}$ and $\kappa^2_{R}$
-on $Z\subset\Z^3$
-
+In \cite{CVIU2014}, we have also defined the 3D digital principal curvature estimators $\kappa^1_{R}$ and $\kappa^2_{R}$
+on $Z\subset\Z^3$:
 \begin{Definition}
@@
 Authors of \cite{CVIU2014} have proved the convergence of these
-estimators when setting the ball radius dependent on the
-grid step $h$: $R = kh^\frac{1}{3}$, where $k$ is a constant related
-to the maximal curvature of the shape. More formally, we get:
+estimators when setting the ball radius $h$ in $R = kh^\frac{1}{3}$,
+where $k$ is a constant related to the maximal curvature of the
+shape. More formally, we get:
 \begin{align}
@@
 when the ball radius is $R = kh^\frac{1}{3}$.
+Additionally, eigenvectors associated with $\hat{\lambda}_1$ and
+$\hat{\lambda}_2$ correspond to principal curvature directions. The
+smallest eigvenvector corresponds to the normal direction at $p$.
+\todo[inline]{finir en citant le chapitre (ou CVIU) pour convergence directions}
+
+\todo[inline]{petite phrase pour dire que R depend de la géométrie
+  (citer DGCI pour paramter free, ou SMI pour dire qu'on peut s'en
+  servir pour feature) et qu'il faut explorer R}
 

### 2015-10-20 latex/article.tex
minor

@@
   $A_{R_d}(p)$ and $V_{R_d}(p)$ are the number of digital points in the
-  intersection between $\DigShape$ and the ball.
+  intersection between $\DigShape$ and the ball, $\DigShape\cap B_{R_d}(\vp)$.
   % Similarly, $\hat{\lambda}_1$

### 2015-10-20 latex/article.tex
intro

@@
 
-\textbf{Contributions}
+Volumetric objects are being more and more popular in many
+applications ranging from object modeling and rendering in Computer
+Graphics to geometry processing in Medical Imaging or Material
+Sciences. When considering large volumetric data, interactive
+visualization of such images (or isovalue surfaces) is a complex
+problem. Such issues become even more difficult when dynamic
+volumetric datasets are considered. Beside such isosurface
+visualization, we are also interested in performing geometry
+processing on the digital object and to explore different parameter
+settings of the geometry processing tool.  In this work, we focus on
+interactive visualization of volumetric data isosurfaces combined with
+a curvature tensor (mean/Gaussian curvature, principal curvatures
+directions\ldots) estimation at each point of the digital
+surface. Curvature maps on a given isosurface are key information when
+exploring 3D structures in Material Sciences \todo{REF}. Furthermore,
+since most curvature estimators require a parameter fixing the scale
+to which the computation is performed. For short, such parameter
+(integration radius, convolution kernel size, \ldots) specifies noise
+level on the object surface. As a consequence, exploring interactively
+different values of such parameter is mandatory.
+
+\noindent\textbf{Contributions}\quad In this work, we propose a framework
+to perform interactive visualization of complex 3D digital structures
+combined with a dynamic curvature tensor estimation. More precisely,
+we define a fully data parallel process on GPU hardware to both
+efficiently extract adaptive isosurface and compute per vertex
+curvature tensor using Integral Invariants estimators. Hence, this system
+allows us to visualize curvature tensor in realtime on large dynamic
+objects.
+
+\noindent\textbf{Related works}\quad Extracting and Visualizing
+isosurface on volumetric data has been widelyo investigated since the
+seminal Marching-Cubes approach by Lorensen and
+Cline~\cite{lorensen1987marching}. This approach being data parallel,
+GPU implementation of this method is very efficient
+\cite{tatarchuk2007real}. However, such technique generates a lot of
+triangles which is not well suited to large digital data. Hence,
+adaptive approaches have been proposed in order to optimize the
+triangular mesh resolution to the object geometry or depending on the
+viewpoint. In this topic, many solutions have been developed in
+Computer
+Graphics~\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.
+The method developed by Lengyel \textit{et al.}
+\cite{lengyel2010voxel} is the best suited to our needs.  However, it
+was developed to visualize in real-time static or near static data and
+present a complex CPU implementation.  In this paper we propose a GPU
+pipeline inspired from this method.  It leaves the CPU free for other
+tasks and avoids synchronisation with the GPU.  Our high framerate
+also allows this method to run in real-time on fully dynamic data.
+The triangulation is controlled by a GPU LoD criterion that ensures
+that triangles project onto more than one pixel, thus removing
+geometrical aliasing.
+
+Curvature estimation on digital surface
 
@@
 
-In our context, we consider digital shapes (any subset of $\Z^d$) and
+\sloppy In our context, we consider digital shapes (any subset of $\Z^d$) and
 boundaries of digital shapes. We denote by $\DSh$ the Gauss

### 2015-10-20 latex/article.tex
intro

@@
 different values of such parameter is mandatory.
+\vspace{0.2cm}
 
-\noindent\textbf{Contributions}\quad In this work, we propose a framework
-to perform interactive visualization of complex 3D digital structures
-combined with a dynamic curvature tensor estimation. More precisely,
-we define a fully data parallel process on GPU hardware to both
-efficiently extract adaptive isosurface and compute per vertex
-curvature tensor using Integral Invariants estimators. Hence, this system
-allows us to visualize curvature tensor in realtime on large dynamic
-objects.
+\noindent\textbf{Contributions}\quad In this work, we propose a
+framework to perform interactive visualization of complex 3D digital
+structures combined with a dynamic curvature tensor estimation. More
+precisely, we define a fully data parallel process on GPU hardware to
+both efficiently extract adaptive isosurface and compute per vertex
+curvature tensor using Integral Invariants estimators. Hence, this
+system allows us to visualize curvature tensor in realtime on large
+dynamic objects. Our approach combines a GPU implementation of
+pointerless octrees to represent the data, an adaptive
+viewpoint-dependent mesh extraction, and a GPU implementation of
+integral invariant curvature estimations.
 
-\noindent\textbf{Related works}\quad Extracting and Visualizing
+\vspace{0.2cm}
+
+\sloppy\noindent\textbf{Related works}\quad Extracting and Visualizing
 isosurface on volumetric data has been widelyo investigated since the
@@
 
-Curvature estimation on digital surface
+Curvature estimation on discrete or digital surface has also been
+widely investigated. In \cite{CVIU2014}, authors propose digital
+versions of Integral Invariant estimators
+\cite{Pottmann2007,Pottmann2009} in order to estimate the complete
+curvature tensor (mean/Gaussian curvatures, principal curvatures,
+principal curvature directions, normal vector field) on digital
+surfaces. Such approaches are based on an integration principle using
+a spherical kernel of a given radius. Additionally, authors have
+demonstrated that these estimators have multigrid convergence
+properties. In this article, we propose an efficient GPU
+implementation of such estimators in order to visualize, in real-time,
+such curvature maps and allowing us to interactively explore different
+values of the spherical kernel radius.
 

### 2015-10-20 latex/article.tex
intro

@@
 angle, an object at distance $d$ from the camera with diameter greater than
-\todo{Extract formulas from text with dots list}\todo{DC: I don't
-  understand what you mean} $2\cdot d\cdot\tan(\alpha)$
+ $2\cdot d\cdot\tan(\alpha)$
  is projected into more than one pixel
@@
 the depth), and
-$2\cdot d_c\cdot\tan(\alpha)$ \todo{idem}
-,$d_c$ being the distance between the cell center and the camera. For a given cell $c$,
+$2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell center and the camera. For a given cell $c$,
 split and merge decision are based on this visibility ratio:

### 2015-10-20 tools/comparison/comparison.cpp
adding offset by the center of mass of shapes

@@ -61,10 +61,37 @@ public:
   {
     return !(*this == p);
   }
+  Position& operator= (const Position& p)
+  {
+    x = p.x;
+    y = p.y;
+    z = p.z;
 
+    return *this;
+  }
+  Position& operator+= (const Position& p)
+  {
+    x += p.x;
+    y += p.y;
+    z += p.z;
+
+    return *this;
+  }
+  Position& operator/= (const int& v)
+  {
+    x /= v;
+    y /= v;
+    z /= v;
+
+    return *this;
+  }
   Position operator-( const Position& p) const
   {
     return Position(x-p.x, y-p.y, z-p.z);
+  }
+  Position operator+( const Position& p) const
+  {
+    return Position(x+p.x, y+p.y, z+p.z);
   }
 };
 
@@ -82,9 +109,31 @@ struct convertCPUtoKhalimsky : std::unary_function <unsigned int, double>
   { return std::floor(v); }
 };
 
+class convertCPUtoGPU : std::unary_function <Position, Position>
+{
+public:
+  convertCPUtoGPU( Position* barycenterGPU, Position* barycenterCPU )
+  {
+    offset = *barycenterGPU - *barycenterCPU;
+  }
+
+  Position operator() (const Position v) const
+  {
+    return v + offset;
+  }
+
+  Position getOffset() const
+  {
+    return offset;
+  }
+private:
+  Position offset;
+};
+
 template< typename Predicate >
 bool loadFile(  const std::string& filename,
                 std::vector< std::pair<Position*, Curvatures*> >& results,
+                Position* barycenter,
                 const Predicate& predicate )
 {
   std::ifstream file( filename.c_str(), std::ifstream::in );
@@ -121,6 +170,8 @@ bool loadFile(  const std::string& filename,
       p->y = predicate( std::atof(words[1].c_str()));
       p->z = predicate( std::atof(words[2].c_str()));
 
+      *barycenter += *p;
+
       Curvatures *c = new Curvatures();
       c->mean = std::atof(words[3].c_str());
       c->k1   = std::atof(words[4].c_str());
@@ -128,6 +179,7 @@ bool loadFile(  const std::string& filename,
 
       results.push_back( std::pair<Position*,Curvatures*>(p,c) );
     }
+    *barycenter /= results.size();
     std::cout << "... done." << std::endl;
     file.close();
   }
[…]

### 2015-10-20 tools/comparison/visuPoints.cpp

@@ -15,6 +15,83 @@
 
 typedef unsigned int uint;
 
+class Position
+{
+public:
+  int x;
+  int y;
+  int z;
+
+public:
+  Position(){ x=0; y=0; z=0; }
+  Position(int _x, int _y, int _z){ x=_x; y=_y; z=_z; }
+
+  bool operator< (const Position& p) const
+  {
+    if ( x != p.x )
+    {
+      return x < p.x;
+    }
+    if ( y != p.y )
+    {
+      return y < p.y;
+    }
+    if ( z != p.z )
+    {
+      return z < p.z;
+    }
+    return false;
+  }
+  bool operator> (const Position& p) const
+  {
+    if( *this == p)
+    {
+      return false;
+    }
+    return !(*this < p);
+  }
+  bool operator== (const Position& p) const
+  {
+    return x == p.x && y == p.y && z == p.y;
+  }
+  bool operator!= (const Position& p) const
+  {
+    return !(*this == p);
+  }
+  Position& operator= (const Position& p)
+  {
+    x = p.x;
+    y = p.y;
+    z = p.z;
+
+    return *this;
+  }
+  Position& operator+= (const Position& p)
+  {
+    x += p.x;
+    y += p.y;
+    z += p.z;
+
+    return *this;
+  }
+  Position& operator/= (const int& v)
+  {
+    x /= v;
+    y /= v;
+    z /= v;
+
+    return *this;
+  }
+  Position operator-( const Position& p) const
+  {
+    return Position(x-p.x, y-p.y, z-p.z);
+  }
+  Position operator+( const Position& p) const
+  {
+    return Position(x+p.x, y+p.y, z+p.z);
+  }
+};
+
 struct convertGPUtoKhalimsky : std::unary_function <unsigned int, double>
 {
   inline
@@ -29,11 +106,32 @@ struct convertCPUtoKhalimsky : std::unary_function <unsigned int, double>
   { return std::floor(v); }
 };
 
+class convertCPUtoGPU : std::unary_function <Position, Position>
+{
+public:
+  convertCPUtoGPU( Position* barycenterGPU, Position* barycenterCPU )
+  {
+    offset = *barycenterGPU - *barycenterCPU;
+  }
+
+  Position operator() (const Position v) const
+  {
+    return v + offset;
+  }
+
+  Position getOffset() const
+  {
+    return offset;
+  }
+private:
+  Position offset;
+};
+
 template< typename Predicate >
[…]

### 2015-10-20 src/cpp/vizo/Definitions.h
WIP hierachy fetching TODO: check the ball decomposition

@@ -116,6 +116,7 @@ enum {
 		TEXTURE_CODE_CLASS_TR, 
 		TEXTURE_CODE_VERTICES_TR ,
 		TEXTURE_CLASS_TRIANGLES_TR,
+		TEXTURE_SUBDIV_SPHERE,
 		TEXTURE_COUNT};
 
 // uniform locations

### 2015-10-20 src/cpp/vizo/Hierarchy.cpp
added forgotten files

@@ -1,0 +1,752 @@
+// Author: Jacques-Olivier Lachaud
+// gcc -O3 -std=c99 -Wall -pedantic hierarchy.c -lm -o hierarchy
+#include <stdlib.h>
+#include <stdio.h>
+#include <math.h>
+#include <assert.h>
+
+#include "Hierarchy.h"
+
+// Not in math.h
+#define PI 3.14159265358979323846
+#define LVL 11
+
+typedef float Value;
+
+// Useful basic functions
+Value square_int( int x );
+Value square( Value x );
+Value cube( Value x );
+Value distance2( int x1, int y1, int z1, int x2, int y2, int z2 );
+Value distance( int x1, int y1, int z1, int x2, int y2, int z2 );
+
+// Defines moment functors
+typedef Value (* VoxelFunctor )( Value data, int x, int y, int z );
+Value moment000( Value data, int x, int y, int z );
+Value moment100( Value data, int x, int y, int z );
+Value moment010( Value data, int x, int y, int z );
+Value moment001( Value data, int x, int y, int z );
+Value moment200( Value data, int x, int y, int z );
+Value moment020( Value data, int x, int y, int z );
+Value moment002( Value data, int x, int y, int z );
+Value moment110( Value data, int x, int y, int z );
+Value moment101( Value data, int x, int y, int z );
+Value moment011( Value data, int x, int y, int z );
+
+int xyzk_list[4*1000+1];
+
+// A 3D image of size (2^lvl)^3
+struct SImage {
+  int size;
+  int lvl;
+  Value* data;
+};
+typedef struct SImage Image;
+
+void  Image_init( Image* img, int k );
+Value Image_get( Image* img, int x, int y, int z );
+void  Image_set( Image* img, int x, int y, int z, Value v );
+void  Image_finish( Image* img );
+
+// A MipMap structure, i.e. a hierarchy of images with coarser and
+// coarser resolution.
+struct SMipMap {
+  int   max_lvl;
+  Image hierarchy[ LVL+1 ];
+};
+typedef struct SMipMap MipMap;
+
[…]

### 2015-10-20 src/cpp/vizo/Hierarchy.h

@@ -1,0 +1,8 @@
+#ifndef HIERARCHY_H_
+#define HIERARCHY_H_
+
+#include "Parameters.h"
+
+void computeSphereSubdivision(int r, int lvl);
+
+#endif

### 2015-10-20 tools/comparison/comparison.cpp
Tools are working now

@@ -7,190 +7,7 @@
 #include <cmath>
 #include <limits>
 
-#define NBDATA 6 /// x y z H k1 k2
-
-typedef unsigned int uint;
-typedef double Value;
-
-struct Curvatures
-{
-  Value mean;
-  Value k1;
-  Value k2;
-};
-class Position
-{
-public:
-  int x;
-  int y;
-  int z;
-
-public:
-  Position(){ x=0; y=0; z=0; }
-  Position(int _x, int _y, int _z){ x=_x; y=_y; z=_z; }
-
-  bool operator< (const Position& p) const
-  {
-    if ( x != p.x )
-    {
-      return x < p.x;
-    }
-    if ( y != p.y )
-    {
-      return y < p.y;
-    }
-    if ( z != p.z )
-    {
-      return z < p.z;
-    }
-    return false;
-  }
-  bool operator> (const Position& p) const
-  {
-    if( *this == p)
-    {
-      return false;
-    }
-    return !(*this < p);
-  }
-  bool operator== (const Position& p) const
-  {
-    return x == p.x && y == p.y && z == p.y;
-  }
-  bool operator!= (const Position& p) const
-  {
-    return !(*this == p);
-  }
-  Position& operator= (const Position& p)
-  {
-    x = p.x;
-    y = p.y;
-    z = p.z;
-
-    return *this;
-  }
-  Position& operator+= (const Position& p)
-  {
-    x += p.x;
-    y += p.y;
-    z += p.z;
-
-    return *this;
-  }
-  Position& operator/= (const int& v)
-  {
-    x /= v;
-    y /= v;
-    z /= v;
-
-    return *this;
-  }
-  Position operator-( const Position& p) const
-  {
-    return Position(x-p.x, y-p.y, z-p.z);
-  }
-  Position operator+( const Position& p) const
-  {
-    return Position(x+p.x, y+p.y, z+p.z);
-  }
-};
-
-struct convertGPUtoKhalimsky : std::unary_function <unsigned int, double>
-{
-  inline
-  unsigned int operator() (const double& v) const
-  { return std::floor(2.0*v); }
-};
-
-struct convertCPUtoKhalimsky : std::unary_function <unsigned int, double>
-{
-  inline
-  unsigned int operator() (const double& v) const
-  { return std::floor(v); }
-};
-
-class convertCPUtoGPU : std::unary_function <Position, Position>
-{
-public:
-  convertCPUtoGPU( Position* barycenterGPU, Position* barycenterCPU )
-  {
[…]

### 2015-10-20 tools/comparison/generateShape.sh

@@ -1,0 +1,6 @@
+#!/bin/zsh
+
+# Example : ./launchMe.sh cube18.raw 18 32
+
+LD_LIBRARY_PATH=/usr/local/lib volgen cube -len 2 -v cube4.vol
+vol2raw cube4

### 2015-10-20 tools/comparison/helpers.h

@@ -1,0 +1,226 @@
+#pragma once
+
+#if defined(helpers_RECURSES)
+#error Recursive header files inclusion detected in helpers.h
+#else // defined(helpers_RECURSES)
+/** Prevents recursive inclusion of headers. */
+#define helpers_RECURSES
+
+#if !defined helpers_h
+/** Prevents repeated inclusion of headers. */
+#define helpers_h
+
+#include <iostream>
+
+typedef unsigned int uint;
+typedef double Value;
+
+struct Curvatures
+{
+  Value mean;
+  Value k1;
+  Value k2;
+};
+class Position
+{
+public:
+  int x;
+  int y;
+  int z;
+
+public:
+  Position(){ x=0; y=0; z=0; }
+  Position(int _x, int _y, int _z){ x=_x; y=_y; z=_z; }
+
+  bool operator< (const Position& p) const
+  {
+    if ( x != p.x )
+    {
+      return x < p.x;
+    }
+    if ( y != p.y )
+    {
+      return y < p.y;
+    }
+    if ( z != p.z )
+    {
+      return z < p.z;
+    }
+    return false;
+  }
+  bool operator> (const Position& p) const
+  {
+    if( *this == p)
+    {
+      return false;
+    }
+    return !(*this < p);
+  }
+  bool operator== (const Position& p) const
+  {
+    return x == p.x && y == p.y && z == p.y;
+  }
+  bool operator!= (const Position& p) const
+  {
+    return !(*this == p);
+  }
+  Position& operator= (const Position& p)
+  {
+    x = p.x;
+    y = p.y;
+    z = p.z;
+
+    return *this;
+  }
+  Position& operator+= (const Position& p)
+  {
+    x += p.x;
+    y += p.y;
+    z += p.z;
+
+    return *this;
+  }
+  Position& operator+= (const int& v)
+  {
+    x += v;
+    y += v;
+    z += v;
+
+    return *this;
+  }
+  Position& operator/= (const int& v)
+  {
+    x /= v;
+    y /= v;
+    z /= v;
+
+    return *this;
+  }
+  Position operator-( const Position& p) const
+  {
+    return Position(x-p.x, y-p.y, z-p.z);
+  }
+  Position operator+( const Position& p) const
+  {
+    return Position(x+p.x, y+p.y, z+p.z);
+  }
+};
+
+struct convertGPUtoKhalimsky : std::unary_function <unsigned int, double>
+{
+  inline
[…]

### 2015-10-20 tools/comparison/joinFiles.cpp

@@ -7,83 +7,12 @@
 #include <cmath>
 #include <limits>
 
+#include "helpers.h"
+
 #define NBDATA 4 /// x y z H k1 k2
 
-typedef unsigned int uint;
-typedef double Value;
-
-struct Curvatures
-{
-  Value mean;
-  Value k1;
-  Value k2;
-};
-class Position
-{
-public:
-  int x;
-  int y;
-  int z;
-
-public:
-  Position(){ x=0; y=0; z=0; }
-  Position(int _x, int _y, int _z){ x=_x; y=_y; z=_z; }
-
-  bool operator< (const Position& p) const
-  {
-    if ( x != p.x )
-    {
-      return x < p.x;
-    }
-    if ( y != p.y )
-    {
-      return y < p.y;
-    }
-    if ( z != p.z )
-    {
-      return z < p.z;
-    }
-    return false;
-  }
-  bool operator> (const Position& p) const
-  {
-    if( *this == p)
-    {
-      return false;
-    }
-    return !(*this < p);
-  }
-  bool operator== (const Position& p) const
-  {
-    return x == p.x && y == p.y && z == p.y;
-  }
-  bool operator!= (const Position& p) const
-  {
-    return !(*this == p);
-  }
-
-  Position operator-( const Position& p) const
-  {
-    return Position(x-p.x, y-p.y, z-p.z);
-  }
-};
-
-struct convertGPUtoKhalimsky : std::unary_function <unsigned int, double>
-{
-  inline
-  unsigned int operator() (const double& v) const
-  { return std::floor(2.0*v); }
-};
-
-struct convertCPUtoKhalimsky : std::unary_function <unsigned int, double>
-{
-  inline
-  unsigned int operator() (const double& v) const
-  { return std::floor(v); }
-};
-
 template< typename Predicate >
-bool loadFile(  const std::string& filename,
+bool loadFile2(  const std::string& filename,
                 std::vector< std::pair<Position*, Value> >& results,
                 const Predicate& predicate )
 {
@@ -200,24 +129,12 @@ void writeFile( const std::string& fileOutput,
   myfile.close();
 }
 
-void deleteVector( std::vector< std::pair<Position*, Value> >& _map )
+void deleteVector2( std::vector< std::pair<Position*, Value> >& _map )
 {
   for(  std::vector< std::pair<Position*, Value> >::iterator it=_map.begin();
[…]

### 2015-10-20 tools/comparison/launchComparison.sh

@@ -1,0 +1,25 @@
+#!/bin/zsh
+# ./launchMe.sh <Raw file in RAW_PATH folder> <size> <texture_size> <radius_size>
+# Example : ./launchMe.sh cube18.raw 18 32 5
+
+ROOT_PATH=$PWD/../..
+TOOLS_PATH=$PWD
+RAW_PATH=$ROOT_PATH/data/raw
+VIZO_PATH=$ROOT_PATH/src/gkit
+DGTALTOOLS_BUILD_PATH=~/Dev/DGtalTools/build
+RADIUS=$4
+
+cd $VIZO_PATH
+./vizo $RAW_PATH/$1 1 $2
+
+cd $TOOLS_PATH
+$DGTALTOOLS_BUILD_PATH/visualisation/3dCurvatureViewer -i $RAW_PATH/$1 -r $4 -t $2 -u 255 --exportDat CPU_mean.txt -m mean
+$DGTALTOOLS_BUILD_PATH/visualisation/3dCurvatureViewer -i $RAW_PATH/$1 -r $4 -t $2 -u 255 --exportDat CPU_k1.txt -m k1
+$DGTALTOOLS_BUILD_PATH/visualisation/3dCurvatureViewer -i $RAW_PATH/$1 -r $4 -t $2 -u 255 --exportDat CPU_k2.txt -m k2
+
+./joinFiles export0_$1:r_r$4.00_cpu.txt CPU_mean.txt CPU_k1.txt CPU_k2.txt
+rm -f CPU_mean.txt
+rm -f CPU_k1.txt
+rm -f CPU_k2.txt
+./visuPoints $VIZO_PATH/export0_$1:r_r15.00_s$3_l0.txt export0_$1:r_r$4.00_cpu.txt
+./comparison $VIZO_PATH/export0_$1:r_r15.00_s$3_l0.txt export0_$1:r_r$4.00_cpu.txt

### 2015-10-20 tools/comparison/visuPoints.cpp

@@ -11,204 +11,82 @@
 #include "DGtal/io/viewers/Viewer3D.h"
 #include "DGtal/helpers/StdDefs.h"
 
-#define NBDATA 3 /// x y z
+#include "helpers.h"
 
-typedef unsigned int uint;
-
-class Position
-{
-public:
-  int x;
-  int y;
-  int z;
-
-public:
-  Position(){ x=0; y=0; z=0; }
-  Position(int _x, int _y, int _z){ x=_x; y=_y; z=_z; }
-
-  bool operator< (const Position& p) const
-  {
-    if ( x != p.x )
-    {
-      return x < p.x;
-    }
-    if ( y != p.y )
-    {
-      return y < p.y;
-    }
-    if ( z != p.z )
-    {
-      return z < p.z;
-    }
-    return false;
-  }
-  bool operator> (const Position& p) const
-  {
-    if( *this == p)
-    {
-      return false;
-    }
-    return !(*this < p);
-  }
-  bool operator== (const Position& p) const
-  {
-    return x == p.x && y == p.y && z == p.y;
-  }
-  bool operator!= (const Position& p) const
-  {
-    return !(*this == p);
-  }
-  Position& operator= (const Position& p)
-  {
-    x = p.x;
-    y = p.y;
-    z = p.z;
-
-    return *this;
-  }
-  Position& operator+= (const Position& p)
-  {
-    x += p.x;
-    y += p.y;
-    z += p.z;
-
-    return *this;
-  }
-  Position& operator/= (const int& v)
-  {
-    x /= v;
-    y /= v;
-    z /= v;
-
-    return *this;
-  }
-  Position operator-( const Position& p) const
-  {
-    return Position(x-p.x, y-p.y, z-p.z);
-  }
-  Position operator+( const Position& p) const
-  {
-    return Position(x+p.x, y+p.y, z+p.z);
-  }
-};
-
-struct convertGPUtoKhalimsky : std::unary_function <unsigned int, double>
-{
-  inline
-  unsigned int operator() (const double& v) const
-  { return std::floor(2.0*v); }
-};
-
-struct convertCPUtoKhalimsky : std::unary_function <unsigned int, double>
-{
-  inline
-  unsigned int operator() (const double& v) const
-  { return std::floor(v); }
-};
-
-class convertCPUtoGPU : std::unary_function <Position, Position>
-{
-public:
-  convertCPUtoGPU( Position* barycenterGPU, Position* barycenterCPU )
-  {
[…]

### 2015-10-20 latex/article.tex

@@
 structures combined with a dynamic curvature tensor estimation. More
-precisely, we define a fully data parallel process on GPU hardware to
+precisely, we define a fully data parallel process on GPU hardware \todo{Definir GPU au cas ou ?} to
 both efficiently extract adaptive isosurface and compute per vertex
@@
 \sloppy\noindent\textbf{Related works}\quad Extracting and Visualizing
-isosurface on volumetric data has been widelyo investigated since the
+isosurface on volumetric data has been widely investigated since the
 seminal Marching-Cubes approach by Lorensen and
@@
 decide if a cell should be split or not.  Figure \ref{fig_lod_octree}
-illustrates the level of details (LoD for short criterion) we
+illustrates the level of details (LoD for short) criterion we
 use. More precisely, in dimension 2, if $\alpha$ denotes the viewing
@@
 \label{sec:inter-visu-gpu}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=\textwidth]{figs/approx}
+  \end{center}
+  \caption{BALBLABLABLA.}
+  \label{fig:approx}
+\end{figure}
 

### 2015-10-21 latex/article.tex
section 2 of article

@@
 \newcommand{\eg}{\emph{e.g.} }
+\newcommand{\wrt}{\emph{w.r.t.} }
 \newcommand{\wnlog}{w.l.o.g. }
@@
 \emph{i.e.}  $\DSh = \Shape \cap (h\Z)^d$. For such digitized set
-$\DigShape$, $\Body{\DigShape}{h}$ \todo{DC: $\partial\Body{.}{h}$,
-  pas $\Body{.}{h}$, c'est pas un bord fait de i-cell} denotes its
+$\DigShape$, $\partial\Body{\DigShape}{h}$ denotes its
 topological boundary, seen as a cellular Cartesian complex (See
@@
           \put(44.5,25){$\vp$}
+          \put(55,45){$B_R(\vx)$}
           \put(42,28.5){$\times$}
@@
           \put(3,11){$\partial \Shape$}
-          \put(15,7){$\Body{\DigShape}{h}$}
+          \put(15,7){$\partial \Body{\DigShape}{h}$}
       \end{overpic}}
@@
 
-% We define the volumetric integral as follow:
-% \begin{Definition}
-%   %
-%   Given $\Shape \in \Shapes$ and a radius $R \in \R^{+*}$, the volumetric
-%   integral $V_R(\vx)$ at $\vx \in \dS$ is given by:
-%   %
-%   \begin{equation}
-%     V_R(\vx) \EqDef \int_{B_R(\vx)} \chi(\vp) d\vp \,,
-%   \end{equation}
-%   %
-%   where $B_R(\vx)$ is the Euclidean ball of radius $R$ centered on $\vx$, and $\chi(\cdot)$ the characteristic function of $\Shape$. In dimension 2, we denote $A_R(\vx)$ such quantity.
-%   %
-% \end{Definition}
-
 In \cite{DGCI2013}, we have defined the 2D digital curvature estimator
@@
 intersection between the shape $\Shape$ and a ball of digital radius $R_d$:
-
+%
 \begin{Definition}
   %
-  Given $\DigShape \subset \Z^2$ (or $\Z^3$ for 3D mean curvature estimator) and
-  $h$ a gridstep, {\em digital curvature estimators} are defined for any pointel
-  $\vp \in \Body{\DigShape}{h}$ as:
+  Given the Gauss digitization $\Body{\DSh}{h}$ of a shape $\Shape \subset \R^2$
+  (or $\R^3$ for the 3D mean curvature estimator) scaled by the digitization
+  step $h$, {\em digital curvature estimators} are defined for any point $\vx
+  \in \R^2$ (or $\R^3$) as:
   %
   \begin{align}
-   \CurvH{R}(\DigShape,\vp) &\EqDef \frac{1}{h} \left( \frac{3 \pi}{2 R_d} - \frac{3 A_{R_d}(\vp)}{{R_d}^3} \right),\label{eq:dig-curvature-estimator-k}\\
-   \MeanCurvH{R}(\DigShape,\vp) &\EqDef \frac{1}{h} \left( \frac{8}{3 R_d} - \frac{4V_{R_d}(\vp)}{{\pi R_d}^4} \right),\label{eq:dig-curvature-estimator-H}
-  %  \\
-  %  \hat{\kappa}^{1}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_2 - 3\hat{\lambda}_1)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),\label{eq:dig-curvature-estimator-k1}\\
-  %  \hat{\kappa}^{2}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_1 - 3\hat{\lambda}_2)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),
-  %  \label{eq:dig-curvature-estimator-k2}
+    \forall 0 < h < R,\quad
+    &\CurvH{R}(\Body{\DSh}{h},\vx,h) \EqDef \frac{3\pi}{2R}
+    - \frac{3\AreaC(\Ball{R/h}{\vx/h} \cap
+    \Body{\DSh}{h}, h)}{R^3}\,,\label{eq:dig-curvature-estimator-k}\\
+    &\MeanCurvH{R}(\Body{\DSh}{h},\vx,h) \EqDef \frac{8}{3R}
+    - \frac{4\VolC(\Ball{R/h}{\vx/h} \cap
+    \Body{\DSh}{h}, h)}{\pi R^4}\,.\label{eq:dig-curvature-estimator-H}
   \end{align}
   %
-  where $R_d = \frac{R}{h}$ is the digitized radius of the ball, and
-  $A_{R_d}(p)$ and $V_{R_d}(p)$ are the number of digital points in the
-  intersection between $\DigShape$ and the ball, $\DigShape\cap B_{R_d}(\vp)$.
+  where $\AreaC(\Ball{R/h}{\vx/h} \cap \Body{\DSh}{h}, h) = h^2 \MCard(
+  \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ and $\VolC(\Ball{R/h}{\vx/h} \cap
+  \Body{\DSh}{h}, h) = h^3 \MCard( \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ are
+  the number of digital points in the intersection between $\Body{\DSh}{h}$ and
+  the ball $\Ball{R/h}{\vx/h}$ of radius $R/h$ centered on $\vx/h$, scaled by
+  $h^d$.\todo[inline]{J: Hum... pas top...}
+  %
   % Similarly, $\hat{\lambda}_1$
@@
 \end{Definition}
-
+%
 We have proved that estimating the 2D curvature and 3D mean curvature on digital
 objets with volumetric integral information have the multigrid convergence
-property (setting $R = kh^\frac{1}{3}$ on convex shapes with at least
-$C^3$-boundary and bounded curvature) \cite{CVIU2014}. For short, when the digital objet becomes
+property (setting $R = kh^\frac{1}{3}$ on convex shapes, where $k$ is a constant
+related to the maximal curvature of the shape, with at least $C^3$-boundary and
+bounded curvature) \cite{DGCI2013}. For short, when the digital objet becomes
 finer and finer, \ie when the digitization step $h$ tends to zero, the estimated
-quantity on $\DSh$  converges (theoretically and experimentally) to
-the associated one on $\partial\Shape$. More precisely, we have:
-
+quantity on $\Bd{\Body{\DSh}{h}}$  converges (theoretically and experimentally)
+to the associated one on $\Bd{\Shape}$. More precisely, we have:
+%
 \begin{align}
-  \CurvH{R}(\DSh,\vx,h) &= \Curv(\Shape,\vx) + O(h^{\frac{1}{3}}),\\
-  \MeanCurvH{R}(\DSh,\vx,h) &= \MeanCurv(\Shape,\vx) + O(h^{\frac{1}{3}}) \,.
+\forall 0 < h \le h_0,\,\, &\forall \vx \in \Bd{\Shape},\,\,
+\forall \vxH \in \Bd{\Body{\DSh}{h}} \text{~with~} \| \vxH -\vx\|_\infty \le h, \nonumber \\
+&\CurvH{R}(\DSh, \vxH, h) = \Curv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,,\\
+&\MeanCurvH{R}(\DSh, \vxH, h) = \MeanCurv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,.
 \end{align}
 
-In \cite{CVIU2014}, we have also defined the 3D digital principal curvature estimators $\kappa^1_{R}$ and $\kappa^2_{R}$
-on $Z\subset\Z^3$:
+In \cite{CVIU2014}, we have also defined the 3D digital principal curvature
+estimators $\PrincCurvH{1}{R}$ and $\PrincCurvH{2}{R}$ on $Z\subset\Z^3$ based
+on digital moments:
+%
 \begin{Definition}
   %
-  Given $\DigShape \subset \Z^3$ and
-  $h$ a gridstep, {\em 3D digital principal curvature estimators} are defined for any pointel
-  $\vp \in \Body{\DigShape}{h}$ as:
+  Given the Gauss digitization $\Body{\DSh}{h}$ of a shape $\Shape \subset \R^3$
+  scaled by the digitization step $h$, {\em 3D digital principal curvature
+  estimators} are defined for any point $\vx \in \R^3$ as:
   %
   \begin{align}
-    \hat{\kappa}^{1}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_2 - 3\hat{\lambda}_1)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),\label{eq:dig-curvature-estimator-k1}\\
-    \hat{\kappa}^{2}(\DigShape,p) &\EqDef \frac{1}{h} \left( \frac{6(\hat{\lambda}_1 - 3\hat{\lambda}_2)}{\pi {{R_d}}^6} + \frac{8}{5{{R_d}}} \right),
+    \PrincCurvH{1}{R}(\Body{\DSh}{h},\vx,h) &\EqDef \frac{6}{\pi {R}^6}(\hat{\lambda}_2 - 3\hat{\lambda}_1) + \frac{8}{5{{R}}} \,,\label{eq:dig-curvature-estimator-k1}\\
+    \PrincCurvH{2}{R}(\Body{\DSh}{h},\vx,h) &\EqDef \frac{6}{\pi {R}^6}(\hat{\lambda}_1 - 3\hat{\lambda}_2) + \frac{8}{5{{R}}} \,,
     \label{eq:dig-curvature-estimator-k2}
@@
   where $R_d = \frac{R}{h}$ is the digitized radius of the ball, and
-  $\hat{\lambda}_1$ and $\hat{\lambda}_2$ are the two greatest eigenvalues of the covariance matrix of the digital points in the intersection between $Z$ and the ball.
+  $\hat{\lambda}_1$ and $\hat{\lambda}_2$ are the two greatest eigenvalues of
+  the covariance matrix of the digital points in the intersection between
+  $\Body{\DSh}{h}$ and the ball $\Ball{R/h}{\vx/h}$ of radius $R/h$ centered on
+  $\vx/h$.\todo[inline]{J: Pareil ici... pas top...}
   %
 \end{Definition}
+%
+The covariance matrix needs to compute digital moments of order $0$, $1$ and $2$
+(see Equation~20 of \cite{CVIU2014} for more details). We have also proved the
+convergence of these estimators when setting the ball radius $h$ in $R =
+kh^\frac{1}{3}$, where $k$ is a constant related to the maximal curvature of the
+shape, on convex shapes with at least $C^3$-boundary and bounded curvature
+\cite{CVIU2014}. More formally, we get:
+%
+\begin{align}
+  \forall 0 < h \le h_0,\,\, &\forall \vx \in \Bd{\Shape},\,\,
+  \forall \vxH \in \Bd{\Body{\DSh}{h}} \text{~with~} \| \vxH -\vx\|_\infty \le h, \nonumber \\
+  &\PrincCurvH{1}{R}(\DigF{\Shape}{h},\vxH, h) = \PrincCurv{1}(\Shape,\vx) + O\left(h^{\frac{1}{3}}\right) \,,\\
+  &\PrincCurvH{2}{R}(\DigF{\Shape}{h},\vxH, h) = \PrincCurv{2}(\Shape,\vx) + O\left(h^{\frac{1}{3}}\right) \,.
+\end{align}
 
-% When dealing with digital data in a multigrid framework, we must pay
-% attention to on how quantities expend where decreasing the grid step
-% $h$. For example, if you fixed $R$, the digital radius will be $R_d
-% = \frac{5}{h}$ and increase when $h$ tends to zero.
-Authors of \cite{CVIU2014} have proved the convergence of these
-estimators when setting the ball radius $h$ in $R = kh^\frac{1}{3}$,
-where $k$ is a constant related to the maximal curvature of the
-shape. More formally, we get:
-\begin{align}
-  \hat{\kappa}^1_{R}(\DigF{\Shape}{h},p) &= \kappa^1(X,x) + O(h^{\frac{1}{3}}),\\
-  \hat{\kappa}^2_{R}(\DigF{\Shape}{h},p) &= \kappa^2(X,x) + O(h^{\frac{1}{3}}),
-\end{align}
-when the ball radius is $R = kh^\frac{1}{3}$.
 Additionally, eigenvectors associated with $\hat{\lambda}_1$ and
-$\hat{\lambda}_2$ correspond to principal curvature directions. The
-smallest eigvenvector corresponds to the normal direction at $p$.
-\todo[inline]{finir en citant le chapitre (ou CVIU) pour convergence directions}
+$\hat{\lambda}_2$ of the covariance matrix correspond to principal curvature
+directions $\PrincDirH{1}{R}$ and $\PrincDirH{2}{R}$. The smallest eigvenvector
+corresponds to the normal direction $\NormalDirH{R}$ at $\vx$. Convergence
+results can be found in \cite{ChapterIICurvature}.\todo[inline]{Changer
+ChapterIICurvature dans le bibtex...}
 
-\todo[inline]{petite phrase pour dire que R depend de la géométrie
-  (citer DGCI pour paramter free, ou SMI pour dire qu'on peut s'en
-  servir pour feature) et qu'il faut explorer R}
+We have shown that the radius of the ball depends to the geometry of the
+underlying shape. In \cite{DGCI2014}, we proposed a parameter-free estimation of
+the radius of the ball by analyzing the shape \wrt the local geometry through to
+the maximal digital straight segments of the boundary of the digital shape. In
+\cite{SMI2015}, we analyze in scale-space (\ie with a range of radii) curvature
+estimation of our algorithm for a given digital shape. This allows us to detect
+features of the shape thanks to the behavior on singularities.
+In both methods, we need to explore the radius of the ball at different sizes and the computation time, depending to the size of the digital objet and the radius of the ball, is an obstacle.
+\todo[inline]{Faut faire une transition...}
+Computing curvatures from our algorithm in real-time can be really useful.
 

### 2015-10-21 latex/article.tex
notations

@@
 was developed to visualize in real-time static or near static data and
-present a complex CPU implementation.  In this paper we propose a GPU
+present a complex CPU implementation.\todo{DC: rajouter une phrase par
+  rapport à lengyel, Helene ? JP?}  In this paper we propose a GPU
 pipeline inspired from this method.  It leaves the CPU free for other
-tasks and avoids synchronisation with the GPU.  Our high framerate
+tasks and avoids synchronization with the GPU.  Our high framerate
 also allows this method to run in real-time on fully dynamic data.
@@
 \emph{i.e.}  $\DSh = \Shape \cap (h\Z)^d$. For such digitized set
-$\DigShape$, $\partial\Body{\DigShape}{h}$ denotes its
-topological boundary, seen as a cellular Cartesian complex (See
-Fig. \ref{fig:notations}-b). It is thus composed of $0$-cells and
-$1$-cells (resp. \emph{pointels} and \emph{linels}), and, for $d=3$,
-with $2$-cells ({\em surfels}), embedded in the digital grid.
+$\DigShape\EqDef\DSh$, $\Body{\DigShape}{h}$ is a subset of $\R^d$ corresponding
+to the union of hypercubes centered at $h\cdot \vz$ for  $\vz\in Z$
+with edge length $h$. By doing so, both $\partial\Shape$ and
+$\partial\Body{Z}{h}$ are topological boundary of objects lying in the
+same space (See
+Fig. \ref{fig:notations}-b). Note that the combinatorial digital boundary
+of $Z$ made of cells in a cellular Cartesian complex (\emph{pointels},
+\emph{linels}, {\em surfels}, \ldots), can be trivally embedded into $\R^d$
+such that it coincides with $\partial\Body{Z}{h}$.
 

### 2015-10-21 src/cpp/vizo/main.cpp
exporting a screenshot also when exporting the data

@@ -219,6 +219,7 @@ private:
 	bool was_culled;
 	int was_showing_dir;
 	int was_gt;
+	int was_wireframe;
 	
 	float last_radius;
 	float last_lvl;
@@ -381,12 +382,14 @@ public:
 			was_culled = Parameters::getInstance()->g_culling;
 			was_regular_grid = Parameters::getInstance()->g_regular;
 			was_showing_dir = Parameters::getInstance()->g_curv_dir;
-			was_gt = Parameters::getInstance()->g_ground_truth;
+			//was_gt = Parameters::getInstance()->g_ground_truth;
+			was_wireframe = Parameters::getInstance()->g_solid_wireframe;
 			
 			Parameters::getInstance()->g_culling = false;
 			Parameters::getInstance()->g_regular = true;
 			Parameters::getInstance()->g_curv_dir = 0;
-			Parameters::getInstance()->g_ground_truth = 1;
+			//Parameters::getInstance()->g_ground_truth = 1;
+			Parameters::getInstance()->g_solid_wireframe = 0;
 		}
 		
 		
@@ -469,6 +472,7 @@ public:
 			radiusShower.run();
 		}
 
+		static int nb_export = 0;
 		if (Parameters::getInstance()->g_draw_triangles)
 		{
 			m_time_shading->begin();
@@ -477,7 +481,6 @@ public:
 			glDisable(GL_RASTERIZER_DISCARD);
 			m_time_shading->end();
 			
-			static int nb_export = 0;
 			if (Parameters::getInstance()->g_export)
 			{
 				std::string file(argv[1]);
@@ -579,7 +582,7 @@ public:
 				Parameters::getInstance()->g_culling = was_culled;
 				Parameters::getInstance()->g_regular = was_regular_grid;
 				Parameters::getInstance()->g_curv_dir = was_showing_dir;
-				Parameters::getInstance()->g_ground_truth = was_gt;
+				//Parameters::getInstance()->g_ground_truth = was_gt;
 
 				fclose(plotfd);
 				printf("Done\n");
@@ -673,6 +676,21 @@ public:
 		blitter.blit();
                 
 		m_time_blit->end();
+		
+		if (Parameters::getInstance()->g_export)
+		{
+			std::string file(argv[1]);
+			file = file.substr(file.find_last_of('/')+1, (file.find_last_of('.')-1)-file.find_last_of('/'));
+			char buf[400];
[…]

### 2015-10-21 latex/article.tex
wip

@@
 
-\sloppy In our context, we consider digital shapes (any subset of $\Z^d$) and
-boundaries of digital shapes. We denote by $\DSh$ the Gauss
-digitization of $\Shape$ in a $d-$dimensional grid with grid step $h$,
-\emph{i.e.}  $\DSh = \Shape \cap (h\Z)^d$. For such digitized set
-$\DigShape\EqDef\DSh$, $\Body{\DigShape}{h}$ is a subset of $\R^d$ corresponding
-to the union of hypercubes centered at $h\cdot \vz$ for  $\vz\in Z$
-with edge length $h$. By doing so, both $\partial\Shape$ and
-$\partial\Body{Z}{h}$ are topological boundary of objects lying in the
-same space (See
-Fig. \ref{fig:notations}-b). Note that the combinatorial digital boundary
-of $Z$ made of cells in a cellular Cartesian complex (\emph{pointels},
-\emph{linels}, {\em surfels}, \ldots), can be trivally embedded into $\R^d$
-such that it coincides with $\partial\Body{Z}{h}$.
+\sloppy In our context, we consider digital shapes (any subset of
+$\Z^d$) and boundaries of digital shapes. We denote by $\DSh$ the
+Gauss digitization of $\Shape$ in a $d-$dimensional grid with grid
+step $h$, \emph{i.e.}  $\DSh \EqDef \{ \vz \in \Z^d,\, h\cdot\vz\in\Shape\}$. For such
+digitized set $\DigShape\EqDef\DSh$, $\Body{\DigShape}{h}$ is a subset
+of $\R^d$ corresponding to the union of hypercubes centered at $h\cdot
+\vz$ for $\vz\in Z$ with edge length $h$. By doing so, both
+$\partial\Shape$ and $\partial\Body{Z}{h}$ are topological boundary of
+objects lying in the same space (See Fig. \ref{fig:notations}-b). Note
+that the combinatorial digital boundary of $Z$ made of cells in a
+cellular Cartesian complex (\emph{pointels}, \emph{linels}, {\em
+  surfels}, \ldots), can be trivally embedded into $\R^d$ such that it
+coincides with $\partial\Body{Z}{h}$.
 
@@
           \put(20,10){$\Shape$}
-      \end{overpic}}
+      \end{overpic}}~~~~~~
       \subfigure[]{\begin{overpic}[width=5cm]{figs/notation_2}
@@
   %
-  Given the Gauss digitization $\Body{\DSh}{h}$ of a shape $\Shape \subset \R^2$
-  (or $\R^3$ for the 3D mean curvature estimator) scaled by the digitization
-  step $h$, {\em digital curvature estimators} are defined for any point $\vx
+  Given the Gauss digitization $Z\EqDef\DSh$ of a shape $\Shape \subset \R^2$
+  (or $\R^3$ for the 3D mean curvature estimator), {\em digital curvature estimators} are defined for any point $\vx
   \in \R^2$ (or $\R^3$) as:
@@
     \forall 0 < h < R,\quad
-    &\CurvH{R}(\Body{\DSh}{h},\vx,h) \EqDef \frac{3\pi}{2R}
+    &\CurvH{R}(Z,\vx,h) \EqDef \frac{3\pi}{2R}
     - \frac{3\AreaC(\Ball{R/h}{\vx/h} \cap
-    \Body{\DSh}{h}, h)}{R^3}\,,\label{eq:dig-curvature-estimator-k}\\
-    &\MeanCurvH{R}(\Body{\DSh}{h},\vx,h) \EqDef \frac{8}{3R}
+    {Z}, h)}{R^3}\,,\label{eq:dig-curvature-estimator-k}\\
+    &\MeanCurvH{R}(Z,\vx,h) \EqDef \frac{8}{3R}
     - \frac{4\VolC(\Ball{R/h}{\vx/h} \cap
-    \Body{\DSh}{h}, h)}{\pi R^4}\,.\label{eq:dig-curvature-estimator-H}
+    Z, h)}{\pi R^4}\,.\label{eq:dig-curvature-estimator-H}
   \end{align}
   %
-  where $\AreaC(\Ball{R/h}{\vx/h} \cap \Body{\DSh}{h}, h) = h^2 \MCard(
+  where $\AreaC(\Ball{R/h}{\vx/h} \cap \Body{\DSh}{h}, h) \EqDef h^2 \MCard(
   \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ and $\VolC(\Ball{R/h}{\vx/h} \cap
-  \Body{\DSh}{h}, h) = h^3 \MCard( \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ are
+  \Body{\DSh}{h}, h) \EqDef h^3 \MCard( \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ are
   the number of digital points in the intersection between $\Body{\DSh}{h}$ and
@@
 
-We have shown that the radius of the ball depends to the geometry of the
-underlying shape. In \cite{DGCI2014}, we proposed a parameter-free estimation of
-the radius of the ball by analyzing the shape \wrt the local geometry through to
-the maximal digital straight segments of the boundary of the digital shape. In
-\cite{SMI2015}, we analyze in scale-space (\ie with a range of radii) curvature
-estimation of our algorithm for a given digital shape. This allows us to detect
-features of the shape thanks to the behavior on singularities.
-In both methods, we need to explore the radius of the ball at different sizes and the computation time, depending to the size of the digital objet and the radius of the ball, is an obstacle.
-\todo[inline]{Faut faire une transition...}
-Computing curvatures from our algorithm in real-time can be really useful.
+We have shown that the radius of the ball depends on the geometry of
+the underlying shape. In \cite{DGCI2014}, we proposed a parameter-free
+estimation of the radius of the ball by analyzing the shape \wrt the
+local shape geometry using maximal digital straight segments of the
+digital boundary. In \cite{SMI2015}, we analyze in scale-space (\ie
+for a range of radii) curvature estimation of our algorithm for a
+given digital shape. This allows us to detect features of the shape
+thanks to the behavior on singularities.
+
+As a consequence, for all these integral invariant based approaches,
+we need to consider different ball radius which could be time
+consuming when implemented on CPU. We propose here a fully parallel
+implementation on GPU allowing us to change the radius and thus update
+the estimated quantities in realtime.
 
@@
 efficiently implemented on GPU hardware as illustrated in
-Figure~\ref{fig_lod_octree}-\emph{right}.
-
-Finally, before constructing the triangulation from remaining cells
-and transition cells, geometrical culling is performed in order to
-skip the triangle patch construction which are not visible. Figure
-\ref{fig_pipeline} illustrates the overall fully data parallel
-pipeline.
+Figure~\ref{fig_lod_octree}-\emph{right}.  Finally, before
+constructing the triangulation from remaining cells and transition
+cells, geometrical culling is performed in order to skip the triangle
+patch construction which are not visible. Figure \ref{fig_pipeline}
+illustrates the overall fully data parallel pipeline.
 
@@
 
-\section{Interactive Computation on GPU}
+\section{Interactive Curvature Computation on GPU}
 \label{sec:inter-visu-gpu}
+
+\subsection{Design principle}
+
+The general idea is to perform and Integral Invariant computation on
+GPU at each vertex of the generated triangular mesh. First note that
+of the LoD criterion is removed, each MC vertex is exactly centered at
+a surfel center. At different depth of the octree, MC vertices still
+correspond to surfel centers of subsampled versions of the input
+object. Hence, Integral Invariant framework defined in
+Section~\ref{sec:curv-tens-estim} is consistent with the triangular
+surface obtained on GPU: triangles are used for visualization purposes
+but all computations are performed on the digital object $Z$ and thus
+estimators
+(\ref{eq:dig-curvature-estimator-k}),
+(\ref{eq:dig-curvature-estimator-H}), (\ref{eq:dig-curvature-estimator-k1})
+and (\ref{eq:dig-curvature-estimator-k2}).
+
+To implement the integration on $B_R(x)\cap\Shape$
+(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
+digital points inside such domain (Fig.~\ref{fig:approx}-$b$) and then
+to estimate the geometrical moment as the sum of the geometrical
+moments of each elementary cubes lying in the intersection. On GPU,
 
@@
   \begin{center}
-    \includegraphics[width=\textwidth]{figs/approx}
+    \subfigure[]{\includegraphics[width=5cm]{figs/approx1}}
+    \subfigure[]{\includegraphics[width=5cm]{figs/approx-reg}}
+    \subfigure[]{\includegraphics[width=5cm]{figs/approx-reg-2}}
+    \subfigure[]{\includegraphics[width=5cm]{figs/approx-bh}}
+    \subfigure[]{\includegraphics[width=5cm]{figs/approx-ada}}
   \end{center}
@@
 \end{figure}
+
+\subsection{Realtime computation on GPU}
 

### 2015-10-21 latex/article.tex
wip

@@
 
-\subsection{Design principle}
+We first present design principles for the GPU implementation and then
+present our approaches.
+
+\subsection{Design principles}
 
@@
 
-To implement the integration on $B_R(x)\cap\Shape$
+To implement the integration on $B_R(\vx)\cap\Shape$\todo{fix Z vs X}
 (Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
@@
 moments of each elementary cubes lying in the intersection. On GPU,
-
+\emph{mipmap} textures to obtain a multiresolution information: if the
+input binary object is stored in a 3D texture, GPU hardware can
+construct a multiresolution pyramid such that 8 neighboring voxel
+intensities at level $l$ are averaged to define the voxel value at
+level $l+1$. If the level 0 corresponds to the binary input object, at
+a given level $l$, a voxel $(x,y,z)$ contains the fraction of $Z$
+belonging to the cube of center $(x,y,z)$ and edge length $2^l$. As a
+consequence, we can approximate the volume of $B_R(x)\cap\Shape$ by
+considering mipmap values at a given resolution $l$
+(Fig.~\ref{fig:approx}-$c$). In this case, errors only occurs for
+cells lying inside $\Shape$ (with density 1) not entirely covered by
+$B_R(\vx)$.
 \begin{figure}
   \begin{center}
-    \subfigure[]{\includegraphics[width=5cm]{figs/approx1}}
-    \subfigure[]{\includegraphics[width=5cm]{figs/approx-reg}}
-    \subfigure[]{\includegraphics[width=5cm]{figs/approx-reg-2}}
+    \subfigure[]{\includegraphics[width=4cm]{figs/approx1}}
+    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-1}}
+    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-2}}
+  \end{center}
+  \caption{Integral computation with an area estimation from pixel
+    counting $(b)$ or from densities (represented by different
+    grayvalues) in a mipmap approximation of $\Shape$.}
+  \label{fig:approx}
+\end{figure}
+
+Using the hierachical nature of the mipmap texture, we could also
+consider hierachical decompisitions of either $B_R(\vx)$
+(Fig.~\ref{fig:approx2}-$a$) or $B_R(\vx)\cap\Shape$
+(Fig.~\ref{fig:approx2}-$b$). The idea would be to decompose the
+regions into mipmap cells of different resolution in order to limit
+the number of texture access (important bottleneck on GPU hardwares)
+and to get better approximated quantities. Note that for the scenario
+in Fig.~\ref{fig:approx2}-$b$, there is no approximation (\wrt the
+regular grid case) since  geometrical moments are additive quantities.
+\begin{figure}
+  \begin{center}
     \subfigure[]{\includegraphics[width=5cm]{figs/approx-bh}}
@@
   \end{center}
-  \caption{BALBLABLABLA.}
-  \label{fig:approx}
+  \caption{Adaptive approximation of the integration using a
+    hierarchical decomposition of the ball $B_R(\vx)$ $(a)$, or a decomposition of $B_R(\vx)\cap\Shape$.}
+  \label{fig:approx2}
 \end{figure}

### 2015-10-21 latex/article.tex
wip
hop

@@
 surface obtained on GPU: triangles are used for visualization purposes
-but all computations are performed on the digital object $Z$ and thus
+but all computations are performed on the digital object $\DSh$ and thus
 estimators
@@
 
-To implement the integration on $B_R(\vx)\cap\Shape$\todo{fix Z vs X}
+To implement the integration on $B_R(\vx)\cap\Shape$\todo{Check ball
+  radii w.r.t. notations in sect2)
 (Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
@@
 level $l+1$. If the level 0 corresponds to the binary input object, at
-a given level $l$, a voxel $(x,y,z)$ contains the fraction of $Z$
+a given level $l$, a voxel $(x,y,z)$ contains the fraction of $\DSh$
 belonging to the cube of center $(x,y,z)$ and edge length $2^l$. As a
@@
 \subsection{Realtime computation on GPU}
+\begin{itemize}
+\item   Variante 1 : hierarchique avec précalcul cells
+\item   Variante 2 : reg avec autoraffinement
+\end{itemize}
 

### 2015-10-21 latex/article.tex
hop

@@
 To implement the integration on $B_R(\vx)\cap\Shape$\todo{Check ball
-  radii w.r.t. notations in sect2)
+  radii w.r.t. notations in sect2}
 (Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all

### 2015-10-21 latex/article.tex
wip
pe

@@
 \cite{lengyel2010voxel} is the best suited to our needs.  However, it
-was developed to visualize in real-time static or near static data and
-present a complex CPU implementation.\todo{DC: rajouter une phrase par
-  rapport à lengyel, Helene ? JP?}  In this paper we propose a GPU
-pipeline inspired from this method.  It leaves the CPU free for other
-tasks and avoids synchronization with the GPU.  Our high framerate
-also allows this method to run in real-time on fully dynamic data.
-The triangulation is controlled by a GPU LoD criterion that ensures
-that triangles project onto more than one pixel, thus removing
-geometrical aliasing.
+was only developed on CPU to visualize in real-time static or near
+static data, combining octree with new Marching-Cubes configurations
+to generate adaptive meshes. In this paper we propose a GPU pipeline
+inspired from this method.  It leaves the CPU free for other tasks and
+avoids synchronization with the GPU.  Our high framerate also allows
+this method to run in real-time on fully dynamic data.  The
+triangulation is controlled by a GPU LoD criterion that ensures that
+triangles project onto more than one pixel, thus removing geometrical
+aliasing.
 
@@
 
-\sloppy In our context, we consider digital shapes (any subset of
-$\Z^d$) and boundaries of digital shapes. We denote by $\DSh$ the
+\sloppy In our context, we consider digital shapes (any subset $Z$ of
+$\Z^d$) and boundaries of digital shapes $\partial Z$. We denote by $\DSh$ the
 Gauss digitization of $\Shape$ in a $d-$dimensional grid with grid
@@
       \subfigure[]{\begin{overpic}[width=5cm]{figs/notation_2}
-          \put(44.5,25){$\vp$}
+          \put(44.5,25){$h \cdot \vz$}
           \put(55,45){$B_R(\vx)$}

### 2015-10-21 latex/article.tex
typo on section 4

@@
 
-The general idea is to perform and Integral Invariant computation on
+The general idea is to perform an Integral Invariant computation on
 GPU at each vertex of the generated triangular mesh. First note that
-of the LoD criterion is removed, each MC vertex is exactly centered at
+when the LoD criterion is removed, each MC vertex is exactly centered at
 a surfel center. At different depth of the octree, MC vertices still
@@
 moments of each elementary cubes lying in the intersection. On GPU,
-\emph{mipmap} textures to obtain a multiresolution information: if the
+\emph{mipmap} textures are used to obtain a multi-resolution information: if the
 input binary object is stored in a 3D texture, GPU hardware can
-construct a multiresolution pyramid such that 8 neighboring voxel
+construct a multi-resolution pyramid such that 8 neighboring voxel
 intensities at level $l$ are averaged to define the voxel value at
@@
 Using the hierachical nature of the mipmap texture, we could also
-consider hierachical decompisitions of either $B_R(\vx)$
+consider hierarchical decompositions of either $B_R(\vx)$
 (Fig.~\ref{fig:approx2}-$a$) or $B_R(\vx)\cap\Shape$

### 2015-10-21 src/cpp/vizo/Hierarchy.cpp
Alignemnt of regular fetching on the mipmap grid

@@ -413,6 +413,74 @@ Value computeHierarchy( MipMap* M, int x0, int y0, int z0, Value r )
   return acc;
 }
 
+Value computeHierarchy( int lvl, int x0, int y0, int z0, Value r )
+{
+  Value weight[ LVL+1 ];
+  Value diag  [ LVL+1 ];
+  int max_k       = lvl; // number of levels in the hierarchy
+  weight[ max_k ] = (Value) 1;
+  diag  [ max_k ] = (Value) (sqrt(3.0)/2.0);
+  for ( int i = max_k - 1; i >= 0; --i )
+    {
+      weight[ i ] = weight[ i+1 ] * (Value) 8;
+      diag  [ i ] = diag  [ i+1 ] * (Value) 2;
+    }
+  int xyzk[ 4 ] = { 0, 0, 0, 0 };
+  Value acc = 0;
+  Value r2  = r*r;
+  do 
+    {
+      nb_iteration_hierarchy += 1;
+      int k = xyzk[ 3 ];  // current level in the hierarchy
+      int h = max_k - k;  // height in hierarchy (max_k - k )
+      // The distance must be computed in a kind of Khalimsky sense
+      // since centers of octree-cells are shifted from the origin (of
+      // (1<<h)/2.0)
+      Value dK2    = distance2( ( 2*xyzk[ 0 ] + 1) << h, ( 2*xyzk[ 1 ] + 1) << h, ( 2*xyzk[ 2 ] + 1 ) << h, 
+                                2*x0+1, 2*y0+1, 2*z0+1 );
+      Value d2     = dK2 / (Value) 4; // Divide by 4 to get back the distance.
+      Value delta2 = square( diag[ k ] );
+      Value upper2 = ( r2 >= delta2 ) ? r2 - 2.0*r*diag[ k ] + delta2 : -1.0; // (r-diag/2)^2
+      Value lower2 = r2 + 2.0*r*diag[ k ] + delta2; // (r+diag/2)^2
+      //printf( "[%d] %d %d %d | l2=%f d2=%f u2=%f\n", k, xyzk[ 0 ], xyzk[ 1 ], xyzk[ 2 ], lower2, d2, upper2 );
+      // Takes care of finest cells.
+      if ( h == 0 ) 
+        {
+          if ( d2 <= r2 ) 
+            { // cell is completely inside
[…]

### 2015-10-21 src/cpp/vizo/main.cpp
Fixed alignment with mipmap grid (a floor and a ceil missing) + exporting the number of probes

@@ -495,8 +495,10 @@ public:
 				if (plotfd == NULL)
 					perror("fopen");
 				
+				int nb_geom = -1;
+				
 				//fprintf(plotfd, "# Frame \t\t TotalCells \t\t RegCells \t\t TrCells \t\t Tgl \t\t LodTime (ms) \t\t CullTime (ms) \t\t RegTglTime (ms) \t\t TrTglTime (ms)\t\t ShadingTime (ms)\t\t ShdLessTime (ms)\t\t TotalTime (ms) \t\t Cpu Time (ns)\n");
-				fprintf(plotfd, "#Vertex \t\tCurv \tK1 \tK2 \tDir Min \t\tDir Max \t\tNormale\n");// \t\tEigenvalues \t\tCovmat Diag \t\tCovmat Upper\n");
+				fprintf(plotfd, "#Vertex \t\tCurv \tK1 \tK2 \tDir Min \t\tDir Max \t\tNormale \t\tNb Probe \n");// \t\tEigenvalues \t\tCovmat Diag \t\tCovmat Upper\n");
 				fprintf(plotfd, "N %d\n", 3*triangles_regular);
 			
 				printf(" [1/2] Copying from the GPU ... \n");
@@ -569,7 +571,18 @@ public:
 						{
 								fprintf(plotfd, "%lf\t", data_normale[nb2++]);
 						}
-						nb2++;
+						int p = data_normale[nb2++];
+						if (nb_geom == -1)
+						{
+							//printf("NBPROBE = %d\n", p);
+							nb_geom = p;
+						}
+						else
+						{
+							if (p != nb_geom)
+								printf("ERROR: %d != ref %d\n", p, nb_geom);
+						}
+						fprintf(plotfd, "%lf\t", p);
 						fprintf(plotfd, "\n");
 					}
 				}

### 2015-10-21 src/cpp/vizo/main.cpp
minor errors (printf format)

@@ -486,16 +486,17 @@ public:
 				std::string file(argv[1]);
 				file = file.substr(file.find_last_of('/')+1, (file.find_last_of('.')-1)-file.find_last_of('/'));
 				char buf[400];
-				sprintf (buf, "export%d_%s_r%.2lf_s%d_l%d.txt", nb_export++, file.c_str(), 
+				sprintf (buf, "export%d_%s_r%.2lf_s%d_l%d_m%d.txt", nb_export++, file.c_str(), 
 						 Parameters::getInstance()->g_curvradius, 
 						 Parameters::getInstance()->g_sizetex, 
-						 (int)Parameters::getInstance()->g_lvl);
+						 (int)Parameters::getInstance()->g_lvl,
+						 (int)Parameters::getInstance()->g_ground_truth);
 				printf("Exporting to %s...\n", buf);
 				plotfd = fopen(buf,"w");
 				if (plotfd == NULL)
 					perror("fopen");
 				
-				int nb_geom = -1;
+				float nb_geom = -1;
 				
 				//fprintf(plotfd, "# Frame \t\t TotalCells \t\t RegCells \t\t TrCells \t\t Tgl \t\t LodTime (ms) \t\t CullTime (ms) \t\t RegTglTime (ms) \t\t TrTglTime (ms)\t\t ShadingTime (ms)\t\t ShdLessTime (ms)\t\t TotalTime (ms) \t\t Cpu Time (ns)\n");
 				fprintf(plotfd, "#Vertex \t\tCurv \tK1 \tK2 \tDir Min \t\tDir Max \t\tNormale \t\tNb Probe \n");// \t\tEigenvalues \t\tCovmat Diag \t\tCovmat Upper\n");
@@ -571,7 +572,7 @@ public:
 						{
 								fprintf(plotfd, "%lf\t", data_normale[nb2++]);
 						}
-						int p = data_normale[nb2++];
+						float p = data_normale[nb2++];
 						if (nb_geom == -1)
 						{
 							//printf("NBPROBE = %d\n", p);
@@ -580,7 +581,7 @@ public:
 						else
 						{
 							if (p != nb_geom)
-								printf("ERROR: %d != ref %d\n", p, nb_geom);
+								printf("ERROR: %lf != ref %lf\n", p, nb_geom);
 						}
 						fprintf(plotfd, "%lf\t", p);
 						fprintf(plotfd, "\n");
@@ -695,10 +696,11 @@ public:
 			std::string file(argv[1]);
[…]

### 2015-10-21 src/cpp/vizo/Hierarchy.cpp
Hierarchical version now reducing texture accesses with symetries.

@@ -294,11 +294,14 @@ Value computeExact(int x0, int y0, int z0, Value r, int lvl)
         {
           if ( distance2( x0, y0, z0, x, y, z ) <= r2 )
             {
-			  xyzk_list[0]++;
-              xyzk_list[ (int)xyzk_list[0]*4 ] = x / pow(2, lvl) - 0.5;
-			  xyzk_list[ (int)xyzk_list[0]*4 + 1 ] = y / pow(2, lvl) - 0.5;
-			  xyzk_list[ (int)xyzk_list[0]*4 + 2 ] = z / pow(2, lvl) - 0.5;
-			  xyzk_list[ (int)xyzk_list[0]*4 + 3 ] = 0;
+				if (x >= 0 && y >= 0 && z >= 0)
+				{
+					xyzk_list[0]++;
+					xyzk_list[ (int)xyzk_list[0]*4 ] = x / pow(2, lvl) - 0.5;
+					xyzk_list[ (int)xyzk_list[0]*4 + 1 ] = y / pow(2, lvl) - 0.5;
+					xyzk_list[ (int)xyzk_list[0]*4 + 2 ] = z / pow(2, lvl) - 0.5;
+					xyzk_list[ (int)xyzk_list[0]*4 + 3 ] = 0;
+				}
             }
 		}
   return acc;
@@ -449,11 +452,16 @@ Value computeHierarchy( int lvl, int x0, int y0, int z0, Value r )
           if ( d2 <= r2 ) 
             { // cell is completely inside
               // printf("[%d] %d %d %d\n", k, xyzk[ 0 ], xyzk[ 1 ], xyzk[ 2 ] );
-              xyzk_list[0]++;
-              xyzk_list[ (int)xyzk_list[0]*4 ] = (xyzk[0] - pow(2, xyzk[3]-1))/pow(2, xyzk[3]);
-			  xyzk_list[ (int)xyzk_list[0]*4 + 1 ] = (xyzk[1] - pow(2, xyzk[3]-1))/pow(2, xyzk[3]);
-			  xyzk_list[ (int)xyzk_list[0]*4 + 2 ] = (xyzk[2] - pow(2, xyzk[3]-1))/pow(2, xyzk[3]);
-			  xyzk_list[ (int)xyzk_list[0]*4 + 3 ] = max_k - xyzk[3];
[…]

### 2015-10-21 latex/article.tex
minor modification about transvoxels; removed mention of aliasing issues since the criteria is a bit disputable on this matter.

@@
 closer we are to the camera, the finer the cells are. In addition to
-the distance criterion, we define an angular criterion to refine cells
-within the camera frustrum. When rendering a mesh, a key stage is the
-rasterization which digitizes triangles projected onto the
-screen. As a consequence, having several triangles whose projections
-lie inside the same pixel is something we should prevent. Hence,
-distance criterion can be set in order to both control the geometrical
-approximation and to ensure that cells project onto more than one
-pixel. This does not prevent all triangles within such cells to be
-projected into more than one pixel but gives us a fast criterion to
-decide if a cell should be split or not.  Figure \ref{fig_lod_octree}
+the distance criterion, we define an angular criterion to prevent refining cells outside the camera frustrum.
+Using a criterion based on the distance between a cell and the camera is well suited to GPU since it can be evaluated independently on all cells.
+Hence, we can efficiently determine if a cell must be subdivided or not.
+Figure \ref{fig_lod_octree}
 illustrates the level of details (LoD for short) criterion we

### 2015-10-21 latex/article.tex
wip section II article.tex

--- 2015-10-21 latex/article.tex
@@
 \cite{lengyel2010voxel} is the best suited to our needs.  However, it
-was only developed on CPU to visualize in real-time static or near
-static data, combining octree with new Marching-Cubes configurations
-to generate adaptive meshes. In this paper we propose a GPU pipeline
-inspired from this method.  It leaves the CPU free for other tasks and
-avoids synchronization with the GPU.  Our high framerate also allows
-this method to run in real-time on fully dynamic data.  The
-triangulation is controlled by a GPU LoD criterion that ensures that
-triangles project onto more than one pixel, thus removing geometrical
-aliasing.
+was developed to visualize in real-time static or near static data and
+present a complex CPU implementation.\todo{DC: rajouter une phrase par
+  rapport à lengyel, Helene ? JP?}  In this paper we propose a GPU
+pipeline inspired from this method.  It leaves the CPU free for other
+tasks and avoids synchronization with the GPU.  Our high framerate
+also allows this method to run in real-time on fully dynamic data.
+The triangulation is controlled by a GPU LoD criterion that ensures
+that triangles project onto more than one pixel, thus removing
+geometrical aliasing.
 
@@
 
-\sloppy In our context, we consider digital shapes (any subset $Z$ of
-$\Z^d$) and boundaries of digital shapes $\partial Z$. We denote by $\DSh$ the
-Gauss digitization of $\Shape$ in a $d-$dimensional grid with grid
-step $h$, \emph{i.e.}  $\DSh \EqDef \{ \vz \in \Z^d,\, h\cdot\vz\in\Shape\}$. For such
-digitized set $\DigShape\EqDef\DSh$, $\Body{\DigShape}{h}$ is a subset
-of $\R^d$ corresponding to the union of hypercubes centered at $h\cdot
-\vz$ for $\vz\in Z$ with edge length $h$. By doing so, both
-$\partial\Shape$ and $\partial\Body{Z}{h}$ are topological boundary of
-objects lying in the same space (See Fig. \ref{fig:notations}-b). Note
-that the combinatorial digital boundary of $Z$ made of cells in a
-cellular Cartesian complex (\emph{pointels}, \emph{linels}, {\em
-  surfels}, \ldots), can be trivally embedded into $\R^d$ such that it
-coincides with $\partial\Body{Z}{h}$.
+\sloppy In our context, we consider digital shapes (any subset $Z$ of $\Z^d$)
+and boundaries of digital shapes $\DigBoundary{Z}$. We denote by $\DSh$ the
+Gauss digitization of $\Shape$ in a $d-$dimensional grid with grid step $h$,
+\emph{i.e.}  $\DSh \EqDef \{ \vz \in \Z^d,\, h\cdot\vz\in\Shape\}$. For such
+digitized set $\DigShape\EqDef\DSh$, $\Body{\DigShape}{h}$ is a subset of $\R^d$
+corresponding to the union of hypercubes centered at $h\cdot \vz$ for $\vz\in Z$
+with edge length $h$. By doing so, both $\partial\Shape$ and
+$\partial\Body{Z}{h}$ are topological boundary of objects lying in the same
+space (See Fig. \ref{fig:notations}-b). Note that the combinatorial digital
+boundary $\DigBoundary{Z}$ of $Z$ made of cells in a cellular Cartesian complex
+(\emph{pointels}, \emph{linels}, \emph{surfels}, \ldots), can be trivally
+embedded into $\R^d$ such that it coincides with $\partial\Body{Z}{h}$.
 
@@
 $\CurvH{R}$ and the 3D digital mean curvature estimator $\MeanCurvH{R}$ based on
-the digital volumetric integral $V_{R_d}$ (or $A_{R_d}$ in dimension 2) of the
-intersection between the shape $\Shape$ and a ball of digital radius $R_d$:
+the digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ with
+$\MCard(Y)$ the number of digital points of $Y$ and $Y \subset \Z^d$ the
+intersection between the digital shape $\DigShape$ and a ball of digital radius
+$R/h$ (we denote such quantity $\AreaC(Y,h)$ in dimension 2):
 %
@@
   Given the Gauss digitization $Z\EqDef\DSh$ of a shape $\Shape \subset \R^2$
-  (or $\R^3$ for the 3D mean curvature estimator), {\em digital curvature estimators} are defined for any point $\vx
-  \in \R^2$ (or $\R^3$) as:
+  (or $\R^3$ for the 3D mean curvature estimator), {\em digital curvature
+  estimators} are defined for any point $\vx \in \R^2$ (or $\R^3$) as:
   %
@@
   %
-  where $\AreaC(\Ball{R/h}{\vx/h} \cap \Body{\DSh}{h}, h) \EqDef h^2 \MCard(
-  \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ and $\VolC(\Ball{R/h}{\vx/h} \cap
-  \Body{\DSh}{h}, h) \EqDef h^3 \MCard( \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ are
-  the number of digital points in the intersection between $\Body{\DSh}{h}$ and
-  the ball $\Ball{R/h}{\vx/h}$ of radius $R/h$ centered on $\vx/h$, scaled by
-  $h^d$.\todo[inline]{J: Hum... pas top...}
+  where $\Ball{R/h}{\vx/h}$ is the ball of digital radius $R/h$ centered on
+  digital point $(\vx/h) \in Z$.
+  %
+  % \AreaC(\Ball{R/h}{\vx/h} \cap \Body{\DSh}{h}, h) \EqDef h^2 \MCard(
+  % \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ and $\VolC(\Ball{R/h}{\vx/h} \cap
+  % \Body{\DSh}{h}, h) \EqDef h^3 \MCard( \Ball{R/h}{\vx/h} \cap \Body{\DSh}{h} )$ are
+  % the number of digital points in the intersection between $\Body{\DSh}{h}$ and
+  % the ball $\Ball{R/h}{\vx/h}$ of radius $R/h$ centered on $\vx/h$, scaled by
+  % $h^d$.\todo[inline]{J: Hum... pas top...}
   %
@@
 objets with volumetric integral information have the multigrid convergence
-property (setting $R = kh^\frac{1}{3}$ on convex shapes, where $k$ is a constant
-related to the maximal curvature of the shape, with at least $C^3$-boundary and
-bounded curvature) \cite{DGCI2013}. For short, when the digital objet becomes
-finer and finer, \ie when the digitization step $h$ tends to zero, the estimated
-quantity on $\Bd{\Body{\DSh}{h}}$  converges (theoretically and experimentally)
-to the associated one on $\Bd{\Shape}$. More precisely, we have:
+property \cite{DGCI2013}. For short, when the digital objet becomes finer and
+finer, \ie when the digitization step $h$ tends to zero, the estimated quantity
+on $\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to the
+associated one on $\Bd{\Shape}$.
+%
+%Since our digital estimators are defined on
+%digital shapes, in order to compare results with the exact curvature on
+%Euclidean shape, we need to match points on boundary of the digital
+%shape and points on the border of the Euclidean one.
+%
+Setting $R = kh^\frac{1}{3}$ on convex shapes
+with at least $C^3$-boundary and bounded curvature, where $k$ is a constant
+related to the maximal curvature of the shape, we have:
 %
@@
   %
-  Given the Gauss digitization $\Body{\DSh}{h}$ of a shape $\Shape \subset \R^3$
-  scaled by the digitization step $h$, {\em 3D digital principal curvature
-  estimators} are defined for any point $\vx \in \R^3$ as:
+  Given the Gauss digitization $Z \EqDef \DSh$ of a shape $\Shape \subset \R^3$,
+  {\em 3D digital principal curvature estimators} are defined for any point $\vx
+  \in \R^3$ as:
   %
   \begin{align}
-    \PrincCurvH{1}{R}(\Body{\DSh}{h},\vx,h) &\EqDef \frac{6}{\pi {R}^6}(\hat{\lambda}_2 - 3\hat{\lambda}_1) + \frac{8}{5{{R}}} \,,\label{eq:dig-curvature-estimator-k1}\\
-    \PrincCurvH{2}{R}(\Body{\DSh}{h},\vx,h) &\EqDef \frac{6}{\pi {R}^6}(\hat{\lambda}_1 - 3\hat{\lambda}_2) + \frac{8}{5{{R}}} \,,
+    \forall 0 < h < R,\quad
+    \PrincCurvH{1}{R}(Z,\vx,h) &\EqDef \frac{6}{\pi {R}^6}(\hat{\lambda}_2 - 3\hat{\lambda}_1) + \frac{8}{5 R} \,,\label{eq:dig-curvature-estimator-k1}\\
+    \PrincCurvH{2}{R}(Z,\vx,h) &\EqDef \frac{6}{\pi {R}^6}(\hat{\lambda}_1 - 3\hat{\lambda}_2) + \frac{8}{5 R} \,,
     \label{eq:dig-curvature-estimator-k2}
@@
   %
-  where $R_d = \frac{R}{h}$ is the digitized radius of the ball, and
-  $\hat{\lambda}_1$ and $\hat{\lambda}_2$ are the two greatest eigenvalues of
-  the covariance matrix of the digital points in the intersection between
-  $\Body{\DSh}{h}$ and the ball $\Ball{R/h}{\vx/h}$ of radius $R/h$ centered on
-  $\vx/h$.\todo[inline]{J: Pareil ici... pas top...}
+  where $\hat{\lambda}_1$ and $\hat{\lambda}_2$ are the two greatest eigenvalues
+  of the covariance matrix of the intersection between the digital shape
+  $\DigShape$ and a ball of digital radius $R/h$ centered on digital point
+  $\vx/h$.
   %
@@
 %
-The covariance matrix needs to compute digital moments of order $0$, $1$ and $2$
-(see Equation~20 of \cite{CVIU2014} for more details). We have also proved the
+The covariance matrix needs to compute digital moments of order $0$
+($\DMom{000}{h}$), of order $1$ ($\DMom{100}{h}$, $\DMom{010}{h}$ and
+$\DMom{001}{h}$) and of order $2$ ($\DMom{200}{h}$, $\DMom{020}{h}$,
+$\DMom{002}{h}$, $\DMom{110}{h}$, $\DMom{011}{h}$ and $\DMom{101}{h}$, see
+Equation~20 of \cite{CVIU2014} for more details). We have also proved the
 convergence of these estimators when setting the ball radius $h$ in $R =

### 2015-10-21 tools/comparison/comparison.cpp
adding a way to compute stats from 2 GPU files by setting 0 in last argument of comparison

@@ -145,7 +145,7 @@ int main( int argc, char** argv )
   //// User's choice
   if ( argc == 1 )
     {
-      std::cout << "Usage: " << argv[0] << "<fileGPU> <fileCPU>" << std::endl;
+      std::cout << "Usage: " << argv[0] << "<fileGPU> <fileCPU> <enableEmbedding>" << std::endl;
       std::cout << "       - computes the difference of results between the" << std::endl;
       std::cout << "         CPU version of the estimator and the GPU version" << std::endl;
       std::cout << "         GPU file : positions are between [0;size]." << std::endl;
@@ -157,6 +157,13 @@ int main( int argc, char** argv )
     }
   std::string fileGPU = argc > 1 ? std::string( argv[ 1 ] ) : "file1.txt";
   std::string fileCPU = argc > 2 ? std::string( argv[ 2 ] ) : "file2.txt";
+  int enableEmbedding = argc > 3 ? std::atoi( argv[ 3 ] ) : 1;
+  if( enableEmbedding != 0 && enableEmbedding != 1 )
+  {
+    std::cout << "EEROR: enableEmbedding must be 0 or 1. Get " << enableEmbedding << " instead." << std::endl;
+    std::cout << "Leaving now..." << std::endl;
+    return 0;
+  }
 
   //// Variables initialization
   std::vector< std::pair<Position*, Curvatures*> > mapGPU;
@@ -169,37 +176,63 @@ int main( int argc, char** argv )
   Position* barycenterCPU = new Position();
 
   //// Loading files
-  if( !loadFile( fileGPU, mapGPU, barycenterGPU, predicateGPU, 6 ))
+  if( enableEmbedding )
   {
+    if( !loadFile( fileGPU, mapGPU, barycenterGPU, predicateGPU, 6 ))
+    {
+      deleteVector( mapGPU );
+      return 0;
+    }
+    if( !loadFile( fileCPU, mapCPU, barycenterCPU, predicateCPU, 6 ))
+    {
+      deleteVector( mapGPU );
+      deleteVector( mapCPU );
+      return 0;
+    }
+
+    //// Normalize inputs
+    convertCPUtoGPU predicateCPUnormalized(barycenterGPU, barycenterCPU);
+    std::cout << "Barycenter of GPU file : {" << barycenterGPU->x << "," << barycenterGPU->y << "," << barycenterGPU->z << "}" << std::endl;
[…]

### 2015-10-21 latex/article.tex

@@
 the number of texture access (important bottleneck on GPU hardwares)
-and to get better approximated quantities. Note that for the scenario
-in Fig.~\ref{fig:approx2}-$b$, there is no approximation (\wrt the
-regular grid case) since  geometrical moments are additive quantities.
+and to get better approximated quantities. Note that the scenario in
+Fig.~\ref{fig:approx2}-$b$, is clearly the best approach: the
+volume is exact  (\wrt the regular grid case) since geometrical moments
+are additive quantities, and the number of texture fetches is  optimal
+at this point.
+
 \begin{figure}
@@
 
-\subsection{Realtime computation on GPU}
+\subsection{Per Vertex Realtime Computation on GPU}
+
+We describe here two different visualization pipeline on GPU that will
+be evaluated in the next section.
+
+\paragraph{Hierarchical decomposition}  As discussed above,
+
+\paragraph{Dynamic refinement}
+
 \begin{itemize}

### 2015-10-21 latex/article.tex
typo

@@
 curvature tensor using Integral Invariants estimators. Hence, this
-system allows us to visualize curvature tensor in realtime on large
+system allows us to visualize curvature tensor in real-time on large
 dynamic objects. Our approach combines a GPU implementation of
@@
 $\hat{\lambda}_2$ of the covariance matrix correspond to principal curvature
-directions $\PrincDirH{1}{R}$ and $\PrincDirH{2}{R}$. The smallest eigvenvector
+directions $\PrincDirH{1}{R}$ and $\PrincDirH{2}{R}$. The smallest eigenvector
 corresponds to the normal direction $\NormalDirH{R}$ at $\vx$. Convergence
@@
 implementation on GPU allowing us to change the radius and thus update
-the estimated quantities in realtime.
+the estimated quantities in real-time.
 
@@
 
-\subsection{Per Vertex Realtime Computation on GPU}
+\subsection{Per Vertex Real-time Computation on GPU}
 

### 2015-10-21 tools/comparison/launchComparison.sh
minor edit

@@ -21,5 +21,5 @@ $DGTALTOOLS_BUILD_PATH/visualisation/3dCurvatureViewer -i $RAW_PATH/$1 -r $4 -t 
 rm -f CPU_mean.txt
 rm -f CPU_k1.txt
 rm -f CPU_k2.txt
-./visuPoints $VIZO_PATH/export0_$1:r_r15.00_s$3_l0.txt export0_$1:r_r$4.00_cpu.txt
-./comparison $VIZO_PATH/export0_$1:r_r15.00_s$3_l0.txt export0_$1:r_r$4.00_cpu.txt
+./visuPoints $VIZO_PATH/export0_$1:r_r$4.00_s$3_l0.txt export0_$1:r_r$4.00_cpu.txt
+./comparison $VIZO_PATH/export0_$1:r_r$4.00_s$3_l0.txt export0_$1:r_r$4.00_cpu.txt

### 2015-10-21 src/cpp/vizo/GpuOctree.cpp
added expe files for density measurement object : octaflower 130 (texture 256^3) radius : 16 - export l[0...4] 	+ timing sum 	+ timing whole curvature 	+ nb_probe - comparison file [l1, l2, l\infty] 	+ mean error to l0 	+ k1 error to l0 	+ k2 error to l0

@@ -67,7 +67,7 @@ void GPUOctree::loadBuffers()
         //const size_t cap = 1 << 28;
 		
 		size_t full_tree = 1;
-		long int side = std::pow(2, 7); //lvl 8 max
+		long int side = std::pow(2, 8); //lvl 8 max
 		full_tree += side*side*side; 
 		
 		size_t full_tree_cap = full_tree * sizeof(float) * sizekey; //1 vec2 for each

### 2015-10-21 src/cpp/vizo/Parameters.cpp

@@ -54,7 +54,7 @@ Parameters::Parameters()
     g_regular = false;
     g_radius_show = true;
 
-	g_curvradius = 10.0;
+	g_curvradius = 5.0;
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 	

### 2015-10-21 src/cpp/vizo/main.cpp

@@ -206,6 +206,7 @@ private:
 	
 	//Plot file
 	FILE* plotfd;
+	FILE* plotfd2;
 	
 	//CPU flags
 	bool plot;
@@ -303,6 +304,20 @@ public:
 		
 		plot = false;
 		transition_cells_displayed = true;
+		
+		std::string file(argv[1]);
+		file = file.substr(file.find_last_of('/')+1, (file.find_last_of('.')-1)-file.find_last_of('/'));
+		printf("%s\n", file.c_str());
+		char buf[400];
+		sprintf (buf, "time_plot_%s_r%.2lf_s%d_l%d_m%d.txt", file.c_str(), 
+						 Parameters::getInstance()->g_curvradius, 
+						 Parameters::getInstance()->g_sizetex, 
+						 (int)Parameters::getInstance()->g_lvl,
+						 (int)Parameters::getInstance()->g_ground_truth);
+		plotfd2 = fopen(buf,"w");
+		if (plotfd2 == NULL)
+				perror("fopen");
+		fprintf(plotfd2, "#Lod\t Cull\t Extraction\t Curvature\n");
 		
 		// OpenGL context flags
 		glEnable (GL_DEPTH_TEST);
@@ -483,10 +498,13 @@ public:
 			
 			if (Parameters::getInstance()->g_export)
 			{
+				//m_time_shading->sync();
+				//gpu_shading_time = m_time_shading->result64() / 1000;
+				
 				std::string file(argv[1]);
 				file = file.substr(file.find_last_of('/')+1, (file.find_last_of('.')-1)-file.find_last_of('/'));
 				char buf[400];
-				sprintf (buf, "export%d_%s_r%.2lf_s%d_l%d_m%d.txt", nb_export++, file.c_str(), 
+				sprintf (buf, "export_%s_r%.2lf_s%d_l%d_m%d.txt", file.c_str(), 
 						 Parameters::getInstance()->g_curvradius, 
 						 Parameters::getInstance()->g_sizetex, 
 						 (int)Parameters::getInstance()->g_lvl,
@@ -500,7 +518,8 @@ public:
 				
[…]

### 2015-10-22 latex/article.tex
sect4

@@
 
-\paragraph{Hierarchical decomposition}  As discussed above,
+\paragraph{Hierarchical Decomposition.}  As discussed above, best
+results in terms of texture fetch can be obtained by the approach
+presented in Fig.~\ref{fig:approx2}-$b$. At each vertex, the
+computation algorithm would consist in a recursive decomposition of
+the domain such that a cell is subdivided if it does not belong to
+$B_R(\vx)\cap\Shape$. However, on GPU hardware, this approach is
+highly inefficient since the hardware optimizes the parallelism only
+when the micro-program described in the shader has a predictive
+execution flow. Hence, implementing the recursive algorithm (or its
+de-recursified version) requires a lot of branches (conditional
+\emph{if} tests) in the flow. Instead of implementing this approach,
+we have considered a fast hierarchical approximation following
+Fig.~\ref{fig:approx2}-$a$: for a given radius $R$, we precompute a
+hierachical decomposition of $B_R$. Such decomposition is made of
+octree cells at different resolutions. At a given MC vertex $\vx$, the
+algorithm becomes simple since we just scan  the ball cells and estimate
+the area (or other moments) from the mipmap values associated to this
+cell. Note that cells in the $B_R$ decomposition may not be aligned
+wuth mipmap cells. However, we can use GPU mipmap functionalities
+which interpolates mipmap values if we probe at non-discrete
+positions. For a given radius $R$, the expected number of cells on
+$B_r$ is in $O(\log{R})$.
 
-\paragraph{Dynamic refinement}
+\todo[inline]{phrase sur approx si on met}
 
-\begin{itemize}
-\item   Variante 1 : hierarchique avec précalcul cells
-\item   Variante 2 : reg avec autoraffinement
-\end{itemize}
+\paragraph{Dynamic Refinement.} In this approach, we want to optimize
+the interactivity and the execution flow or parallelism on GPU. The
+integration is simply computed using a regular grid at different
+resolution $l$ (Fig. \ref{fig:approx}-$b$ and $c$). The shader code
+becomes trivial (simple triple loop) and a lot of texture fetched are
+involved, but interactivity can be easily obtained. Indeed, we
+consider the following multi-pass approach:
+\begin{enumerate}
+\item When the surface geometry has been computed,we set the current
+  level $l$ at an high level $l\EqDef l_{max}$ of the mipmap
+  pyramid.
+\item We compute the integrals (and the curvature tensor) at the
+  mipmap level $l$ and  send the estimated quantities to the
+  visualization stage.
+\item If the user changes the camera position or the computation
+  parameters, we return to step 1.
+\item If the current framerate is above a given threshold, we decrease
+  $l$ and return to step 2 if the final $l_0$ level has not been
+  reached yet.
+\end{enumerate}
+A consequence of the multi-pass approach is that is there is no
+interaction (camera settings, parameters), the GPU automatically
+refine the estimation. Even if step 2 is quite expensive, in
+$O\left(\left(\frac{R}{2^l}\right)^3\right)$, the interactive control
+ in step 3 considerably improves the interactive exploration of the
+ tensor with fast preliminary approximations which are quickly refined.
 
@@
 
-\appendix
-\section{Hierarchical Probing Algorithm}
+%% \appendix
+%% \section{Hierarchical Probing Algorithm}
 
-A {\em cell} is a tuple $(k,x,y,z)$, which represents a region of the space of size $2^k \times
-2^k \times 2^k$, characterized by its integer coordinates $x,y,z$,
-with $0 \le x < 2^k$, $0 \le y < 2^k$, $0 \le z < 2^k$. Cells forms an
-octree decomposition of a cubic space. We use functions Up, Down and
-Next to navigate between cells.
+%% A {\em cell} is a tuple $(k,x,y,z)$, which represents a region of the space of size $2^k \times
+%% 2^k \times 2^k$, characterized by its integer coordinates $x,y,z$,
+%% with $0 \le x < 2^k$, $0 \le y < 2^k$, $0 \le z < 2^k$. Cells forms an
+%% octree decomposition of a cubic space. We use functions Up, Down and
+%% Next to navigate between cells.
 
-\begin{algorithm}
-\KwIn{Integers $p,q,r$ \tcp*{the moment orders, with $0 \le p+q+r \le 2$}}
-\KwIn{Integer $k$ \tcp*{$(2^k)^3$ is the size of the digital shape image}}
-\KwIn{Mipmap $V$ \tcp*{array of $k+1$ images of sizes $(2^k)^3,  (2^{k-1})^3, \ldots,  1^3$}}
-\KwIn{Integers $x_0,y_0,z_0$, Real $r$ \tcp*{Ball radius $r$ and center $(x_0,y_0,z_0)$}}
-\KwOut{Real $m$ \tcp*{estimation of the $p,q,r$-moment of $X \cap B_r(x_0,y_0,z_0)$}}
-\KwData{Cell $c :=  (k,0,0,0)$ \tcp*{Starts from biggest cell}}
-\KwData{Integer $n := 2^k$ \tcp*{Size of each cell}}
-\KwData{Real $d,\delta,l$ \tcp*{variables for intermediate computations}}
-\Begin{
-    m := 0 \;
-    \Repeat{$c[0] = k$}{
-      \tcp{Distance between cell and ball centers}
-      $d := \frac{1}{2}\| 2^k(2c[1]+1,2c[2]+1,2c[3]+1) - (2x_0+1,2y_0+1,2z_0+1) \|_2$\;
-      $\delta := \frac{\sqrt{3}}{2}2^{c[0]}$ \tcp*{half-length of cell diagonal}
-      \If(\tcp*[f]{Is it a unit cell ?}){$c[0] = 0$}{
-        \If(\tcp*[f]{Is cell center inside ball ?}){$d^2 \le r^2$}{
-          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$ \;
-        }
-        $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
-      } \Else{
-        $l := \max(r-\delta,0)$\;
-        \If(\tcp*[f]{Is cell completely inside ball ?}){$d^2 < l^2$}{
-          $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$\;
-          $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
-        }\ElseIf(\tcp*[f]{Is cell outside ball ?}){$d^2 > (r+\delta)^2$}{
-          $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
-        }\lElse(\tcp*[f]{Go to a finer cell}){$c := \textsc{Down}(c)$}
-      }
-    }
-    \Return{m}\;
-  }
-  \caption{Derecursified hierarchical algorithm for computing the
-    $p,q,r$-moment of set $X \cap B_r(x_0,y_0,z_0)$, given a mipmap
-    $V$ that represents the volume of a shape $X$ in each cell, and
-    ball parameters $x_0,y_0,z_0,r$.}
-\end{algorithm}
+%% \begin{algorithm}
+%% \KwIn{Integers $p,q,r$ \tcp*{the moment orders, with $0 \le p+q+r \le 2$}}
+%% \KwIn{Integer $k$ \tcp*{$(2^k)^3$ is the size of the digital shape image}}
+%% \KwIn{Mipmap $V$ \tcp*{array of $k+1$ images of sizes $(2^k)^3,  (2^{k-1})^3, \ldots,  1^3$}}
+%% \KwIn{Integers $x_0,y_0,z_0$, Real $r$ \tcp*{Ball radius $r$ and center $(x_0,y_0,z_0)$}}
+%% \KwOut{Real $m$ \tcp*{estimation of the $p,q,r$-moment of $X \cap B_r(x_0,y_0,z_0)$}}
+%% \KwData{Cell $c :=  (k,0,0,0)$ \tcp*{Starts from biggest cell}}
+%% \KwData{Integer $n := 2^k$ \tcp*{Size of each cell}}
+%% \KwData{Real $d,\delta,l$ \tcp*{variables for intermediate computations}}
+%% \Begin{
+%%     m := 0 \;
+%%     \Repeat{$c[0] = k$}{
+%%       \tcp{Distance between cell and ball centers}
+%%       $d := \frac{1}{2}\| 2^k(2c[1]+1,2c[2]+1,2c[3]+1) - (2x_0+1,2y_0+1,2z_0+1) \|_2$\;
+%%       $\delta := \frac{\sqrt{3}}{2}2^{c[0]}$ \tcp*{half-length of cell diagonal}
+%%       \If(\tcp*[f]{Is it a unit cell ?}){$c[0] = 0$}{
+%%         \If(\tcp*[f]{Is cell center inside ball ?}){$d^2 \le r^2$}{
+%%           $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$ \;
+%%         }
+%%         $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
+%%       } \Else{
+%%         $l := \max(r-\delta,0)$\;
+%%         \If(\tcp*[f]{Is cell completely inside ball ?}){$d^2 < l^2$}{
+%%           $m := m + V[c] * (2^k c[1])^p * (2^k c[2])^q * (2^k c[3])^r$\;
+%%           $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
+%%         }\ElseIf(\tcp*[f]{Is cell outside ball ?}){$d^2 > (r+\delta)^2$}{
+%%           $c := \textsc{Next}(c)$ \tcp*{Go to next cell}
+%%         }\lElse(\tcp*[f]{Go to a finer cell}){$c := \textsc{Down}(c)$}
+%%       }
+%%     }
+%%     \Return{m}\;
+%%   }
+%%   \caption{Derecursified hierarchical algorithm for computing the
+%%     $p,q,r$-moment of set $X \cap B_r(x_0,y_0,z_0)$, given a mipmap
+%%     $V$ that represents the volume of a shape $X$ in each cell, and
+%%     ball parameters $x_0,y_0,z_0,r$.}
+%% \end{algorithm}
 
-\begin{function}
-  \caption{Up( Cell $c$ ) : Cell}
-  \Return{Cell( $c[0]+1$, $c[1]/2$, $c[2]/2$, $c[3]/2$ )}
-\end{function}
-\begin{function}
-  \caption{Down( Cell $c$ ) : Cell}
-  \Return{Cell( $c[0]-1$, $c[1]*2$, $c[2]*2$, $c[3]*2$ )}
-\end{function}
-\begin{function}
-  \caption{Next( Cell $c$ ) : Cell}
-  \lWhile{$\mathrm{Odd}(c[1])$ and $\mathrm{Odd}(c[2])$ and $\mathrm{Odd}(c[3])$}{$c := \mathrm{Up}(c)$}
-  \lIf{$\mathrm{Even}(c[1])$}{$c[1] := c[1]+1$}
-  \Else{$c[1] := c[1] - 1$\;
-    \lIf{$\mathrm{Even}(c[2])$}{$c[2] := c[2]+1$}
-    \Else{$c[2] := c[2] - 1$\;
-      $c[3] := c[3]+1$}
-  }
-  \Return{c}
-\end{function}
+%% \begin{function}
+%%   \caption{Up( Cell $c$ ) : Cell}
+%%   \Return{Cell( $c[0]+1$, $c[1]/2$, $c[2]/2$, $c[3]/2$ )}
+%% \end{function}
+%% \begin{function}
+%%   \caption{Down( Cell $c$ ) : Cell}
+%%   \Return{Cell( $c[0]-1$, $c[1]*2$, $c[2]*2$, $c[3]*2$ )}
+%% \end{function}
+%% \begin{function}
+%%   \caption{Next( Cell $c$ ) : Cell}
+%%   \lWhile{$\mathrm{Odd}(c[1])$ and $\mathrm{Odd}(c[2])$ and $\mathrm{Odd}(c[3])$}{$c := \mathrm{Up}(c)$}
+%%   \lIf{$\mathrm{Even}(c[1])$}{$c[1] := c[1]+1$}
+%%   \Else{$c[1] := c[1] - 1$\;
+%%     \lIf{$\mathrm{Even}(c[2])$}{$c[2] := c[2]+1$}
+%%     \Else{$c[2] := c[2] - 1$\;
+%%       $c[3] := c[3]+1$}
+%%   }
+%%   \Return{c}
+%% \end{function}
 

### 2015-10-22 latex/article.tex
sect4

@@
 
+ Compared to the hierarchical approach, no precomputation is required
+ for a given radius $R$. As a consequence, we could even locally adapt
+ the ball radius to the geometry (for instance following the octree
+ depth of the current MC vertex). In the next section, we evaluate the
+ performances of both approaches.
+
 \section{Experiments}
 \label{sec:experiments}
+
+\subsection{Full resolution experiment}
+
+\subsection{Fully adaptive evaluation}
 
@@
 
-\bibliographystyle{splncs03}
-\bibliography{ictv}
+\bibliographystyle{splncs03} \bibliography{ictv}
 \end{document}

### 2015-10-22 latex/article.tex
template

@@
 \usepackage{tikz}        % standard LaTeX graphics tool
+\usepackage{pgfplots}
+
 %\usetikzlibrary{arrows}
@@
 \usepackage{todonotes}
+
+\usepackage{booktabs}
 
@@
 
+\begin{table}
+  \begin{center}
+    \begin{tabular}{@{}lrrrrrr@{}}
+      \toprule
+    Quantities & H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
+      \midrule
+      Number of texture fetches & & & & & &\\
+      Time (in ms) & & & & & &\\
+      $L_\infty$ error (\wrt $l_0$) & & & & & &\\
+      \bottomrule
+    \end{tabular}
+  \end{center}
+  \caption{object, size, radius, full res, num of vertices (timings
+    only consider the curvature estimation step).\label{tab:full-res-stat}}
+\end{table}
+
 \subsection{Fully adaptive evaluation}
+
+\begin{figure}[!htbp]
+  \begin{center}
+    \begin{tikzpicture}[scale=0.7]
+      \begin{axis}[
+          ybar stacked,
+	  bar width=15pt,
+	  nodes near coords,
+          enlargelimits=0.15,
+          legend style={at={(0.5,-0.20)},
+            anchor=north,legend columns=-1},
+          ylabel={\#Time (in ms)},
+          symbolic x coords={Octa-R1, Octa-R2, Snow-R1, Snow-R2, 
+	    xxx-R1, xxx-R2},
+          xtick=data,
+          x tick label style={rotate=45,anchor=east},
+        ]
+        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,2) 
+          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,0)};
+        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,0) 
+          (Snow-R1,0) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,0)};
+        \addplot+[ybar] plot coordinates {(Octa-R1,6) (Octa-R2,6)
+          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
+        \addplot+[ybar] plot coordinates {(Octa-R1,4) (Octa-R2,2) 
+          (Snow-R1,0) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
+        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
+      \end{axis}
+    \end{tikzpicture}
+     \begin{tikzpicture}[scale=0.7]
+      \begin{axis}[
+          ybar stacked,
+	  bar width=15pt,
+	  nodes near coords,
+          enlargelimits=0.15,
+          legend style={at={(0.5,-0.20)},
+            anchor=north,legend columns=-1},
+         % ylabel={\#Time (in ms)},
+          symbolic x coords={Octa-R1, Octa-R2, Snow-R1, Snow-R2, 
+	    xxx-R1, xxx-R2},
+          xtick=data,
+          x tick label style={rotate=45,anchor=east},
+        ]
+        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,2) 
+          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,0)};
+        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,0) 
+          (Snow-R1,0) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,0)};
+        \addplot+[ybar] plot coordinates {(Octa-R1,6) (Octa-R2,6)
+          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
+        \addplot+[ybar] plot coordinates {(Octa-R1,4) (Octa-R2,2) 
+          (Snow-R1,0) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
+       % \legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
+      \end{axis}
+    \end{tikzpicture}
+  \end{center}
+  \caption{Adaptive timings H vs. rafined (tout : adaptatif, 2 rayons par formes, 4
+    formes + images).}
+  \label{fig:timings}
+\end{figure}
 

### 2015-10-22 src/cpp/vizo/DataLoader.cpp
DataLoader in NEAREST. Showing mean curvature from volume in app

@@ -4,10 +4,10 @@
 
 #include <cstring>
 
-const GLenum MIN_FILT = GL_LINEAR_MIPMAP_LINEAR;
-const GLenum MAG_FILT = GL_LINEAR;
-//const GLenum MIN_FILT = GL_NEAREST_MIPMAP_NEAREST;
-//const GLenum MAG_FILT = GL_NEAREST;
+//const GLenum MIN_FILT = GL_LINEAR_MIPMAP_LINEAR;
+//const GLenum MAG_FILT = GL_LINEAR;
+const GLenum MIN_FILT = GL_NEAREST_MIPMAP_NEAREST;
+const GLenum MAG_FILT = GL_NEAREST;
 
 bool mymipmap = true;
 

### 2015-10-22 latex/article.tex
wip

@@
   \begin{center}
-    \subfigure{}{\includegraphics[width=\textwidth]{figs/morton}}
+    \subfigure{}{\includegraphics[width=0.9\textwidth]{figs/morton}}
     %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
@@
   \begin{center}
-    \begin{overpic}[width=4cm]{figs/criterion}
+    \begin{overpic}[width=3.5cm]{figs/criterion}
       \put(33,40){$\alpha$}
@@
     \end{overpic}~~~~~
-    \includegraphics[width=4cm]{viewlod2_small}~~~~~
-    \includegraphics[width=3.5cm]{subdivision}
+    \includegraphics[width=3.5cm]{viewlod2_small}~~~~~
+    \includegraphics[width=3cm]{subdivision}
   \end{center}
@@
   \begin{center}
-    \subfigure[]{\includegraphics[width=5cm]{figs/approx-bh}}
-    \subfigure[]{\includegraphics[width=5cm]{figs/approx-ada}}
+    \subfigure[]{\includegraphics[width=4cm]{figs/approx-bh}}
+    \subfigure[]{\includegraphics[width=4cm]{figs/approx-ada}}
   \end{center}
@@
 
+We first evaluate the curvature estimation on a full-resolution
+geometry obtained by disabling the LoD criterion at the mesh
+generation step.
+
 \begin{table}
   \begin{center}
-    \begin{tabular}{@{}lrrrrrr@{}}
+    \begin{tabular}{@{}lrrrrrrrrrrrr@{}}
       \toprule
-    Quantities & H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
+      & \multicolumn{6}{c}{$R=$}   & \multicolumn{6}{c}{$R=$}\\
+      \cmidrule(r){2-12}
+    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$& ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
       \midrule
-      Number of texture fetches & & & & & &\\
-      Time (in ms) & & & & & &\\
-      $L_\infty$ error (\wrt $l_0$) & & & & & &\\
+      Number of texture fetches & & & & & & & & & & & &\\
+      Time (in ms) & & & & & && & & & & &\\
+      $L_\infty$ error (\wrt $l_0$) & & & & & && & & & & &\\
       \bottomrule

### 2015-10-22 latex/article.tex
wip

@@
 octree cells at different resolutions. At a given MC vertex $\vx$, the
-algorithm becomes simple since we just scan  the ball cells and estimate
-the area (or other moments) from the mipmap values associated to this
-cell. Note that cells in the $B_R$ decomposition may not be aligned
-wuth mipmap cells. However, we can use GPU mipmap functionalities
-which interpolates mipmap values if we probe at non-discrete
-positions. For a given radius $R$, the expected number of cells on
-$B_r$ is in $O(\log{R})$.
+algorithm becomes simple since we just scan the ball cells and
+estimate the area (or other moments) from the mipmap values associated
+to this cell. Note that cells in the $B_R$ decomposition may not be
+aligned wuth mipmap cells. However, we can use GPU mipmap
+functionalities which interpolates mipmap values if we probe at
+non-discrete positions. For a given radius $R$, the expected number of
+cells on $B_r$ is in $O(\log{R})$. Implementation details on the
+hierarchical octree representation can be found in the supplementary
+material (see Section \ref{sec:discussion}).
 
@@
 
+\begin{figure}
+  \begin{center}
+    \subfigure[]{\framebox{octa $l_4$}}
+   \subfigure[]{\framebox{octa $l_3$}}
+   \subfigure[]{\framebox{octa $l_2$}}
+   \subfigure[]{\framebox{octa $l_1$}}
+   \subfigure[]{\framebox{octa $l_0$}}
+  \end{center}
+  \caption{fig multiresolution, courbure moyenne par ex}
+  \label{fig:refine}
+\end{figure}
+\todo[inline]{blabla experiments}
+
 \subsection{Fully adaptive evaluation}
@@
 \end{figure}
+
+\begin{figure}
+  \begin{center}
+    \subfigure[]{\framebox{K}}
+   \subfigure[]{\framebox{H}}
+   \subfigure[]{\framebox{DIR1}}
+   \subfigure[]{\framebox{DIR2}}
+   \subfigure[]{\framebox{normales}}\\
+    \subfigure[]{\framebox{K}}
+   \subfigure[]{\framebox{H}}
+   \subfigure[]{\framebox{DIR1}}
+   \subfigure[]{\framebox{DIR2}}
+   \subfigure[]{\framebox{normales}}
+
+  \end{center}
+  \caption{fig illustration complete (adaptative, ...) plusieurs
+    objets.. + dynamique.}
+  \label{fig:full}
+\end{figure}
+
+\todo[inline]{blabla experiments}
+
+For dynamic datasets, we consider a time varying impicit
+surface. Since it would have been to expensive to update the a mipmap texture
+of densities at each time step, we simply evaluate the implicit
+expression at each vertex of a cell to decide if such cell is included
+or not into $B_R(\vx)\cap X$.
+\todo[inline]{blabla experiments}
 

### 2015-10-22 latex/article.tex
CCL

@@
 
+In this article, we have propose a full data parallel framework on GPU
+hardware which combines an adaptive isosurface construction from
+digital data with a curvature tensor estimation at each vertex. Using
+this approach, we can explore in realtime different curvature
+measurements (mean, Gaussian, principal directions) with different
+ball radii on potentially large dynamic dataset. Our proposal relies
+on both a linear octree representation with Morton codes and an
+efficient integral computation on GPU.  The source code and additional
+material (video\ldots) are available on the project website
+(\url{https://github.com/dcoeurjo/ICVT}).
+
 %% \appendix

### 2015-10-22 latex/article.tex
typo

--- 2015-10-22 latex/article.tex
@@
           \put(46,31){$\vx$}
-          \put(55,45){$B_R(\vx)$}
+          \put(55,45){$\Ball{R}{\vx}$}
           \put(1,10){$\dS$}
@@
           \put(44.5,25){$h \cdot \vz$}
-          \put(55,45){$B_R(\vx)$}
+          \put(55,45){$\Ball{R}{\vx}$}
           \put(42,28.5){$\times$}
@@
 
-To implement the integration on $B_R(\vx)\cap\Shape$\todo{Check ball
-  radii w.r.t. notations in sect2}
+To implement the integration on $\Ball{R}{\vx} \cap \Shape$
 (Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
@@
 belonging to the cube of center $(x,y,z)$ and edge length $2^l$. As a
-consequence, we can approximate the volume of $B_R(x)\cap\Shape$ by
+consequence, we can approximate the volume of $\Ball{R}{\vx}\cap\Shape$ by
 considering mipmap values at a given resolution $l$
@@
 cells lying inside $\Shape$ (with density 1) not entirely covered by
-$B_R(\vx)$.
+$\Ball{R}{\vx}$.
 \begin{figure}
@@
 Using the hierachical nature of the mipmap texture, we could also
-consider hierarchical decompositions of either $B_R(\vx)$
-(Fig.~\ref{fig:approx2}-$a$) or $B_R(\vx)\cap\Shape$
+consider hierarchical decompositions of either $\Ball{R}{\vx}$
+(Fig.~\ref{fig:approx2}-$a$) or $\Ball{R}{\vx}\cap\Shape$
 (Fig.~\ref{fig:approx2}-$b$). The idea would be to decompose the
@@
   \caption{Adaptive approximation of the integration using a
-    hierarchical decomposition of the ball $B_R(\vx)$ $(a)$, or a decomposition of $B_R(\vx)\cap\Shape$.}
+    hierarchical decomposition of the ball $\Ball{R}{\vx}$ $(a)$, or a decomposition of $\Ball{R}{\vx}\cap\Shape$.}
   \label{fig:approx2}
@@
 the domain such that a cell is subdivided if it does not belong to
-$B_R(\vx)\cap\Shape$. However, on GPU hardware, this approach is
+$\Ball{R}{\vx}\cap\Shape$. However, on GPU hardware, this approach is
 highly inefficient since the hardware optimizes the parallelism only
@@
 non-discrete positions. For a given radius $R$, the expected number of
-cells on $B_r$ is in $O(\log{R})$. Implementation details on the
+cells on $B_R$ is in $O(\log{R})$. Implementation details on the
 hierarchical octree representation can be found in the supplementary
@@
 expression at each vertex of a cell to decide if such cell is included
-or not into $B_R(\vx)\cap X$.
+or not into $\Ball{R}{\vx}\cap \Shape$.
 \todo[inline]{blabla experiments}

### 2015-10-22 latex/article.tex
URL
typo

--- 2015-10-22 latex/article.tex
@@
 exploring 3D structures in Material Sciences \todo{REF}. Furthermore,
-since most curvature estimators require a parameter fixing the scale
+most curvature estimators require a parameter fixing the scale
 to which the computation is performed. For short, such parameter
@@
 
-\noindent\textbf{Contributions}\quad In this work, we propose a
-framework to perform interactive visualization of complex 3D digital
-structures combined with a dynamic curvature tensor estimation. More
-precisely, we define a fully data parallel process on GPU hardware \todo{Definir GPU au cas ou ?} to
-both efficiently extract adaptive isosurface and compute per vertex
-curvature tensor using Integral Invariants estimators. Hence, this
-system allows us to visualize curvature tensor in real-time on large
-dynamic objects. Our approach combines a GPU implementation of
-pointerless octrees to represent the data, an adaptive
-viewpoint-dependent mesh extraction, and a GPU implementation of
-integral invariant curvature estimations.
+\noindent\textbf{Contributions}\quad In this work, we propose a framework to
+perform interactive visualization of complex 3D digital structures combined with
+a dynamic curvature tensor estimation. More precisely, we define a fully data
+parallel process on GPU (Graphics Processor Unit) hardware to both efficiently
+extract adaptive isosurface and compute per vertex curvature tensor using
+Integral Invariants estimators. Hence, this system allows us to visualize
+curvature tensor in real-time on large dynamic objects. Our approach combines a
+GPU implementation of pointerless octrees to represent the data, an adaptive
+viewpoint-dependent mesh extraction, and a GPU implementation of integral
+invariant curvature estimators.
 

### 2015-10-22 latex/article.tex

@@
 
+In this article, we have propose a full data parallel framework on GPU
+hardware which combines an adaptive isosurface construction from
+digital data with a curvature tensor estimation at each vertex. Using
+this approach, we can explore in realtime different curvature
+measurements (mean, Gaussian, principal directions) with different
+ball radii on potentially large dynamic dataset. Our proposal relies
+on both a linear octree representation with Morton codes and an
+efficient integral computation on GPU.  The source code and additional
+material (video\ldots) are available on the project website
+(\url{https://github.com/dcoeurjo/ICTV}).
+
 %% \appendix

### 2015-10-22 latex/article.tex
reverting destructive commit >_<

--- 2015-10-22 latex/article.tex
@@
           \put(46,31){$\vx$}
-          \put(55,45){$\Ball{R}{\vx}$}
+          \put(55,45){$B_R(\vx)$}
           \put(1,10){$\dS$}
@@
           \put(44.5,25){$h \cdot \vz$}
-          \put(55,45){$\Ball{R}{\vx}$}
+          \put(55,45){$B_R(\vx)$}
           \put(42,28.5){$\times$}
@@
   \begin{center}
-    \subfigure{}{\includegraphics[width=0.9\textwidth]{figs/morton}}
+    \subfigure{}{\includegraphics[width=\textwidth]{figs/morton}}
     %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
@@
   \begin{center}
-    \begin{overpic}[width=3.5cm]{figs/criterion}
+    \begin{overpic}[width=4cm]{figs/criterion}
       \put(33,40){$\alpha$}
@@
     \end{overpic}~~~~~
-    \includegraphics[width=3.5cm]{viewlod2_small}~~~~~
-    \includegraphics[width=3cm]{subdivision}
+    \includegraphics[width=4cm]{viewlod2_small}~~~~~
+    \includegraphics[width=3.5cm]{subdivision}
   \end{center}
@@
 
-To implement the integration on $\Ball{R}{\vx} \cap \Shape$
+To implement the integration on $B_R(\vx)\cap\Shape$\todo{Check ball
+  radii w.r.t. notations in sect2}
 (Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
@@
 belonging to the cube of center $(x,y,z)$ and edge length $2^l$. As a
-consequence, we can approximate the volume of $\Ball{R}{\vx}\cap\Shape$ by
+consequence, we can approximate the volume of $B_R(x)\cap\Shape$ by
 considering mipmap values at a given resolution $l$
@@
 cells lying inside $\Shape$ (with density 1) not entirely covered by
-$\Ball{R}{\vx}$.
+$B_R(\vx)$.
 \begin{figure}
@@
 Using the hierachical nature of the mipmap texture, we could also
-consider hierarchical decompositions of either $\Ball{R}{\vx}$
-(Fig.~\ref{fig:approx2}-$a$) or $\Ball{R}{\vx}\cap\Shape$
+consider hierarchical decompositions of either $B_R(\vx)$
+(Fig.~\ref{fig:approx2}-$a$) or $B_R(\vx)\cap\Shape$
 (Fig.~\ref{fig:approx2}-$b$). The idea would be to decompose the
@@
   \begin{center}
-    \subfigure[]{\includegraphics[width=4cm]{figs/approx-bh}}
-    \subfigure[]{\includegraphics[width=4cm]{figs/approx-ada}}
+    \subfigure[]{\includegraphics[width=5cm]{figs/approx-bh}}
+    \subfigure[]{\includegraphics[width=5cm]{figs/approx-ada}}
   \end{center}
   \caption{Adaptive approximation of the integration using a
-    hierarchical decomposition of the ball $\Ball{R}{\vx}$ $(a)$, or a decomposition of $\Ball{R}{\vx}\cap\Shape$.}
+    hierarchical decomposition of the ball $B_R(\vx)$ $(a)$, or a decomposition of $B_R(\vx)\cap\Shape$.}
   \label{fig:approx2}
@@
 the domain such that a cell is subdivided if it does not belong to
-$\Ball{R}{\vx}\cap\Shape$. However, on GPU hardware, this approach is
+$B_R(\vx)\cap\Shape$. However, on GPU hardware, this approach is
 highly inefficient since the hardware optimizes the parallelism only
@@
 octree cells at different resolutions. At a given MC vertex $\vx$, the
-algorithm becomes simple since we just scan the ball cells and
-estimate the area (or other moments) from the mipmap values associated
-to this cell. Note that cells in the $B_R$ decomposition may not be
-aligned wuth mipmap cells. However, we can use GPU mipmap
-functionalities which interpolates mipmap values if we probe at
-non-discrete positions. For a given radius $R$, the expected number of
-cells on $B_R$ is in $O(\log{R})$. Implementation details on the
-hierarchical octree representation can be found in the supplementary
-material (see Section \ref{sec:discussion}).
+algorithm becomes simple since we just scan  the ball cells and estimate
+the area (or other moments) from the mipmap values associated to this
+cell. Note that cells in the $B_R$ decomposition may not be aligned
+wuth mipmap cells. However, we can use GPU mipmap functionalities
+which interpolates mipmap values if we probe at non-discrete
+positions. For a given radius $R$, the expected number of cells on
+$B_r$ is in $O(\log{R})$.
 
@@
 
-We first evaluate the curvature estimation on a full-resolution
-geometry obtained by disabling the LoD criterion at the mesh
-generation step.
-
 \begin{table}
   \begin{center}
-    \begin{tabular}{@{}lrrrrrrrrrrrr@{}}
+    \begin{tabular}{@{}lrrrrrr@{}}
       \toprule
-      & \multicolumn{6}{c}{$R=$}   & \multicolumn{6}{c}{$R=$}\\
-      \cmidrule(r){2-12}
-    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$& ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
+    Quantites  & H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
       \midrule
-      Number of texture fetches & & & & & & & & & & & &\\
-      Time (in ms) & & & & & && & & & & &\\
-      $L_\infty$ error (\wrt $l_0$) & & & & & && & & & & &\\
+      Number of texture fetches & & & & & & \\
+      Time (in ms) & & & & & & \\
+      $L_\infty$ error (\wrt $l_0$) & & & & & & \\
       \bottomrule
@@
 \end{table}
-
-\begin{figure}
-  \begin{center}
-    \subfigure[]{\framebox{octa $l_4$}}
-   \subfigure[]{\framebox{octa $l_3$}}
-   \subfigure[]{\framebox{octa $l_2$}}
-   \subfigure[]{\framebox{octa $l_1$}}
-   \subfigure[]{\framebox{octa $l_0$}}
-  \end{center}
-  \caption{fig multiresolution, courbure moyenne par ex}
-  \label{fig:refine}
-\end{figure}
-\todo[inline]{blabla experiments}
 
@@
 
-\begin{figure}
-  \begin{center}
-    \subfigure[]{\framebox{K}}
-   \subfigure[]{\framebox{H}}
-   \subfigure[]{\framebox{DIR1}}
-   \subfigure[]{\framebox{DIR2}}
-   \subfigure[]{\framebox{normales}}\\
-    \subfigure[]{\framebox{K}}
-   \subfigure[]{\framebox{H}}
-   \subfigure[]{\framebox{DIR1}}
-   \subfigure[]{\framebox{DIR2}}
-   \subfigure[]{\framebox{normales}}
-
-  \end{center}
-  \caption{fig illustration complete (adaptative, ...) plusieurs
-    objets.. + dynamique.}
-  \label{fig:full}
-\end{figure}
-
-\todo[inline]{blabla experiments}
-
-For dynamic datasets, we consider a time varying impicit
-surface. Since it would have been to expensive to update the a mipmap texture
-of densities at each time step, we simply evaluate the implicit
-expression at each vertex of a cell to decide if such cell is included
-or not into $\Ball{R}{\vx}\cap \Shape$.
-\todo[inline]{blabla experiments}
-
 \section{Conclusion and Discussion}
@@
 material (video\ldots) are available on the project website
-(\url{https://github.com/dcoeurjo/ICVT}).
+(\url{https://github.com/dcoeurjo/ICTV}).
 

### 2015-10-22 latex/article.tex
typo

--- 2015-10-22 latex/article.tex
@@
 
-\author{H\'el\`ene Perrier\inst{1}\and J\'eré\'emy Levallois\inst{1,2}\and David
+\author{H\'el\`ene Perrier\inst{1}\and J\'er\'emy Levallois\inst{1,2}\and David
 Coeurjolly\inst{1}\and Jean-Philippe Farrugia\inst{1}\and Jean-Claude

### 2015-10-22 latex/article.tex
fig. 1 edit
minor edit section 2 of the article

@@
           \put(42,28){$\times$}
-          \put(46,31){$\vx$}
+          \put(46,32){$\vx$}
           \put(55,45){$\Ball{R}{\vx}$}
           \put(1,10){$\dS$}
-          \put(20,10){$\Shape$}
+          \put(15,5){$\Shape$}
       \end{overpic}}~~~~~~
       \subfigure[]{\begin{overpic}[width=5cm]{figs/notation_2}
-          \put(44.5,25){$h \cdot \vz$}
+          \put(62,0.5){$h \cdot \vz \in \Shape \cap \Ball{R}{\vx}$}
           \put(55,45){$\Ball{R}{\vx}$}
@@
           %\put(88,39){$\Proj(p)$}
-          \put(3,11){$\partial \Shape$}
-          \put(15,7){$\partial \Body{\DigShape}{h}$}
+          \put(1.5,10){$\partial \Shape$}
+          \put(15,7){$\partial \Body{\DSh}{h}$}
       \end{overpic}}
@@
 
-In \cite{DGCI2013}, we have defined the 2D digital curvature estimator
+In \cite{DGCI2013}, authors have defined the 2D digital curvature estimator
 $\CurvH{R}$ and the 3D digital mean curvature estimator $\MeanCurvH{R}$ based on
@@
 %
-We have proved that estimating the 2D curvature and 3D mean curvature on digital
+They have proved that estimating the 2D curvature and 3D mean curvature on digital
 objets with volumetric integral information have the multigrid convergence
@@
 with at least $C^3$-boundary and bounded curvature, where $k$ is a constant
-related to the maximal curvature of the shape, we have:
+related to the maximal curvature of the shape, they have:
 %
@@
 
-In \cite{CVIU2014}, we have also defined the 3D digital principal curvature
+In \cite{CVIU2014}, authors have also defined the 3D digital principal curvature
 estimators $\PrincCurvH{1}{R}$ and $\PrincCurvH{2}{R}$ on $Z\subset\Z^3$ based
@@
 $\DMom{002}{h}$, $\DMom{110}{h}$, $\DMom{011}{h}$ and $\DMom{101}{h}$, see
-Equation~20 of \cite{CVIU2014} for more details). We have also proved the
+Equation~20 of \cite{CVIU2014} for more details). They have also proved the
 convergence of these estimators when setting the ball radius $h$ in $R =
@@
 shape, on convex shapes with at least $C^3$-boundary and bounded curvature
-\cite{CVIU2014}. More formally, we get:
+\cite{CVIU2014}. More formally, they get:
 %
@@
 
-We have shown that the radius of the ball depends on the geometry of
-the underlying shape. In \cite{DGCI2014}, we proposed a parameter-free
-estimation of the radius of the ball by analyzing the shape \wrt the
-local shape geometry using maximal digital straight segments of the
-digital boundary. In \cite{SMI2015}, we analyze in scale-space (\ie
-for a range of radii) curvature estimation of our algorithm for a
-given digital shape. This allows us to detect features of the shape
-thanks to the behavior on singularities.
+It has been shown that the radius of the ball depends on the geometry of the
+underlying shape. In \cite{DGCI2014}, authors proposed a parameter-free
+estimation of the radius of the ball by analyzing the shape \wrt the local shape
+geometry using maximal digital straight segments of the digital boundary. In
+\cite{SMI2015}, authors analyzed in scale-space (for a range of radii) these
+estimators for a given digital shape. This allows them to detect features of the
+shape thanks to the behavior of the estimators on singularities.
 
-As a consequence, for all these integral invariant based approaches,
-we need to consider different ball radius which could be time
-consuming when implemented on CPU. We propose here a fully parallel
-implementation on GPU allowing us to change the radius and thus update
-the estimated quantities in real-time.
+As a consequence, for all these integral invariant based approaches, we need to
+consider different ball radius which could be time consuming when implemented on
+CPU. We propose here a fully parallel implementation on GPU allowing us to
+change the radius and thus update the estimated quantities in real-time.
 

### 2015-10-22 src/cpp/vizo/DataLoader.cpp
Added expe results for the heriarchical vs regular Started to measure the stacked bar for timings with an adaptive geometry => CAREFUL, vizo is no longer exporting at full res !

@@ -4,10 +4,10 @@
 
 #include <cstring>
 
-//const GLenum MIN_FILT = GL_LINEAR_MIPMAP_LINEAR;
-//const GLenum MAG_FILT = GL_LINEAR;
-const GLenum MIN_FILT = GL_NEAREST_MIPMAP_NEAREST;
-const GLenum MAG_FILT = GL_NEAREST;
+const GLenum MIN_FILT = GL_LINEAR_MIPMAP_LINEAR;
+const GLenum MAG_FILT = GL_LINEAR;
+//const GLenum MIN_FILT = GL_NEAREST_MIPMAP_NEAREST;
+//const GLenum MAG_FILT = GL_NEAREST;
 
 bool mymipmap = true;
 

### 2015-10-22 src/cpp/vizo/Parameters.cpp

@@ -58,7 +58,7 @@ Parameters::Parameters()
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 	
-    g_scale = 5;
+    g_scale = 15;
     g_tessel = 1.0;
     g_isosurface = 0;
 	

### 2015-10-22 src/cpp/vizo/main.cpp

@@ -231,6 +231,8 @@ private:
 	
 	int min_lvl;
 	
+	int nb_probe;
+	
 public:
 	Vizo(int _argc, char** _argv) : gk::App()
 	{
@@ -300,8 +302,9 @@ public:
 		unmovedCells = 0;
 		frame = 0;
 		fps = 0;
+		nb_probe = 0;
 		
-		plot = false;
+		plot = true;
 		transition_cells_displayed = true;
 		
 		std::string file(argv[1]);
@@ -316,7 +319,8 @@ public:
 		plotfd2 = fopen(buf,"w");
 		if (plotfd2 == NULL)
 				perror("fopen");
-		fprintf(plotfd2, "#Lod\t Cull\t Extraction\t Curvature\n");
+		fprintf(plotfd2, "# Frame Lvl \t\t TotalCells \t\t RegCells \t\t TrCells \t\t Tgl \t\t LodTime (ms) \t\t CullTime (ms) \t\t RegTglTime (ms) \t\t TrTglTime (ms)\t\t ShadingTime (ms)\t\t ShdLessTime (ms)\t\t TotalTime (ms) \t\t Cpu Time (ns)\n");
+		
 		
 		// OpenGL context flags
 		glEnable (GL_DEPTH_TEST);
@@ -332,7 +336,7 @@ public:
 		else 
 			load_viewPoint();
 		
-		min_lvl = 4.0;//(int)floor(log2(Parameters::getInstance()->g_curvradius));
+		min_lvl = (int)ceil(log2(Parameters::getInstance()->g_curvradius));
 		Parameters::getInstance()->g_lvl = min_lvl;
 		
 		last_radius = Parameters::getInstance()->g_curvradius;
@@ -378,6 +382,8 @@ public:
 			}
 			else if (Parameters::getInstance()->g_auto_refine && fps > 30 && Parameters::getInstance()->g_lvl > 0)
 			{
+				/*if (Parameters::getInstance()->g_lvl == 0)
+					exit(0);*/
 				Parameters::getInstance()->g_lvl -= 1;
 				Parameters::getInstance()->g_compute_min_max = true;
 			}
@@ -393,14 +399,14 @@ public:
 		//return;
 		if (Parameters::getInstance()->g_export)
 		{
-			was_culled = Parameters::getInstance()->g_culling;
-			was_regular_grid = Parameters::getInstance()->g_regular;
+			//was_culled = Parameters::getInstance()->g_culling;
+			//was_regular_grid = Parameters::getInstance()->g_regular;
[…]

### 2015-10-22 src/cpp/vizo/main.cpp
removed annoying printf

@@ -695,7 +695,7 @@ public:
 				free(data_dirmax);
 				free(data_dirmin);
 				
-				printf("(NB %d) Min %lf Max %lf\n", nb, min, max);
+				//printf("(NB %d) Min %lf Max %lf\n", nb, min, max);
 				
 				Parameters::getInstance()->g_curvmin = min-0.01;
 				Parameters::getInstance()->g_curvmax = max+0.01;

### 2015-10-22 latex/article.tex
minor edit

@@
 \title{Interactive Curvature Tensor Visualization on Digital
-Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}}
+Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow}
+ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex}
+ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}}
 
@@
 a curvature tensor (mean/Gaussian curvature, principal curvatures
-directions\ldots) estimation at each point of the digital
+directions, \ldots) estimation at each point of the digital
 surface. Curvature maps on a given isosurface are key information when
@@
 isosurface on volumetric data has been widely investigated since the
-seminal Marching-Cubes approach by Lorensen and
-Cline~\cite{lorensen1987marching}. This approach being data parallel,
+seminal Marching Cubes approach by \textsc{Lorensen} and
+\textsc{Cline}~\cite{lorensen1987marching}. This approach being data parallel,
 GPU implementation of this method is very efficient
@@
 Graphics~\cite{shu1995adaptive,schaefer2004dual,lengyel2010voxel,DBLP:journals/cgf/LewinerMPPL10,DBLP:journals/cvgip/LobelloDD14}.
-The method developed by Lengyel \textit{et al.}
+The method developed by \textsc{Lengyel} \textit{et al.}
 \cite{lengyel2010voxel} is the best suited to our needs.  However, it
 was only developed on CPU to visualize in real-time static or near
-static data, combining octree with new Marching-Cubes configurations
+static data, combining octree with new Marching Cubes configurations
 to generate adaptive meshes. In this paper we propose a GPU pipeline
@@
 %
-The covariance matrix needs to compute digital moments of order $0$
-($\DMom{000}{h}$), of order $1$ ($\DMom{100}{h}$, $\DMom{010}{h}$ and
-$\DMom{001}{h}$) and of order $2$ ($\DMom{200}{h}$, $\DMom{020}{h}$,
-$\DMom{002}{h}$, $\DMom{110}{h}$, $\DMom{011}{h}$ and $\DMom{101}{h}$, see
-Equation~20 of \cite{CVIU2014} for more details). They have also proved the
-convergence of these estimators when setting the ball radius $h$ in $R =
-kh^\frac{1}{3}$, where $k$ is a constant related to the maximal curvature of the
-shape, on convex shapes with at least $C^3$-boundary and bounded curvature
-\cite{CVIU2014}. More formally, they get:
+The covariance matrix needs to compute digital moments of order $0$, order $1$
+and order $2$ (see Equation~20 of \cite{CVIU2014} for more details).
+% ($\DMom{000}{h}$), of order $1$ ($\DMom{100}{h}$, $\DMom{010}{h}$ and
+% $\DMom{001}{h}$) and of order $2$ ($\DMom{200}{h}$, $\DMom{020}{h}$,
+% $\DMom{002}{h}$, $\DMom{110}{h}$, $\DMom{011}{h}$ and $\DMom{101}{h}$, see
+% Equation~20 of \cite{CVIU2014} for more details).
+They have also proved the convergence of these estimators when setting the ball
+radius $h$ in $R = kh^\frac{1}{3}$, where $k$ is a constant related to the
+maximal curvature of the shape, on convex shapes with at least $C^3$-boundary
+and bounded curvature \cite{CVIU2014}. More formally, they get:
 %
@@
 corresponds to the normal direction $\NormalDirH{R}$ at $\vx$. Convergence
-results can be found in \cite{ChapterIICurvature}.\todo[inline]{Changer
+results can be found in \cite{ChapterIICurvature}.\todo{Changer
 ChapterIICurvature dans le bibtex...}
@@
 to handle large datasets and to locally adapt the level of details
-with respect to the geometry or camera position. We first present the
+\wrt the geometry or camera position. We first present the
 octree representation and then the isosurface extraction from
@@
   quadtree cells whose depth is view point dependent
-  \emph{(middle)}. Finally, adaptive Marching-Cubes is used to
+  \emph{(middle)}. Finally, adaptive Marching Cubes is used to
   generate the triangulation \emph{(right)}.}
@@
 
-Representing a hierachical structure on GPU is usually challenging
-since the GPU memory is limited and non consistent \todo{fix coherent/aligned/coalesced?}
-memory access (\emph{e.g.} tree traversal using pointer dereferencing)
-may lead to huge payload from cache misses.  Efficient spatial tree
-encoding can be achieved using pointerless structures. We use
-linear quadtrees or octrees to represent classical quadtree/octreee
-trees, see for instance Gargantini
-\cite{gargantini1982effective}. This structure consists in indexing
-each cell by a \emph{Morton code}: the code of children cells are
-defined by the code of the parent suffixed by two bits (in dimension
-2, three bits in dimension 3) (see Figure
-\ref{fig_quadtree_partitionning}-\emph{left}). A cell's code encodes
- its position with respect to its parent cell and its
-complete path to the tree root. Hence, whatever their depth, all cell
-codes are simply stored in a linear vector on memory. Furthermore,
-cell operations such as subdivision, merging, neighbors access can be
-efficiently implemented using bitwise operations on the Morton code.
-In the following, we use the GPU implementation proposed by Dupuy
-\textit{et al.}  \cite{dupuy2014quadtrees}. By using their approach, Morton
-codes and bitwise operations are optimized to match with GPU hardware
-requirements.
+Representing a hierachical structure on GPU is usually challenging since the GPU
+memory is limited and non consistent \todo{fix coherent/aligned/coalesced?}
+memory access (\emph{e.g.} tree traversal using pointer dereferencing) may lead
+to huge payload from cache misses.  Efficient spatial tree encoding can be
+achieved using pointerless structures. We use linear quadtrees or octrees to
+represent classical quadtree/octree trees, see for instance
+\textsc{Gargantini}~\cite{gargantini1982effective}. This structure consists in
+indexing each cell by a \emph{Morton code}: the code of children cells are
+defined by the code of the parent suffixed by two bits (in dimension 2, three
+bits in dimension 3) (see Figure \ref{fig_quadtree_partitionning}-\emph{left}).
+A cell's code encodes its position with respect to its parent cell and its
+complete path to the tree root. Hence, whatever their depth, all cell codes are
+simply stored in a linear vector on memory. Furthermore, cell operations such as
+subdivision, merging, neighbors access can be efficiently implemented using
+bitwise operations on the Morton code. In the following, we use the GPU
+implementation proposed by \textsc{Dupuy} \textit{et al.}~\cite{dupuy2014quadtrees}. By
+using their approach, Morton codes and bitwise operations are optimized to match
+with GPU hardware requirements.
 
@@
 Using this spatial datastructure, triangulated mesh can be constructed
-from a Marching-Cubes approach \cite{lorensen1987marching} (MC for short): the
+from a Marching Cubes approach \cite{lorensen1987marching} (MC for short): the
 triangulation is generated from local triangle patches computed on
@@
 hardwares. However, since adjacent cells may not have the same depth
-on the octree, original Lorensen and Cline's rules need to be
+on the octree, original \textsc{Lorensen} and \textsc{Cline}'s rules need to be
 updated (see Figure~\ref{fig_quadtree_partitionning}-\emph{right}). Many authors have addressed this problem both for primal and
@@
 In the following, we use the extension of MC configurations to handle
-adaptive structures proposed by Lengyel \emph{et al.}
-\cite{lengyel2010voxel}. First this approach constrains the octree
+adaptive structures proposed by \textsc{Lengyel} \emph{et al.}~\cite{lengyel2010voxel}. First this approach constrains the octree
 structure in order to make sure that the depth difference between any
-two adjacent cells is at most one. Then, Lengyel \emph{et al.} propose
+two adjacent cells is at most one. Then, \textsc{Lengyel} \emph{et al.} propose
 specific MC configurations for such transition cells,  leading to a
@@
 to this cell. Note that cells in the $B_R$ decomposition may not be
-aligned wuth mipmap cells. However, we can use GPU mipmap
+aligned with mipmap cells. However, we can use GPU mipmap
 functionalities which interpolates mipmap values if we probe at
@@
 efficient integral computation on GPU.  The source code and additional
-material (video\ldots) are available on the project website
+material (video, \ldots) are available on the project website
 (\url{https://github.com/dcoeurjo/ICTV}).

### 2015-10-22 latex/article.tex
minor edit

@@
 bits in dimension 3) (see Figure \ref{fig_quadtree_partitionning}-\emph{left}).
-A cell's code encodes its position with respect to its parent cell and its
+A cell's code encodes its position \wrt its parent cell and its
 complete path to the tree root. Hence, whatever their depth, all cell codes are
@@
 
-Using this spatial datastructure, triangulated mesh can be constructed
+Using this spatial data structure, triangulated mesh can be constructed
 from a Marching Cubes approach \cite{lorensen1987marching} (MC for short): the
@@
 In the following, we use the extension of MC configurations to handle
-adaptive structures proposed by \textsc{Lengyel} \emph{et al.}~\cite{lengyel2010voxel}. First this approach constrains the octree
+adaptive structures proposed by \textsc{Lengyel} \emph{et al.}~\cite{lengyel2010voxel}. First, this approach constrains the octree
 structure in order to make sure that the depth difference between any
@@
 each triangle patch can be constructed in parallel (done by
-in the \emph{geometry shader} in the GPU graphic pipeline).
+the \emph{geometry shader} in the GPU graphic pipeline).
 

### 2015-10-22 latex/article.tex
minor edit

@@
 
-As illustrated in Figure
-\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
-dependent criterion to decide if a cell needs to be refined: the
-closer we are to the camera, the finer the cells are. In addition to
-the distance criterion, we define an angular criterion to prevent refining cells outside the camera frustrum.
-Using a criterion based on the distance between a cell and the camera is well suited to GPU since it can be evaluated independently on all cells.
-Hence, we can efficiently determine if a cell must be subdivided or not.
-Figure \ref{fig_lod_octree}
-illustrates the level of details (LoD for short) criterion we
-use. More precisely, in dimension 2, if $\alpha$ denotes the viewing
-angle, an object at distance $d$ from the camera with diameter greater than
- $2\cdot d\cdot\tan(\alpha)$
- is projected into more than one pixel
-(see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance
-criterion is based on the ratio (\emph{visibility ratio} in the
-following)between the cell diameter $l(c)$ (power of 2 depending on
-the depth), and
-$2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell center and the camera. For a given cell $c$,
-split and merge decision are based on this visibility ratio:
+As illustrated in Figure~\ref{fig_quadtree_partitionning}-\emph{middle}, we
+propose a viewpoint dependent criterion to decide if a cell needs to be refined:
+the closer we are to the camera, the finer the cells are. In addition to the
+distance criterion, we define an angular criterion to prevent refining cells
+outside the camera frustrum. Using a criterion based on the distance between a
+cell and the camera is well suited to GPU since it can be evaluated
+independently on all cells. Hence, we can efficiently determine if a cell must
+be subdivided or not. Figure~\ref{fig_lod_octree} illustrates the level of
+details (LoD for short) criterion we use. More precisely, in dimension 2, if
+$\alpha$ denotes the viewing angle, an object at distance $d$ from the camera
+with diameter greater than $2\cdot d\cdot\tan(\alpha)$ is projected into more
+than one pixel (see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the
+distance criterion is based on the ratio (\emph{visibility ratio} in the
+following) between the cell diameter $l(c)$ (power of 2 depending on the depth),
+and $2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell
+center and the camera. For a given cell $c$, split and merge decision are based
+on this visibility ratio:
+%
 \begin{itemize}
-\item $c$ is split if its children cells have a visibility ratio
-  greater than  constant $k$\,;
-\item $c$ and its sibling cells are merged if their parent cell $c'$
-  have av visibility ratio lower than $k$\;
+  \item $c$ is split if its children
+cells have a visibility ratio greater than  constant $k$\,;
+  \item $c$ and its sibling cells are merged if their parent cell $c'$ have a visibility ratio lower than $k$\;
   \item otherwise, the cell $c$ stays for the next frame.
@@
   \end{center}
-  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and
-    angular criterion \emph{(middle)}. Based on LoD criterion
-    evaluation, the cell buffer is
-  updated between each frame \emph{(right)}.}
+  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and angular criterion \emph{(middle)}. Based on LoD criterion
+    evaluation, the cell buffer is updated between each frame \emph{(right)}.}
   \label{fig_lod_octree}
@@
 cells, geometrical culling is performed in order to skip the triangle
-patch construction which are not visible. Figure \ref{fig_pipeline}
+patch construction which are not visible. Figure~\ref{fig_pipeline}
 illustrates the overall fully data parallel pipeline.

### 2015-10-22 latex/article.tex
upgrade figure 5
Added part of the figures on the paper

--- 2015-10-22 latex/article.tex
@@
   \begin{center}
-    \begin{tabular}{@{}lrrrrrrrrrrrr@{}}
+%    \begin{tabular}{@{}lrrrrrrrrrrr@{}}
+%      \toprule
+%      & \multicolumn{5}{c}{$R=8$}   & \multicolumn{6}{c}{$R=16$}\\
+%      \cmidrule(r){2-12}
+%    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$& ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
+%      \midrule
+%      Number of texture fetches &
+%      1468 & 2 & 28 & 260 & 2104 & 
+%      5706 & 2 & 28 & 90 & 2120 & 1780\\
+%      Time (in ms) &
+%      208 & 15 & 26 & 93 & 642 &
+%      826 & 14 & 26 & 252 & 606 & 4801\\
+%      $L_\infty$ error (\wrt $l_0$) &
+%      0.051 & 0.306 & 0.085 & 0.047 & 0 & 
+%      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
+%      $L_2$ error (\wrt $l_0$) &
+%      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0 & 
+%      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
+%      \bottomrule
+%    \end{tabular}
+
+	\begin{tabular}{@{}lrrrrr@{}}
       \toprule
-      & \multicolumn{6}{c}{$R=$}   & \multicolumn{6}{c}{$R=$}\\
-      \cmidrule(r){2-12}
-    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$& ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
+      & \multicolumn{5}{c}{$R=8$}\\
+      \cmidrule(r){2-6}
+    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
       \midrule
-      Number of texture fetches & & & & & & & & & & & &\\
-      Time (in ms) & & & & & && & & & & &\\
-      $L_\infty$ error (\wrt $l_0$) & & & & & && & & & & &\\
+      Number of texture fetches &
+      1468 & 2 & 28 & 260 & 2104\\
+      Time (in ms) &
+      208 & 15 & 26 & 93 & 642\\
+      $L_\infty$ error (\wrt $l_0$) &
+      0.051 & 0.306 & 0.085 & 0.047 & 0\\
+      $L_2$ error (\wrt $l_0$) &
+      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
       \bottomrule
     \end{tabular}
+
+	\begin{tabular}{@{}lrrrrrr@{}}
+      \toprule
+      & \multicolumn{6}{c}{$R=16$}\\
+      \cmidrule(r){2-7}
+    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
+      \midrule
+      Number of texture fetches &
+      5706 & 2 & 28 & 90 & 2120 & 1780\\
+      Time (in ms) &
+      826 & 14 & 26 & 252 & 606 & 4801\\
+      $L_\infty$ error (\wrt $l_0$) &
+      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
+      $L_2$ error (\wrt $l_0$) &
+      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
+      \bottomrule
+    \end{tabular}
+
   \end{center}
@@
           ybar stacked,
-	  bar width=15pt,
+          ymode = log,
+	  	  bar width=20pt,
 	  	  nodes near coords,
+	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
           enlargelimits=0.15,
-          legend style={at={(0.5,-0.20)},
-            anchor=north,legend columns=-1},
           ylabel={\#Time (in ms)},
-          symbolic x coords={Octa-R1, Octa-R2, Snow-R1, Snow-R2,
+          symbolic x coords={Octa-R8, Octa-R16, Snow-R1, Snow-R2, 
 	      xxx-R1, xxx-R2},
           xtick=data,
+          point meta=rawy,	
           x tick label style={rotate=45,anchor=east},
         ]
-        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,2)
-          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,0)};
-        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,0)
-          (Snow-R1,0) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,0)};
-        \addplot+[ybar] plot coordinates {(Octa-R1,6) (Octa-R2,6)
+        \addplot+[ybar] plot coordinates {(Octa-R8,11.7) (Octa-R16,11.682000) 
+          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,1)};
+        \addplot+[ybar] plot coordinates {(Octa-R8,7.401000) (Octa-R16,7.666000) 
+          (Snow-R1,1) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,1)};
+        \addplot+[ybar] plot coordinates {(Octa-R8,27.226000) (Octa-R16,25.328000)
           (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
-        \addplot+[ybar] plot coordinates {(Octa-R1,4) (Octa-R2,2)
-          (Snow-R1,0) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
+        \addplot+[ybar] plot coordinates {(Octa-R8,184.161000) (Octa-R16,169.501000) 
+          (Snow-R1,1) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
+        \addplot+[ybar] plot coordinates {(Octa-R8, 1) (Octa-R16,1189.127000) 
+          (Snow-R1,1) (Snow-R2,1) (xxx-R1,1) (xxx-R2,1)};
         %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
       \end{axis}
-    \end{tikzpicture}
-     \begin{tikzpicture}[scale=0.7]
-      \begin{axis}[
-          ybar stacked,
-	  bar width=15pt,
-	  nodes near coords,
-          enlargelimits=0.15,
-          legend style={at={(0.5,-0.20)},
-            anchor=north,legend columns=-1},
-         % ylabel={\#Time (in ms)},
-          symbolic x coords={Octa-R1, Octa-R2, Snow-R1, Snow-R2,
-	    xxx-R1, xxx-R2},
-          xtick=data,
-          x tick label style={rotate=45,anchor=east},
-        ]
-        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,2)
-          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,0)};
-        \addplot+[ybar] plot coordinates {(Octa-R1,0) (Octa-R2,0)
-          (Snow-R1,0) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,0)};
-        \addplot+[ybar] plot coordinates {(Octa-R1,6) (Octa-R2,6)
-          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
-        \addplot+[ybar] plot coordinates {(Octa-R1,4) (Octa-R2,2)
-          (Snow-R1,0) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
-       % \legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
-      \end{axis}
+
      \end{tikzpicture}

### 2015-10-22 src/cpp/vizo/GpuOctree.cpp

@@ -80,7 +80,7 @@ void GPUOctree::loadBuffers()
 		
 		
 		size_t full_tree = 1;
-		long int side = std::pow(2, 8); //lvl 8 max
+		long int side = std::pow(2, 7); //lvl 8 max
 		full_tree += side*side*side; 
 		
 		size_t full_tree_cap = full_tree * sizeof(float) * sizekey; //1 vec2 for each

### 2015-10-22 src/cpp/vizo/Parameters.cpp

@@ -58,7 +58,7 @@ Parameters::Parameters()
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 	
-    g_scale = 15;
+    g_scale = 5;
     g_tessel = 1.0;
     g_isosurface = 0;
 	

### 2015-10-22 latex/article.tex

@@
 
-As illustrated in Figure
-\ref{fig_quadtree_partitionning}-\emph{middle}, we propose a viewpoint
-dependent criterion to decide if a cell needs to be refined: the
-closer we are to the camera, the finer the cells are. In addition to
-the distance criterion, we define an angular criterion to prevent refining cells outside the camera frustrum.
-Using a criterion based on the distance between a cell and the camera is well suited to GPU since it can be evaluated independently on all cells.
-Hence, we can efficiently determine if a cell must be subdivided or not.
-Figure \ref{fig_lod_octree}
-illustrates the level of details (LoD for short) criterion we
-use. More precisely, in dimension 2, if $\alpha$ denotes the viewing
-angle, an object at distance $d$ from the camera with diameter greater than
- $2\cdot d\cdot\tan(\alpha)$
- is projected into more than one pixel
-(see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the distance
-criterion is based on the ratio (\emph{visibility ratio} in the
-following)between the cell diameter $l(c)$ (power of 2 depending on
-the depth), and
-$2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell center and the camera. For a given cell $c$,
-split and merge decision are based on this visibility ratio:
+As illustrated in Figure~\ref{fig_quadtree_partitionning}-\emph{middle}, we
+propose a viewpoint dependent criterion to decide if a cell needs to be refined:
+the closer we are to the camera, the finer the cells are. In addition to the
+distance criterion, we define an angular criterion to prevent refining cells
+outside the camera frustrum. Using a criterion based on the distance between a
+cell and the camera is well suited to GPU since it can be evaluated
+independently on all cells. Hence, we can efficiently determine if a cell must
+be subdivided or not. Figure~\ref{fig_lod_octree} illustrates the level of
+details (LoD for short) criterion we use. More precisely, in dimension 2, if
+$\alpha$ denotes the viewing angle, an object at distance $d$ from the camera
+with diameter greater than $2\cdot d\cdot\tan(\alpha)$ is projected into more
+than one pixel (see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the
+distance criterion is based on the ratio (\emph{visibility ratio} in the
+following) between the cell diameter $l(c)$ (power of 2 depending on the depth),
+and $2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell
+center and the camera. For a given cell $c$, split and merge decision are based
+on this visibility ratio:
+%
 \begin{itemize}
-\item $c$ is split if its children cells have a visibility ratio
-  greater than  constant $k$\,;
-\item $c$ and its sibling cells are merged if their parent cell $c'$
-  have av visibility ratio lower than $k$\;
+  \item $c$ is split if its children
+cells have a visibility ratio greater than  constant $k$\,;
+  \item $c$ and its sibling cells are merged if their parent cell $c'$ has a visibility ratio lower than $k$\;
   \item otherwise, the cell $c$ stays for the next frame.

### 2015-10-22 latex/article.tex
upgrade figure 5

--- 2015-10-22 latex/article.tex
@@
 cells have a visibility ratio greater than  constant $k$\,;
-  \item $c$ and its sibling cells are merged if their parent cell $c'$ have a visibility ratio lower than $k$\;
+  \item $c$ and its sibling cells are merged if their parent cell $c'$ has a visibility ratio lower than $k$\;
   \item otherwise, the cell $c$ stays for the next frame.
@@
 $\Ball{R}{\vx}$.
+Furthermore, \emph{mipmap} textures give us a fast method to know if a voxel is inside $\Shape$, for all levels.
+Indeed, if the mipmap value is greater than $0.5$, the voxel associated is \emph{at least} half inside $\Shape$.
 \begin{figure}
@@
     counting $(b)$ or from densities (represented by different
-    grayvalues) in a mipmap approximation of $\Shape$.}
+    gray values) in a mipmap approximation of $\Shape$.}
   \label{fig:approx}

### 2015-10-22 src/cpp/vizo/GpuOctree.cpp
Screenshots++

@@ -80,7 +80,7 @@ void GPUOctree::loadBuffers()
 		
 		
 		size_t full_tree = 1;
-		long int side = std::pow(2, 7); //lvl 8 max
+		long int side = std::pow(2, 8); //lvl 8 max
 		full_tree += side*side*side; 
 		
 		size_t full_tree_cap = full_tree * sizeof(float) * sizekey; //1 vec2 for each

### 2015-10-22 src/cpp/vizo/Parameters.cpp

@@ -54,7 +54,7 @@ Parameters::Parameters()
     g_regular = false;
     g_radius_show = true;
 
-	g_curvradius = 8.0;
+	g_curvradius = 10.0;
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 	

### 2015-10-22 src/cpp/vizo/main.cpp

@@ -699,7 +699,7 @@ public:
 				
 				Parameters::getInstance()->g_curvmin = min-0.01;
 				Parameters::getInstance()->g_curvmax = max+0.01;
-				
+			
 				Parameters::getInstance()->g_compute_min_max = false;
 			}
 		}

### 2015-10-22 latex/article.tex
Redid timing figures with measurements from my laptop (since they are a whole lot better than those of my computers for some unknown reason)

@@
       1468 & 2 & 28 & 260 & 2104\\
-      Time (in ms) &
-      208 & 15 & 26 & 93 & 642\\
+      %Time (in ms) &
+      %208 & 15 & 26 & 93 & 642\\
       $L_\infty$ error (\wrt $l_0$) &
@@
       5706 & 2 & 28 & 90 & 2120 & 1780\\
-      Time (in ms) &
-      826 & 14 & 26 & 252 & 606 & 4801\\
+      %Time (in ms) &
+      %826 & 14 & 26 & 252 & 606 & 4801\\
       $L_\infty$ error (\wrt $l_0$) &
@@
     \begin{tikzpicture}[scale=0.7]
+%      \begin{axis}[
+%          ybar stacked,
+%          ymode = log,
+%	  	  bar width=20pt,
+%	  	  nodes near coords,
+%	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
+%          enlargelimits=0.15,
+%          ylabel={\#Time (in ms)},
+%          symbolic x coords={Octa-R8, Octa-R16, Snow-R1, Snow-R2, 
+%	      xxx-R1, xxx-R2},
+%          xtick=data,
+%          point meta=rawy,	
+%          x tick label style={rotate=45,anchor=east},
+%        ]
+%        \addplot+[ybar] plot coordinates {(Octa-R8,11.7) (Octa-R16,11.682000) 
+%          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,1)};
+%        \addplot+[ybar] plot coordinates {(Octa-R8,7.401000) (Octa-R16,7.666000) 
+%          (Snow-R1,1) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,1)};
+%        \addplot+[ybar] plot coordinates {(Octa-R8,27.226000) (Octa-R16,25.328000)
+%          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
+%        \addplot+[ybar] plot coordinates {(Octa-R8,184.161000) (Octa-R16,169.501000) 
+%          (Snow-R1,1) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
+%        \addplot+[ybar] plot coordinates {(Octa-R8, 1) (Octa-R16,1189.127000) 
+%          (Snow-R1,1) (Snow-R2,1) (xxx-R1,1) (xxx-R2,1)};
+%        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
+%      \end{axis}
+
       \begin{axis}[
@@
           ylabel={\#Time (in ms)},
-          symbolic x coords={Octa-R8, Octa-R16, Snow-R1, Snow-R2, 
+          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20, 
 	      xxx-R1, xxx-R2},
@@
         ]
-        \addplot+[ybar] plot coordinates {(Octa-R8,11.7) (Octa-R16,11.682000) 
-          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,1)};
-        \addplot+[ybar] plot coordinates {(Octa-R8,7.401000) (Octa-R16,7.666000) 
-          (Snow-R1,1) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,1)};
-        \addplot+[ybar] plot coordinates {(Octa-R8,27.226000) (Octa-R16,25.328000)
-          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
-        \addplot+[ybar] plot coordinates {(Octa-R8,184.161000) (Octa-R16,169.501000) 
-          (Snow-R1,1) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
-        \addplot+[ybar] plot coordinates {(Octa-R8, 1) (Octa-R16,1189.127000) 
-          (Snow-R1,1) (Snow-R2,1) (xxx-R1,1) (xxx-R2,1)};
+        %Geometry Generation
+        \addplot+[ybar] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000) 
+          (Snow-R10,9.831000) (Snow-R20,9.653000)  (xxx-R1,1) (xxx-R2,1)};
+        %l4
+        \addplot+[ybar] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000) 
+          (Snow-R10,6.085000) (Snow-R20,9.445000)  (xxx-R1,1) (xxx-R2,1)};
+        %l3
+        \addplot+[ybar] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
+          (Snow-R10,10.629000) (Snow-R20,11.542000) (xxx-R1,1) (xxx-R2,1)};
+        %l2
+        \addplot+[ybar] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000) 
+          (Snow-R10,13.777000) (Snow-R20,37.700000) (xxx-R1,1) (xxx-R2,1)};
+        %l1
+        \addplot+[ybar] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000) 
+          (Snow-R10,39.627000) (Snow-R20,217.954000) (xxx-R1,1) (xxx-R2,1)};
+        %l0
+        \addplot+[ybar] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000) 
+          (Snow-R10,236.194000) (Snow-R20,1655.680000) (xxx-R1,1) (xxx-R2,1)};
+        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
+      \end{axis}
+	  \end{tikzpicture}
+
+      \begin{tikzpicture}[scale=0.7]
+      \begin{axis}[
+          ybar stacked,
+          ymode = log,
+	  	  bar width=20pt,
+	  	  nodes near coords,
+	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
+          enlargelimits=0.15,
+          ylabel={\#Time (in ms)},
+          symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20, 
+	      xxx-R1, xxx-R2},
+          xtick=data,
+          point meta=rawy,	
+          x tick label style={rotate=45,anchor=east},
+        ]
+        %Geometry Generation
+        \addplot+[ybar] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000) 
+          (Snow-R10,9.383000) (Snow-R20,9.767000)  (xxx-R1,1) (xxx-R2,1)};
+        %Hierarchical measurement
+        \addplot+[ybar] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000) 
+          (Snow-R10,96.747000) (Snow-R20,364.547000)  (xxx-R1,1) (xxx-R2,1)};
         %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}

### 2015-10-22 src/cpp/vizo/Parameters.cpp

@@ -43,26 +43,26 @@ Parameters::Parameters()
     g_gui = true;
     g_radial_length = true;
     g_textured_data = false;
-	g_auto_refine = false;
+	g_auto_refine = true;
 	g_k1k2_normals = true;
 	g_curv_dir = 0;
 	g_curv_val = 1;
 	g_lvl = 2;
 
-    g_ground_truth = 3;
+    g_ground_truth = 2;
     
     g_regular = false;
-    g_radius_show = true;
+    g_radius_show = false;
 
 	g_curvradius = 10.0;
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 	
-    g_scale = 5;
+    g_scale = 10;
     g_tessel = 1.0;
     g_isosurface = 0;
 	
-	g_export = false;
+	g_export = true;
 	g_compute_min_max = true;
 
     g_sizetex = 0;

### 2015-10-22 src/cpp/vizo/main.cpp

@@ -336,7 +336,7 @@ public:
 		else 
 			load_viewPoint();
 		
-		min_lvl = (int)ceil(log2(Parameters::getInstance()->g_curvradius));
+		min_lvl = (int)ceil(log2(Parameters::getInstance()->g_curvradius)) + 2;
 		Parameters::getInstance()->g_lvl = min_lvl;
 		
 		last_radius = Parameters::getInstance()->g_curvradius;
@@ -380,10 +380,10 @@ public:
 				Parameters::getInstance()->g_lvl =  min_lvl;
 				Parameters::getInstance()->g_compute_min_max = true;
 			}
-			else if (Parameters::getInstance()->g_auto_refine && fps > 30 && Parameters::getInstance()->g_lvl > 0)
+			else if (Parameters::getInstance()->g_auto_refine)// && fps > 30 && Parameters::getInstance()->g_lvl > 0)
 			{
-				/*if (Parameters::getInstance()->g_lvl == 0)
-					exit(0);*/
+				if (Parameters::getInstance()->g_lvl == 0)
+					exit(0);
 				Parameters::getInstance()->g_lvl -= 1;
 				Parameters::getInstance()->g_compute_min_max = true;
 			}
@@ -602,11 +602,11 @@ public:
 							printf("NBPROBE = %lf\n", p);
 							nb_geom = p;
 						}
-						else
+						/*else
 						{
 							if (p != nb_geom)
 								printf("ERROR: %lf != ref %lf\n", p, nb_geom);
-						}
+						}*/
 						nb_probe = nb_geom;
 						fprintf(plotfd, "%lf\t", p);
 						fprintf(plotfd, "\n");

### 2015-10-23 src/cpp/vizo/Parameters.cpp
Tried to fix alpha on the morton figure Changed the pipeline figure to fit the curvature framework

@@ -43,7 +43,7 @@ Parameters::Parameters()
     g_gui = true;
     g_radial_length = true;
     g_textured_data = false;
-	g_auto_refine = true;
+	g_auto_refine = false;
 	g_k1k2_normals = true;
 	g_curv_dir = 0;
 	g_curv_val = 1;
@@ -62,7 +62,7 @@ Parameters::Parameters()
     g_tessel = 1.0;
     g_isosurface = 0;
 	
-	g_export = true;
+	g_export = false;
 	g_compute_min_max = true;
 
     g_sizetex = 0;

### 2015-10-23 latex/article.tex
Tried to fix alpha on the morton figure Changed the pipeline figure to fit the curvature framework
minor edit

@@
 the digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ with
-$\MCard(Y)$ the number of digital points of $Y$ and $Y \subset \Z^d$ the
-intersection between the digital shape $\DigShape$ and a ball of digital radius
-$R/h$ (we denote such quantity $\AreaC(Y,h)$ in dimension 2):
+$\MCard(Y)$ the number of digital points of the intersection between a ball
+$\Ball{R/h}{\vx/h}$ of digital radius $R/h$ and $\DigShape$ (we denote such
+quantity $\AreaC(Y,h)$ in dimension 2):
 %
@@
   \begin{center}
-    \subfigure{}{\includegraphics[width=0.9\textwidth]{figs/morton}}
+    \subfigure{}{\includegraphics[width=0.9\textwidth]{figs/morton2}}
     %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
@@
   \centering
-  \includegraphics[width=0.9\textwidth]{figs/pipeline}
+  \includegraphics[width=0.9\textwidth]{figs/pipeline2}
   \caption{ Summary our GPU pipeline. Data buffers are
@@
   \end{center}
-  \caption{fig multiresolution, courbure moyenne par ex}
+  \caption{Illustration of mean curvature computation on an OctaFlower using mipmap approximation of different levels : $l_4$, $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
+  %
+  For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
   \label{fig:refine}
@@
   \end{center}
-  \caption{fig illustration complete (adaptative, ...) plusieurs
-    objets.. + dynamique.}
+  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
+    objets.. + dynamique.
+    %
+    For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
   \label{fig:full}

### 2015-10-23 latex/article.tex
added expe for 512 object on my laptop

--- 2015-10-22 latex/article.tex
@@
           symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20, 
-	      xxx-R1, xxx-R2},
+	      Dragon-R8, Dragon-R20},
           xtick=data,
@@
         \addplot+[ybar] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000) 
-          (Snow-R10,9.831000) (Snow-R20,9.653000)  (xxx-R1,1) (xxx-R2,1)};
+          (Snow-R10,9.831000) (Snow-R20,9.653000)  (Dragon-R8,136.300000) (Dragon-R20,145.450000)};
         %l4
         \addplot+[ybar] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000) 
-          (Snow-R10,6.085000) (Snow-R20,9.445000)  (xxx-R1,1) (xxx-R2,1)};
+          (Snow-R10,6.085000) (Snow-R20,9.445000)  (Dragon-R8,3.389000) (Dragon-R20,20.228000)};
         %l3
         \addplot+[ybar] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
-          (Snow-R10,10.629000) (Snow-R20,11.542000) (xxx-R1,1) (xxx-R2,1)};
+          (Snow-R10,10.629000) (Snow-R20,11.542000) (Dragon-R8,20.397000) (Dragon-R20,26.710000)};
         %l2
         \addplot+[ybar] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000) 
-          (Snow-R10,13.777000) (Snow-R20,37.700000) (xxx-R1,1) (xxx-R2,1)};
+          (Snow-R10,13.777000) (Snow-R20,37.700000) (Dragon-R8,29.967000) (Dragon-R20,92.435000)};
         %l1
         \addplot+[ybar] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000) 
-          (Snow-R10,39.627000) (Snow-R20,217.954000) (xxx-R1,1) (xxx-R2,1)};
+          (Snow-R10,39.627000) (Snow-R20,217.954000) (Dragon-R8,59.840000) (Dragon-R20,506.549000)};
         %l0
         \addplot+[ybar] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000) 
-          (Snow-R10,236.194000) (Snow-R20,1655.680000) (xxx-R1,1) (xxx-R2,1)};
+          (Snow-R10,236.194000) (Snow-R20,1655.680000) (Dragon-R8,322.674000) (Dragon-R20,3763.422000)};
         %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
@@
         \addplot+[ybar] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000) 
-          (Snow-R10,9.383000) (Snow-R20,9.767000)  (xxx-R1,1) (xxx-R2,1)};
+          (Snow-R10,9.383000) (Snow-R20,9.767000)  (Dragon-R8,127.347000) (Dragon-R20,127.166000)};
         %Hierarchical measurement
         \addplot+[ybar] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000) 
-          (Snow-R10,96.747000) (Snow-R20,364.547000)  (xxx-R1,1) (xxx-R2,1)};
+          (Snow-R10,96.747000) (Snow-R20,364.547000)  (Dragon-R8,147.662000) (Dragon-R20,787.459000)};
         %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}

### 2015-10-23 src/cpp/vizo/Parameters.cpp

@@ -43,7 +43,7 @@ Parameters::Parameters()
     g_gui = true;
     g_radial_length = true;
     g_textured_data = false;
-	g_auto_refine = false;
+	g_auto_refine = true;
 	g_k1k2_normals = true;
 	g_curv_dir = 0;
 	g_curv_val = 1;
@@ -51,10 +51,10 @@ Parameters::Parameters()
 
     g_ground_truth = 2;
     
-    g_regular = false;
+    g_regular = true;
     g_radius_show = false;
 
-	g_curvradius = 10.0;
+	g_curvradius = 8.0;
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 	
@@ -62,7 +62,7 @@ Parameters::Parameters()
     g_tessel = 1.0;
     g_isosurface = 0;
 	
-	g_export = false;
+	g_export = true;
 	g_compute_min_max = true;
 
     g_sizetex = 0;

### 2015-10-23 src/cpp/vizo/main.cpp

@@ -283,9 +283,11 @@ public:
 		}
 		dl->loadFile(argv[1]);
 		dl->loadData32BGpu();
+		/*
 		dl->loadx2y2z2();
 		dl->loadxyyzxz();
 		dl->loadxyz();
+		*/
 		
 		lodManager.init();
 		extractor.init();

### 2015-10-23 latex/article.tex
figures in article

--- 2015-10-23 latex/article.tex
@@
       Number of texture fetches &
-      5706 & 2 & 28 & 90 & 2120 & 1780\\
+      5706 & 2 & 28 & 90 & 2120 & 17080\\
       %Time (in ms) &
@@
   \end{center}
-  \caption{object, size, radius, full res, num of vertices (timings
+  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error obtained on  object, size, radius, full res, num of vertices (timings
     only consider the curvature estimation step).\label{tab:full-res-stat}}
@@
 
-\begin{figure}
+\begin{figure}[!htbp]
   \begin{center}
-    \subfigure[]{\framebox{octa $l_4$}}
-   \subfigure[]{\framebox{octa $l_3$}}
-   \subfigure[]{\framebox{octa $l_2$}}
-   \subfigure[]{\framebox{octa $l_1$}}
-   \subfigure[]{\framebox{octa $l_0$}}
+   {\includegraphics[width=2.7cm]{figs/octa_r10_l3_a}}
+   {\includegraphics[width=2.7cm]{figs/octa_r10_l2_a}}
+   {\includegraphics[width=2.7cm]{figs/octa_r10_l1_a}}
+   {\includegraphics[width=2.7cm]{figs/octa_r10_l0_a}}
   \end{center}
-  \caption{Illustration of mean curvature computation on an OctaFlower using mipmap approximation of different levels : $l_4$, $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
+  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
   %
@@
 	  \end{tikzpicture}
-
+%
     \begin{tikzpicture}[scale=0.7]

### 2015-10-23 latex/article.tex
Colring and captionning figure for the resulting timings

--- 2015-10-23 latex/article.tex
@@
 \newcommand{\E}{\ensuremath{\mathcal{E}}}
+
+\definecolor{cgeometry}{RGB}{255, 120, 0}
+\definecolor{clquatre}{RGB}{198,219,239}
+\definecolor{cltrois}{RGB}{158,202,225}
+\definecolor{cldeux}{RGB}{107,174,214}
+\definecolor{clun}{RGB}{49,130,189}
+\definecolor{clzero}{RGB}{8,81,156}
 
@@
   \end{center}
-  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error obtained on  object, size, radius, full res, num of vertices (timings
-    only consider the curvature estimation step).\label{tab:full-res-stat}}
+  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error obtained on OctaFlower with a digital domain of $130^3$. We measured it using radii of 8 and 16.
+  The object was triangulated at full resolution with a regular grid and contains 282396 vertices. The timings
+    only consider the curvature estimation step.\label{tab:full-res-stat}}
 \end{table}
@@
 	  	  nodes near coords,
-	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
+	  	  every node near coord/.style={ font=\tiny, inner sep=0pt},
           enlargelimits=0.15,
@@
         %Geometry Generation
-        \addplot+[ybar] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000)
-          (Snow-R10,9.831000) (Snow-R20,9.653000)  (xxx-R1,1) (xxx-R2,1)};
+        \addplot+[ybar, color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,18.458000) 
+          (Snow-R10,9.831000) (Snow-R20,9.653000)  (Dragon-R8,136.300000) (Dragon-R20,145.450000)};
         %l4
-        \addplot+[ybar] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000)
-          (Snow-R10,6.085000) (Snow-R20,9.445000)  (xxx-R1,1) (xxx-R2,1)};
+        \addplot+[ybar, color=black, fill=clquatre] plot coordinates {(Octa-R8,1) (Octa-R16,2.509000) 
+          (Snow-R10,6.085000) (Snow-R20,9.445000)  (Dragon-R8,3.389000) (Dragon-R20,20.228000)};
         %l3
-        \addplot+[ybar] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
-          (Snow-R10,10.629000) (Snow-R20,11.542000) (xxx-R1,1) (xxx-R2,1)};
+        \addplot+[ybar, color=black, fill=cltrois] plot coordinates {(Octa-R8,2.527000) (Octa-R16,4.159000)
+          (Snow-R10,10.629000) (Snow-R20,11.542000) (Dragon-R8,20.397000) (Dragon-R20,26.710000)};
         %l2
-        \addplot+[ybar] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000)
-          (Snow-R10,13.777000) (Snow-R20,37.700000) (xxx-R1,1) (xxx-R2,1)};
+        \addplot+[ybar, color=black, fill=cldeux] plot coordinates {(Octa-R8,3.783000) (Octa-R16,9.006000) 
+          (Snow-R10,13.777000) (Snow-R20,37.700000) (Dragon-R8,29.967000) (Dragon-R20,92.435000)};
         %l1
-        \addplot+[ybar] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000)
-          (Snow-R10,39.627000) (Snow-R20,217.954000) (xxx-R1,1) (xxx-R2,1)};
+        \addplot+[ybar, color=black, fill=clun] plot coordinates {(Octa-R8, 11.004000) (Octa-R16,38.687000) 
+          (Snow-R10,39.627000) (Snow-R20,217.954000) (Dragon-R8,59.840000) (Dragon-R20,506.549000)};
         %l0
-        \addplot+[ybar] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000)
-          (Snow-R10,236.194000) (Snow-R20,1655.680000) (xxx-R1,1) (xxx-R2,1)};
+        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8, 37.273000) (Octa-R16,244.353000) 
+          (Snow-R10,236.194000) (Snow-R20,1655.680000) (Dragon-R8,322.674000) (Dragon-R20,3763.422000)};
         %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
@@
           enlargelimits=0.15,
-          ylabel={\#Time (in ms)},
+          %ylabel={\#Time (in ms)},
           symbolic x coords={Octa-R8, Octa-R16, Snow-R10, Snow-R20, 
-	      xxx-R1, xxx-R2},
+	      Dragon-R8, Dragon-R20},
           xtick=data,
@@
         %Geometry Generation
-        \addplot+[ybar] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000)
-          (Snow-R10,9.383000) (Snow-R20,9.767000)  (xxx-R1,1) (xxx-R2,1)};
+        \addplot+[ybar,color=black, fill=cgeometry] plot coordinates {(Octa-R8,17.283000) (Octa-R16,17.183000) 
+          (Snow-R10,9.383000) (Snow-R20,9.767000)  (Dragon-R8,127.347000) (Dragon-R20,127.166000)};
         %Hierarchical measurement
-        \addplot+[ybar] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000)
-          (Snow-R10,96.747000) (Snow-R20,364.547000)  (xxx-R1,1) (xxx-R2,1)};
+        \addplot+[ybar, color=black, fill=clzero] plot coordinates {(Octa-R8,18.095000) (Octa-R16,64.186000) 
+          (Snow-R10,96.747000) (Snow-R20,364.547000)  (Dragon-R8,147.662000) (Dragon-R20,787.459000)};
         %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
@@
      \end{center}
-  \caption{Adaptive timings H vs. rafined (tout : adaptatif, 2 rayons par formes, 4
-    formes + images).}
+  \caption{Timings obtained while visualising an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm. 		
+  With a regular grid, the curvature computation refines at every frame until it reaches the ground truth result.
+  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$)}
   \label{fig:timings}

### 2015-10-23 latex/article.tex
figures

--- 2015-10-23 latex/article.tex
@@
 corresponds to the normal direction $\NormalDirH{R}$ at $\vx$. Convergence
-results can be found in \cite{ChapterIICurvature}.\todo{Changer
-ChapterIICurvature dans le bibtex...}
+results can be found in \cite{CVIU2014}.%%% Changer avec le chapitre de Jaco à un moment
 
@@
 Representing a hierachical structure on GPU is usually challenging since the GPU
-memory is limited and non consistent \todo{fix coherent/aligned/coalesced?}
+memory is limited and non consistent %\todo{fix coherent/aligned/coalesced?}
 memory access (\emph{e.g.} tree traversal using pointer dereferencing) may lead
 to huge payload from cache misses.  Efficient spatial tree encoding can be
-achieved using pointerless structures. We use linear quadtrees or octrees to
-represent classical quadtree/octree trees, see for instance
-\textsc{Gargantini}~\cite{gargantini1982effective}. This structure consists in
-indexing each cell by a \emph{Morton code}: the code of children cells are
-defined by the code of the parent suffixed by two bits (in dimension 2, three
-bits in dimension 3) (see Figure \ref{fig_quadtree_partitionning}-\emph{left}).
-A cell's code encodes its position \wrt its parent cell and its
-complete path to the tree root. Hence, whatever their depth, all cell codes are
-simply stored in a linear vector on memory. Furthermore, cell operations such as
-subdivision, merging, neighbors access can be efficiently implemented using
-bitwise operations on the Morton code. In the following, we use the GPU
-implementation proposed by \textsc{Dupuy} \textit{et al.}~\cite{dupuy2014quadtrees}. By
-using their approach, Morton codes and bitwise operations are optimized to match
-with GPU hardware requirements.
+achieved using pointerless structures such as linear quadtrees or octrees, see
+for instance \textsc{Gargantini}~\cite{gargantini1982effective}. This structure
+consists in indexing each cell by a \emph{Morton code}: the code of children
+cells are defined by the code of the parent suffixed by two bits (in dimension
+2, three bits in dimension 3) (see Figure
+\ref{fig_quadtree_partitionning}-\emph{left}). A cell's code encodes its
+position \wrt its parent cell and its complete path to the tree root. Hence,
+whatever their depth, all cell codes are simply stored in a linear vector on
+memory. Furthermore, cell operations such as subdivision, merging, neighbors
+access can be efficiently implemented using bitwise operations on the Morton
+code. In the following, we use the GPU implementation proposed by \textsc{Dupuy}
+\textit{et al.}~\cite{dupuy2014quadtrees}. By using their approach, Morton codes
+and bitwise operations are optimized to match with GPU hardware requirements.
 
@@
 
-\todo[inline]{phrase sur approx si on met}
+%\todo[inline]{phrase sur approx si on met}
 
@@
 generation step.
+
+For all illustrations, we use directly normal vectors computed by algorithm
+discussed in Section~\ref{sec:curv-tens-estim}
 
@@
   \begin{center}
-    \subfigure[]{\framebox{K}}
-   \subfigure[]{\framebox{H}}
-   \subfigure[]{\framebox{DIR1}}
-   \subfigure[]{\framebox{DIR2}}
-   \subfigure[]{\framebox{normales}}\\
-    \subfigure[]{\framebox{K}}
-   \subfigure[]{\framebox{H}}
-   \subfigure[]{\framebox{DIR1}}
-   \subfigure[]{\framebox{DIR2}}
-   \subfigure[]{\framebox{normales}}
+   \includegraphics[width=5cm]{figs/snow_I08iso_233_r20_l0_m3}
 
+  \end{center}
+  \caption{Illustration of mean curvature computation of snow microstructures.}
+  \label{fig:full}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
+    {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
+    {\includegraphics[width=2.7cm]{figs/EG_dragon_k1}}
+    {\includegraphics[width=2.7cm]{figs/EG_dragon_k2}}\\
+    {\includegraphics[width=2.7cm]{figs/EG_dragon_normal_zoom}}
+    {\includegraphics[width=2.7cm]{figs/EG_dragon_dir_min_zoom}}
+    {\includegraphics[width=2.7cm]{figs/EG_dragon_dir_max_zoom}}\\
+    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
   \end{center}
@@
     %
-    For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
+    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
   \label{fig:full}

### 2015-10-23 latex/article.tex
minor edit

@@
 To implement the integration on $\Ball{R}{\vx} \cap \Shape$
-(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
-digital points inside such domain (Fig.~\ref{fig:approx}-$b$) and then
-to estimate the geometrical moment as the sum of the geometrical
-moments of each elementary cubes lying in the intersection. On GPU,
-\emph{mipmap} textures are used to obtain a multi-resolution information: if the
-input binary object is stored in a 3D texture, GPU hardware can
-construct a multi-resolution pyramid such that 8 neighboring voxel
-intensities at level $l$ are averaged to define the voxel value at
-level $l+1$. If the level 0 corresponds to the binary input object, at
-a given level $l$, a voxel $(x,y,z)$ contains the fraction of $\DSh$
-belonging to the cube of center $(x,y,z)$ and edge length $2^l$. As a
-consequence, we can approximate the volume of $\Ball{R}{\vx}\cap\Shape$ by
-considering mipmap values at a given resolution $l$
-(Fig.~\ref{fig:approx}-$c$). In this case, errors only occurs for
-cells lying inside $\Shape$ (with density 1) not entirely covered by
-$\Ball{R}{\vx}$.
-Furthermore, \emph{mipmap} textures give us a fast method to know if a voxel is inside $\Shape$, for all levels.
-Indeed, if the mipmap value is greater than $0.5$, the voxel associated is \emph{at least} half inside $\Shape$.
+(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all digital
+points inside such domain (Fig.~\ref{fig:approx}-$b$) and then to estimate the
+geometrical moment as the sum of the geometrical moments of each elementary
+cubes lying in the intersection. On GPU, \emph{mipmap} textures are used to
+obtain a multi-resolution information: if the input binary object is stored in a
+3D texture, GPU hardware can construct a multi-resolution pyramid such that 8
+neighboring voxel intensities at level $l$ are averaged to define the voxel
+value at level $l+1$. If the level 0 corresponds to the binary input object, at
+a given level $l$, a voxel $(x,y,z)$ contains the fraction of $\DSh$ belonging
+to the cube of center $(x,y,z)$ and edge length $2^l$. As a consequence, we can
+approximate the volume of $\Ball{R}{\vx}\cap\Shape$ by considering mipmap values
+at a given resolution $l$ (Fig.~\ref{fig:approx}-$c$). In this case, errors only
+occurs for cells lying inside $\Shape$ (with density 1) not entirely covered by
+$\Ball{R}{\vx}$. Furthermore, the \emph{mipmap} texture can be used to design,
+using a single texture probe, a fast inclusion test of a given cell $c$ at level
+$l$ into the shapes: we say that $c$ is in $\Shape$ if its density (retrieved
+from the texture probe at level l) is greater than $1/2$. The idea here is to
+mimic a lend of adaptive Gauss digitization process.
+
 \begin{figure}

### 2015-10-23 latex/article.tex
small text about the full res experiment

--- 2015-10-23 latex/article.tex
@@
 geometry obtained by disabling the LoD criterion at the mesh
-generation step.
+generation step. We compare the approximation made to accelerate 
+visualisation with the ground truth result obtained at level $l_0$.
+We also compare it with the hierarchical algorithm.
+The results are presented table \ref{tab:full-res-stat}, and illustrated
+figure \ref{fig:refine}.
+
+We can first see that the number of texel fetch required to compute
+the curvature reduces drastically when computing the approximations.
+This is mandatory if we want to increase the framerate.
+However, we can also note that the error increases quite slowly. 
+The errors obtained comparing $l_1$, or for bigger radii $l_2$ approximations
+with the $l_0$ level are small. The errors measured comparing higher levels
+are of course much bigger and those level are thus never used in practice.
+They are presented here to illustrate how the refining process converges to 
+the $l_0$ level.
+Thanks to this low error, higher approximation levels are visually 
+very similar to the $l_0$ level. We can therefore use them for exploring our 
+datasets in real time, changing the radii on the fly and visualising dynamic datasets.
+
+Bare in mind that those results were measured on a full resolution triangulation.
+Since we compute the curvature of each vertices of the final mesh, a highly triangulated object will
+be much slower to process.
+We therefore use in practice an adaptive triangulation of the object, refining the mesh
+when it is closer from the camera and thus reducing the number of vertices to compute.
 
@@
   \begin{center}
-%    \begin{tabular}{@{}lrrrrrrrrrrr@{}}
-%      \toprule
-%      & \multicolumn{5}{c}{$R=8$}   & \multicolumn{6}{c}{$R=16$}\\
-%      \cmidrule(r){2-12}
-%    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$& ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
-%      \midrule
-%      Number of texture fetches &
-%      1468 & 2 & 28 & 260 & 2104 &
-%      5706 & 2 & 28 & 90 & 2120 & 1780\\
-%      Time (in ms) &
-%      208 & 15 & 26 & 93 & 642 &
-%      826 & 14 & 26 & 252 & 606 & 4801\\
-%      $L_\infty$ error (\wrt $l_0$) &
-%      0.051 & 0.306 & 0.085 & 0.047 & 0 &
-%      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
-%      $L_2$ error (\wrt $l_0$) &
-%      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0 &
-%      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
-%      \bottomrule
-%    \end{tabular}
 

### 2015-10-23 latex/article.tex
figs

--- 2015-10-23 latex/article.tex
@@
   \begin{center}
-    \subfigure[]{\includegraphics[width=4cm]{figs/approx1}}
-    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-1}}
-    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-2}}
+    {\includegraphics[width=4cm]{figs/approx1}}
+    {\includegraphics[width=4cm]{figs/approx-reg-1}}
+    {\includegraphics[width=4cm]{figs/approx-reg-2}}
   \end{center}
-  \caption{Integral computation with an area estimation from pixel
-    counting $(b)$ or from densities (represented by different
-    gray values) in a mipmap approximation of $\Shape$.}
+  \caption{Integral computation with an area estimation (\emph{left}) from pixel
+    counting (\emph{middle}) or from densities (represented by different
+    gray values) in a mipmap approximation of $\Shape$ (\emph{right}).}
   \label{fig:approx}
@@
   \begin{center}
-    \subfigure[]{\includegraphics[width=4cm]{figs/approx-bh}}
-    \subfigure[]{\includegraphics[width=4cm]{figs/approx-ada}}
+    {\includegraphics[width=4cm]{figs/approx-bh}}
+    {\includegraphics[width=4cm]{figs/approx-ada}}
   \end{center}
   \caption{Adaptive approximation of the integration using a
-    hierarchical decomposition of the ball $\Ball{R}{\vx}$ $(a)$, or a decomposition of $\Ball{R}{\vx}\cap\Shape$.}
+    hierarchical decomposition of the ball $\Ball{R}{\vx}$ (\emph{left}), or a decomposition of $\Ball{R}{\vx}\cap\Shape$ (\emph{right}).}
   \label{fig:approx2}
@@
     {\includegraphics[width=2.7cm]{figs/EG_dragon_k2}}\\
-    {\includegraphics[width=2.7cm]{figs/EG_dragon_normal_zoom}}
-    {\includegraphics[width=2.7cm]{figs/EG_dragon_dir_min_zoom}}
-    {\includegraphics[width=2.7cm]{figs/EG_dragon_dir_max_zoom}}\\
+    {\includegraphics[height=2.0cm]{figs/EG_dragon_normal_zoom}}
+    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_min_zoom}}
+    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}
+    {\includegraphics[height=2.0cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
     {\includegraphics[width=2.2cm]{figs/function_mean_0}}

### 2015-10-23 latex/article.tex

--- 2015-10-23 latex/article.tex
@@
 when it is closer from the camera and thus reducing the number of vertices to compute.
+
+For all illustrations, we use directly normal vectors computed by algorithm
+discussed in Section~\ref{sec:curv-tens-estim}
 

### 2015-10-23 latex/article.tex
figs

@@
   \begin{center}
-   \includegraphics[width=5cm]{figs/snow_I08iso_233_r20_l0_m3}
-
-  \end{center}
-  \caption{Illustration of mean curvature computation of snow microstructures.}
-  \label{fig:full}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
     {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
@@
     objets.. + dynamique.
+    Illustration of mean curvature computation of snow microstructures.
     %

### 2015-10-23 latex/article.tex
figs

@@
 The results are presented table \ref{tab:full-res-stat}, and illustrated
-figure \ref{fig:refine}.
+figure \ref{fig:refine}. For all illustrations, we use directly normal vectors computed by algorithm
+discussed in Section~\ref{sec:curv-tens-estim}
 
@@
 
-For all illustrations, we use directly normal vectors computed by algorithm
-discussed in Section~\ref{sec:curv-tens-estim}
-
 \begin{table}
   \begin{center}
-
 	\begin{tabular}{@{}lrrrrr@{}}
@@
   \end{center}
-  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
-  %
-  For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
+  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).}
   \label{fig:refine}
@@
     {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
-    {\includegraphics[width=2.7cm]{figs/EG_dragon_k1}}
-    {\includegraphics[width=2.7cm]{figs/EG_dragon_k2}}\\
-    {\includegraphics[height=2.0cm]{figs/EG_dragon_normal_zoom}}
     {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_min_zoom}}
-    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}
-    {\includegraphics[height=2.0cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
+    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}\\
+    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
+    {\includegraphics[height=4.0cm]{figs/xyzrgb_dragon-510_R8_mean}}
+    {\includegraphics[height=3.5cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
     {\includegraphics[width=2.2cm]{figs/function_mean_0}}

### 2015-10-23 latex/article.tex
pre pull

--- 2015-10-23 latex/article.tex
@@
 \end{figure}
-\todo[inline]{blabla experiments}
 
@@
 
+In this experiments, we measure the timings obtained when running our framework on a
+GeForce GTX 850M. Here, the triangulation is dynamically refining according to its distance to the camera.
+At each frame, both the curvature and the triangulation are recomputed.
+If the visualisation stays unchanged, we compute the curvature at a level $l-1$ until the level $l_0$ is reached.
+We measured those timings using the regular and the hierarchical algorithm. The results are presented
+figure \ref{fig:timings}.
+
+\subsection{Visualisation}
+
+For dynamic datasets, we consider a time varying implicit
+surface. Since it would have been to expensive to update the a mipmap texture
+of densities at each time step, we simply evaluate the implicit
+expression at each vertex of a cell to decide if such cell is included
+or not into $\Ball{R}{\vx}\cap \Shape$.
+\todo[inline]{blabla experiments}
+
 \begin{figure}
@@
 \end{figure}
-
-\todo[inline]{blabla experiments}
-
-For dynamic datasets, we consider a time varying impicit
-surface. Since it would have been to expensive to update the a mipmap texture
-of densities at each time step, we simply evaluate the implicit
-expression at each vertex of a cell to decide if such cell is included
-or not into $\Ball{R}{\vx}\cap \Shape$.
-\todo[inline]{blabla experiments}
 

### 2015-10-23 latex/article.tex
figs

--- 2015-10-23 latex/article.tex
@@
 
-We first evaluate the curvature estimation on a full-resolution
-geometry obtained by disabling the LoD criterion at the mesh
-generation step. We compare the approximation made to accelerate
+\begin{figure}
+  \begin{center}
+    {\includegraphics[width=2.7cm]{figs/Octa_mean}}
+    {\includegraphics[width=2.7cm]{figs/Octa_gaussian}}
+    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
+    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
+    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
+    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
+    {\includegraphics[height=2.5cm]{figs/Octa_dir_min_zoom}}
+    {\includegraphics[height=2.5cm]{figs/Octa_dir_max_zoom}}\\
+    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
+  \end{center}
+  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
+    objets.. + dynamique.
+    Illustration of mean curvature computation of snow microstructures.
+    %
+    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
+  \label{fig:full}
+\end{figure}
+
+We first evaluate the curvature estimation on a full-resolution geometry
+obtained by disabling the LoD criterion at the mesh generation step.
+Figure~\ref{fig:full}-top and middle show results of curvature tensor estimation
+(mean, Gaussian curvature, first and second principal curvatures, first and
+second principal directions) on an OctaFlower. Figure~\ref{fig:full}-bottom
+shows the mean curvature estimation in real-time on a dynamic object.
+
+We compare the approximation made to accelerate
 visualisation with the ground truth result obtained at level $l_0$.
@@
   \begin{center}
-    {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
-    {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
-    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_min_zoom}}
-    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}\\
-    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
     {\includegraphics[height=4.0cm]{figs/xyzrgb_dragon-510_R8_mean}}
-    {\includegraphics[height=3.5cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
-    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
-    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
-    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
-    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
-    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
+    {\includegraphics[height=3.5cm]{figs/snow_I08iso_233_r20_l0_m3}}
   \end{center}
@@
     \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
-  \label{fig:full}
+  \label{fig:adaptive}
 \end{figure}

### 2015-10-23 latex/article.tex
modif expe full resolution

@@
     {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
-    {\includegraphics[height=2.5cm]{figs/Octa_dir_min_zoom}}
-    {\includegraphics[height=2.5cm]{figs/Octa_dir_max_zoom}}\\
+    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
+    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
     % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
@@
   \end{center}
-  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
-    objets.. + dynamique.
-    Illustration of mean curvature computation of snow microstructures.
-    %
-    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
+  \caption{\emph{Third row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
+  \emph{Second row:} First and second principal directions estimation (and zoom) on an OctaFlower.
+  \emph{Third row:} Mean curvature computed in real-time on a dynamic object.}
   \label{fig:full}
@@
 second principal directions) on an OctaFlower. Figure~\ref{fig:full}-bottom
-shows the mean curvature estimation in real-time on a dynamic object.
+shows the mean curvature estimation in real-time on a dynamic object. For all
+illustrations, we use directly normal vectors computed by algorithm discussed in
+Section~\ref{sec:curv-tens-estim}.
 
-We compare the approximation made to accelerate
-visualisation with the ground truth result obtained at level $l_0$.
-We also compare it with the hierarchical algorithm.
-The results are presented table \ref{tab:full-res-stat}, and illustrated
-figure \ref{fig:refine}. For all illustrations, we use directly normal vectors computed by algorithm
-discussed in Section~\ref{sec:curv-tens-estim}
+We compare the approximation made to accelerate visualisation with the ground
+truth result obtained at level $l_0$. We also compare it with the hierarchical
+algorithm. The results are presented Table~\ref{tab:full-res-stat}, and
+illustrated Figure~\ref{fig:refine}.
 

### 2015-10-23 latex/article.tex
Adaptive res text

--- 2015-10-23 latex/article.tex
@@
 The results are presented table \ref{tab:full-res-stat}, and illustrated
-figure \ref{fig:refine}. For all illustrations, we use directly normal vectors computed by algorithm
-discussed in Section~\ref{sec:curv-tens-estim}
+figure \ref{fig:refine}.
 
@@
 
+For all illustrations, we use directly normal vectors computed by algorithm
+discussed in Section~\ref{sec:curv-tens-estim}
+
 \begin{table}
   \begin{center}
+
 	\begin{tabular}{@{}lrrrrr@{}}
@@
   \end{center}
-  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).}
+  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
+  %
+  For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
   \label{fig:refine}
@@
           ymode = log,
+          ymax = 6000,
 	  	  bar width=20pt,
@@
           ybar stacked,
+          ymax = 6000,
           ymode = log,
@@
   \caption{Timings obtained while visualising an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm. 		
-  With a regular grid, the curvature computation refines at every frame until it reaches the ground truth result.
-  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$)}
+  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (drak blue).
+  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii (8, 10, 16, 20)}
   \label{fig:timings}
@@
 If the visualisation stays unchanged, we compute the curvature at a level $l-1$ until the level $l_0$ is reached.
-We measured those timings using the regular and the hierarchical algorithm. The results are presented
-figure \ref{fig:timings}.
+We measured those timings using the regular and the hierarchical algorithm. The results are presented in 
+logarithmic scale figure \ref{fig:timings}.
+
+We can first note that the required time for an object to compute ground truth curvature is usually
+as high as the time required to extract the geometry and compute all the above levels.
+Using approximations is thus mandatory, since for big objects such as the XYZ Dragon (Digital Domain $510^3$)
+with high radii, the computation is seconds faster, the $l_0$ visualisation takes more than 4 seconds to compute, whereas
+the approximated visualisation at $l_2$ takes only 300ms.
+We can thus get an approximated visualisation of our object as soon as we run the application, allowing for
+real time interactions with the object (changing the visualised value, the curvature radius, etc ...).
+Once an interesting portion if the object is reached, it only takes a few seconds to the application to display
+ground truth curvature estimation.
+
+It is also clear on those graphs that using a hierarchical decomposition reduces the curvature computation time.
+For the XYZ Dragon with a radius of 20, it needs almost 4 seconds to compute the $l_0$ level, whereas using the
+hierarchical algorithm, it only needs 700ms. However, due to the precomputation, this algorithm is biased and
+creates an error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered
 
@@
     {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
+    {\includegraphics[width=2.7cm]{figs/EG_dragon_k1}}
+    {\includegraphics[width=2.7cm]{figs/EG_dragon_k2}}\\
+    {\includegraphics[height=2.0cm]{figs/EG_dragon_normal_zoom}}
     {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_min_zoom}}
-    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}\\
-    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
-    {\includegraphics[height=4.0cm]{figs/xyzrgb_dragon-510_R8_mean}}
-    {\includegraphics[height=3.5cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
+    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}
+    {\includegraphics[height=2.0cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
     {\includegraphics[width=2.2cm]{figs/function_mean_0}}

### 2015-10-23 latex/article.tex
modif expe full resolution

--- 2015-10-23 latex/article.tex
@@
 \subsection{Per Vertex Real-time Computation on GPU}
+\label{sec:hierarchical}
 
@@
 obtained by disabling the LoD criterion at the mesh generation step.
-Figure~\ref{fig:full}-top and middle show results of curvature tensor estimation
-(mean, Gaussian curvature, first and second principal curvatures, first and
-second principal directions) on an OctaFlower. Figure~\ref{fig:full}-bottom
-shows the mean curvature estimation in real-time on a dynamic object. For all
-illustrations, we use directly normal vectors computed by algorithm discussed in
-Section~\ref{sec:curv-tens-estim}.
+Figure~\ref{fig:full}-top and middle shows results of curvature tensor
+estimation (mean, Gaussian, first and second principal curvatures, first and
+second principal directions) on an OctaFlower at level $l_0$ (ground truth).
+Figure~\ref{fig:full}-bottom shows mean curvature estimation in real-time on a
+dynamic object. For all illustrations, we use directly normal vectors computed
+by algorithm discussed in Section~\ref{sec:curv-tens-estim}.
 
-We compare the approximation made to accelerate visualisation with the ground
-truth result obtained at level $l_0$. We also compare it with the hierarchical
-algorithm. The results are presented Table~\ref{tab:full-res-stat}, and
-illustrated Figure~\ref{fig:refine}.
+Then, we compare the approximation made by computing curvature from level $l >
+l_0$ in order to accelerate visualisation with the ground truth result obtained
+at level $l_0$. We also compare them with the hierarchical algorithm discussed
+in Section~\ref{sec:hierarchical}. The results are presented in
+Table~\ref{tab:full-res-stat}, and illustrated in Figure~\ref{fig:refine}.
 

### 2015-10-23 latex/article.tex

--- 2015-10-23 latex/article.tex
@@
 
-We first evaluate the curvature estimation on a full-resolution
-geometry obtained by disabling the LoD criterion at the mesh
-generation step. We compare the approximation made to accelerate 
-visualisation with the ground truth result obtained at level $l_0$.
-We also compare it with the hierarchical algorithm.
-The results are presented table \ref{tab:full-res-stat}, and illustrated
-figure \ref{fig:refine}.
+\begin{figure}
+  \begin{center}
+    {\includegraphics[width=2.7cm]{figs/Octa_mean}}
+    {\includegraphics[width=2.7cm]{figs/Octa_gaussian}}
+    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
+    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
+    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
+    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
+    {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
+    {\includegraphics[height=2.0cm]{figs/Octa_dir_max_zoom}}\\
+    % {\includegraphics[height=4.0cm]{figs/EG_dragon_normal_zoom}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
+    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
+  \end{center}
+  \caption{\emph{Third row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
+  \emph{Second row:} First and second principal directions estimation (and zoom) on an OctaFlower.
+  \emph{Third row:} Mean curvature computed in real-time on a dynamic object.}
+  \label{fig:full}
+\end{figure}
+
+We first evaluate the curvature estimation on a full-resolution geometry
+obtained by disabling the LoD criterion at the mesh generation step.
+Figure~\ref{fig:full}-top and middle show results of curvature tensor estimation
+(mean, Gaussian curvature, first and second principal curvatures, first and
+second principal directions) on an OctaFlower. Figure~\ref{fig:full}-bottom
+shows the mean curvature estimation in real-time on a dynamic object. For all
+illustrations, we use directly normal vectors computed by algorithm discussed in
+Section~\ref{sec:curv-tens-estim}.
+
+We compare the approximation made to accelerate visualisation with the ground
+truth result obtained at level $l_0$. We also compare it with the hierarchical
+algorithm. The results are presented Table~\ref{tab:full-res-stat}, and
+illustrated Figure~\ref{fig:refine}.
 
@@
   \begin{center}
-    {\includegraphics[width=2.7cm]{figs/EG_dragon_mean}}
-    {\includegraphics[width=2.7cm]{figs/EG_dragon_gaussian}}
-    {\includegraphics[width=2.7cm]{figs/EG_dragon_k1}}
-    {\includegraphics[width=2.7cm]{figs/EG_dragon_k2}}\\
-    {\includegraphics[height=2.0cm]{figs/EG_dragon_normal_zoom}}
-    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_min_zoom}}
-    {\includegraphics[height=2.0cm]{figs/EG_dragon_dir_max_zoom}}
-    {\includegraphics[height=2.0cm]{figs/snow_I08iso_233_r20_l0_m3}}\\
-    {\includegraphics[width=2.2cm]{figs/function_mean_0}}
-    {\includegraphics[width=2.2cm]{figs/function_mean_1}}
-    {\includegraphics[width=2.2cm]{figs/function_mean_2}}
-    {\includegraphics[width=2.2cm]{figs/function_mean_3}}
-    {\includegraphics[width=2.2cm]{figs/function_mean_4}}
+    {\includegraphics[height=4.0cm]{figs/xyzrgb_dragon-510_R8_mean}}
+    {\includegraphics[height=3.5cm]{figs/snow_I08iso_233_r20_l0_m3}}
   \end{center}

### 2015-10-23 latex/article.tex
modif expe full resolution

--- 2015-10-23 latex/article.tex
@@
 $l$ into the shapes: we say that $c$ is in $\Shape$ if its density (retrieved
-from the texture probe at level l) is greater than $1/2$. The idea here is to
+from the texture probe at level $l$) is greater than $1/2$. The idea here is to
 mimic a lend of adaptive Gauss digitization process.
@@
 Then, we compare the approximation made by computing curvature from level $l >
-l_0$ in order to accelerate visualisation with the ground truth result obtained
+l_0$ in order to accelerate visualization with the ground truth result obtained
 at level $l_0$. We also compare them with the hierarchical algorithm discussed
@@
 very similar to the $l_0$ level. We can therefore use them for exploring our
-datasets in real time, changing the radii on the fly and visualising dynamic datasets.
+datasets in real time, changing the radii on the fly and visualizing dynamic datasets.
 
@@
      \end{center}
-  \caption{Timings obtained while visualising an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm.
+  \caption{Timings obtained while visualizing an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm.
   With a regular grid, the curvature computation refines at every frame until it reaches the ground truth result.

### 2015-10-23 latex/article.tex

--- 2015-10-23 latex/article.tex
@@
 They are presented here to illustrate how the refining process converges to
-the $l_0$ level.
-Thanks to this low error, higher approximation levels are visually 
+the $l_0$ level. Thanks to this low error, higher approximation levels are visually
 very similar to the $l_0$ level. We can therefore use them for exploring our
-datasets in real time, changing the radii on the fly and visualising dynamic datasets.
+datasets in real time, changing the radii on the fly and visualizing dynamic datasets.
 
@@
      \end{center}
-  \caption{Timings obtained while visualising an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm. 		
-  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (drak blue).
-  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii (8, 10, 16, 20)}
+  \caption{Timings obtained while visualizing an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm.
+  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (dark blue).
+  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii ($8$, $10$, $16$ and $20$)}
   \label{fig:timings}

### 2015-10-23 latex/article.tex
small phrase in full res

--- 2015-10-23 latex/article.tex
@@
 
-Bare in mind that those results were measured on a full resolution triangulation.
+When computing results using the hierachical algorithm, a higher error can be noted.
+This is due to the precomputation of the subdivision that no longer ensures to fetch data
+at the center of a mipmap cell. The interpolation done by the GPU reduces the bias but
+does not remove it.
+
+Bear also in mind that those results were measured on a full resolution triangulation.
 Since we compute the curvature of each vertices of the final mesh, a highly triangulated object will

### 2015-10-23 latex/article.tex
modif table timings

--- 2015-10-23 latex/article.tex
@@
     \begin{tikzpicture}[scale=0.7]
-%      \begin{axis}[
-%          ybar stacked,
-%          ymode = log,
-%	  	  bar width=20pt,
-%	  	  nodes near coords,
-%	  	  every node near coord/.style={ at={(0,0)}, font=\tiny, inner sep=0pt},
-%          enlargelimits=0.15,
-%          ylabel={\#Time (in ms)},
-%          symbolic x coords={Octa-R8, Octa-R16, Snow-R1, Snow-R2,
-%	      xxx-R1, xxx-R2},
-%          xtick=data,
-%          point meta=rawy,
-%          x tick label style={rotate=45,anchor=east},
-%        ]
-%        \addplot+[ybar] plot coordinates {(Octa-R8,11.7) (Octa-R16,11.682000)
-%          (Snow-R1,2) (Snow-R2,3)  (xxx-R1,2) (xxx-R2,1)};
-%        \addplot+[ybar] plot coordinates {(Octa-R8,7.401000) (Octa-R16,7.666000)
-%          (Snow-R1,1) (Snow-R2,3)  (xxx-R1,1) (xxx-R2,1)};
-%        \addplot+[ybar] plot coordinates {(Octa-R8,27.226000) (Octa-R16,25.328000)
-%          (Snow-R1,3) (Snow-R2,2) (xxx-R1,2) (xxx-R2,6)};
-%        \addplot+[ybar] plot coordinates {(Octa-R8,184.161000) (Octa-R16,169.501000)
-%          (Snow-R1,1) (Snow-R2,2) (xxx-R1,1) (xxx-R2,4)};
-%        \addplot+[ybar] plot coordinates {(Octa-R8, 1) (Octa-R16,1189.127000)
-%          (Snow-R1,1) (Snow-R2,1) (xxx-R1,1) (xxx-R2,1)};
-%        %\legend{\strut Geometry, \strut Curvature, \strut xx, \strut xx}
-%      \end{axis}
-
       \begin{axis}[
@@
       \end{axis}
-
      \end{tikzpicture}
      \end{center}
-  \caption{Timings obtained while visualizing an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm.
-  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (dark blue).
-  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii ($8$, $10$, $16$ and $20$)}
+  %
+  \caption{Timings in milliseconds obtained while visualizing an adaptive
+  triangulation on three objects -- OctaFlower (digital domain of $130^3$ ), Snow
+  Microstructures ($233^3$) and XYZ-Dragon ($510^3$) --  by computing the
+  curvature with a regular grid (\emph{left}) and with hierarchical
+  algorithm (\emph{right}), with two different radii for each object.
+  %
+  In \emph{orange color}: time required to extract the triangulation.
+  %
+  In \emph{blue color}: time required to compute the curvature tensor at
+  different levels: from $l_4$ (light blue) to $l_0$ (dark blue).
+  %
+  }
+  %
   \label{fig:timings}

### 2015-10-23 latex/article.tex
???

--- 2015-10-23 latex/article.tex
@@
 $l$ into the shapes: we say that $c$ is in $\Shape$ if its density (retrieved
-from the texture probe at level $l$) is greater than $1/2$. The idea here is to
+from the texture probe at level l) is greater than $1/2$. The idea here is to
 mimic a lend of adaptive Gauss digitization process.
@@
 Then, we compare the approximation made by computing curvature from level $l >
-l_0$ in order to accelerate visualization with the ground truth result obtained
+l_0$ in order to accelerate visualisation with the ground truth result obtained
 at level $l_0$. We also compare them with the hierarchical algorithm discussed
@@
 They are presented here to illustrate how the refining process converges to 
-the $l_0$ level. Thanks to this low error, higher approximation levels are visually
+the $l_0$ level.
+Thanks to this low error, higher approximation levels are visually 
 very similar to the $l_0$ level. We can therefore use them for exploring our 
-datasets in real time, changing the radii on the fly and visualizing dynamic datasets.
+datasets in real time, changing the radii on the fly and visualising dynamic datasets.
 
@@
      \end{center}
-  \caption{Timings obtained while visualizing an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm.
-  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (dark blue).
-  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii ($8$, $10$, $16$ and $20$)}
+  \caption{Timings obtained while visualising an adaptive triangulation of an object (left) computing the curvature with a regular grid and (right) computing it with the hierarchical algorithm. 		
+  Orange is the required time to extract the triangulation, and blue are the curvature computations from level $l_4$ (light blue) to level $l_0$ (drak blue).
+  We measured three datasets, OctaFlower (digital domain of $130^3$ ), snow micro structures($233^3$) and the XYZ Dragon ($510^3$), with different radii (8, 10, 16, 20)}
   \label{fig:timings}
@@
 
-\subsection{Visualisation}
-
-For dynamic datasets, we consider a time varying implicit
-surface. Since it would have been to expensive to update the a mipmap texture
-of densities at each time step, we simply evaluate the implicit
-expression at each vertex of a cell to decide if such cell is included
-or not into $\Ball{R}{\vx}\cap \Shape$.
-\todo[inline]{blabla experiments}
+%\subsection{Visualisation}
+%
+%For dynamic datasets, we consider a time varying implicit
+%surface. Since it would have been to expensive to update the a mipmap texture
+%of densities at each time step, we simply evaluate the implicit
+%expression at each vertex of a cell to decide if such cell is included
+%or not into $\Ball{R}{\vx}\cap \Shape$.
+%\todo[inline]{blabla experiments}
 

### 2015-10-23 latex/article.tex
Discussion

@@
 
+In a future work, this framework could be used for feature detection purposes
+such as presented in \cite{SMI2015}. The point classification is done by computing
+the curvature at different radii and comparing them. Using our framework,
+this may be done in a real-time manner.
+The computed curvature could also be used to control the refinement of the
+triangulation. We are for now only using the normal computation for shading
+purposes but we could imagine using it along with the vertices to do a
+Poisson reconstruction of the object.
+
 %% \appendix

### 2015-10-23 latex/article.tex
modif table timings

--- 2015-10-23 latex/article.tex
@@
   \end{center}
-  \caption{\emph{Third row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
+  \caption{\emph{First row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
   \emph{Second row:} First and second principal directions estimation (and zoom) on an OctaFlower.
@@
   %
-  \caption{Timings in milliseconds obtained while visualizing an adaptive
+  \caption{Timings in milliseconds (in logscale) obtained while visualizing an adaptive
   triangulation on three objects -- OctaFlower (digital domain of $130^3$ ), Snow
@@
   %
+  Timings are given using a NVIDIA GeForce GTX 850M GPU.
   }
@@
 
-In this experiments, we measure the timings obtained when running our framework on a
-GeForce GTX 850M. Here, the triangulation is dynamically refining according to its distance to the camera.
-At each frame, both the curvature and the triangulation are recomputed.
-If the visualisation stays unchanged, we compute the curvature at a level $l-1$ until the level $l_0$ is reached.
-We measured those timings using the regular and the hierarchical algorithm. The results are presented in 
-logarithmic scale figure \ref{fig:timings}.
+When dealing with large datasets, we can not expect real-time curvature tensor
+estimation due to the huge amount of data to process. By computing an
+dynamically refined approximate curvature tensor estimation joined with an
+adaptive triangulation (as discussed in Section~\ref{sec:hierarchical}), we
+manage to maintain a real time framerate by giving control over the amount of
+data to process at each frame. In Figure~\ref{fig:timings}, we compare timings
+(in logarithmic scale) when the triangulation is dynamically refining according
+to its distance to the camera. We measured those timings using the regular and
+the hierarchical algorithm.
 
-We can first note that the required time for an object to compute ground truth curvature is usually
-as high as the time required to extract the geometry and compute all the above levels.
-Using approximations is thus mandatory, since for big objects such as the XYZ Dragon (Digital Domain $510^3$)
-with high radii, the computation is seconds faster, the $l_0$ visualisation takes more than 4 seconds to compute, whereas
-the approximated visualisation at $l_2$ takes only 300ms.
-We can thus get an approximated visualisation of our object as soon as we run the application, allowing for
-real time interactions with the object (changing the visualised value, the curvature radius, etc ...).
-Once an interesting portion if the object is reached, it only takes a few seconds to the application to display
+We can first note that the required time for an object to compute ground truth
+curvature is usually as high as the time required to extract the geometry and
+compute all the above levels. Using approximations is thus mandatory, since for
+big objects such as the XYZ Dragon (Digital Domain $510^3$) with high radii, the
+computation is seconds faster, the $l_0$ visualisation takes more than 4 seconds
+to compute, whereas the approximated visualisation at $l_2$ takes only 300ms. We
+can thus get an approximated visualisation of our object as soon as we run the
+application, allowing for real time interactions with the object (changing the
+visualised value, the curvature radius, etc ...). Once an interesting portion if
+the object is reached, it only takes a few seconds to the application to display
 ground truth curvature estimation.
 
-It is also clear on those graphs that using a hierarchical decomposition reduces the curvature computation time.
-For the XYZ Dragon with a radius of 20, it needs almost 4 seconds to compute the $l_0$ level, whereas using the
-hierarchical algorithm, it only needs 700ms. However, due to the precomputation, this algorithm is biased and
-creates an error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered
+It is also clear on those graphs that using a hierarchical decomposition reduces
+the curvature computation time. For the XYZ Dragon with a radius of 20, it needs
+almost 4 seconds to compute the $l_0$ level, whereas using the hierarchical
+algorithm, it only needs 700ms. However, due to the precomputation, this
+algorithm is biased and creates an error (presented in
+Table~\ref{tab:full-res-stat}) that needs to be considered
 
-%\subsection{Visualisation}
-%
-%For dynamic datasets, we consider a time varying implicit
-%surface. Since it would have been to expensive to update the a mipmap texture
-%of densities at each time step, we simply evaluate the implicit
-%expression at each vertex of a cell to decide if such cell is included
-%or not into $\Ball{R}{\vx}\cap \Shape$.
-%\todo[inline]{blabla experiments}
+\subsection{Visualisation}
+
+For dynamic datasets, we consider a time varying implicit
+surface. Since it would have been to expensive to update the a mipmap texture
+of densities at each time step, we simply evaluate the implicit
+expression at each vertex of a cell to decide if such cell is included
+or not into $\Ball{R}{\vx}\cap \Shape$.
+\todo[inline]{blabla experiments}
 
@@
 digital data with a curvature tensor estimation at each vertex. Using
-this approach, we can explore in realtime different curvature
+this approach, we can explore in real-time different curvature
 measurements (mean, Gaussian, principal directions) with different

### 2015-10-23 latex/article.tex

@@
 They are presented here to illustrate how the refining process converges to
-the $l_0$ level. Thanks to this low error, higher approximation levels are visually
+the $l_0$ level.
+Thanks to this low error, higher approximation levels are visually
 very similar to the $l_0$ level. We can therefore use them for exploring our
-datasets in real time, changing the radii on the fly and visualizing dynamic datasets.
+datasets in real time, changing the radii on the fly and visualising dynamic datasets.
 
@@
 (\url{https://github.com/dcoeurjo/ICTV}).
+
+In a future work, this framework could be used for feature detection purposes
+such as presented in \cite{SMI2015}. The point classification is done by computing
+the curvature at different radii and comparing them. Using our framework,
+this may be done in a real-time manner.
+The computed curvature could also be used to control the refinement of the
+triangulation. We are for now only using the normal computation for shading
+purposes but we could imagine using it along with the vertices to do a
+Poisson reconstruction of the object.
 

### 2015-10-23 latex/article.tex
expe article

@@
 Figure~\ref{fig:full}-bottom shows mean curvature estimation in real-time on a
-dynamic object. For all illustrations, we use directly normal vectors computed
-by algorithm discussed in Section~\ref{sec:curv-tens-estim}.
+dynamic object. For this case, we simply evaluate the implicit expression at
+each vertex of a cell to decide if such cell is included or not into
+$\Ball{R}{\vx}\cap \Shape$ instead of updating the \emph{mipmap texture} of
+densities at each time step. For all illustrations, we use directly normal
+vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}.
 
@@
 compute all the above levels. Using approximations is thus mandatory, since for
-big objects such as the XYZ Dragon (Digital Domain $510^3$) with high radii, the
-computation is seconds faster, the $l_0$ visualisation takes more than 4 seconds
-to compute, whereas the approximated visualisation at $l_2$ takes only 300ms. We
-can thus get an approximated visualisation of our object as soon as we run the
-application, allowing for real time interactions with the object (changing the
-visualised value, the curvature radius, etc ...). Once an interesting portion if
-the object is reached, it only takes a few seconds to the application to display
-ground truth curvature estimation.
+big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
+computation is faster than the $l_0$ while results are enough close to the
+$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
+only $300$ms while the $l_0$ visualization takes more than $4$ seconds.
 
-It is also clear on those graphs that using a hierarchical decomposition reduces
-the curvature computation time. For the XYZ Dragon with a radius of 20, it needs
-almost 4 seconds to compute the $l_0$ level, whereas using the hierarchical
-algorithm, it only needs 700ms. However, due to the precomputation, this
-algorithm is biased and creates an error (presented in
-Table~\ref{tab:full-res-stat}) that needs to be considered
-
-%\subsection{Visualisation}
-%
-%For dynamic datasets, we consider a time varying implicit
-%surface. Since it would have been to expensive to update the a mipmap texture
-%of densities at each time step, we simply evaluate the implicit
-%expression at each vertex of a cell to decide if such cell is included
-%or not into $\Ball{R}{\vx}\cap \Shape$.
-%\todo[inline]{blabla experiments}
+We can thus get an approximated visualisation of our object as soon as we run
+the application, allowing for real time interactions with the object (changing
+the visualized value, the curvature radius, \cdots). It is also clear on those
+graphs that using a hierarchical decomposition reduces the curvature computation
+time. For the XYZ-Dragon with $R=20$, it needs almost $4$ seconds to compute the
+$l_0$ level, whereas using the hierarchical algorithm, it only needs $700$ms.
+However, due to the precomputation, this algorithm is biased and creates an
+error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered.
 

### 2015-10-23 latex/article.tex
minor edit

@@
 
-For all illustrations, we use directly normal vectors computed by algorithm
-discussed in Section~\ref{sec:curv-tens-estim}
-
 \begin{table}
@@
   \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error obtained on OctaFlower with a digital domain of $130^3$. We measured it using radii of 8 and 16.
-  The object was triangulated at full resolution with a regular grid and contains 282396 vertices. The timings
+  The object was triangulated at full resolution with a regular grid and contains 282,396 vertices. The timings
     only consider the curvature estimation step.\label{tab:full-res-stat}}
@@
 $l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
-only $300$ms while the $l_0$ visualization takes more than $4$ seconds.
+only 300ms while the $l_0$ visualization takes more than 4 seconds.
 
@@
 the application, allowing for real time interactions with the object (changing
-the visualized value, the curvature radius, \cdots). It is also clear on those
+the visualized value, curvature radius, \cdots). It is also clear on those
 graphs that using a hierarchical decomposition reduces the curvature computation
-time. For the XYZ-Dragon with $R=20$, it needs almost $4$ seconds to compute the
-$l_0$ level, whereas using the hierarchical algorithm, it only needs $700$ms.
+time. For the XYZ-Dragon with $R=20$, it needs almost 4 seconds to compute the
+$l_0$ level, whereas using the hierarchical algorithm, it only needs 700ms.
 However, due to the precomputation, this algorithm is biased and creates an
@@
 \end{figure}
+
+Figure~\ref{fig:adaptive} shows curvature computation and exploration in
+real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
+Snow microstructures ($233^3$).
 

### 2015-10-23 latex/article.tex
minor edit

@@
 the application, allowing for real time interactions with the object (changing
-the visualized value, curvature radius, \cdots). It is also clear on those
+the visualized value, curvature radius, \ldots). It is also clear on those
 graphs that using a hierarchical decomposition reduces the curvature computation
@@
 In a future work, this framework could be used for feature detection purposes
-such as presented in \cite{SMI2015}. The point classification is done by computing
-the curvature at different radii and comparing them. Using our framework,
-this may be done in a real-time manner.
-The computed curvature could also be used to control the refinement of the
-triangulation. We are for now only using the normal computation for shading
-purposes but we could imagine using it along with the vertices to do a
-Poisson reconstruction of the object.
+such as presented in \cite{SMI2015}. The point classification is done by
+computing the curvature at different radii and comparing them. Using our
+framework, this may be done in a real-time manner. The computed curvature could
+also be used to control the refinement of the triangulation. We are for now only
+using the normal computation for shading purposes but we could imagine using it
+along with the vertices to do a Poisson reconstruction of the object.
 

### 2015-10-23 latex/article.tex
minor edit

@@
 graphs that using a hierarchical decomposition reduces the curvature computation
-time. For the XYZ-Dragon with $R=20$, it needs almost 4 seconds to compute the
-$l_0$ level, whereas using the hierarchical algorithm, it only needs 700ms.
-However, due to the precomputation, this algorithm is biased and creates an
-error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered.
+time, especially with big radii. For the XYZ-Dragon with $R=20$, it needs almost
+4 seconds to compute the $l_0$ level, whereas using the hierarchical algorithm,
+it only needs 700ms. However, due to the precomputation and current hierarchical
+structure, this algorithm is biased and creates an error (presented in
+Table~\ref{tab:full-res-stat}) that needs to be considered.
 

### 2015-10-23 latex/article.tex
minor modifications

--- 2015-10-23 latex/article.tex
@@
 Sciences. When considering large volumetric data, interactive
-visualization of such images (or isovalue surfaces) is a complex
+%visualization of such images (or isovalue surfaces) is a complex
+visualization of those objects (or isosurfaces) is a complex
 problem. Such issues become even more difficult when dynamic
-volumetric datasets are considered. Beside such isosurface
+%volumetric datasets are considered. Beside such isosurface
+volumetric datasets are considered. Beside
 visualization, we are also interested in performing geometry
@@
 directions, \ldots) estimation at each point of the digital
-surface. Curvature maps on a given isosurface are key information when
-exploring 3D structures in Material Sciences \todo{REF}. Furthermore,
+surface. 
+%Curvature maps on a given isosurface are key information when
+%exploring 3D structures in Material Sciences \todo{REF}. 
+Furthermore,
 most curvature estimators require a parameter fixing the scale
@@
 The method developed by \textsc{Lengyel} \textit{et al.}
-\cite{lengyel2010voxel} is the best suited to our needs.  However, it
-was only developed on CPU to visualize in real-time static or near
-static data, combining octree with new Marching Cubes configurations
-to generate adaptive meshes. In this paper we propose a GPU pipeline
-inspired from this method.  It leaves the CPU free for other tasks and
-avoids synchronization with the GPU.  Our high framerate also allows
-this method to run in real-time on fully dynamic data.  The
-triangulation is controlled by a GPU LoD criterion that ensures that
-triangles project onto more than one pixel, thus removing geometrical
-aliasing.
+\cite{lengyel2010voxel} is the best suited to our needs. 
+%However, it
+%was only developed on CPU to visualize in real-time static or near
+%static data, combining octree with new Marching Cubes configurations
+%to generate adaptive meshes. 
+It combines an octree space partitioning with new Marching Cubes configuration
+to generate adaptive meshes, but was only developed on the CPU to visualize
+static or near static data.
+In this paper we propose a full GPU pipeline
+%inspired from this method.  
+inspired from this method, using a GPU-friendly Lod criterion to maintain a view dependent triangulation.
+%It leaves the CPU free for other tasks and avoids synchronization with the GPU.  
+%Our high framerate also allows
+Our high framerate allows
+this method to run in real-time on fully dynamic data.  
+%The triangulation is controlled by a GPU LoD criterion 
+%that ensures that
+%triangles project onto more than one pixel, thus removing geometrical
+%aliasing.
 
@@
 boundary $\DigBoundary{Z}$ of $Z$ made of cells in a cellular Cartesian complex
-(\emph{pointels}, \emph{linels}, \emph{surfels}, \ldots), can be trivally
+(\emph{pointels}, \emph{linels}, \emph{surfels}, \ldots), can be trivially
 embedded into $\R^d$ such that it coincides with $\partial\Body{Z}{h}$.
@@
 In this section, we detail the adaptive isosurface extraction
-algorithm. The proposed approach is based on an octree representation
-of the input object on which an efficient adaptive triangulation
-of the isosurface is constructed on GPU. Such approach is motivated by
+algorithm. 
+%The proposed approach is based on an octree representation
+%of the input object on which an efficient adaptive triangulation
+%of the isosurface is constructed on GPU. 
+The proposed approch use an octree representation of the input object
+on which an adaptive Marching Cube is used to build the isosurface efficiently.
+Such approach is motivated by
 the fact that the hierarchical representation of the object allows us
@@
 
-Representing a hierachical structure on GPU is usually challenging since the GPU
-memory is limited and non consistent %\todo{fix coherent/aligned/coalesced?}
-memory access (\emph{e.g.} tree traversal using pointer dereferencing) may lead
-to huge payload from cache misses.  Efficient spatial tree encoding can be
-achieved using pointerless structures such as linear quadtrees or octrees, see
-for instance \textsc{Gargantini}~\cite{gargantini1982effective}. This structure
-consists in indexing each cell by a \emph{Morton code}: the code of children
+Representing a hierachical structure on GPU is usually challenging since
+the GPU is a data parallel component and is unable to handle recursivity.
+
+%since the GPU
+%memory is limited and non consistent %\todo{fix coherent/aligned/coalesced?}
+%memory access (\emph{e.g.} tree traversal using pointer dereferencing) may lead
+%to huge payload from cache misses.
+
+Efficient spatial tree encoding can be
+achieved using pointerless structures such as linear quadtrees or octrees ( see
+for instance \textsc{Gargantini}~\cite{gargantini1982effective} ). This structure
+%consists in indexing each cell by a \emph{Morton code}: the code of children
+indexes each cell by a \emph{Morton code}: the code of children
 cells are defined by the code of the parent suffixed by two bits (in dimension
@@
 \ref{fig_quadtree_partitionning}-\emph{left}). A cell's code encodes its
-position \wrt its parent cell and its complete path to the tree root. Hence,
-whatever their depth, all cell codes are simply stored in a linear vector on
-memory. Furthermore, cell operations such as subdivision, merging, neighbors
+position \wrt its parent cell and its complete path to the tree root. 
+%Hence, whatever their depth, all cell codes are simply stored in a linear vector on memory. 
+Hence, the tree is fully represented as a linear vector of its leaves, whatever their depth.
+Furthermore, cell operations such as subdivision, merging, neighbors
 access can be efficiently implemented using bitwise operations on the Morton
 code. In the following, we use the GPU implementation proposed by \textsc{Dupuy}
-\textit{et al.}~\cite{dupuy2014quadtrees}. By using their approach, Morton codes
+\textit{et al.}~\cite{dupuy2014quadtrees} that we extended to the third dimension. 
+By using their approach, Morton codes
 and bitwise operations are optimized to match with GPU hardware requirements.
@@
 hardwares. However, since adjacent cells may not have the same depth
-on the octree, original \textsc{Lorensen} and \textsc{Cline}'s rules need to be
+in the octree, original \textsc{Lorensen} and \textsc{Cline}'s rules need to be
 updated (see Figure~\ref{fig_quadtree_partitionning}-\emph{right}). Many authors have addressed this problem both for primal and
@@
 In the following, we use the extension of MC configurations to handle
-adaptive structures proposed by \textsc{Lengyel} \emph{et al.}~\cite{lengyel2010voxel}. First, this approach constrains the octree
+adaptive structures proposed by \textsc{Lengyel} \emph{et al.}~\cite{lengyel2010voxel}. 
+First, this approach constrains the octree
 structure in order to make sure that the depth difference between any
-two adjacent cells is at most one. Then, \textsc{Lengyel} \emph{et al.} propose
-specific MC configurations for such transition cells,  leading to a
-crack-free triangulation.
+two adjacent cells is at most one. 
+Then, \textsc{Lengyel} \emph{et al.} introduce the concept of transition cells.
+Those cells are defined to be inserted between two neighbouring octree cells of different depth.
+With specific MC configurations for such transition cells, a crack free triangulation can
+be extracted.
+%Then, \textsc{Lengyel} \emph{et al.} propose
+%specific MC configurations for such transition cells,  leading to a
+%crack-free triangulation.
 
@@
 propose a viewpoint dependent criterion to decide if a cell needs to be refined:
-the closer we are to the camera, the finer the cells are. In addition to the
-distance criterion, we define an angular criterion to prevent refining cells
-outside the camera frustrum. Using a criterion based on the distance between a
+the closer we are to the camera, the finer the cells are. 
+%In addition to the
+%distance criterion, we define an angular criterion to prevent refining cells
+%outside the camera frustrum. 
+Using a criterion based on the distance between a
 cell and the camera is well suited to GPU since it can be evaluated
@@
   \end{center}
-  \caption{\emph{First row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
+  \caption{\emph{Third row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
   \emph{Second row:} First and second principal directions estimation (and zoom) on an OctaFlower.
@@
 Figure~\ref{fig:full}-bottom shows mean curvature estimation in real-time on a
-dynamic object. For this case, we simply evaluate the implicit expression at
-each vertex of a cell to decide if such cell is included or not into
-$\Ball{R}{\vx}\cap \Shape$ instead of updating the \emph{mipmap texture} of
-densities at each time step. For all illustrations, we use directly normal
-vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}.
+dynamic object. For all illustrations, we use directly normal vectors computed
+by algorithm discussed in Section~\ref{sec:curv-tens-estim}.
 
@@
   \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error obtained on OctaFlower with a digital domain of $130^3$. We measured it using radii of 8 and 16.
-  The object was triangulated at full resolution with a regular grid and contains 282,396 vertices. The timings
+  The object was triangulated at full resolution with a regular grid and contains 282396 vertices. The timings
     only consider the curvature estimation step.\label{tab:full-res-stat}}
@@
   %
-  \caption{Timings in milliseconds (in logscale) obtained while visualizing an adaptive
+  \caption{Timings in milliseconds obtained while visualizing an adaptive
   triangulation on three objects -- OctaFlower (digital domain of $130^3$ ), Snow
@@
   %
-  Timings are given using a NVIDIA GeForce GTX 850M GPU.
   }
@@
 
-When dealing with large datasets, we can not expect real-time curvature tensor
-estimation due to the huge amount of data to process. By computing an
-dynamically refined approximate curvature tensor estimation joined with an
-adaptive triangulation (as discussed in Section~\ref{sec:hierarchical}), we
-manage to maintain a real time framerate by giving control over the amount of
-data to process at each frame. In Figure~\ref{fig:timings}, we compare timings
-(in logarithmic scale) when the triangulation is dynamically refining according
-to its distance to the camera. We measured those timings using the regular and
-the hierarchical algorithm.
+In this experiments, we measure the timings obtained when running our framework on a
+GeForce GTX 850M. Here, the triangulation is dynamically refining according to its distance to the camera.
+At each frame, both the curvature and the triangulation are recomputed.
+If the visualisation stays unchanged, we compute the curvature at a level $l-1$ until the level $l_0$ is reached.
+We measured those timings using the regular and the hierarchical algorithm. The results are presented in 
+logarithmic scale figure \ref{fig:timings}.
 
-We can first note that the required time for an object to compute ground truth
-curvature is usually as high as the time required to extract the geometry and
-compute all the above levels. Using approximations is thus mandatory, since for
-big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
-computation is faster than the $l_0$ while results are enough close to the
-$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
-only 300ms while the $l_0$ visualization takes more than 4 seconds.
+We can first note that the required time for an object to compute ground truth curvature is usually
+as high as the time required to extract the geometry and compute all the above levels.
+Using approximations is thus mandatory, since for big objects such as the XYZ Dragon (Digital Domain $510^3$)
+with high radii, the computation is seconds faster, the $l_0$ visualisation takes more than 4 seconds to compute, whereas
+the approximated visualisation at $l_2$ takes only 300ms.
+We can thus get an approximated visualisation of our object as soon as we run the application, allowing for
+real time interactions with the object (changing the visualised value, the curvature radius, etc ...).
+Once an interesting portion if the object is reached, it only takes a few seconds to the application to display
+ground truth curvature estimation.
 
-We can thus get an approximated visualisation of our object as soon as we run
-the application, allowing for real time interactions with the object (changing
-the visualized value, curvature radius, \ldots). It is also clear on those
-graphs that using a hierarchical decomposition reduces the curvature computation
-time. For the XYZ-Dragon with $R=20$, it needs almost 4 seconds to compute the
-$l_0$ level, whereas using the hierarchical algorithm, it only needs 700ms.
-However, due to the precomputation, this algorithm is biased and creates an
-error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered.
+It is also clear on those graphs that using a hierarchical decomposition reduces the curvature computation time.
+For the XYZ Dragon with a radius of 20, it needs almost 4 seconds to compute the $l_0$ level, whereas using the
+hierarchical algorithm, it only needs 700ms. However, due to the precomputation, this algorithm is biased and
+creates an error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered
+
+%\subsection{Visualisation}
+%
+%For dynamic datasets, we consider a time varying implicit
+%surface. Since it would have been to expensive to update the a mipmap texture
+%of densities at each time step, we simply evaluate the implicit
+%expression at each vertex of a cell to decide if such cell is included
+%or not into $\Ball{R}{\vx}\cap \Shape$.
+%\todo[inline]{blabla experiments}
 
@@
 
-Figure~\ref{fig:adaptive} shows curvature computation and exploration in
-real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
-Snow microstructures ($233^3$).
-
 \section{Conclusion and Discussion}
@@
 digital data with a curvature tensor estimation at each vertex. Using
-this approach, we can explore in real-time different curvature
+this approach, we can explore in realtime different curvature
 measurements (mean, Gaussian, principal directions) with different
@@
 
-In a future work, this framework could be used for feature detection purposes
-such as presented in \cite{SMI2015}. The point classification is done by
-computing the curvature at different radii and comparing them. Using our
-framework, this may be done in a real-time manner. The computed curvature could
-also be used to control the refinement of the triangulation. We are for now only
-using the normal computation for shading purposes but we could imagine using it
-along with the vertices to do a Poisson reconstruction of the object.
+An extension of this framework could be to implement an approximate hierarchical
+algorithm. From there, we could use the dynamic refinement scheme to compute
+the curvature with the hierarchical algorithm, thus massively reducing the number of probes.
+We could also use trexture streaming to compute on the fly on the CPU the subdivision and
+stream it to the GPU, allowing dynamic radii change with the hierarchical algorithm.
+This framework could also be used for feature detection purposes
+such as presented in \cite{SMI2015}. The point classification is done by computing
+the curvature at different radii and comparing them. Using our framework,
+this may be done in a real-time manner.
+The computed curvature could finally be used to control the refinement of the
+triangulation. We are for now only using the normal computation for shading
+purposes but we could imagine using it along with the vertices to do a
+Poisson reconstruction of the object.
 

### 2015-10-23 latex/article.tex

@@
 when it is closer from the camera and thus reducing the number of vertices to compute.
-
-For all illustrations, we use directly normal vectors computed by algorithm
-discussed in Section~\ref{sec:curv-tens-estim}
 
@@
 
-In this experiments, we measure the timings obtained when running our framework on a
-GeForce GTX 850M. Here, the triangulation is dynamically refining according to its distance to the camera.
-At each frame, both the curvature and the triangulation are recomputed.
-If the visualisation stays unchanged, we compute the curvature at a level $l-1$ until the level $l_0$ is reached.
-We measured those timings using the regular and the hierarchical algorithm. The results are presented in 
-logarithmic scale figure \ref{fig:timings}.
+When dealing with large datasets, we can not expect real-time curvature tensor
+estimation due to the huge amount of data to process. By computing an
+dynamically refined approximate curvature tensor estimation joined with an
+adaptive triangulation (as discussed in Section~\ref{sec:hierarchical}), we
+manage to maintain a real time framerate by giving control over the amount of
+data to process at each frame. In Figure~\ref{fig:timings}, we compare timings
+(in logarithmic scale) when the triangulation is dynamically refining according
+to its distance to the camera. We measured those timings using the regular and
+the hierarchical algorithm.
 
-We can first note that the required time for an object to compute ground truth curvature is usually
-as high as the time required to extract the geometry and compute all the above levels.
-Using approximations is thus mandatory, since for big objects such as the XYZ Dragon (Digital Domain $510^3$)
-with high radii, the computation is seconds faster, the $l_0$ visualisation takes more than 4 seconds to compute, whereas
-the approximated visualisation at $l_2$ takes only 300ms.
-We can thus get an approximated visualisation of our object as soon as we run the application, allowing for
-real time interactions with the object (changing the visualised value, the curvature radius, etc ...).
-Once an interesting portion if the object is reached, it only takes a few seconds to the application to display
-ground truth curvature estimation.
+We can first note that the required time for an object to compute ground truth
+curvature is usually as high as the time required to extract the geometry and
+compute all the above levels. Using approximations is thus mandatory, since for
+big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
+computation is faster than the $l_0$ while results are enough close to the
+$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
+only 300ms while the $l_0$ visualization takes more than 4 seconds.
 
-It is also clear on those graphs that using a hierarchical decomposition reduces the curvature computation time.
-For the XYZ Dragon with a radius of 20, it needs almost 4 seconds to compute the $l_0$ level, whereas using the
-hierarchical algorithm, it only needs 700ms. However, due to the precomputation, this algorithm is biased and
-creates an error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered
-
-%\subsection{Visualisation}
-%
-%For dynamic datasets, we consider a time varying implicit
-%surface. Since it would have been to expensive to update the a mipmap texture
-%of densities at each time step, we simply evaluate the implicit
-%expression at each vertex of a cell to decide if such cell is included
-%or not into $\Ball{R}{\vx}\cap \Shape$.
-%\todo[inline]{blabla experiments}
+We can thus get an approximated visualisation of our object as soon as we run
+the application, allowing for real time interactions with the object (changing
+the visualized value, curvature radius, \ldots). It is also clear on those
+graphs that using a hierarchical decomposition reduces the curvature computation
+time, especially with big radii. For the XYZ-Dragon with $R=20$, it needs almost
+4 seconds to compute the $l_0$ level, whereas using the hierarchical algorithm,
+it only needs 700ms. However, due to the precomputation and current hierarchical
+structure, this algorithm is biased and creates an error (presented in
+Table~\ref{tab:full-res-stat}) that needs to be considered.
 
@@
 
+Figure~\ref{fig:adaptive} shows curvature computation and exploration in
+real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
+Snow microstructures ($233^3$).
+
 \section{Conclusion and Discussion}

### 2015-10-23 latex/article.tex
minor edit

--- 2015-10-23 latex/article.tex
@@
 
-Then, we compare the approximation made by computing curvature from level $l >
-l_0$ in order to accelerate visualisation with the ground truth result obtained
+Then, we compare the approximation made by computing curvature from level $l >=
+l_0$ in Figure~\ref{fig:refine}. We can see that results using approximation
+seems to fastly converge to the ground truth results.
+Table~\ref{tab:full-res-stat} shows numerical results of $L_\infty$ error (worst
+case) and $L_2$ error (mean), as well the number of \emph{mipmap texture}
+fetches. We can first see that the number of texel fetch required to compute the
+curvature reduces drastically when computing the approximations. This is
+mandatory if we want to increase the framerate.
+
+ in order to accelerate visualisation with the ground truth result obtained
 at level $l_0$. We also compare them with the hierarchical algorithm discussed
@@
 
-We can first see that the number of texel fetch required to compute
-the curvature reduces drastically when computing the approximations.
-This is mandatory if we want to increase the framerate.
 However, we can also note that the error increases quite slowly.
@@
     \end{tabular}
-
 	\begin{tabular}{@{}lrrrrrr@{}}
@@
     \end{tabular}
-
   \end{center}
-  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error obtained on OctaFlower with a digital domain of $130^3$. We measured it using radii of 8 and 16.
-  The object was triangulated at full resolution with a regular grid and contains 282,396 vertices. The timings
-    only consider the curvature estimation step.\label{tab:full-res-stat}}
+  %
+  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error
+  obtained on OctaFlower with a digital domain of $130^3$ when computing mean
+  curvature, with two radii: 8 and 16. The object is triangulated at full
+  resolution with a regular grid and contains 282,396 vertices.
+  %
+  \label{tab:full-res-stat}}
+  %
 \end{table}

### 2015-10-23 latex/article.tex
minor edit

@@
 
-Then, we compare the approximation made by computing curvature from level $l >=
+Then, we compare the approximation made by computing curvature from level $l \ge
 l_0$ in Figure~\ref{fig:refine}. We can see that results using approximation
@@
   \begin{center}
+  \setlength{\tabcolsep}{0.15cm}
+	\begin{tabular}{@{}llrrrrrr@{}}
+      \toprule
+        & & H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
+      \midrule
+      \multirow{2}{2.2cm}{Number of texture fetches} & $R=8$ & 1468 & & 2 & 28 & 260 & 2104 \\
+                                & $R=16$ & 5706 & 2 & 28 & 90 & 2120 & 17080\\\midrule
 
-	\begin{tabular}{@{}lrrrrr@{}}
-      \toprule
-      & \multicolumn{5}{c}{$R=8$}\\
-      \cmidrule(r){2-6}
-    Quantities & ~~~H & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
-      \midrule
-      Number of texture fetches &
-      1468 & 2 & 28 & 260 & 2104\\
-      %Time (in ms) &
-      %208 & 15 & 26 & 93 & 642\\
-      $L_\infty$ error (\wrt $l_0$) &
-      0.051 & 0.306 & 0.085 & 0.047 & 0\\
-      $L_2$ error (\wrt $l_0$) &
-      3.51e-05 & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
-      \bottomrule
-    \end{tabular}
-	\begin{tabular}{@{}lrrrrrr@{}}
-      \toprule
-      & \multicolumn{6}{c}{$R=16$}\\
-      \cmidrule(r){2-7}
-    Quantities & ~~~H & $l_4$ & $l_3$ & $l_2$ & $l_1$ & $l_0$\\
-      \midrule
-      Number of texture fetches &
-      5706 & 2 & 28 & 90 & 2120 & 17080\\
-      %Time (in ms) &
-      %826 & 14 & 26 & 252 & 606 & 4801\\
-      $L_\infty$ error (\wrt $l_0$) &
-      0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\
-      $L_2$ error (\wrt $l_0$) &
-      4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
+      \multirow{2}{2.2cm}{$L_\infty$ error (\wrt $l_0$)} & $R=8$ & 0.051 & & 0.306 & 0.085 & 0.047 & 0\\
+                                    & $R=16$ & 0.053 & 0.146 & 0.041 & 0.017 & 0.005 & 0\\\midrule
+
+      \multirow{2}{2.1cm}{$L_2$ error (\wrt $l_0$)} & $R=8$ & 3.51e-05 & & 2.67e-04 & 7.57e-05 & 2.02e-05 & 0\\
+                               & $R=16$ & 4.43e-05 & 1.39e-04 & 4.16e-05 & 1.57e-05 & 2.07e-06 & 0\\
       \bottomrule
@@
   obtained on OctaFlower with a digital domain of $130^3$ when computing mean
-  curvature, with two radii: 8 and 16. The object is triangulated at full
-  resolution with a regular grid and contains 282,396 vertices.
+  curvature with two radii: 8 and 16, with hierarchical algorithm (H) and $l \ge
+  l_0$ approximation algorithms. The object is triangulated at full resolution
+  with a regular grid and contains 282,396 vertices.
   %

### 2015-10-23 latex/article.tex
added convergence graph

--- 2015-10-23 latex/article.tex
@@
 
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.5\textwidth]{figs/graph_cmp_l0_l4_mean_octa130_Linf}
+  \end{center}
+  \caption{Error $L\infty$ on the measured Mean curvature between a $l_n$ approximation and the
+  $l_0$ measurement. The red curve present the results when computing the volume from a mipmap quantitized to 0 or 1, and the green one
+  present the results when computing it from the real mipmap values.}
+  \label{fig:graph_convergence}
+\end{figure}
+
 We first evaluate the curvature estimation on a full-resolution geometry
@@
 
-Then, we compare the approximation made by computing curvature from level $l >=
-l_0$ in Figure~\ref{fig:refine}. We can see that results using approximation
-seems to fastly converge to the ground truth results.
-Table~\ref{tab:full-res-stat} shows numerical results of $L_\infty$ error (worst
-case) and $L_2$ error (mean), as well the number of \emph{mipmap texture}
-fetches. We can first see that the number of texel fetch required to compute the
-curvature reduces drastically when computing the approximations. This is
-mandatory if we want to increase the framerate.
-
- in order to accelerate visualisation with the ground truth result obtained
+Then, we compare the approximation made by computing curvature from level $l >
+l_0$ in order to accelerate visualisation with the ground truth result obtained
 at level $l_0$. We also compare them with the hierarchical algorithm discussed
@@
 
+We can first see that the number of texel fetch required to compute
+the curvature reduces drastically when computing the approximations.
+This is mandatory if we want to increase the framerate.
 However, we can also note that the error increases quite slowly.
@@
 the $l_0$ level.
+
+This convergence is shown in Figure \ref{fig:convergence}. It has been evaluated using
+two different strategy for volume computation. The first one reads the interpolated
+data from the mipmap is adds 1 to the volume if this value is above a threshold. 
+The second strategy adds directly to the volume the interpolated data read from the mipmap.
+The results are shown Figure \ref{fig:graph_convergence}. It can be seen that the
+interpolation done by the mipmap allows the resulting curvature to converge
+faster to the $l_0$ level.
+
 Thanks to this low error, higher approximation levels are visually
@@
     \end{tabular}
+
 	\begin{tabular}{@{}lrrrrrr@{}}
@@
     \end{tabular}
+
   \end{center}
-  %
-  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error
-  obtained on OctaFlower with a digital domain of $130^3$ when computing mean
-  curvature, with two radii: 8 and 16. The object is triangulated at full
-  resolution with a regular grid and contains 282,396 vertices.
-  %
-  \label{tab:full-res-stat}}
-  %
+  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error obtained on OctaFlower with a digital domain of $130^3$. We measured it using radii of 8 and 16.
+  The object was triangulated at full resolution with a regular grid and contains 282,396 vertices. The timings
+    only consider the curvature estimation step.\label{tab:full-res-stat}}
 \end{table}

### 2015-10-23 latex/article.tex
figs

@@
   \begin{center}
-    {\includegraphics[width=2.7cm]{figs/Octa_mean}}
-    {\includegraphics[width=2.7cm]{figs/Octa_gaussian}}
-    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
-    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
-    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
-    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
+    {\includegraphics[width=2.2cm]{figs/Octa_mean}}
+    {\includegraphics[width=2.2cm]{figs/Octa_gaussian}}
+    % {\includegraphics[width=2.7cm]{figs/Octa_k1}}
+    % {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
+    % {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
+    % {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
     {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
@@
   \end{center}
-  \caption{\emph{First row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
-  \emph{Second row:} First and second principal directions estimation (and zoom) on an OctaFlower.
+  \caption{\emph{First row}: Mean and Gaussian curvature estimation, (zoom of) first and second principal directions estimation on an OctaFlower with a digital domain of $130^3$.
+  % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
   \emph{Third row:} Mean curvature computed in real-time on a dynamic object.}
@@
 big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
-computation is faster than the $l_0$ while results are enough close to the
-$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
-only 300ms while the $l_0$ visualization takes more than 4 seconds.
+computation is faster than the $l_0$ while results are close enough. For
+example, with $R=20$, the approximated visualization at $l_2$ takes only 300ms
+while the $l_0$ visualization takes more than 4 seconds.
 

### 2015-10-23 latex/article.tex
changed figure pipeline

--- 2015-10-23 latex/article.tex
@@
 
-In this article, we have propose a full data parallel framework on GPU
+In this article, we have proposed a full data parallel framework on GPU
 hardware which combines an adaptive isosurface construction from
@@
 stream it to the GPU, allowing dynamic radii change with the hierarchical algorithm.
+Another improvement would be to implement the hierarchical pattern presented Figure~\ref{fig:approx}-$b$.
+This would prevent bias addition from adding cells of density 1 but only partly convered by the ball.
+
 This framework could also be used for feature detection purposes

### 2015-10-23 latex/article.tex
article

--- 2015-10-23 latex/article.tex
@@
 $\partial\Body{Z}{h}$ are topological boundary of objects lying in the same
-space (See Fig. \ref{fig:notations}-b). Note that the combinatorial digital
+space (see Fig. \ref{fig:notations}-b). Note that the combinatorial digital
 boundary $\DigBoundary{Z}$ of $Z$ made of cells in a cellular Cartesian complex
@@
     \begin{center}
-      \subfigure[]{\begin{overpic}[width=5cm]{figs/integral2D_2}
+      {\begin{overpic}[width=5cm]{figs/integral2D_2}
           \put(42,28){$\times$}
@@
       \end{overpic}}~~~~~~
-      \subfigure[]{\begin{overpic}[width=5cm]{figs/notation_2}
+      {\begin{overpic}[width=5cm]{figs/notation_2}
           \put(62,0.5){$h \cdot \vz \in \Shape \cap \Ball{R}{\vx}$}
@@
     \end{center}}
-    \caption{Integral invariant computation $(a)$ and
-      notations $(b)$ in dimension 2 \cite{CVIU2014}.\label{fig:notations}}
+    \caption{Integral invariant computation (\emph{left}) and
+      notations (\emph{right}) in dimension 2 \cite{CVIU2014}.\label{fig:notations}}
+    \vspace{-0.35cm}
 \end{figure}
@@
 \begin{figure}[!htbp]
+  \vspace{-0.35cm}
   \begin{center}
@@
   \end{center}
+  \vspace{-0.35cm}
 \caption{Morton codes associated to cells of a linear quatree. Each
@@
 Efficient spatial tree encoding can be
-achieved using pointerless structures such as linear quadtrees or octrees ( see
-for instance \textsc{Gargantini}~\cite{gargantini1982effective} ). This structure
+achieved using pointerless structures such as linear quadtrees or octrees (see
+for instance \textsc{Gargantini}~\cite{gargantini1982effective}). This structure
 %consists in indexing each cell by a \emph{Morton code}: the code of children
@@
     \end{overpic}~~~~~
-    \includegraphics[width=3.5cm]{viewlod2_small}~~~~~
+    \includegraphics[width=3cm]{viewlod2_small}~~~~~
     \includegraphics[width=3cm]{subdivision}
@@
 \begin{figure}
+  \vspace{-0.35cm}
   \begin{center}
@@
   \end{center}
+  \vspace{-0.35cm}
   \caption{Integral computation with an area estimation (\emph{left}) from pixel
@@
   \label{fig:approx}
+  \vspace{-0.35cm}
 \end{figure}
@@
   \end{center}
+  \vspace{-0.35cm}
   \caption{Adaptive approximation of the integration using a
@@
 material (see Section \ref{sec:discussion}).
-
-%\todo[inline]{phrase sur approx si on met}
 
@@
   \end{center}
+  \vspace{-0.35cm}
   \caption{\emph{First row}: Mean and Gaussian curvature estimation, (zoom of) first and second principal directions estimation on an OctaFlower with a digital domain of $130^3$.
@@
 
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.5\textwidth]{figs/graph_cmp_l0_l4_mean_octa130_Linf}
-  \end{center}
-  \caption{Error $L\infty$ on the measured Mean curvature between a $l_n$ approximation and the
-  $l_0$ measurement. The red curve present the results when computing the volume from a mipmap quantitized to 0 or 1, and the green one
-  present the results when computing it from the real mipmap values.}
-  \label{fig:graph_convergence}
-\end{figure}
+% \begin{figure}
+%   \begin{center}
+%     \includegraphics[width=0.5\textwidth]{figs/graph_cmp_l0_l4_mean_octa130_Linf}
+%   \end{center}
+%   \caption{Error $L\infty$ on the measured Mean curvature between a $l_n$ approximation and the
+%   $l_0$ measurement. The red curve present the results when computing the volume from a mipmap quantitized to 0 or 1, and the green one
+%   present the results when computing it from the real mipmap values.}
+%   \label{fig:graph_convergence}
+% \end{figure}
 
@@
 case) and $L_2$ error (mean), as well the number of \emph{mipmap texture}
-fetches. We can first see that the number of texel fetch required to compute the
-curvature reduces drastically when computing the approximations. This is
-mandatory if we want to increase the framerate.
+fetches. We can also see that the number of texel fetch, required to compute the
+curvature, reduces drastically when computing approximations. When measuring
+results with higher levels, we get consequently much bigger errors. Those level
+are thus never used in practice, they are presented here to illustrate how the
+refining process converges to the $l_0$ level. We see that levels close to $l_0$
+give few errors than $l_0$, and should be considered for exploring our datasets
+in real time, changing parameters on-the-fly and visualizing dynamic datasets.
 
- in order to accelerate visualisation with the ground truth result obtained
-at level $l_0$. We also compare them with the hierarchical algorithm discussed
-in Section~\ref{sec:hierarchical}. The results are presented in
-Table~\ref{tab:full-res-stat}, and illustrated in Figure~\ref{fig:refine}.
-
-However, we can also note that the error increases quite slowly.
-The errors obtained comparing $l_1$, or for bigger radii $l_2$ approximations
-with the $l_0$ level are small. The errors measured comparing higher levels
-are of course much bigger and those level are thus never used in practice.
-They are presented here to illustrate how the refining process converges to
-the $l_0$ level.
-
-This convergence is shown in Figure \ref{fig:convergence}. It has been evaluated using
-two different strategy for volume computation. The first one reads the interpolated
-data from the mipmap is adds 1 to the volume if this value is above a threshold.
-The second strategy adds directly to the volume the interpolated data read from the mipmap.
-The results are shown Figure \ref{fig:graph_convergence}. It can be seen that the
-interpolation done by the mipmap allows the resulting curvature to converge
-faster to the $l_0$ level.
-
-Thanks to this low error, higher approximation levels are visually
-very similar to the $l_0$ level. We can therefore use them for exploring our
-datasets in real time, changing the radii on the fly and visualising dynamic datasets.
-
-When computing results using the hierachical algorithm, a higher error can be noted.
-This is due to the precomputation of the subdivision that no longer ensures to fetch data
-at the center of a mipmap cell. The interpolation done by the GPU reduces the bias but
-does not remove it.
-
-Bear also in mind that those results were measured on a full resolution triangulation.
-Since we compute the curvature of each vertices of the final mesh, a highly triangulated object will
-be much slower to process.
-We therefore use in practice an adaptive triangulation of the object, refining the mesh
-when it is closer from the camera and thus reducing the number of vertices to compute.
+We also compare them with the hierarchical algorithm (as discussed in
+Section~\ref{sec:hierarchical}). This method introduce a higher error than
+$l_0$. This is due to the precomputation of the subdivision that no longer
+ensures to fetch data at the center of a mipmap cell. Then, the GPU performes an
+interpolation to reduce the bias, but it doesn't remove it.
 
@@
   \label{tab:full-res-stat}}
+  \vspace{-1.5cm}
   %
@@
   \end{center}
+  \vspace{-0.35cm}
   \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
@@
   \label{fig:refine}
+  \vspace{-0.35cm}
 \end{figure}
+
+Bear also in mind that those results were measured on a full resolution
+triangulation. Since we compute the curvature of each vertices of the final
+mesh, a highly triangulated object will be much slower to process. We therefore
+use in practice an adaptive triangulation of the object, refining the mesh when
+it is closer from the camera and thus reducing the number of vertices to
+compute.
 
@@
   %
+  \vspace{-0.35cm}
   \caption{Timings in milliseconds (in logscale) obtained while visualizing an adaptive
@@
   \label{fig:timings}
+  \vspace{-0.35cm}
 \end{figure}
@@
 \begin{figure}
+  \vspace{-0.35cm}
   \begin{center}
-    {\includegraphics[height=4.0cm]{figs/xyzrgb_dragon-510_R8_mean}}
-    {\includegraphics[height=3.5cm]{figs/snow_I08iso_233_r20_l0_m3}}
+    {\includegraphics[height=3.5cm]{figs/xyzrgb_dragon-510_R8_mean}}
+    {\includegraphics[height=3.0cm]{figs/snow_I08iso_233_r20_l0_m3}}
   \end{center}
-  \caption{Illustration fig illustration complete (adaptative, ...) plusieurs
-    objets.. + dynamique.
-    Illustration of mean curvature computation of snow microstructures.
-    %
-    \emph{Third row:} mean curvature computed in real-time on a dynamic object.}
+  \caption{Illustration of mean curvature computation of two large datasets: XYZ-Dragon (with digital domain of $512^3$) and Snow microstructures ($233^3$).}
   \label{fig:adaptive}
+  \vspace{-0.35cm}
 \end{figure}

### 2015-10-23 latex/article.tex

@@
   \label{tab:full-res-stat}}
-  \vspace{-1.5cm}
   %

### 2015-10-23 latex/article.tex
change a few words

--- 2015-10-23 latex/article.tex
@@
 perform interactive visualization of complex 3D digital structures combined with
-a dynamic curvature tensor estimation. More precisely, we define a fully data
-parallel process on GPU (Graphics Processor Unit) hardware to both efficiently
+%a dynamic curvature tensor estimation. More precisely, we define a fully data
+a dynamic curvature tensor estimation. We define a fully data
+%parallel process on GPU (Graphics Processor Unit) hardware to both efficiently
+parallel process on the GPU (Graphics Processor Unit) to both efficiently
 extract adaptive isosurface and compute per vertex curvature tensor using
-Integral Invariants estimators. Hence, this system allows us to visualize
+Integral Invariants estimators. 
+%Hence, this system allows us to visualize
+This system allow us to visualize
 curvature tensor in real-time on large dynamic objects. Our approach combines a
@@
 %to generate adaptive meshes. 
-It combines an octree space partitioning with new Marching Cubes configuration
-to generate adaptive meshes, but was only developed on the CPU to visualize
+It combines an octree space partitioning with new Marching Cubes configurations
+to generate adaptive meshes on the CPU from 
+%, but was only developed on the CPU to visualize
 static or near static data.
@@
 %inspired from this method.  
-inspired from this method, using a GPU-friendly Lod criterion to maintain a view dependent triangulation.
+inspired from this method, 
+%using a GPU-friendly Lod criterion 
+to maintain a view dependent triangulation.
 %It leaves the CPU free for other tasks and avoids synchronization with the GPU.  
 %Our high framerate also allows
-Our high framerate allows
-this method to run in real-time on fully dynamic data.  
+%Our high framerate allows this method to run in real-time on fully dynamic data.  
+Our high framerate allows to visualize fully dynamic data in real-time.
 %The triangulation is controlled by a GPU LoD criterion 
@@
 demonstrated that these estimators have multigrid convergence
-properties. In this article, we propose an efficient GPU
-implementation of such estimators in order to visualize, in real-time,
-such curvature maps and allowing us to interactively explore different
-values of the spherical kernel radius.
+properties. In this article, we also propose an efficient GPU
+implementation of such estimators to visualize%, in real-time,
+such curvature maps in real-time and %allowing us 
+to interactively change the %explore different
+value of the spherical kernel radius.
 
@@
   \begin{center}
-    {\includegraphics[width=2.2cm]{figs/Octa_mean}}
-    {\includegraphics[width=2.2cm]{figs/Octa_gaussian}}
-    % {\includegraphics[width=2.7cm]{figs/Octa_k1}}
-    % {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
-    % {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
-    % {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
+    {\includegraphics[width=2.7cm]{figs/Octa_mean}}
+    {\includegraphics[width=2.7cm]{figs/Octa_gaussian}}
+    {\includegraphics[width=2.7cm]{figs/Octa_k1}}
+    {\includegraphics[width=2.7cm]{figs/Octa_k2}}\\
+    {\includegraphics[width=2.7cm]{figs/Octa_dir_min}}
+    {\includegraphics[width=2.7cm]{figs/Octa_dir_max}}
     {\includegraphics[height=2.0cm]{figs/Octa_dir_min_zoom}}
@@
   \end{center}
-  \caption{\emph{First row}: Mean and Gaussian curvature estimation, (zoom of) first and second principal directions estimation on an OctaFlower with a digital domain of $130^3$.
-  % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
+  \caption{\emph{First row:} Mean, Gaussian, first and second principal curvature estimation on an OctaFlower with a digital domain of $130^3$.
+  \emph{Second row:} First and second principal directions estimation (and zoom) on an OctaFlower.
   \emph{Third row:} Mean curvature computed in real-time on a dynamic object.}
@@
 big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
-computation is faster than the $l_0$ while results are close enough. For
-example, with $R=20$, the approximated visualization at $l_2$ takes only 300ms
-while the $l_0$ visualization takes more than 4 seconds.
+computation is faster than the $l_0$ while results are enough close to the
+$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
+only 300ms while the $l_0$ visualization takes more than 4 seconds.
 

### 2015-10-23 latex/article.tex

--- 2015-10-23 latex/article.tex
@@
 %inspired from this method.  
-inspired from this method, using a GPU-friendly Lod criterion to maintain a view dependent triangulation.
+inspired from this method, 
+%using a GPU-friendly Lod criterion 
+to maintain a view dependent triangulation.
 %It leaves the CPU free for other tasks and avoids synchronization with the GPU.  
 %Our high framerate also allows
-Our high framerate allows
-this method to run in real-time on fully dynamic data.
+%Our high framerate allows this method to run in real-time on fully dynamic data.  
+Our high framerate allows to visualize fully dynamic data in real-time.
 %The triangulation is controlled by a GPU LoD criterion 
@@
   \end{center}
+
   \vspace{-0.35cm}
@@
   % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
-  \emph{Third row:} Mean curvature computed in real-time on a dynamic object.}
+  \emph{Second row:} Mean curvature computed in real-time on a dynamic object.}
   \label{fig:full}

### 2015-10-23 latex/article.tex
article

@@
   \begin{center}
-    {\includegraphics[width=4cm]{figs/approx1}}
-    {\includegraphics[width=4cm]{figs/approx-reg-1}}
-    {\includegraphics[width=4cm]{figs/approx-reg-2}}
+    {\includegraphics[width=4.0cm]{figs/approx1}}
+    {\includegraphics[width=4.0cm]{figs/approx-reg-1}}
+    {\includegraphics[width=4.0cm]{figs/approx-reg-2}}
   \end{center}
@@
   \label{fig:approx2}
+  \vspace{-0.35cm}
 \end{figure}
@@
   \end{center}
-
   \vspace{-0.35cm}
@@
   \label{fig:full}
+  \vspace{-0.35cm}
 \end{figure}
@@
 Table~\ref{tab:full-res-stat}) that needs to be considered.
-
-\begin{figure}
-  \vspace{-0.35cm}
-  \begin{center}
-    {\includegraphics[height=3.5cm]{figs/xyzrgb_dragon-510_R8_mean}}
-    {\includegraphics[height=3.0cm]{figs/snow_I08iso_233_r20_l0_m3}}
-  \end{center}
-  \caption{Illustration of mean curvature computation of two large datasets: XYZ-Dragon (with digital domain of $512^3$) and Snow microstructures ($233^3$).}
-  \label{fig:adaptive}
-  \vspace{-0.35cm}
-\end{figure}
-
-Figure~\ref{fig:adaptive} shows curvature computation and exploration in
-real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
-Snow microstructures ($233^3$).
+%
+% \begin{figure}
+%   \vspace{-0.35cm}
+%   \begin{center}
+%     {\includegraphics[height=3.5cm]{figs/xyzrgb_dragon-510_R8_mean}}
+%     {\includegraphics[height=3.0cm]{figs/snow_I08iso_233_r20_l0_m3}}
+%   \end{center}
+%   \caption{Illustration of mean curvature computation of two large datasets: XYZ-Dragon (with digital domain of $512^3$) and Snow microstructures ($233^3$).}
+%   \label{fig:adaptive}
+%   \vspace{-0.35cm}
+% \end{figure}
+%
+% Figure~\ref{fig:adaptive} shows curvature computation and exploration in
+% real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
+% Snow microstructures ($233^3$).
 
@@
 An extension of this framework could be to implement an approximate hierarchical
-algorithm. From there, we could use the dynamic refinement scheme to compute
-the curvature with the hierarchical algorithm, thus massively reducing the number of probes.
-We could also use trexture streaming to compute on the fly on the CPU the subdivision and
-stream it to the GPU, allowing dynamic radii change with the hierarchical algorithm.
-Another improvement would be to implement the hierarchical pattern presented Figure~\ref{fig:approx}-$b$.
-This would prevent bias addition from adding cells of density 1 but only partly convered by the ball.
-
-This framework could also be used for feature detection purposes
-such as presented in \cite{SMI2015}. The point classification is done by computing
-the curvature at different radii and comparing them. Using our framework,
-this may be done in a real-time manner.
-The computed curvature could finally be used to control the refinement of the
-triangulation. We are for now only using the normal computation for shading
-purposes but we could imagine using it along with the vertices to do a
-Poisson reconstruction of the object.
+algorithm. From there, we could use the dynamic refinement scheme to compute the
+curvature with the hierarchical algorithm, thus massively reducing the number of
+probes. We could also use trexture streaming to compute on the fly on the CPU
+the subdivision and stream it to the GPU, allowing dynamic radii change with the
+hierarchical algorithm. Another improvement would be to implement the
+hierarchical pattern presented Figure~\ref{fig:approx}-$b$. This would prevent
+bias addition from adding cells of density 1 but only partly convered by the
+ball.
+
+% This framework could also be used for feature detection purposes such as
+% presented in \cite{SMI2015}. The point classification is done by computing the
+% curvature at different radii and comparing them. Using our framework, this may
+% be done in a real-time manner. The computed curvature could finally be used to
+% control the refinement of the triangulation. We are for now only using the
+% normal computation for shading purposes but we could imagine using it along with
+% the vertices to do a Poisson reconstruction of the object.
 

### 2015-10-23 latex/article.tex
papier version quasi finale

@@
 the digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ with
-$\MCard(Y)$ the number of digital points of the intersection between a ball
+$\MCard(Y)$, the number of digital points of the intersection between a ball
 $\Ball{R/h}{\vx/h}$ of digital radius $R/h$ and $\DigShape$ (we denote such
@@
 %
-They have proved that estimating the 2D curvature and 3D mean curvature on digital
+They have proved that estimating both 2D curvature and 3D mean curvature on digital
 objets with volumetric integral information have the multigrid convergence
@@
 
-In \cite{CVIU2014}, authors have also defined the 3D digital principal curvature
+In \cite{CVIU2014}, authors have also defined 3D digital principal curvature
 estimators $\PrincCurvH{1}{R}$ and $\PrincCurvH{2}{R}$ on $Z\subset\Z^3$ based
@@
 
-Additionally, eigenvectors associated with $\hat{\lambda}_1$ and
+Additionally, eigenvectors associated to $\hat{\lambda}_1$ and
 $\hat{\lambda}_2$ of the covariance matrix correspond to principal curvature
@@
 corresponds to the normal direction $\NormalDirH{R}$ at $\vx$. Convergence
-results can be found in \cite{CVIU2014}.%%% Changer avec le chapitre de Jaco à un moment
+results can be found in \cite{ChapterIICurvature}.%%% Changer avec le chapitre de Jaco à un moment
 
@@
 estimators for a given digital shape. This allows them to detect features of the
-shape thanks to the behavior of the estimators on singularities.
+shape thanks to the behavior of estimators on singularities.
 
@@
 %of the isosurface is constructed on GPU.
-The proposed approch use an octree representation of the input object
-on which an adaptive Marching Cube is used to build the isosurface efficiently.
-Such approach is motivated by
-the fact that the hierarchical representation of the object allows us
+The proposed approch uses an octree representation of the input object
+on which an adaptive Marching Cube builds the isosurface efficiently.
+Such 
+%approach is motivated by the fact that the 
+hierarchical representation of the object allows us
 to handle large datasets and to locally adapt the level of details
 \wrt the geometry or camera position. We first present the
-octree representation and then the isosurface extraction from
-hierarchical octree cells.
+octree representation and then the isosurface extraction.
+% from hierarchical octree cells.
 
@@
 Representing a hierachical structure on GPU is usually challenging since
-the GPU is a data parallel component and is unable to handle recursivity.
+such a data parallel component is unable to handle recursivity.
 
@@
 Efficient spatial tree encoding can be
-achieved using pointerless structures such as linear quadtrees or octrees (see
-for instance \textsc{Gargantini}~\cite{gargantini1982effective}). This structure
+achieved using pointerless structures such as linear quadtrees or octrees 
+%(seefor instance
+ \textsc{Gargantini}~\cite{gargantini1982effective}. This structure
 %consists in indexing each cell by a \emph{Morton code}: the code of children
@@
 %Hence, whatever their depth, all cell codes are simply stored in a linear vector on memory.
-Hence, the tree is fully represented as a linear vector of its leaves, whatever their depth.
-Furthermore, cell operations such as subdivision, merging, neighbors
-access can be efficiently implemented using bitwise operations on the Morton
-code. In the following, we use the GPU implementation proposed by \textsc{Dupuy}
-\textit{et al.}~\cite{dupuy2014quadtrees} that we extended to the third dimension.
-By using their approach, Morton codes
-and bitwise operations are optimized to match with GPU hardware requirements.
+Hence, the tree is fully represented as a linear vector of its leaves.%, whatever their depth.
+Furthermore, cell operations such as subdivision, merging %, neighbors access 
+can be efficiently implemented using bitwise operations on the Morton
+code. In the following, we use the GPU 
+friendly 
+implementation proposed by \textsc{Dupuy}
+\textit{et al.}~\cite{dupuy2014quadtrees}.% that we extended to the third dimension.
+%By using their approach, Morton codes
+%and bitwise operations are optimized to match with GPU hardware requirements.
 
@@
 
-Using this spatial data structure, triangulated mesh can be constructed
-from a Marching Cubes approach \cite{lorensen1987marching} (MC for short): the
+Using this spatial data structure, a triangulated mesh can be constructed
+%from a Marching Cubes approach \cite{lorensen1987marching} (MC for short): the
+using Marching Cubes\cite{lorensen1987marching} (MC for short): the
 triangulation is generated from local triangle patches computed on
-local cell configurations. Since triangle patches are locally
-computed, such approach is fully parallel and easy to implement on GPU
-hardwares. However, since adjacent cells may not have the same depth
+local cell configurations. 
+%Since triangle patches are locally computed,
+Such approach is fully parallel and easy to implement on the GPU.
+However, since adjacent cells may not have the same depth
 in the octree, original \textsc{Lorensen} and \textsc{Cline}'s rules need to be
-updated (see Figure~\ref{fig_quadtree_partitionning}-\emph{right}). Many authors have addressed this problem both for primal and
+updated (see Figure~\ref{fig_quadtree_partitionning}-\emph{right}). 
+Many authors have addressed this problem both for primal and
 dual meshes
@@
 
-In the following, we use the extension of MC configurations to handle
-adaptive structures proposed by \textsc{Lengyel} \emph{et al.}~\cite{lengyel2010voxel}.
+In the following, we use the 
+%extension  of MC configurations to handle adaptive structures 
+algorithm
+proposed by \textsc{Lengyel} \emph{et al.}~\cite{lengyel2010voxel}.
 First, this approach constrains the octree
-structure in order to make sure that the depth difference between any
+structure 
+%in order 
+to make sure that the depth difference between any
 two adjacent cells is at most one.
 Then, \textsc{Lengyel} \emph{et al.} introduce the concept of transition cells.
-Those cells are defined to be inserted between two neighbouring octree cells of different depth.
-With specific MC configurations for such transition cells, a crack free triangulation can
+Those cells are defined to be inserted between two neighboring octree cells of different depth.
+With specific MC configurations for their triangulation, a crack free mesh can
 be extracted.
@@
 
-Similarly to original MC algorithm, this approach is perfectly adapted
-to GPU hardwares: Given a set of cells (a vector of morton codes),
-each triangle patch can be constructed in parallel (done by
-the \emph{geometry shader} in the GPU graphic pipeline).
+Similarly to original MC algorithm, this approach is well suited%perfectly adapted
+to the GPU: Given a set of cells (a vector of morton codes),
+each triangle patch can be extracted in parallel for both the regular cell and the transition cells.
+%(done by the \emph{geometry shader} in the GPU graphic pipeline).
 
@@
 As illustrated in Figure~\ref{fig_quadtree_partitionning}-\emph{middle}, we
+%propose a viewpoint dependent criterion to decide if a cell needs to be refined:
 propose a viewpoint dependent criterion to decide if a cell needs to be refined:
@@
 %outside the camera frustrum.
-Using a criterion based on the distance between a
-cell and the camera is well suited to GPU since it can be evaluated
-independently on all cells. Hence, we can efficiently determine if a cell must
-be subdivided or not. Figure~\ref{fig_lod_octree} illustrates the level of
-details (LoD for short) criterion we use. More precisely, in dimension 2, if
-$\alpha$ denotes the viewing angle, an object at distance $d$ from the camera
-with diameter greater than $2\cdot d\cdot\tan(\alpha)$ is projected into more
-than one pixel (see Figure~\ref{fig_lod_octree}-\emph{left}). Hence, the
-distance criterion is based on the ratio (\emph{visibility ratio} in the
+Such a criterion is also well suited to GPU since it can be evaluated
+independently on all cells. 
+%Hence, we can efficiently determine if a cell must be subdivided or not. 
+Figure~\ref{fig_lod_octree} illustrates our the level of
+details (LoD for short) criterion% we use. More precisely, 
+In dimension 2, if $\alpha$ denotes the viewing angle, an object at a distance $d$ from the camera
+%with diameter greater than $2\cdot d\cdot\tan(\alpha)$ is projected into more
+has a projected size on screen of $2\cdot d\cdot\tan(\alpha)$.
+%than one pixel 
+(see Figure~\ref{fig_lod_octree}-\emph{left}). 
+%Hence, the
+Our distance criterion is based on the ratio (\emph{visibility ratio} in the
 following) between the cell diameter $l(c)$ (power of 2 depending on the depth),
-and $2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell
-center and the camera. For a given cell $c$, split and merge decision are based
+and its projected size. %$2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell
+%center and the camera. 
+For a given cell $c$, split and merge decision are based
 on this visibility ratio:
@@
     \includegraphics[width=3cm]{viewlod2_small}~~~~~
-    \includegraphics[width=3cm]{subdivision}
+    %\includegraphics[width=3cm]{subdivision}
   \end{center}
-  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and angular criterion \emph{(middle)}. Based on LoD criterion
-    evaluation, the cell buffer is updated between each frame \emph{(right)}.}
+  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and angular criterion \emph{(right)}. 
+  %Based on LoD criterion evaluation, the cell buffer is updated between each frame \emph{(right)}.
+  }
   \label{fig_lod_octree}
@@
 %
-In addition to the distance criterion, we add an angular term in order
-to prevent subdivision of cells far from the camera frustrum (see
-Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
-details but please note that stay, split and merge decisions of all cells are computed in
-parallel from all cell morton codes.
-
-Once decisions have been made, a new set of cells are sent to the mesh
-generation step described above. Updating the cell buffer can be
-efficiently implemented on GPU hardware as illustrated in
-Figure~\ref{fig_lod_octree}-\emph{right}.  Finally, before
+%In addition to the distance criterion, we add an angular term in order
+%to prevent subdivision of cells far from the camera frustrum (see
+%Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
+%details but please note that stay, split and merge decisions of all cells are computed in
+%parallel from all cell morton codes.
+Using such a criterion, split and merge decisions are computed in%of all cells are computed in
+parallel from all cell's morton codes.
+
+Once decisions have been made, a new set of cells is sent to the mesh
+generation step described above. 
+%Updating the cell buffer can be
+%efficiently implemented on GPU hardware as illustrated in
+%Figure~\ref{fig_lod_octree}-\emph{right}.  
+Finally, before
 constructing the triangulation from remaining cells and transition
 cells, geometrical culling is performed in order to skip the triangle
-patch construction which are not visible. Figure~\ref{fig_pipeline}
+patch construction for cells that are not visible. Figure~\ref{fig_pipeline}
 illustrates the overall fully data parallel pipeline.
@@
 the domain such that a cell is subdivided if it does not belong to
-$\Ball{R}{\vx}\cap\Shape$. However, on GPU hardware, this approach is
+$\Ball{R}{\vx}\cap\Shape$. However, on the GPU %hardware, 
+this approach is
 highly inefficient since the hardware optimizes the parallelism only
@@
 to this cell. Note that cells in the $B_R$ decomposition may not be
-aligned with mipmap cells. However, we can use GPU mipmap
+aligned with mipmap cells. However, we can use GPU %mipmap
 functionalities which interpolates mipmap values if we probe at
@@
 obtained by disabling the LoD criterion at the mesh generation step.
-Figure~\ref{fig:full}-top and middle shows results of curvature tensor
-estimation (mean, Gaussian, first and second principal curvatures, first and
+Figure~\ref{fig:full}-top shows results of curvature tensor
+estimation (mean, Gaussian, first and
 second principal directions) on an OctaFlower at level $l_0$ (ground truth).
@@
 fetches. We can also see that the number of texel fetch, required to compute the
-curvature, reduces drastically when computing approximations. When measuring
-results with higher levels, we get consequently much bigger errors. Those level
+curvature, reduces drastically when computing approximations. However, at higher levels, 
+we get consequently much bigger errors. Those levels
 are thus never used in practice, they are presented here to illustrate how the
 refining process converges to the $l_0$ level. We see that levels close to $l_0$
-give few errors than $l_0$, and should be considered for exploring our datasets
-in real time, changing parameters on-the-fly and visualizing dynamic datasets.
+lead very few error% than $l_0$, 
+and should be considered for exploring our datasets
+in real-time, changing parameters on-the-fly and visualizing dynamic datasets.
 
 We also compare them with the hierarchical algorithm (as discussed in
-Section~\ref{sec:hierarchical}). This method introduce a higher error than
+Section~\ref{sec:hierarchical}). This method introduces a higher error when compared with
 $l_0$. This is due to the precomputation of the subdivision that no longer
-ensures to fetch data at the center of a mipmap cell. Then, the GPU performes an
-interpolation to reduce the bias, but it doesn't remove it.
+ensures to fetch data at the center of a mipmap cell. 
+The GPU's interpolation reduces the bias, but it doesn't remove it.
+
+%Bear also in mind that those results were measured on a full resolution
+%triangulation. Since we compute the curvature of each vertices of the final
+%mesh, a highly triangulated object will be much slower to process. We therefore
+%use in practice an adaptive triangulation of the object, refining the mesh when
+%it is closer from the camera and thus reducing the number of vertices to
+%compute.
+
+Those results were measured on a full resolution triangulation. 
+However, since we compute the curvature of each vertices of the final
+mesh, a highly triangulated object will be much slower to process.
+
+\subsection{Fully adaptive evaluation}
+
+When dealing with large datasets, we can not expect real-time curvature tensor
+estimation due to the huge amount of data to process. By computing a
+dynamically refined approximate curvature tensor estimation joined with an
+adaptive triangulation (as discussed in Section~\ref{sec:hierarchical}), we
+manage to maintain a real-time framerate by giving control over the amount of
+data to process at each frame. In Figure~\ref{fig:timings}, we compare timings
+(in logarithmic scale) for a triangulation that is dynamically refining according
+to its distance to the camera. We measured those timings using the regular and
+the hierarchical algorithm.
+
+%We can first note that the required time for an object to compute ground truth
+%curvature is usually as high as the time required to extract the geometry and
+%compute all the above levels. Using approximations is thus mandatory, since for
+%large objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
+%computation is faster than the $l_0$ while results are enough close to the
+%$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
+%only 300ms while the $l_0$ visualization takes more than 4 seconds.
+
+We can first note that the required time for an object to compute ground truth
+curvature is usually as high as the time required to extract the geometry and
+compute all of the above levels. Using approximations is thus mandatory.
+Another advantage with approximation, is that it allows us to get a visualisation of our object as soon as we run
+the application. This allows for real-time interactions with the object, required in order to change
+the visualized value, curvature radius, \ldots.
+
+It is also visible in Figure~\ref{fig:timings} that using a hierarchical decomposition greatly reduces the curvature computation
+time, especially with big radii. 
+%For the XYZ-Dragon with $R=20$, it needs almost
+%4 seconds to compute the $l_0$ level, whereas using the hierarchical algorithm,
+%it only needs 700ms. 
+However, due to the precomputation and current hierarchical
+structure, this algorithm is biased and creates an error (presented in
+Table~\ref{tab:full-res-stat}) that needs to be considered.
+%
+% \begin{figure}
+%   \vspace{-0.35cm}
+%   \begin{center}
+%     {\includegraphics[height=3.5cm]{figs/xyzrgb_dragon-510_R8_mean}}
+%     {\includegraphics[height=3.0cm]{figs/snow_I08iso_233_r20_l0_m3}}
+%   \end{center}
+%   \caption{Illustration of mean curvature computation of two large datasets: XYZ-Dragon (with digital domain of $512^3$) and Snow microstructures ($233^3$).}
+%   \label{fig:adaptive}
+%   \vspace{-0.35cm}
+% \end{figure}
+%
+% Figure~\ref{fig:adaptive} shows curvature computation and exploration in
+% real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
+% Snow microstructures ($233^3$).
 
@@
   %
-  For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
+  %For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}
+  }
   \label{fig:refine}
@@
 \end{figure}
-
-Bear also in mind that those results were measured on a full resolution
-triangulation. Since we compute the curvature of each vertices of the final
-mesh, a highly triangulated object will be much slower to process. We therefore
-use in practice an adaptive triangulation of the object, refining the mesh when
-it is closer from the camera and thus reducing the number of vertices to
-compute.
-
-\subsection{Fully adaptive evaluation}
 
@@
 
-When dealing with large datasets, we can not expect real-time curvature tensor
-estimation due to the huge amount of data to process. By computing an
-dynamically refined approximate curvature tensor estimation joined with an
-adaptive triangulation (as discussed in Section~\ref{sec:hierarchical}), we
-manage to maintain a real time framerate by giving control over the amount of
-data to process at each frame. In Figure~\ref{fig:timings}, we compare timings
-(in logarithmic scale) when the triangulation is dynamically refining according
-to its distance to the camera. We measured those timings using the regular and
-the hierarchical algorithm.
-
-We can first note that the required time for an object to compute ground truth
-curvature is usually as high as the time required to extract the geometry and
-compute all the above levels. Using approximations is thus mandatory, since for
-big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
-computation is faster than the $l_0$ while results are enough close to the
-$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
-only 300ms while the $l_0$ visualization takes more than 4 seconds.
-
-We can thus get an approximated visualisation of our object as soon as we run
-the application, allowing for real time interactions with the object (changing
-the visualized value, curvature radius, \ldots). It is also clear on those
-graphs that using a hierarchical decomposition reduces the curvature computation
-time, especially with big radii. For the XYZ-Dragon with $R=20$, it needs almost
-4 seconds to compute the $l_0$ level, whereas using the hierarchical algorithm,
-it only needs 700ms. However, due to the precomputation and current hierarchical
-structure, this algorithm is biased and creates an error (presented in
-Table~\ref{tab:full-res-stat}) that needs to be considered.
-%
-% \begin{figure}
-%   \vspace{-0.35cm}
-%   \begin{center}
-%     {\includegraphics[height=3.5cm]{figs/xyzrgb_dragon-510_R8_mean}}
-%     {\includegraphics[height=3.0cm]{figs/snow_I08iso_233_r20_l0_m3}}
-%   \end{center}
-%   \caption{Illustration of mean curvature computation of two large datasets: XYZ-Dragon (with digital domain of $512^3$) and Snow microstructures ($233^3$).}
-%   \label{fig:adaptive}
-%   \vspace{-0.35cm}
-% \end{figure}
-%
-% Figure~\ref{fig:adaptive} shows curvature computation and exploration in
-% real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
-% Snow microstructures ($233^3$).
-
 \section{Conclusion and Discussion}
@@
 
-In this article, we have proposed a full data parallel framework on GPU
+In this article, we have proposed a fully data parallel framework on GPU
 hardware which combines an adaptive isosurface construction from
@@
 curvature with the hierarchical algorithm, thus massively reducing the number of
-probes. We could also use trexture streaming to compute on the fly on the CPU
+probes. We could also use texture streaming to compute on the fly on the CPU
 the subdivision and stream it to the GPU, allowing dynamic radii change with the
 hierarchical algorithm. Another improvement would be to implement the
-hierarchical pattern presented Figure~\ref{fig:approx}-$b$. This would prevent
-bias addition from adding cells of density 1 but only partly convered by the
+hierarchical pattern presented in Figure\ref{fig:approx2}-$b$. This would prevent
+bias from adding cells of density 1 but only partly convered by the
 ball.

### 2015-10-23 latex/article.tex
Final paper version

@@
 estimation (mean, Gaussian, first and
-second principal directions) on an OctaFlower at level $l_0$ (ground truth).
+second principal directions) on an OctaFlower at level $l_0$ (considered as our ground truth in the following).
 Figure~\ref{fig:full}-bottom shows mean curvature estimation in real-time on a
@@
 l_0$ in Figure~\ref{fig:refine}. We can see that results using approximation
-seems to fastly converge to the ground truth results.
-Table~\ref{tab:full-res-stat} shows numerical results of $L_\infty$ error (worst
-case) and $L_2$ error (mean), as well the number of \emph{mipmap texture}
+seems to quickly converge to the ground truth results.
+Table~\ref{tab:full-res-stat} shows numerical results of $L_\infty$ error (maximal absolute difference for all vertices )
+and $L_2$ error (mean absolute error of all vertices), as well the number of \emph{mipmap texture}
 fetches. We can also see that the number of texel fetch, required to compute the
 curvature, reduces drastically when computing approximations. However, at higher levels, 
-we get consequently much bigger errors. Those levels
+approximation errors become more important. Those levels
 are thus never used in practice, they are presented here to illustrate how the
-refining process converges to the $l_0$ level. We see that levels close to $l_0$
-lead very few error% than $l_0$, 
-and should be considered for exploring our datasets
-in real-time, changing parameters on-the-fly and visualizing dynamic datasets.
+refining process converges to the $l_0$ level. 
+%We see that levels close to $l_0$
+%lead very few error% than $l_0$, 
+%and should be considered for exploring our datasets
+%in real-time, changing parameters on-the-fly and visualizing dynamic datasets.
 
@@
 ensures to fetch data at the center of a mipmap cell. 
-The GPU's interpolation reduces the bias, but it doesn't remove it.
+The GPU interpolation reduces the bias, but it doesn't remove it.
 
@@
 
-Those results were measured on a full resolution triangulation. 
-However, since we compute the curvature of each vertices of the final
-mesh, a highly triangulated object will be much slower to process.
+%Those results were measured on a full resolution triangulation. 
+%However, since we compute the curvature of each vertices of the final
+%mesh, a highly triangulated object will be much slower to process.
 
@@
 When dealing with large datasets, we can not expect real-time curvature tensor
-estimation due to the huge amount of data to process. By computing a
+estimation if we consider the full resolution geometry, due the the huge amount of data process. By computing a
 dynamically refined approximate curvature tensor estimation joined with an
@@
 data to process at each frame. In Figure~\ref{fig:timings}, we compare timings
-(in logarithmic scale) for a triangulation that is dynamically refining according
-to its distance to the camera. We measured those timings using the regular and
+(in logarithmic scale) for a triangulation that is dynamically refined according
+to its distance to the camera. We measured those timings using the multiresolution regular and
 the hierarchical algorithm.
@@
 
-We can first note that the required time for an object to compute ground truth
-curvature is usually as high as the time required to extract the geometry and
+We can first note that the required time for an object to compute the ground truth 
+curvature is usually as high as the time required to extract the geometry and to
 compute all of the above levels. Using approximations is thus mandatory.
-Another advantage with approximation, is that it allows us to get a visualisation of our object as soon as we run
+Another advantage with approximations, is that it allows us to get a visualisation of our object as soon as we run
 the application. This allows for real-time interactions with the object, required in order to change
-the visualized value, curvature radius, \ldots.
-
-It is also visible in Figure~\ref{fig:timings} that using a hierarchical decomposition greatly reduces the curvature computation
+the visualized value, curvature radius, \ldots
+
+It is also visible in Figure~\ref{fig:timings} that a hierarchical decomposition greatly reduces the curvature computation
 time, especially with big radii. 
@@
 %it only needs 700ms. 
-However, due to the precomputation and current hierarchical
+However, due to the precomputation and the current hierarchical
 structure, this algorithm is biased and creates an error (presented in
 Table~\ref{tab:full-res-stat}) that needs to be considered.
-%
-% \begin{figure}
-%   \vspace{-0.35cm}
-%   \begin{center}
-%     {\includegraphics[height=3.5cm]{figs/xyzrgb_dragon-510_R8_mean}}
-%     {\includegraphics[height=3.0cm]{figs/snow_I08iso_233_r20_l0_m3}}
-%   \end{center}
-%   \caption{Illustration of mean curvature computation of two large datasets: XYZ-Dragon (with digital domain of $512^3$) and Snow microstructures ($233^3$).}
-%   \label{fig:adaptive}
-%   \vspace{-0.35cm}
-% \end{figure}
-%
-% Figure~\ref{fig:adaptive} shows curvature computation and exploration in
-% real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
-% Snow microstructures ($233^3$).
 
@@
 
+ \begin{figure}[h!]
+   \vspace{-0.35cm}
+   \begin{center}
+   	 {\includegraphics[width=0.45\textwidth]{figs/snow_r10}}
+     {\includegraphics[width=0.5\textwidth]{figs/snow2_r10}}
+     {\includegraphics[width=0.6\textwidth]{figs/xyzrgb_dragon-510_R8_mean}}
+   \end{center}
+   \caption{\emph{First row}: Mean curvature estimation on Snow Microstructures with a digital domain of $233^3$ and a radius of 10. 
+   (left) Full snow object (right) exploration within the object
+  \emph{Second row:} Mean curvature estimation on XYZ Dragon with a digital domain of $510^3$ and a radius of 8.}
+   \label{fig:adaptive}
+   \vspace{-0.35cm}
+ \end{figure}
+
+ Figure~\ref{fig:adaptive} shows curvature computation and exploration in
+ real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
+ Snow microstructures ($233^3$).
+
 \section{Conclusion and Discussion}
@@
 
-An extension of this framework could be to implement an approximate hierarchical
-algorithm. From there, we could use the dynamic refinement scheme to compute the
-curvature with the hierarchical algorithm, thus massively reducing the number of
-probes. We could also use texture streaming to compute on the fly on the CPU
-the subdivision and stream it to the GPU, allowing dynamic radii change with the
-hierarchical algorithm. Another improvement would be to implement the
-hierarchical pattern presented in Figure\ref{fig:approx2}-$b$. This would prevent
-bias from adding cells of density 1 but only partly convered by the
-ball.
+%An extension of this framework could be to implement an approximate hierarchical
+%algorithm. From there, we could use the dynamic refinement scheme to compute the
+%curvature with the hierarchical algorithm, thus massively reducing the number of
+%probes. We could also use texture streaming to compute on the fly on the CPU
+%the subdivision and stream it to the GPU, allowing dynamic radii change with the
+%hierarchical algorithm. Another improvement would be to implement the
+%hierarchical pattern presented in Figure\ref{fig:approx2}-$b$. This would prevent
+%bias from adding cells of density 1 but only partly convered by the
+%ball.
 

### 2015-10-23 src/cpp/vizo/Parameters.cpp

@@ -43,18 +43,18 @@ Parameters::Parameters()
     g_gui = true;
     g_radial_length = true;
     g_textured_data = false;
-	g_auto_refine = true;
+	g_auto_refine = false;
 	g_k1k2_normals = true;
 	g_curv_dir = 0;
 	g_curv_val = 1;
 	g_lvl = 2;
 
-    g_ground_truth = 2;
+    g_ground_truth = 3;
     
-    g_regular = true;
+    g_regular = false;
     g_radius_show = false;
 
-	g_curvradius = 8.0;
+	g_curvradius = 10.0;
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 	
@@ -62,7 +62,7 @@ Parameters::Parameters()
     g_tessel = 1.0;
     g_isosurface = 0;
 	
-	g_export = true;
+	g_export = false;
 	g_compute_min_max = true;
 
     g_sizetex = 0;

### 2015-10-23 src/cpp/vizo/main.cpp

@@ -338,7 +338,7 @@ public:
 		else 
 			load_viewPoint();
 		
-		min_lvl = (int)ceil(log2(Parameters::getInstance()->g_curvradius)) + 2;
+		min_lvl = 2.0;//(int)ceil(log2(Parameters::getInstance()->g_curvradius)) + 2;
 		Parameters::getInstance()->g_lvl = min_lvl;
 		
 		last_radius = Parameters::getInstance()->g_curvradius;

### 2015-10-26 latex/article.tex
redid last figure

@@
    \begin{center}
-   	 {\includegraphics[width=0.45\textwidth]{figs/snow_r10}}
-     {\includegraphics[width=0.5\textwidth]{figs/snow2_r10}}
-     {\includegraphics[width=0.6\textwidth]{figs/xyzrgb_dragon-510_R8_mean}}
+   	 {\includegraphics[width=0.4\textwidth]{figs/snow_r8}}
+   	 {\includegraphics[width=0.4\textwidth]{figs/xyzrgb_dragon-510_R8_mean}}
+
+     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_min}}
+	 {\includegraphics[width=0.4\textwidth]{figs/dragon_r8}}
+
+     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_max}}
+	 {\includegraphics[width=0.4\textwidth]{figs/dragon_r8_max}}
+
+     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_normales}}
+     {\includegraphics[width=0.4\textwidth]{figs/dragon_r8_normales}}
+
    \end{center}
-   \caption{\emph{First row}: Mean curvature estimation on Snow Microstructures with a digital domain of $233^3$ and a radius of 10. 
-   (left) Full snow object (right) exploration within the object
-  \emph{Second row:} Mean curvature estimation on XYZ Dragon with a digital domain of $510^3$ and a radius of 8.}
+   \caption{\emph{Left column}: Mean curvature, first and second principal directions and normales estimation on Snow Microstructures with a digital domain of $233^3$ and a radius of 8. 
+  \emph{Right column:} Mean curvature, first and second principal directions and normales estimantion on XYZ Dragon with a digital domain of $510^3$ and a radius of 8.}
    \label{fig:adaptive}

### 2015-10-26 src/cpp/vizo/DataLoader.cpp

@@ -321,7 +321,7 @@ void DataRaw::loadFile(char* file)
 		a*= 2;
 	}
 	
-	unsigned long int size_p2 = a;
+	unsigned long int size_p2 = sizex;
 
 	unsigned long int total = size_p2 * size_p2 * size_p2;
     data = (float*) malloc(sizeof(float)*total);

### 2015-10-26 src/cpp/vizo/Parameters.cpp

@@ -43,7 +43,7 @@ Parameters::Parameters()
     g_gui = true;
     g_radial_length = true;
     g_textured_data = false;
-	g_auto_refine = false;
+	g_auto_refine = true;
 	g_k1k2_normals = true;
 	g_curv_dir = 0;
 	g_curv_val = 1;
@@ -52,13 +52,13 @@ Parameters::Parameters()
     g_ground_truth = 3;
     
     g_regular = false;
-    g_radius_show = false;
+    g_radius_show = true;
 
-	g_curvradius = 10.0;
+	g_curvradius = 8.0;
     g_curvmin = -0.5;
     g_curvmax = 0.5;
 	
-    g_scale = 10;
+    g_scale = 10.0;
     g_tessel = 1.0;
     g_isosurface = 0;
 	

### 2015-10-26 src/cpp/vizo/main.cpp

@@ -20,8 +20,7 @@
 
 #include <cmath>
 #include <string>
-
-#define CAM_SPEED 20
+#define CAM_SPEED CAM_SPEED_MAX / 20.0
 #define CAM_SPEED_MAX Parameters::getInstance()->g_geometry.scale[0] / 5.0
 #define CAM_ROTATE 0.1f
 #define CAM_ROTATE_MAX 1.0f
@@ -338,7 +337,7 @@ public:
 		else 
 			load_viewPoint();
 		
-		min_lvl = 2.0;//(int)ceil(log2(Parameters::getInstance()->g_curvradius)) + 2;
+		min_lvl = (int)ceil(log2(Parameters::getInstance()->g_curvradius));
 		Parameters::getInstance()->g_lvl = min_lvl;
 		
 		last_radius = Parameters::getInstance()->g_curvradius;
@@ -382,10 +381,10 @@ public:
 				Parameters::getInstance()->g_lvl =  min_lvl;
 				Parameters::getInstance()->g_compute_min_max = true;
 			}
-			else if (Parameters::getInstance()->g_auto_refine)// && fps > 30 && Parameters::getInstance()->g_lvl > 0)
+			else if (Parameters::getInstance()->g_auto_refine && fps > 30 && Parameters::getInstance()->g_lvl > 0)
 			{
-				if (Parameters::getInstance()->g_lvl == 0)
-					exit(0);
+				//if (Parameters::getInstance()->g_lvl == 0)
+				//	exit(0);
 				Parameters::getInstance()->g_lvl -= 1;
 				Parameters::getInstance()->g_compute_min_max = true;
 			}
@@ -835,6 +834,21 @@ public:
 			Parameters::getInstance()->g_export = true;
 			key('e') = 0;
 		}
+		
+		if (key('l'))
+		{
+			Parameters::getInstance()->g_curv_dir = ((int)Parameters::getInstance()->g_curv_dir+1)%5;
+			
+			if (Parameters::getInstance()->g_curv_dir == 3)
+				Parameters::getInstance()->g_curv_dir = 4;
+			
+			if (Parameters::getInstance()->g_curv_dir != 0)
+				Parameters::getInstance()->g_curv_val=0;
+			else
+				Parameters::getInstance()->g_curv_val=1;
+			
+			key('l') = 0;
+		}
 	}
     
 	void testMovement()
@@ -956,6 +970,7 @@ public:
 
 		if (animate)
[…]

### 2015-10-26 src/gkit/gKit/Widgets/nvSDLFont.h

@@ -23,7 +23,7 @@ class SdlFont : public UIFont
 public:
     //~ SdlFont( const char *filename= "verdana.ttf", const int size= 14 );
     //~ SdlFont( const char *filename= "ubuntu.ttf", const int size= 16 );
-    SdlFont( const char *filename= "droid.ttf", const int size= 11 );
+    SdlFont( const char *filename= "droid.ttf", const int size= 12 );
     ~SdlFont( );
     
     int init( );

### 2015-10-26 latex/article.tex
typos

@@
    \end{center}
-   \caption{\emph{Left column}: Mean curvature, first and second principal directions and normales estimation on Snow Microstructures with a digital domain of $233^3$ and a radius of 8. 
-  \emph{Right column:} Mean curvature, first and second principal directions and normales estimantion on XYZ Dragon with a digital domain of $510^3$ and a radius of 8.}
+   \caption{\emph{Left column}: Mean curvature, first and second
+     principal directions and normal vector field estimation on Snow Microstructures ($233^3$ and  $R=8$). 
+  \emph{Right column:} Mean curvature, first and second principal
+  directions and normal vector field estimantion on XYZ Dragon($510^3$
+  and $R=8$). Normal vectors are colored with a mapping their
+  component to RGB color space.}
    \label{fig:adaptive}

### 2015-10-27 latex/article.tex
typo

@@
   \emph{Right column:} Mean curvature, first and second principal
-  directions and normal vector field estimantion on XYZ Dragon($510^3$
-  and $R=8$). Normal vectors are colored with a mapping their
+  directions and normal vector field estimation on XYZ-Dragon ($510^3$
+  and $R=8$). Normal vectors are colored with a mapping of their
   component to RGB color space.}

### 2015-10-27 src/cpp/vizo/Curvature.cpp
removed the type argument (the useless 1)

@@ -1,473 +1,0 @@
-#include "Curvature.h"
-#include <boost/concept_check.hpp>
-
-#include "GL/GLQuery.h"
-#include "GL/GLTexture.h"
-#include "GL/GLVertexArray.h"
-#include "GL/GLBuffer.h"
-#include "ProgramManager.h"
-
-#include "ImageIO.h"
-#include "Image.h"
-
-void configure_curv(GLuint program, GLuint first_loc)
-{
-	/*
-	LOCATION_SHADING_SIZE,
-	LOCATION_SHADING_DENSITY,
-	LOCATION_SHADING_VIEWPORT,
-	LOCATION_SHADING_TAN_FOVY,
-	LOCATION_SHADING_SCALE,
-	LOCATION_SHADING_WIREFRAME,
-	LOCATION_SHADING_CAMERA,
-	LOCATION_SHADING_CURVRADIUS,
-	LOCATION_SHADING_CURVMIN,
-	LOCATION_SHADING_CURVMAX,
-	LOCATION_SHADING_GROUNDTRUTH,
-	LOCATION_SHADING_SIZETEX,
-	*/
-	glProgramUniform3f (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc],//LOCATION_SHADING_SIZE+first_loc],
-			Parameters::getInstance()->g_geometry.scale[0], Parameters::getInstance()->g_geometry.scale[1], Parameters::getInstance()->g_geometry.scale[2]);
-	glProgramUniform1i (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+1],
-			TEXTURE_DENSITY);
-	glProgramUniform2f (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+2],
-			Parameters::getInstance()->g_window.width, Parameters::getInstance()->g_window.height);
-
-	glProgramUniform1f (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+3],
-			tanf (Parameters::getInstance()->g_camera.fovy / 360.f * 3.14159f));
-	glProgramUniform1f(program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+4],
-			Parameters::getInstance()->g_scale);
-
-	glProgramUniform1i (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+5],
-			Parameters::getInstance()->g_solid_wireframe);
-
-	glProgramUniform3f (program,
[…]

### 2015-10-27 src/cpp/vizo/Parameters.cpp

@@ -1,78 +1,0 @@
-#include "Parameters.h"
-
-#include <stdlib.h>
-
-Parameters* Parameters::instance = NULL;
-
-Parameters::Parameters()
-{
-    g_window.width = 1500;
-    g_window.height = 1000;
-    g_window.major = 3;
-    g_window.minor = 2;
-    g_window.msaa_factor = 1; // multisampling level
-    g_window.msaa_fixedsamplelocations = true; // fixed sample locations for msaa
-
-    g_framebuffer_region.p = gk::TVec2<float>(0, 0);
-    g_framebuffer_region.mag = 1;
-
-    g_capture.enabled = false;
-    g_capture.count = 0;
-    g_capture.frame = 0;
-
-    g_geometry.affine.identity();
-    g_geometry.pingpong = 1;
-    g_geometry.freeze = false;
-    g_geometry.scale[0] = 512;
-    g_geometry.scale[1] = 512;
-    g_geometry.scale[2] = 512;
-
-    g_camera.fovy = 45.f;
-    g_camera.znear = 0.01f;
-    g_camera.zfar = 10000.f;
-    g_camera.exposure = 3.f;
-
-    g_mouse = MOUSE_GEOMETRY;
-    
-    g_draw_cells = false;
-    g_draw_triangles = true;
-    g_culling = true;
-    g_fromtexture = true;
-    g_solid_wireframe = true;
-    g_controls = false;
-    g_gui = true;
-    g_radial_length = true;
-    g_textured_data = false;
-	g_auto_refine = true;
-	g_k1k2_normals = true;
-	g_curv_dir = 0;
-	g_curv_val = 1;
-	g_lvl = 2;
-
-    g_ground_truth = 3;
-    
-    g_regular = false;
-    g_radius_show = true;
-
-	g_curvradius = 8.0;
-    g_curvmin = -0.5;
-    g_curvmax = 0.5;
-	
-    g_scale = 10.0;
-    g_tessel = 1.0;
-    g_isosurface = 0;
-	
-	g_export = false;
-	g_compute_min_max = true;
-
-    g_sizetex = 0;
-    
-    g_time_elapsed = 0;
-}
-
-Parameters* Parameters::getInstance()
-{
-    if (instance == NULL)
-        instance = new Parameters();
-    return instance;
-}

### 2015-10-27 src/cpp/vizo/Triangulation.cpp

@@ -1,58 +1,0 @@
-#include "Triangulation.h"
-
-#include "GL/GLQuery.h"
-#include "GL/GLTexture.h"
-#include "GL/GLVertexArray.h"
-#include "GL/GLBuffer.h"
-#include "ProgramManager.h"
-
-void Triangulation::loadVA()
-{
-	//Drawing the octree
-        //As the buffers pingpong between LoD and Culling, it requires two VAO to pingpong with
-	glGenVertexArrays (1, Parameters::getInstance()->g_vertex_arrays + VERTEX_ARRAY_OCTREE_RENDER1);
-	glBindVertexArray(Parameters::getInstance()->g_vertex_arrays[VERTEX_ARRAY_OCTREE_RENDER1]);
-	glEnableVertexAttribArray(0);
-	glEnableVertexAttribArray(1);
-	glBindBuffer(GL_ARRAY_BUFFER, Parameters::getInstance()->g_buffers[BUFFER_LTREE_DATA1]);
-	glVertexAttribIPointer(0, 4, GL_UNSIGNED_INT, 0, 0);
-	glVertexAttribDivisor(0, 1);
-	glBindBuffer (GL_ARRAY_BUFFER, Parameters::getInstance()->g_buffers[BUFFER_VERTEX_CUBE]);
-	glVertexAttribPointer (1, 3, GL_FLOAT, 0, 0, 0);
-	glBindBuffer (GL_ELEMENT_ARRAY_BUFFER, Parameters::getInstance()->g_buffers[BUFFER_INDEX_CUBE]);
-        glBindBuffer (GL_ARRAY_BUFFER, Parameters::getInstance()->g_buffers[BUFFER_VERTEX_CUBE]);
-	glVertexAttribPointer (1, 3, GL_FLOAT, 0, 0, 0);
-	glBindVertexArray(0);
-	
-	glGenVertexArrays (1, Parameters::getInstance()->g_vertex_arrays + VERTEX_ARRAY_OCTREE_RENDER2);
-	glBindVertexArray(Parameters::getInstance()->g_vertex_arrays[VERTEX_ARRAY_OCTREE_RENDER2]);
-	glEnableVertexAttribArray(0);
-	glEnableVertexAttribArray(1);
-	glBindBuffer(GL_ARRAY_BUFFER, Parameters::getInstance()->g_buffers[BUFFER_LTREE_DATA2]);
[…]

### 2015-10-27 src/cpp/vizo/TriangulationTables.h

@@ -1,1027 +1,0 @@
-//================================================================================
-//
-// The Transvoxel Algorithm look-up tables
-//
-// The following data originates from Eric Lengyel's Transvoxel Algorithm.
-// http://www.terathon.com/voxels/
-//
-// The data in this file may be freely used in implementations of the Transvoxel
-// Algorithm. If you do use this data, or any transformation of it, in your own
-// projects, commercial or otherwise, please give credit by indicating in your
-// source code that the data is part of the author's implementation of the
-// Transvoxel Algorithm and that it came from the web address given above.
-// (Simply copying and pasting the two lines of the previous paragraph would be
-// perfect.) If you distribute a commercial product with source code included,
-// then the credit in the source code is required.
-//
-// If you distribute any kind of product that uses this data, a credit visible to
-// the end-user would be appreciated, but it is not required. However, you may
-// not claim that the entire implementation of the Transvoxel Algorithm is your
-// own if you use the data in this file or any transformation of it.
-//
-// The format of the data in this file is described in the dissertation "Voxel-
-// Based Terrain for Real-Time Virtual Simulations", available at the web page
-// given above. References to sections and figures below pertain to that paper.
-//
-//================================================================================
-
-
-// The RegularCellData structure holds information about the triangulation
[…]

### 2015-10-27 src/cpp/vizo/Utils.cpp

@@ -1,292 +1,0 @@
-#include "Utils.h"
-
-#include <fstream>
-
-void rotateLocal_noTranslation(gk::Transform& m, gk::Vector axis, float angle)
-{
-	float tr1[4][4] = { {0} };
-	for(int i=0; i<3; i++)
-	for(int j=0; j<4; j++)
-	tr1[i][j] = m.matrix().m[i][j];
-	tr1[3][3] = 1;
-
-	gk::Transform tmp(tr1);
-	tmp = gk::Rotate(angle, axis) * tmp;
-	for(int i=0; i<3; i++)
-	for(int j=0; j<4; j++)
-		tr1[i][j] = tmp.matrix().m[i][j];
-	tr1[3][3] = 1;
-	tr1[0][3] = m.matrix().m[0][3];
-	tr1[1][3] = m.matrix().m[1][3];
-	tr1[2][3] = m.matrix().m[2][3];
-
-	m = gk::Transform(tr1);
-}
-void rotateGlobal_noTranslation(gk::Transform& m, gk::Vector axis, float angle)
-{
-	float tr1[4][4] = { {0} };
-	for(int i=0; i<3; i++)
-	for(int j=0; j<4; j++)
-	tr1[i][j] = m.matrix().m[i][j];
-	tr1[3][3] = 1;
-
-	gk::Transform tmp(tr1);
-	tmp = tmp * gk::Rotate(angle, axis);
-	for(int i=0; i<3; i++)
-	for(int j=0; j<4; j++)
-	tr1[i][j] = tmp.matrix().m[i][j];
-	tr1[3][3] = 1;
-	tr1[0][3] = m.matrix().m[0][3];
-	tr1[1][3] = m.matrix().m[1][3];
-	tr1[2][3] = m.matrix().m[2][3];
-
-	m = gk::Transform(tr1);
-}
-
-void normalizePlane(float* plane)
-{
-	float lenght = sqrt(plane[0]*plane[0] + plane[1]*plane[1] + plane[2]*plane[2] );
-	plane[0] *= lenght;
-	plane[1] *= lenght;
-	plane[2] *= lenght;
-	plane[3] *= lenght;
-}
-void buildFrustum(float* frustum, gk::Matrix4x4 projection)
-{
-	//left
-	frustum[0] = projection.m[0][3] + projection.m[0][0];
-	frustum[1] = projection.m[1][3] + projection.m[1][0];
[…]

### 2015-10-27 src/cpp/vizo_light/Curvature.cpp

@@ -1,433 +1,0 @@
-#include "Curvature.h"
-#include <boost/concept_check.hpp>
-
-#include "GL/GLQuery.h"
-#include "GL/GLTexture.h"
-#include "GL/GLVertexArray.h"
-#include "GL/GLBuffer.h"
-#include "ProgramManager.h"
-
-#include "ImageIO.h"
-#include "Image.h"
-
-
-void configure_curv(GLuint program, GLuint first_loc)
-{
-	/*
-	LOCATION_SHADING_SIZE,
-	LOCATION_SHADING_DENSITY,
-	LOCATION_SHADING_VIEWPORT,
-	LOCATION_SHADING_TAN_FOVY,
-	LOCATION_SHADING_SCALE,
-	LOCATION_SHADING_WIREFRAME,
-	LOCATION_SHADING_CAMERA,
-	LOCATION_SHADING_CURVRADIUS,
-	LOCATION_SHADING_CURVMIN,
-	LOCATION_SHADING_CURVMAX,
-	LOCATION_SHADING_GROUNDTRUTH,
-	LOCATION_SHADING_SIZETEX,
-	*/
-	glProgramUniform3f (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc],//LOCATION_SHADING_SIZE+first_loc],
-			Parameters::getInstance()->g_geometry.scale[0], Parameters::getInstance()->g_geometry.scale[1], Parameters::getInstance()->g_geometry.scale[2]);
-	glProgramUniform1i (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+1],
-			TEXTURE_DENSITY);
-	glProgramUniform2f (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+2],
-			Parameters::getInstance()->g_window.width, Parameters::getInstance()->g_window.height);
-
-	glProgramUniform1f (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+3],
-			tanf (Parameters::getInstance()->g_camera.fovy / 360.f * 3.14159f));
-	glProgramUniform1f(program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+4],
-			Parameters::getInstance()->g_scale);
-
-	glProgramUniform1i (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+5],
-			Parameters::getInstance()->g_solid_wireframe);
-
-	glProgramUniform3f (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+6],
[…]

### 2015-10-27 src/cpp/vizo_light/Definitions.h

@@ -1,279 +1,0 @@
-#ifndef DEFINITIONS_H_
-#define DEFINITIONS_H_
-
-#include "Vec.h"
-#include "Transform.h"
-
-// window params
-struct window_t {
-    int width,
-        height,
-        major,
-        minor;
-    int msaa_factor, // multisampling level
-        msaa_fixedsamplelocations; // fixed sample locations for msaa
-};
-
-// framebuffer region params
-struct framebuffer_region_t {
-    gk::TVec2<float> p; // region center
-    float mag; // magnification factor
-};
-
-// screen recording params
-struct capture_t {
-    bool enabled;
-    int frame, // frame id
-        count; // capture id
-};
-
-// geometry params
-struct geometry_t {
-    gk::Transform affine;
-    //const char *dmap;
-    int pingpong; // ping pong variable for quadtree
-    bool freeze;   // freeze updates
-    float scale[3];  // sceen scale
-        //dscale; // displacement scale
-};
-
-struct shading_t {
-    int mode,
-        wire;
-    unsigned char 
-		tr_colour[4],
-		colour[4],
-		wire_colour[4];
-};
-
-// camera params
-struct camera_t {
-    float fovy,
-            znear,
-            zfar,
-            exposure;
-    gk::Vector pos;
-};
-
-// transforms
-struct transforms_t {
-    gk::Matrix4x4
-            modelview,
-            projection,
-            modelviewprojection,
-            invmodelview;
-};
-
[…]

### 2015-10-27 src/cpp/vizo_light/PrimitiveDraw.cpp

@@ -1,148 +1,0 @@
-#include "PrimitiveDraw.h"
-
-#include "GL/GLQuery.h"
-#include "GL/GLTexture.h"
-#include "GL/GLVertexArray.h"
-#include "GL/GLBuffer.h"
-#include "ProgramManager.h"
-#include "Parameters.h"
-
-void SphereDraw::configureProgram()
-{
-	glProgramUniform1f (Parameters::getInstance()->g_programs[PROGRAM_SPHEREDRAW],
-                    Parameters::getInstance()->g_uniform_locations[LOCATION_SPHEREDRAW_CURVRADIUS],
-                    Parameters::getInstance()->g_curvradius);
-	glProgramUniform1f(Parameters::getInstance()->g_programs[PROGRAM_SPHEREDRAW],
-                    Parameters::getInstance()->g_uniform_locations[LOCATION_SPHEREDRAW_SIZETEX],
-                    Parameters::getInstance()->g_sizetex);
-	glProgramUniform3f (Parameters::getInstance()->g_programs[PROGRAM_SPHEREDRAW],
-                    Parameters::getInstance()->g_uniform_locations[LOCATION_SPHEREDRAW_SCENE_SIZE],
-                    Parameters::getInstance()->g_geometry.scale[0], Parameters::getInstance()->g_geometry.scale[1], Parameters::getInstance()->g_geometry.scale[2]);
-}
-
-void SphereDraw::loadProgram()
-{
-	GLuint *program = &Parameters::getInstance()->g_programs[PROGRAM_SPHEREDRAW];
-    
-    fprintf (stderr, "loading sphere drawing program... "); fflush (stderr);
-    gk::GLCompiler& c = gk::loadProgram( SHADER_PATH("drawsphere.glsl"));
-    c.include(SHADER_PATH("noise.glsl") );
-    c.include(SHADER_PATH("octree_common.glsl") );
-    c.include(SHADER_PATH("ltree.glsl") );
-    GLProgram* tmp = c.make();
-    if (tmp->errors)
-        exit(-1);
-    *program = tmp->name;
-
-    Parameters::getInstance()->g_uniform_locations[LOCATION_SPHEREDRAW_SCENE_SIZE] =
[…]

### 2015-10-27 src/cpp/vizo_light/RegularTriangulation.cpp

@@ -1,256 +1,0 @@
-#include "Triangulation.h"
-
-#include "GL/GLQuery.h"
-#include "GL/GLTexture.h"
-#include "GL/GLVertexArray.h"
-#include "GL/GLBuffer.h"
-#include "ProgramManager.h"
-
-void RegularTriangulation::loadTables()
-{
-	//Code to Class (256 -> 18)
-	glGenTextures(1, &Parameters::getInstance()->g_textures[TEXTURE_CODE_CLASS]);
-	glBindTexture(GL_TEXTURE_1D, Parameters::getInstance()->g_textures[TEXTURE_CODE_CLASS]);
-
-	std::vector<char> table_id(256, 0);
-	
-	for(int i=0; i<256; i++)
-		table_id[i] = regularCellClass[i];
-	
-	glTexImage1D(GL_TEXTURE_1D, 0, GL_R8UI, 256, 0, GL_RED_INTEGER, GL_UNSIGNED_BYTE, &(table_id[0]));
-
-	glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MIN_FILTER, GL_NEAREST);
-	glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MAG_FILTER, GL_NEAREST);
-	glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_WRAP_S, GL_CLAMP_TO_EDGE);
-	glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_WRAP_T, GL_CLAMP_TO_EDGE);
-	glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_WRAP_R, GL_CLAMP_TO_EDGE);
-	
-	glBindTexture(GL_TEXTURE_1D, 0);
-	
-	
-	//Code to vertices
-	glGenTextures(1, &Parameters::getInstance()->g_textures[TEXTURE_CODE_VERTICES]);	
-	glBindTexture(GL_TEXTURE_2D, Parameters::getInstance()->g_textures[TEXTURE_CODE_VERTICES]);
-
-	std::vector<unsigned short int> table_vertices(256*4*3, 0);
-	
-	for(int i=0; i<256*3; i+=3)
-	{
-		int class_code = regularCellClass[i/3];
-		int nb_vertices = (regularCellData[class_code].geometryCounts >> 4);
-
-		for(int v=0; v<nb_vertices; v++)
-		{
[…]

### 2015-10-27 src/cpp/vizo_light/TransitionTriangulation.cpp

@@ -1,247 +1,0 @@
-#include "Triangulation.h"
-
-#include "GL/GLQuery.h"
-#include "GL/GLTexture.h"
-#include "GL/GLVertexArray.h"
-#include "GL/GLBuffer.h"
-#include "ProgramManager.h"
-
-void TransitionTriangulation::loadTables()
-{
-	glGenTextures(1, &Parameters::getInstance()->g_textures[TEXTURE_CODE_CLASS_TR]);
-	glBindTexture(GL_TEXTURE_1D, Parameters::getInstance()->g_textures[TEXTURE_CODE_CLASS_TR]);
-
-	std::vector<unsigned char> table_id_tr(512, 0);
-	
-	for(int i=0; i<512; i++)
-		table_id_tr[i] = transitionCellClass[i];
-	
-	glTexImage1D(GL_TEXTURE_1D, 0, GL_R8UI, 512, 0, GL_RED_INTEGER, GL_UNSIGNED_BYTE, &(table_id_tr[0]));
-
-	glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MIN_FILTER, GL_NEAREST);
-	glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MAG_FILTER, GL_NEAREST);
-	glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_WRAP_S, GL_CLAMP_TO_EDGE);
-	glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_WRAP_T, GL_CLAMP_TO_EDGE);
-	glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_WRAP_R, GL_CLAMP_TO_EDGE);
-	
-	glBindTexture(GL_TEXTURE_1D, 0);
-
-	//Transition Code to vertices
-	glGenTextures(1, &Parameters::getInstance()->g_textures[TEXTURE_CODE_VERTICES_TR]);
-	glBindTexture(GL_TEXTURE_2D, Parameters::getInstance()->g_textures[TEXTURE_CODE_VERTICES_TR]);
-
-	std::vector<unsigned short int> table_vertices_tr(512*4*3, 0);
-	
-	for(int i=0; i<512*3; i+=3)
-	{
-		unsigned char class_code = transitionCellClass[i/3];
-		class_code &= 0x7F;
-		int nb_vertices = (transitionCellData[class_code].geometryCounts >> 4);
-
[…]

### 2015-10-30 tools/comparison/comparison.cpp
Might have forgotten the code in tools while licensing everything ... ^^" But it's fixed now :)

@@ -1,3 +1,28 @@
+/*
+ * Copyright 2015 
+ * Hélène Perrier <helene.perrier@liris.cnrs.fr>
+ * Jérémy Levallois <jeremy.levallois@liris.cnrs.fr>
+ * David Coeurjolly <david.coeurjolly@liris.cnrs.fr>
+ * Jacques-Olivier Lachaud <jacques-olivier.lachaud@univ-savoie.fr>
+ * Jean-Philippe Farrugia <jean-philippe.farrugia@liris.cnrs.fr>
+ * Jean-Claude Iehl <jean-claude.iehl@liris.cnrs.fr>
+ * 
+ * This file is part of ICTV.
+ * 
+ * ICTV is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 3 of the License, or
+ * (at your option) any later version.
+ * 
+ * ICTV is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ * 
+ * You should have received a copy of the GNU General Public License
+ * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
+ */
+
 #include <iostream>
 #include <cstdlib>
 #include <boost/algorithm/string.hpp>

### 2015-10-30 tools/comparison/helpers.h

@@ -1,3 +1,28 @@
+/*
+ * Copyright 2015 
+ * Hélène Perrier <helene.perrier@liris.cnrs.fr>
+ * Jérémy Levallois <jeremy.levallois@liris.cnrs.fr>
+ * David Coeurjolly <david.coeurjolly@liris.cnrs.fr>
+ * Jacques-Olivier Lachaud <jacques-olivier.lachaud@univ-savoie.fr>
+ * Jean-Philippe Farrugia <jean-philippe.farrugia@liris.cnrs.fr>
+ * Jean-Claude Iehl <jean-claude.iehl@liris.cnrs.fr>
+ * 
+ * This file is part of ICTV.
+ * 
+ * ICTV is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 3 of the License, or
+ * (at your option) any later version.
+ * 
+ * ICTV is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ * 
+ * You should have received a copy of the GNU General Public License
+ * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
+ */
+
 #pragma once
 
 #if defined(helpers_RECURSES)

### 2015-10-30 tools/hierarchy/hierarchy.c

@@ -1,3 +1,29 @@
+/*
+ * Copyright 2015 
+ * Hélène Perrier <helene.perrier@liris.cnrs.fr>
+ * Jérémy Levallois <jeremy.levallois@liris.cnrs.fr>
+ * David Coeurjolly <david.coeurjolly@liris.cnrs.fr>
+ * Jacques-Olivier Lachaud <jacques-olivier.lachaud@univ-savoie.fr>
+ * Jean-Philippe Farrugia <jean-philippe.farrugia@liris.cnrs.fr>
+ * Jean-Claude Iehl <jean-claude.iehl@liris.cnrs.fr>
+ * 
+ * This file is part of ICTV.
+ * 
+ * ICTV is free software: you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation, either version 3 of the License, or
+ * (at your option) any later version.
+ * 
+ * ICTV is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ * 
+ * You should have received a copy of the GNU General Public License
+ * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
+ */
+
+
 // Author: Jacques-Olivier Lachaud
 // gcc -O3 -std=c99 -Wall -pedantic hierarchy.c -lm -o hierarchy
 #include <stdlib.h>

### 2015-10-30 src/cpp/DataLoader.cpp
removed Eric's files loading

@@ -290,7 +290,7 @@ unsigned long int f(unsigned int sf, unsigned long int x, unsigned long int y, u
 	return ((z*sf) + x)*sf + y;
 }
 
-//Files provided by Eric
+/*//Files provided by Eric
 void DataTerrain::loadFile(char* file)
 {
 	printf("Loading Eric's file as float %s ... ", file); fflush(stdout);
@@ -327,7 +327,7 @@ void DataTerrain::loadFile(char* file)
 		data[i++] = ((float)data_char[f(sf, x, y, z)] / 255.0) - 0.5;
 
 	printf("Complete\n");
-}
+}*/
 
 //Files .raw provided by http://www.tc18.org/code_data_set/3D_images.php
 void DataRaw::loadFile(char* file)
@@ -341,13 +341,19 @@ void DataRaw::loadFile(char* file)
 		return;
 	}
 	
+	bool padding = true; //if set to true, the texture is padded until it has the size of the next power of 2 resolution
+	
 	unsigned long int a = 1;
 	while(a < sizex)
 	{
 		a*= 2;
 	}
 	
-	unsigned long int size_p2 = sizex;
+	unsigned long int size_p2;
+	if (padding)
+		size_p2 = a;
+	else
+		size_p2 = sizex;
 
 	unsigned long int total = size_p2 * size_p2 * size_p2;
     data = (float*) malloc(sizeof(float)*total);

### 2015-10-30 src/cpp/DataLoader.h

@@ -56,13 +56,13 @@ public:
 	virtual void releaseData() { free(data); }
 };
 
-class DataTerrain : public DataLoader
+/*class DataTerrain : public DataLoader
 {
 public:	
 	virtual float* get32BData() { return data; }
 	virtual unsigned char* get8BData() { return data_char; }
 	virtual void loadFile(char* file);
-};
+};*/
 
 class DataRaw : public DataLoader
 {

### 2015-10-30 src/cpp/DataLoader.cpp
removed useless textures

@@ -71,6 +71,7 @@ void DataLoader::loadData8BGpu()
 	glBindTexture(GL_TEXTURE_3D, 0);
 }
 
+/*
 void loadNxtMipmap(int size, float* texture, float** miptexture)
 {
 	int sizemip = size/2;
@@ -233,11 +234,6 @@ void DataLoader::loadxyz()
 		float norm_j = j;
 		float norm_k = k;
 		
-		/*
-		mmt[nb*3] = norm_i;
-		mmt[nb*3 + 1] = norm_j;
-		mmt[nb*3 + 2] = norm_k;
-		*/
 		mmt[nb*3] = norm_i*data[nb];
 		mmt[nb*3 + 1] = norm_j*data[nb];
 		mmt[nb*3 + 2] = norm_k*data[nb];
@@ -283,13 +279,14 @@ void DataLoader::loadxyz()
 	
 	//free(mmt);
 }
+*/
 
-
+/*
 unsigned long int f(unsigned int sf, unsigned long int x, unsigned long int y, unsigned long int z)
 {
 	return ((z*sf) + x)*sf + y;
 }
-
+*/
 /*//Files provided by Eric
 void DataTerrain::loadFile(char* file)
 {

### 2015-10-30 src/cpp/DataLoader.h

@@ -49,9 +49,9 @@ public:
 	
 	virtual void loadData32BGpu();
 	virtual void loadData8BGpu();
-	virtual void loadx2y2z2();
+	/*virtual void loadx2y2z2();
 	virtual void loadxyyzxz();
-	virtual void loadxyz();
+	virtual void loadxyz();*/
 	
 	virtual void releaseData() { free(data); }
 };

### 2015-10-30 src/cpp/Definitions.h

@@ -126,17 +126,17 @@ enum {SHADING_COLOUR, SHADING_NORMAL, SHADING_TEXCOORDS, SHADING_LAMBERT};
 // textures
 enum {
 		TEXTURE_RGBA, TEXTURE_Z, 
-		TEXTURE_COLOR_X,
+		/*TEXTURE_COLOR_X,
 		TEXTURE_COLOR_Y,
 		TEXTURE_COLOR_Z,
 		TEXTURE_BUMP_X,
 		TEXTURE_BUMP_Y,
 		TEXTURE_BUMP_Z,
-		TEXTURE_ENVMAP,
+		TEXTURE_ENVMAP,*/
 		TEXTURE_DENSITY, 
-		TEXTURE_X2Y2Z2,
+		/*TEXTURE_X2Y2Z2,
 		TEXTURE_XY_YZ_XZ,
-		TEXTURE_XYZ,
+		TEXTURE_XYZ,*/
 		TEXTURE_CODE_CLASS, 
 		TEXTURE_CODE_VERTICES, 
 		TEXTURE_CLASS_TRIANGLES, 

### 2015-10-30 latex/article.tex
Working on 1 and 2.

@@
 
+\newcommand{\Jaco}[1]{{\color{orange}#1}}
+
 \graphicspath{{./figs/}}
@@
   to efficiently explore the curvature tensor on the boundary of
-  potentially large and dynamic digital objects (mean and gaussian curvature,
+  potentially large and dynamic digital objects (mean and gaussian curvatures,
   principal curvatures, principal directions and normal vector
@@
   interactively different radii and thus select the appropriate scale
-  to which the computation is performed and visualized.
+  \Jaco{at} which the computation is performed and visualized.
 
@@
 most curvature estimators require a parameter fixing the scale
-to which the computation is performed. For short, such parameter
-(integration radius, convolution kernel size, \ldots) specifies noise
-level on the object surface. As a consequence, exploring interactively
+\Jaco{at} which the computation is performed. For short, such parameter
+(integration radius, convolution kernel size, \ldots) specifies \Jaco{a scale for analyzing the object surface, and is naturally related to the amount of perturbation on input data}.
+As a consequence, exploring interactively
 different values of such parameter is mandatory.
@@
 
-\sloppy\noindent\textbf{Related works}\quad Extracting and Visualizing
+\sloppy\noindent\textbf{Related works}\quad Extracting and visualizing
 isosurface on volumetric data has been widely investigated since the
@@
 adaptive approaches have been proposed in order to optimize the
-triangular mesh resolution to the object geometry or depending on the
-viewpoint. In this topic, many solutions have been developed in
+\Jaco{triangulated} mesh resolution \Jaco{according to the object geometry or the
+viewpoint}. In this topic, many solutions have been developed in
 Computer
@@
 The method developed by \textsc{Lengyel} \textit{et al.}
-\cite{lengyel2010voxel} is the best suited to our needs.
+\cite{lengyel2010voxel} \Jaco{suits best our needs}.
 %However, it
@@
 It combines an octree space partitioning with new Marching Cubes configurations
-to generate adaptive meshes on the CPU from
+to generate adaptive meshes on CPU from
 %, but was only developed on the CPU to visualize
 static or near static data.
-In this paper we propose a full GPU pipeline
+We propose here a full GPU pipeline
 %inspired from this method.
-inspired from this method,
+inspired \Jaco{by} this method,
 %using a GPU-friendly Lod criterion
-to maintain a view dependent triangulation.
+\Jaco{that maintains} a view dependent triangulation.
 %It leaves the CPU free for other tasks and avoids synchronization with the GPU.
@@
 %Our high framerate allows this method to run in real-time on fully dynamic data.
-Our high framerate allows to visualize fully dynamic data in real-time.
+Our high framerate allows \Jaco{us} to inspect dynamic 3D data in real-time.
 %The triangulation is controlled by a GPU LoD criterion
@@
 surfaces. Such approaches are based on an integration principle using
-a spherical kernel of a given radius. Additionally, authors have
+a \Jaco{ball} kernel of a given radius. Additionally, authors have
 demonstrated that these estimators have multigrid convergence
 properties. In this article, we also propose an efficient GPU
-implementation of such estimators to visualize%, in real-time,
-such curvature maps in real-time and %allowing us
-to interactively change the %explore different
-value of the spherical kernel radius.
+implementation of such estimators to visualize
+%, in real-time,
+such curvature \Jaco{fields} in real-time and
+%allowing us
+to interactively change the
+%explore different
+value of the kernel radius.
 
@@
 $\CurvH{R}$ and the 3D digital mean curvature estimator $\MeanCurvH{R}$ based on
-the digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ with
-$\MCard(Y)$, the number of digital points of the intersection between a ball
-$\Ball{R/h}{\vx/h}$ of digital radius $R/h$ and $\DigShape$ (we denote such
-quantity $\AreaC(Y,h)$ in dimension 2):
+the digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ \Jaco{(we denote such
+quantity $\AreaC(Y,h)$ in dimension 2):}
+%% Redite
+%% \Jaco{Given some point $\vx \in \R^d$, the set $Y$ is the digital intersection of $\DigShape$ with the ball of radius $R/h$ and center $\vx/h$.}
+%% where $Y$ is the intersection of $\DigShape$ with a ball
+%% $\Ball{R/h}{\vx/h}$ with $\MCard(Y)$, the number of digital points of
+%% the intersection between a ball $\Ball{R/h}{\vx/h}$ of digital radius
+%% $R/h$ and $\DigShape$ (we denote such quantity $\AreaC(Y,h)$ in
+%% dimension 2):
 %
@@
 Additionally, eigenvectors associated to $\hat{\lambda}_1$ and
-$\hat{\lambda}_2$ of the covariance matrix correspond to principal curvature
-directions $\PrincDirH{1}{R}$ and $\PrincDirH{2}{R}$. The smallest eigenvector
-corresponds to the normal direction $\NormalDirH{R}$ at $\vx$. Convergence
-results can be found in \cite{ChapterIICurvature}.%%% Changer avec le chapitre de Jaco à un moment
+$\hat{\lambda}_2$ of the covariance matrix \Jaco{are} principal
+curvature direction \Jaco{estimators} $\PrincDirH{1}{R}$ and
+$\PrincDirH{2}{R}$. The smallest eigenvector corresponds to the normal
+direction $\NormalDirH{R}$ at $\vx$. Convergence results can be found
+in \cite{ChapterIICurvature}.
+%%% Changer avec le chapitre de Jaco à un moment
 

### 2015-10-30 latex/article.tex
Working on 3.

@@
 %of the isosurface is constructed on GPU.
-The proposed approch uses an octree representation of the input object
+The proposed approach uses an octree representation of the input object
 on which an adaptive Marching Cube builds the isosurface efficiently.
@@
 %Hence, whatever their depth, all cell codes are simply stored in a linear vector on memory.
-Hence, the tree is fully represented as a linear vector of its leaves.%, whatever their depth.
+Hence, the tree is fully represented as a linear vector of its leaves.
+%, whatever their depth.
 Furthermore, cell operations such as subdivision, merging %, neighbors access
@@
 %from a Marching Cubes approach \cite{lorensen1987marching} (MC for short): the
-using Marching Cubes\cite{lorensen1987marching} (MC for short): the
+using Marching Cubes \cite{lorensen1987marching} (MC for short): the
 triangulation is generated from local triangle patches computed on
@@
 
-Similarly to original MC algorithm, this approach is well suited%perfectly adapted
-to the GPU: Given a set of cells (a vector of morton codes),
-each triangle patch can be extracted in parallel for both the regular cell and the transition cells.
+Similarly to original MC algorithm, this approach is well suited %perfectly adapted
+to a GPU implemntation: given a set of cells (a vector of morton codes),
+each triangle patch can be extracted in parallel for both regular cells and transition cells.
 %(done by the \emph{geometry shader} in the GPU graphic pipeline).
@@
 Such a criterion is also well suited to GPU since it can be evaluated
-independently on all cells.
+independently on \Jaco{every} cell.
 %Hence, we can efficiently determine if a cell must be subdivided or not.
-Figure~\ref{fig_lod_octree} illustrates our the level of
-details (LoD for short) criterion% we use. More precisely,
+Figure~\ref{fig_lod_octree} illustrates our level of
+details (LoD for short) criterion.
+% we use. More precisely,
 In dimension 2, if $\alpha$ denotes the viewing angle, an object at a distance $d$ from the camera
@@
 %parallel from all cell morton codes.
-Using such a criterion, split and merge decisions are computed in%of all cells are computed in
-parallel from all cell's morton codes.
+Using such a criterion, split and merge decisions are computed in
+%of all cells are computed in
+parallel from the morton codes of all cells.
 
@@
   \includegraphics[width=0.9\textwidth]{figs/pipeline2}
-  \caption{ Summary our GPU pipeline. Data buffers are
+  \caption{\Jaco{GPU pipeline summary}. Data buffers are
     represented in green and computations in red. Each computation
@@
 The general idea is to perform an Integral Invariant computation on
-GPU at each vertex of the generated triangular mesh. First note that
+GPU at each vertex of the generated \Jaco{triangulated} mesh. First note that
 when the LoD criterion is removed, each MC vertex is exactly centered at

### 2015-10-30 latex/article.tex
Working on 4.

@@
 object. Hence, Integral Invariant framework defined in
-Section~\ref{sec:curv-tens-estim} is consistent with the triangular
+Section~\ref{sec:curv-tens-estim} is consistent with the \Jaco{triangulated}
 surface obtained on GPU: triangles are used for visualization purposes
-but all computations are performed on the digital object $\DSh$ and thus
+but all computations are performed on the digital object $\DSh$ \Jaco{for}
 estimators
@@
 from the texture probe at level l) is greater than $1/2$. The idea here is to
-mimic a lend of adaptive Gauss digitization process.
+mimic a \Jaco{blend ?} of adaptive Gauss digitization process.
 
@@
 and to get better approximated quantities. Note that the scenario in
-Fig.~\ref{fig:approx2}-$b$, is clearly the best approach: the
+Fig.~\ref{fig:approx2}-$b$ is clearly the best approach: the
 volume is exact  (\wrt the regular grid case) since geometrical moments
@@
 non-discrete positions. For a given radius $R$, the expected number of
-cells on $B_R$ is in $O(\log{R})$. Implementation details on the
+cells \Jaco{in} $B_R$ is in $O(\log{R})$. Implementation details on the
 hierarchical octree representation can be found in the supplementary
@@
 resolution $l$ (Fig. \ref{fig:approx}-$b$ and $c$). The shader code
-becomes trivial (simple triple loop) and a lot of texture fetched are
+becomes trivial (simple triple loop) and a lot of texture \Jaco{fetches} are
 involved, but interactivity can be easily obtained. Indeed, we
@@
 \begin{enumerate}
-\item When the surface geometry has been computed,we set the current
+\item When the surface geometry has been computed, we set the current
   level $l$ at an high level $l\EqDef l_{max}$ of the mipmap
@@
 \end{enumerate}
-A consequence of the multi-pass approach is that is there is no
+A consequence of the multi-pass approach is that \Jaco{when} there is no
 interaction (camera settings, parameters), the GPU automatically
-refine the estimation. Even if step 2 is quite expensive, in
+refines the estimation. Even if step 2 is quite expensive, in
 $O\left(\left(\frac{R}{2^l}\right)^3\right)$, the interactive control

### 2015-10-30 latex/article.tex
Working on 5 and 6.

@@
   \vspace{-0.35cm}
-  \caption{\emph{First row}: Mean and Gaussian curvature estimation, (zoom of) first and second principal directions estimation on an OctaFlower with a digital domain of $130^3$.
+  \caption{\emph{First row}: Mean and Gaussian curvature estimation, (zoom of) first and second principal directions estimation on ``OctaFlower'' with a digital domain of $130^3$.
   % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
@@
 
-We first evaluate the curvature estimation on a full-resolution geometry
+We first evaluate curvature estimations on a full-resolution geometry
 obtained by disabling the LoD criterion at the mesh generation step.
-Figure~\ref{fig:full}-top shows results of curvature tensor
-estimation (mean, Gaussian, first and
-second principal directions) on an OctaFlower at level $l_0$ (considered as our ground truth in the following).
-Figure~\ref{fig:full}-bottom shows mean curvature estimation in real-time on a
-dynamic object. For this case, we simply evaluate the implicit expression at
-each vertex of a cell to decide if such cell is included or not into
-$\Ball{R}{\vx}\cap \Shape$ instead of updating the \emph{mipmap texture} of
-densities at each time step. For all illustrations, we use directly normal
-vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}.
-
-Then, we compare the approximation made by computing curvature from level $l \ge
-l_0$ in Figure~\ref{fig:refine}. We can see that results using approximation
-seems to quickly converge to the ground truth results.
-Table~\ref{tab:full-res-stat} shows numerical results of $L_\infty$ error (maximal absolute difference for all vertices )
-and $L_2$ error (mean absolute error of all vertices), as well the number of \emph{mipmap texture}
-fetches. We can also see that the number of texel fetch, required to compute the
-curvature, reduces drastically when computing approximations. However, at higher levels,
-approximation errors become more important. Those levels
-are thus never used in practice, they are presented here to illustrate how the
+Figure~\ref{fig:full}-top shows results of curvature tensor estimation
+(mean, Gaussian, first and second principal directions) on
+``OctaFlower'' at level $l_0$ (considered as our ground truth in the
+following).  Figure~\ref{fig:full}-bottom shows mean curvature
+estimation in real-time on a dynamic object. For this case, we simply
+evaluate the implicit expression at each vertex of a cell to decide if
+such cell is included or not into $\Ball{R}{\vx}\cap \Shape$ instead
+of updating the \emph{mipmap texture} of densities at each time
+step. For all illustrations, we use directly normal vectors computed
+by algorithm discussed in Section~\ref{sec:curv-tens-estim}.
+
+Then, we compare the approximations made by computing curvature from
+level $l \ge l_0$ in Figure~\ref{fig:refine}. We can see that results
+using approximation seems to quickly converge to ground truth results.
+Table~\ref{tab:full-res-stat} shows numerical results of $L_\infty$
+error (maximal absolute difference for all vertices) and $L_2$ error
+(mean \Jaco{squared errors} of all vertices), as well the number of
+\emph{mipmap texture} fetches. We can also see that the number of
+texel fetch, required to compute the curvature, reduces drastically
+when computing approximations. However, at higher levels,
+approximation errors become more important. Those levels are thus
+never used in practice, they are presented here to illustrate how the
 refining process converges to the $l_0$ level.
@@
 ensures to fetch data at the center of a mipmap cell.
-The GPU interpolation reduces the bias, but it doesn't remove it.
+The GPU interpolation reduces the bias, but it does \Jaco{not} remove it.
 
@@
 
-When dealing with large datasets, we can not expect real-time curvature tensor
-estimation if we consider the full resolution geometry, due the the huge amount of data process. By computing a
+When dealing with large datasets, we \Jaco{cannot} expect real-time curvature tensor
+estimation if we consider the full resolution geometry, due the the huge amount of data \Jaco{to} process. By computing a
 dynamically refined approximate curvature tensor estimation joined with an
@@
 
-We can first note that the required time for an object to compute the ground truth
-curvature is usually as high as the time required to extract the geometry and to
-compute all of the above levels. Using approximations is thus mandatory.
-Another advantage with approximations, is that it allows us to get a visualisation of our object as soon as we run
-the application. This allows for real-time interactions with the object, required in order to change
-the visualized value, curvature radius, \ldots
+\Jaco{First} we can note that the required time to
+compute the ground truth curvature \Jaco{for an object} is usually as high as the time
+required to extract its geometry and to compute all of the above
+levels. Using approximations is thus mandatory.  Another advantage
+with approximations is that it allows us to get a visualisation of
+our object as soon as we run the application. This allows for
+real-time interactions with the object, required in order to change
+the visualized \Jaco{quantity}, curvature radius, etc.
 

### 2015-10-30 src/cpp/DataLoader.h
wip

@@ -53,7 +53,7 @@ public:
 	virtual void loadxyyzxz();
 	virtual void loadxyz();*/
 	
-	virtual void releaseData() { free(data); }
+	virtual void releaseData() { free(data); free(data_char); }
 };
 
 /*class DataTerrain : public DataLoader

### 2015-10-30 src/cpp/main.cpp

@@ -365,6 +365,7 @@ public:
 		}
 		else
 		{
+			dl = NULL;
 			Parameters::getInstance()->g_sizetex = size;
 			generatePotentialGlsl(argv[1]);
 		}
@@ -848,6 +849,8 @@ public:
 		glDeleteQueries(1, &Parameters::getInstance()->g_query[QUERY_TRANSITION]);
 		if (plot)
 			fclose(plotfd2);
+		if (dl != NULL)
+			dl->releaseData();
 		return 0;
 	}
 

### 2015-10-30 latex/article.tex

@@
+% Copyright 2015
+% Hélène Perrier <helene.perrier@liris.cnrs.fr>
+% Jérémy Levallois <jeremy.levallois@liris.cnrs.fr>
+% David Coeurjolly <david.coeurjolly@liris.cnrs.fr>
+% Jean-Philippe Farrugia <jean-philippe.farrugia@liris.cnrs.fr>
+% Jean-Claude Iehl <jean-claude.iehl@liris.cnrs.fr>
+% Jacques-Olivier Lachaud <jacques-olivier.lachaud@univ-savoie.fr>
+%
+% This file and related figures are under Creative Commons CC BY-NC-SA 2.0
+% See <https://creativecommons.org/licenses/by-nc-sa/2.0/>
+
 \documentclass{llncs}
@@
    \and
-Universit\'e de Savoie, CNRS\\
+Universit\'e de Savoie Mont Blanc, CNRS\\
 LAMA, UMR5127, F-73776, France\\
@@
   to efficiently explore the curvature tensor on the boundary of
-  potentially large and dynamic digital objects (mean and gaussian curvatures,
+  potentially large and dynamic digital objects (mean and Gaussian curvatures,
   principal curvatures, principal directions and normal vector
@@
   interactively different radii and thus select the appropriate scale
-  \Jaco{at} which the computation is performed and visualized.
+  at which the computation is performed and visualized.
 
@@
 most curvature estimators require a parameter fixing the scale
-\Jaco{at} which the computation is performed. For short, such parameter
-(integration radius, convolution kernel size, \ldots) specifies \Jaco{a scale for analyzing the object surface, and is naturally related to the amount of perturbation on input data}.
+at which the computation is performed. For short, such parameter
+(integration radius, convolution kernel size, \ldots) specifies a scale for analyzing the object surface, and is naturally related to the amount of perturbation on input data.
 As a consequence, exploring interactively
@@
 adaptive approaches have been proposed in order to optimize the
-\Jaco{triangulated} mesh resolution \Jaco{according to the object geometry or the
-viewpoint}. In this topic, many solutions have been developed in
+triangulated mesh resolution according to the object geometry or the
+viewpoint. In this topic, many solutions have been developed in
 Computer
@@
 The method developed by \textsc{Lengyel} \textit{et al.}
-\cite{lengyel2010voxel} \Jaco{suits best our needs}.
+\cite{lengyel2010voxel} suits best our needs.
 %However, it
@@
 %inspired from this method.
-inspired \Jaco{by} this method,
+inspired by this method,
 %using a GPU-friendly Lod criterion
-\Jaco{that maintains} a view dependent triangulation.
+that maintains a view dependent triangulation.
 %It leaves the CPU free for other tasks and avoids synchronization with the GPU.
@@
 %Our high framerate allows this method to run in real-time on fully dynamic data.
-Our high framerate allows \Jaco{us} to inspect dynamic 3D data in real-time.
+Our high framerate allows us to inspect dynamic 3D data in real-time.
 %The triangulation is controlled by a GPU LoD criterion
@@
 surfaces. Such approaches are based on an integration principle using
-a \Jaco{ball} kernel of a given radius. Additionally, authors have
+a ball kernel of a given radius. Additionally, authors have
 demonstrated that these estimators have multigrid convergence
@@
 %, in real-time,
-such curvature \Jaco{fields} in real-time and
+such curvature fields in real-time and
 %allowing us
@@
 $\CurvH{R}$ and the 3D digital mean curvature estimator $\MeanCurvH{R}$ based on
-the digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ \Jaco{(we denote such
-quantity $\AreaC(Y,h)$ in dimension 2):}
+the digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ (we denote such
+quantity $\AreaC(Y,h)$ in dimension 2):
 %% Redite
@@
 They have proved that estimating both 2D curvature and 3D mean curvature on digital
-objets with volumetric integral information have the multigrid convergence
-property \cite{DGCI2013}. For short, when the digital objet becomes finer and
+objects with volumetric integral information have the multigrid convergence
+property \cite{DGCI2013}. For short, when the digital object becomes finer and
 finer, \ie when the digitization step $h$ tends to zero, the estimated quantity
@@
 Additionally, eigenvectors associated to $\hat{\lambda}_1$ and
-$\hat{\lambda}_2$ of the covariance matrix \Jaco{are} principal
-curvature direction \Jaco{estimators} $\PrincDirH{1}{R}$ and
+$\hat{\lambda}_2$ of the covariance matrix are principal
+curvature direction estimators $\PrincDirH{1}{R}$ and
 $\PrincDirH{2}{R}$. The smallest eigenvector corresponds to the normal
@@
 
-Representing a hierachical structure on GPU is usually challenging since
+Representing a hierarchical structure on GPU is usually challenging since
 such a data parallel component is unable to handle recursivity.
@@
 Similarly to original MC algorithm, this approach is well suited %perfectly adapted
-to a GPU implemntation: given a set of cells (a vector of morton codes),
+to a GPU implementation: given a set of cells (a vector of morton codes),
 each triangle patch can be extracted in parallel for both regular cells and transition cells.
@@
 Such a criterion is also well suited to GPU since it can be evaluated
-independently on \Jaco{every} cell.
+independently on every cell.
 %Hence, we can efficiently determine if a cell must be subdivided or not.
@@
   \includegraphics[width=0.9\textwidth]{figs/pipeline2}
-  \caption{\Jaco{GPU pipeline summary}. Data buffers are
+  \caption{GPU pipeline summary. Data buffers are
     represented in green and computations in red. Each computation
@@
 The general idea is to perform an Integral Invariant computation on
-GPU at each vertex of the generated \Jaco{triangulated} mesh. First note that
+GPU at each vertex of the generated triangulated mesh. First note that
 when the LoD criterion is removed, each MC vertex is exactly centered at
@@
 object. Hence, Integral Invariant framework defined in
-Section~\ref{sec:curv-tens-estim} is consistent with the \Jaco{triangulated}
+Section~\ref{sec:curv-tens-estim} is consistent with the triangulated
 surface obtained on GPU: triangles are used for visualization purposes
-but all computations are performed on the digital object $\DSh$ \Jaco{for}
+but all computations are performed on the digital object $\DSh$ for
 estimators
@@
 from the texture probe at level l) is greater than $1/2$. The idea here is to
-mimic a \Jaco{blend ?} of adaptive Gauss digitization process.
+mimic a kind of adaptive Gauss digitization process.
 
@@
 
-Using the hierachical nature of the mipmap texture, we could also
+Using the hierarchical nature of the mipmap texture, we could also
 consider hierarchical decompositions of either $\Ball{R}{\vx}$
@@
 Fig.~\ref{fig:approx2}-$a$: for a given radius $R$, we precompute a
-hierachical decomposition of $B_R$. Such decomposition is made of
+hierarchical decomposition of $B_R$. Such decomposition is made of
 octree cells at different resolutions. At a given MC vertex $\vx$, the
@@
 non-discrete positions. For a given radius $R$, the expected number of
-cells \Jaco{in} $B_R$ is in $O(\log{R})$. Implementation details on the
+cells in $B_R$ is in $O(\log{R})$. Implementation details on the
 hierarchical octree representation can be found in the supplementary
@@
 resolution $l$ (Fig. \ref{fig:approx}-$b$ and $c$). The shader code
-becomes trivial (simple triple loop) and a lot of texture \Jaco{fetches} are
+becomes trivial (simple triple loop) and a lot of texture fetches are
 involved, but interactivity can be easily obtained. Indeed, we
@@
 \end{enumerate}
-A consequence of the multi-pass approach is that \Jaco{when} there is no
+A consequence of the multi-pass approach is that when there is no
 interaction (camera settings, parameters), the GPU automatically
@@
 error (maximal absolute difference for all vertices) and $L_2$ error
-(mean \Jaco{squared errors} of all vertices), as well the number of
+(mean squared errors of all vertices), as well the number of
 \emph{mipmap texture} fetches. We can also see that the number of
@@
 ensures to fetch data at the center of a mipmap cell.
-The GPU interpolation reduces the bias, but it does \Jaco{not} remove it.
+The GPU interpolation reduces the bias, but it does not remove it.
 
@@
 
-When dealing with large datasets, we \Jaco{cannot} expect real-time curvature tensor
-estimation if we consider the full resolution geometry, due the the huge amount of data \Jaco{to} process. By computing a
+When dealing with large datasets, we cannot expect real-time curvature tensor
+estimation if we consider the full resolution geometry, due the the huge amount of data to process. By computing a
 dynamically refined approximate curvature tensor estimation joined with an
@@
 
-\Jaco{First} we can note that the required time to
-compute the ground truth curvature \Jaco{for an object} is usually as high as the time
+First we can note that the required time to
+compute the ground truth curvature for an object is usually as high as the time
 required to extract its geometry and to compute all of the above
 levels. Using approximations is thus mandatory.  Another advantage
-with approximations is that it allows us to get a visualisation of
+with approximations is that it allows us to get a visualization of
 our object as soon as we run the application. This allows for
 real-time interactions with the object, required in order to change
-the visualized \Jaco{quantity}, curvature radius, etc.
+the visualized quantity, curvature radius, etc.
 
@@
   \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error
-  obtained on OctaFlower with a digital domain of $130^3$ when computing mean
+  obtained on ``OctaFlower'' with a digital domain of $130^3$ when computing mean
   curvature with two radii: 8 and 16, with hierarchical algorithm (H) and $l \ge
@@
   \vspace{-0.35cm}
-  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
+  \caption{Illustration of mean curvature computation on ``OctaFlower'' (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
   %
@@
   \caption{Timings in milliseconds (in logscale) obtained while visualizing an adaptive
-  triangulation on three objects -- OctaFlower (digital domain of $130^3$ ), Snow
-  Microstructures ($233^3$) and XYZ-Dragon ($510^3$) --  by computing the
+  triangulation on three objects -- ``OctaFlower'' (digital domain of $130^3$ ), ``Snow microstructures'' ($233^3$) and ``XYZ-Dragon'' ($510^3$) --  by computing the
   curvature with a regular grid (\emph{left}) and with hierarchical
@@
    \caption{\emph{Left column}: Mean curvature, first and second
-     principal directions and normal vector field estimation on Snow Microstructures ($233^3$ and $R=8$).
+     principal directions and normal vector field estimation on ``Snow microstructures'' ($233^3$ and $R=8$).
   \emph{Right column:} Mean curvature, first and second principal
-  directions and normal vector field estimation on XYZ-Dragon ($510^3$
+  directions and normal vector field estimation on ``XYZ-Dragon'' ($510^3$
   and $R=8$). Normal vectors are colored with a mapping of their
@@
  Figure~\ref{fig:adaptive} shows curvature computation and exploration in
- real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
- Snow microstructures ($233^3$).
+ real-time on large datasets: ``XYZ-Dragon'' (with digital domain of $512^3$) and
+ ``Snow microstructures'' ($233^3$).
 

### 2015-10-30 src/cpp/Curvature.cpp
fixed merge conflicts

@@ -23,9 +23,7 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
 #include "Curvature.h"
-#include <boost/concept_check.hpp>
 
 #include "GL/GLQuery.h"
 #include "GL/GLTexture.h"
@@ -38,68 +36,70 @@
 
 void configure_curv(GLuint program, GLuint first_loc)
 {
-	/*
-	LOCATION_SHADING_SIZE,
-	LOCATION_SHADING_DENSITY,
-	LOCATION_SHADING_VIEWPORT,
-	LOCATION_SHADING_TAN_FOVY,
-	LOCATION_SHADING_SCALE,
-	LOCATION_SHADING_WIREFRAME,
-	LOCATION_SHADING_CAMERA,
-	LOCATION_SHADING_CURVRADIUS,
-	LOCATION_SHADING_CURVMIN,
-	LOCATION_SHADING_CURVMAX,
-	LOCATION_SHADING_GROUNDTRUTH,
-	LOCATION_SHADING_SIZETEX,
-	*/
 	glProgramUniform3f (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc],//LOCATION_SHADING_SIZE+first_loc],
+			Parameters::getInstance()->g_uniform_locations[first_loc],
 			Parameters::getInstance()->g_geometry.scale[0], Parameters::getInstance()->g_geometry.scale[1], Parameters::getInstance()->g_geometry.scale[2]);
 	glProgramUniform1i (program,
 			Parameters::getInstance()->g_uniform_locations[first_loc+1],
 			TEXTURE_DENSITY);
+	
 	glProgramUniform2f (program,
 			Parameters::getInstance()->g_uniform_locations[first_loc+2],
 			Parameters::getInstance()->g_window.width, Parameters::getInstance()->g_window.height);
 
-	glProgramUniform1f (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+3],
-			tanf (Parameters::getInstance()->g_camera.fovy / 360.f * 3.14159f));
-	glProgramUniform1f(program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+4],
-			Parameters::getInstance()->g_scale);
-
 	glProgramUniform1i (program,
-			Parameters::getInstance()->g_uniform_locations[first_loc+5],
+			Parameters::getInstance()->g_uniform_locations[first_loc+3],
[…]

### 2015-10-30 src/cpp/DataLoader.cpp

@@ -23,7 +23,6 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
 #include "DataLoader.h"
 
 #include "GL/GLTexture.h"
@@ -71,6 +70,7 @@ void DataLoader::loadData8BGpu()
 	glBindTexture(GL_TEXTURE_3D, 0);
 }
 
+/*
 void loadNxtMipmap(int size, float* texture, float** miptexture)
 {
 	int sizemip = size/2;
@@ -233,11 +233,6 @@ void DataLoader::loadxyz()
 		float norm_j = j;
 		float norm_k = k;
 		
-		/*
-		mmt[nb*3] = norm_i;
-		mmt[nb*3 + 1] = norm_j;
-		mmt[nb*3 + 2] = norm_k;
-		*/
 		mmt[nb*3] = norm_i*data[nb];
 		mmt[nb*3 + 1] = norm_j*data[nb];
 		mmt[nb*3 + 2] = norm_k*data[nb];
@@ -283,14 +278,15 @@ void DataLoader::loadxyz()
 	
 	//free(mmt);
 }
+*/
 
-
+/*
 unsigned long int f(unsigned int sf, unsigned long int x, unsigned long int y, unsigned long int z)
 {
 	return ((z*sf) + x)*sf + y;
 }
-
-//Files provided by Eric
+*/
+/*//Files provided by Eric
 void DataTerrain::loadFile(char* file)
 {
 	printf("Loading Eric's file as float %s ... ", file); fflush(stdout);
@@ -327,7 +323,7 @@ void DataTerrain::loadFile(char* file)
 		data[i++] = ((float)data_char[f(sf, x, y, z)] / 255.0) - 0.5;
 
 	printf("Complete\n");
-}
+}*/
 
 //Files .raw provided by http://www.tc18.org/code_data_set/3D_images.php
 void DataRaw::loadFile(char* file)
@@ -341,20 +337,28 @@ void DataRaw::loadFile(char* file)
 		return;
 	}
 	
+	bool padding = true; //if set to true, the texture is padded until it has the size of the next power of 2 resolution
+	
 	unsigned long int a = 1;
 	while(a < sizex)
 	{
 		a*= 2;
 	}
 	
-	unsigned long int size_p2 = sizex;
+	unsigned long int size_p2;
+	if (padding)
+		size_p2 = a;
+	else
+		size_p2 = sizex;
 
 	unsigned long int total = size_p2 * size_p2 * size_p2;
[…]

### 2015-10-30 src/cpp/Definitions.h

@@ -23,8 +23,6 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
-
 #ifndef DEFINITIONS_H_
 #define DEFINITIONS_H_
 
@@ -102,7 +100,7 @@ enum {PROGRAM_LTREE_LOD, PROGRAM_LTREE_CULL, PROGRAM_CELL_DRAW, PROGRAM_REGULAR_
 			PROGRAM_SPHEREDRAW, PROGRAM_COUNT};
 enum {FRAMEBUFFER_DEFAULT, FRAMEBUFFER_COUNT};
 enum {VERTEX_ARRAY_EMPTY, VERTEX_ARRAY_LTREE_UPDATE1, VERTEX_ARRAY_LTREE_UPDATE2, 
-		VERTEX_ARRAY_OCTREE_RENDER1, VERTEX_ARRAY_OCTREE_RENDER2,
+		//VERTEX_ARRAY_OCTREE_RENDER1, VERTEX_ARRAY_OCTREE_RENDER2,
 		VERTEX_ARRAY_LTREE_RENDER1, VERTEX_ARRAY_LTREE_RENDER2, 
 		VERTEX_ARRAY_LTREE_RENDER1_TR, VERTEX_ARRAY_LTREE_RENDER2_TR,
         VERTEX_ARRAY_CURVATURE, VERTEX_ARRAY_CURVATURE_TR,
@@ -113,8 +111,8 @@ enum {FEEDBACK_LTREE1, FEEDBACK_LTREE2, FEEDBACK_TRIANGULATION, FEEDBACK_TRIANGU
 enum {BUFFER_TRANSFORMS, BUFFER_FRUSTUM, 
 		BUFFER_LTREE_DATA1, BUFFER_LTREE_DATA2, BUFFER_CODE,
 		BUFFER_LTREE_DATA1_TR, BUFFER_LTREE_DATA2_TR, BUFFER_NEIGHBOURS,
-		BUFFER_VERTEX_CUBE, BUFFER_INDEX_CUBE, 
-		BUFFER_EXPORT_TGL, BUFFER_EXPORT_K1K2, BUFFER_EXPORT_DIRMIN, BUFFER_EXPORT_DIRMAX, BUFFER_EXPORT_NORMALES,
+		//BUFFER_VERTEX_CUBE, BUFFER_INDEX_CUBE, 
[…]

### 2015-10-30 src/cpp/GpuOctree.cpp

@@ -23,7 +23,6 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
 #include "GpuOctree.h"
 
 #include "GL/GLQuery.h"
@@ -32,8 +31,10 @@
 #include "GL/GLBuffer.h"
 #include "ProgramManager.h"
 
+int sizekey = 2;
+
 //Cube data, used for cells drawing
-const GLfloat g_cubeVertices[] = {  0.5f, -0.5f, -0.5f,   // 0 
+/*const GLfloat g_cubeVertices[] = {  0.5f, -0.5f, -0.5f,   // 0 
 					0.5f,  0.5f, -0.5f,   // 1
 					0.5f,  0.5f,  0.5f,   // 2
 					0.5f, -0.5f,  0.5f,   // 3
@@ -47,7 +48,7 @@ const GLushort g_cubeIndexes[] = { 0,1,1,2,2,3,3,0,   // front
 					5,4,4,7,7,6,6,5,   // back
 					4,0,0,3,3,7,7,4,   // left
 					2,3,3,7,7,6,6,2,   // top
-					0,4,4,5,5,1,1,0 }; // bottom
+					0,4,4,5,5,1,1,0 }; // bottom*/
 							
 
 void streamFrustum (void) 
@@ -87,14 +88,13 @@ void streamFrustum (void)
 
 void GPUOctree::loadBuffers()
 {
-        const int root[] = {0,0,0,0};
-        //const size_t cap = 1 << 28;
+        const int root[] = {0,0};
 		
 		size_t full_tree = 1;
-		unsigned long int side = pow(2, 9);
-		full_tree += side*side*side;
+		long int side = std::pow(2, 8); //lvl 8 max
+		full_tree += side*side*side; 
 		
-		size_t full_tree_cap = full_tree * sizeof(float) * 2.0; //1 vec2 for each
+		size_t full_tree_cap = full_tree * sizeof(float) * sizekey; //1 vec2 for each
 		
 		printf("LOD CAPACITY %lu (%lu)\n", full_tree, full_tree_cap);
 		
@@ -102,10 +102,10 @@ void GPUOctree::loadBuffers()
 		tr_cells = full_tree/100.0; //a lot less than tree cells
 		printf("TR CAPACITY %lu\n", tr_cells);
 		
-		size_t tr_cells_cap = tr_cells * sizeof(float) * 2.0; //1 vec2 for each
[…]

### 2015-10-30 src/cpp/Hierarchy.cpp

@@ -33,6 +33,7 @@
 // Not in math.h
 #define PI 3.14159265358979323846
 #define LVL 11
+#define MAX_SUBDIV 5000
 
 typedef float Value;
 
@@ -56,7 +57,7 @@ Value moment110( Value data, int x, int y, int z );
 Value moment101( Value data, int x, int y, int z );
 Value moment011( Value data, int x, int y, int z );
 
-float xyzk_list[4*10000+1];
+float xyzk_list[4*MAX_SUBDIV+1];
 
 // A 3D image of size (2^lvl)^3
 struct SImage {
@@ -322,6 +323,11 @@ Value computeExact(float x0, float y0, float z0, Value r, int lvl)
 					z / pow(2, lvl) - 0.5 >= 0)
 				{
 					xyzk_list[0]++;
+					if(xyzk_list[0] >= MAX_SUBDIV)
+					{
+						printf("Cannot compute hierarchical decomposition for it contains more than %d elements\n", MAX_SUBDIV);
+						return acc;
+					}
 					xyzk_list[ (int)xyzk_list[0]*4 ] = x / pow(2, lvl) - 0.5;
 					xyzk_list[ (int)xyzk_list[0]*4 + 1 ] = y / pow(2, lvl) - 0.5;
 					xyzk_list[ (int)xyzk_list[0]*4 + 2 ] = z / pow(2, lvl) - 0.5;
@@ -441,7 +447,7 @@ Value computeHierarchy( MipMap* M, int x0, int y0, int z0, Value r )
   return acc;
 }
 
-Value computeHierarchy( int lvl, int x0, int y0, int z0, Value r )
+void computeHierarchy( int lvl, int x0, int y0, int z0, Value r )
 {
   Value weight[ LVL+1 ];
   Value diag  [ LVL+1 ];
@@ -454,7 +460,7 @@ Value computeHierarchy( int lvl, int x0, int y0, int z0, Value r )
       diag  [ i ] = diag  [ i+1 ] * (Value) 2;
     }
   int xyzk[ 4 ] = { 0, 0, 0, 0 };
-  Value acc = 0;
+  //Value acc = 0;
   Value r2  = r*r;
   do 
     {
[…]

### 2015-10-30 src/cpp/Parameters.cpp

@@ -23,7 +23,6 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
 #include "Parameters.h"
 
 #include <stdlib.h>
@@ -63,21 +62,21 @@ Parameters::Parameters()
     g_draw_cells = false;
     g_draw_triangles = true;
     g_culling = true;
-    g_fromtexture = true;
+    //g_fromtexture = true;
     g_solid_wireframe = true;
     g_controls = false;
     g_gui = true;
-    g_radial_length = true;
-    g_textured_data = false;
+    //g_radial_length = true;
+    //g_textured_data = false;
 	g_auto_refine = true;
-	g_k1k2_normals = true;
+	g_triangle_normals = false;
 	g_curv_dir = 0;
 	g_curv_val = 1;
 	g_lvl = 2;
 
-    g_ground_truth = 3;
+    g_ground_truth = 1;
     
-    g_regular = false;
+    g_adaptive_geom = true;
     g_radius_show = true;
 
 	g_curvradius = 8.0;
@@ -86,7 +85,7 @@ Parameters::Parameters()
 	
     g_scale = 10.0;
     g_tessel = 1.0;
-    g_isosurface = 0;
+    //g_isosurface = 0;
 	
 	g_export = false;
 	g_compute_min_max = true;

### 2015-10-30 src/cpp/PrimitiveDraw.cpp

@@ -23,7 +23,6 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
 #include "PrimitiveDraw.h"
 
 #include "GL/GLQuery.h"

### 2015-10-30 src/cpp/QuaternionCamera.cpp

@@ -23,7 +23,6 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
 #include "QuaternionCamera.h"
 
 #include <cmath>

### 2015-10-30 src/cpp/QuaternionCamera.h

@@ -23,7 +23,6 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
 #ifndef QUATERNIONCAMERA_H_
 #define QUATERNIONCAMERA_H_
 

### 2015-10-30 src/cpp/RegularTriangulation.cpp

@@ -23,7 +23,6 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
 #include "Triangulation.h"
 
 #include "GL/GLQuery.h"
@@ -143,13 +142,13 @@ void RegularTriangulation::configurePrograms()
                             Parameters::getInstance()->g_scale);
         glProgramUniform1f(Parameters::getInstance()->g_programs[PROGRAM_REGULAR_DRAW],
 			    Parameters::getInstance()->g_uniform_locations[LOCATION_REGULAR_ISOSURFACE],
-                            Parameters::getInstance()->g_isosurface);
+                            0);//Parameters::getInstance()->g_isosurface);
 	glProgramUniform1i (Parameters::getInstance()->g_programs[PROGRAM_REGULAR_DRAW],
 			    Parameters::getInstance()->g_uniform_locations[LOCATION_REGULAR_FROMTEXTURE],
-			    Parameters::getInstance()->g_fromtexture);
+			    1);//Parameters::getInstance()->g_fromtexture);
 	glProgramUniform1i (Parameters::getInstance()->g_programs[PROGRAM_REGULAR_DRAW],
 			    Parameters::getInstance()->g_uniform_locations[LOCATION_REGULAR_METRIC],
-			    Parameters::getInstance()->g_radial_length);
+			    1);//Parameters::getInstance()->g_radial_length);
 	glProgramUniform1f (Parameters::getInstance()->g_programs[PROGRAM_REGULAR_DRAW],
                             Parameters::getInstance()->g_uniform_locations[LOCATION_REGULAR_TIME],
                             Parameters::getInstance()->g_time_elapsed);

### 2015-10-30 src/cpp/Shading.cpp

@@ -23,9 +23,7 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
 #include "Shading.h"
-
 
 #include "GL/GLQuery.h"
 #include "GL/GLTexture.h"
@@ -125,7 +123,7 @@ void load(GLuint program, GLuint first_loc)
 		glGetUniformLocation (program, "u_scene_size");
 	
 	Parameters::getInstance()->g_uniform_locations[first_loc+1] =
-			glGetUniformLocation (program, "u_viewport");
+		glGetUniformLocation (program, "u_viewport");
 
 	Parameters::getInstance()->g_uniform_locations[first_loc+2] =
 		glGetUniformLocation (program, "solid_wireframe");

### 2015-10-30 src/cpp/TransitionTriangulation.cpp

@@ -23,7 +23,6 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
 #include "Triangulation.h"
 
 #include "GL/GLQuery.h"
@@ -142,13 +141,13 @@ void TransitionTriangulation::configurePrograms()
 			    (int)Parameters::getInstance()->g_tessel);
         glProgramUniform1f(Parameters::getInstance()->g_programs[PROGRAM_TRANSITION_DRAW],
                             Parameters::getInstance()->g_uniform_locations[LOCATION_TRANSITION_ISOSURFACE],
-                            Parameters::getInstance()->g_isosurface);
+                            0);//Parameters::getInstance()->g_isosurface);
 	glProgramUniform1i (Parameters::getInstance()->g_programs[PROGRAM_TRANSITION_DRAW],
 			    Parameters::getInstance()->g_uniform_locations[LOCATION_TRANSITION_FROMTEXTURE],
-                            Parameters::getInstance()->g_fromtexture);
+                            1);//Parameters::getInstance()->g_fromtexture);
 	glProgramUniform1i (Parameters::getInstance()->g_programs[PROGRAM_TRANSITION_DRAW],
                             Parameters::getInstance()->g_uniform_locations[LOCATION_TRANSITION_METRIC],
-                            Parameters::getInstance()->g_radial_length);
+                            0);//Parameters::getInstance()->g_radial_length);
 	glProgramUniform1f(Parameters::getInstance()->g_programs[PROGRAM_TRANSITION_DRAW],
                             Parameters::getInstance()->g_uniform_locations[LOCATION_TRANSITION_TIME],
                             Parameters::getInstance()->g_time_elapsed);

### 2015-10-30 src/cpp/Utils.cpp

@@ -23,7 +23,6 @@
  * along with ICTV.  If not, see <http://www.gnu.org/licenses/>
  */
 
-
 #include "Utils.h"
 
 #include <fstream>

### 2016-01-18 latex/article.tex
fixed some orthographic mistakes in the paper

@@
   Interactive visualization is a very convenient tool to explore
-  complex scientific data or to explore different parameter settings
+  complex scientific data or to try different parameter settings
   for a given processing algorithm. In this article, we present a tool
-  to efficiently explore the curvature tensor on the boundary of
+  to efficiently analyze the curvature tensor on the boundary of
   potentially large and dynamic digital objects (mean and Gaussian curvatures,
@@
   based on integral invariants. Integral invariants being parametrized
-  by a given ball radius, our proposal allows us to explore
+  by a given ball radius, our proposal allows to explore
   interactively different radii and thus select the appropriate scale
@@
 %Hence, this system allows us to visualize
-This system allow us to visualize
+This system allows us to visualize
 curvature tensor in real-time on large dynamic objects. Our approach combines a
@@
 with edge length $h$. By doing so, both $\partial\Shape$ and
-$\partial\Body{Z}{h}$ are topological boundary of objects lying in the same
+$\partial\Body{Z}{h}$ are topological boundaries of objects lying in the same
 space (see Fig. \ref{fig:notations}-b). Note that the combinatorial digital
@@
 
-In \cite{DGCI2013}, authors have defined the 2D digital curvature estimator
+In \cite{DGCI2013}, estimators are defined based on the 2D digital curvature estimator
 $\CurvH{R}$ and the 3D digital mean curvature estimator $\MeanCurvH{R}$ based on
@@
 %
-They have proved that estimating both 2D curvature and 3D mean curvature on digital
-objects with volumetric integral information have the multigrid convergence
+Estimators of both 2D curvature and 3D mean curvature on digital
+objects with volumetric integral information are proved to be multigrid convergent
 property \cite{DGCI2013}. For short, when the digital object becomes finer and
@@
 % Equation~20 of \cite{CVIU2014} for more details).
-They have also proved the convergence of these estimators when setting the ball
+These estimators are proven convergent when setting the ball
 radius $h$ in $R = kh^\frac{1}{3}$, where $k$ is a constant related to the
 maximal curvature of the shape, on convex shapes with at least $C^3$-boundary
-and bounded curvature \cite{CVIU2014}. More formally, they get:
+and bounded curvature \cite{CVIU2014}. More formally, it leads to:
 %
@@
 It has been shown that the radius of the ball depends on the geometry of the
-underlying shape. In \cite{DGCI2014}, authors proposed a parameter-free
+underlying shape. In \cite{DGCI2014}, a proposal was made for a parameter-free
 estimation of the radius of the ball by analyzing the shape \wrt the local shape
 geometry using maximal digital straight segments of the digital boundary. In
-\cite{SMI2015}, authors analyzed in scale-space (for a range of radii) these
-estimators for a given digital shape. This allows them to detect features of the
+\cite{SMI2015}, these estimators have been analyzed in scale-space (for a range of radii)  for a given digital shape. This allows to detect features of the
 shape thanks to the behavior of estimators on singularities.
@@
 proposed by \textsc{Lengyel} \emph{et al.}~\cite{lengyel2010voxel}.
-First, this approach constrains the octree
+First, this approach forces the octree
 structure
@@
 When dealing with large datasets, we cannot expect real-time curvature tensor
-estimation if we consider the full resolution geometry, due the the huge amount of data to process. By computing a
+estimation if we consider the full resolution geometry, due to the huge amount of data to process. By computing a
 dynamically refined approximate curvature tensor estimation joined with an

### 2016-01-19 latex/article.tex
Passe 1 sur le DGCI (désolée David j'ai tout pété la section 4 ... tu lis, tu me dis ce que tu en penses et si ça va pas je reviendrai à l'ancienne version)

@@
 processing on the digital object and to explore different parameter
-settings of the geometry processing tool.  In this work, we focus on
-interactive visualization of volumetric data isosurfaces combined with
-a curvature tensor (mean/Gaussian curvature, principal curvatures
-directions, \ldots) estimation at each point of the digital
-surface.
+settings of the geometry processing tool.
+\color{blue}
+Here, we focus on curvature tensor estimators.
+Most of them require a parameter fixing the scale
+at which the computation is performed. For short, such parameter
+(integration radius, convolution kernel size, \ldots) specifies a scale for analyzing the object surface, 
+and is naturally related to the amount of perturbation on input data. As a consequence, when using
+such tensors, exploring different values of this parameter is mandatory.
+However, this is usually an offline process, due to the amount of computations that
+needs to be done.
+\normalcolor
+%In this work, we present an interactive visualization of volumetric data isosurfaces combined with
+%a curvature tensor (mean/Gaussian curvature, principal curvatures
+%directions, \ldots) estimation at each point of the digital
+%surface.
 %Curvature maps on a given isosurface are key information when
 %exploring 3D structures in Material Sciences \todo{REF}.
-Furthermore,
-most curvature estimators require a parameter fixing the scale
-at which the computation is performed. For short, such parameter
-(integration radius, convolution kernel size, \ldots) specifies a scale for analyzing the object surface, and is naturally related to the amount of perturbation on input data.
-As a consequence, exploring interactively
-different values of such parameter is mandatory.
+
 \vspace{0.2cm}
@@
 
+\vspace{0.2cm}
+\color{blue}
+In this paper, we will first present the previous works on
+curvature tensor estimation. Then, we will see how we can
+efficiently extract a triangulation of an object on the GPU
+and finally, we will present how we can evaluate the curvature tensor in
+real time and discuss on the several approaches that we tried.
+\normalcolor
+
 \section{Curvature Tensor Estimation}
@@
 on $\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to the
-associated one on $\Bd{\Shape}$.
+\color{blue}
+associated one on $\Bd{\Shape}$ in $O\left(h^{\frac{1}{3}}\right)$ for
+convex shapes with at least $C^3$-boundary and bounded curvature.
+\normalcolor
 %
@@
 %
-Setting $R = kh^\frac{1}{3}$ on convex shapes
-with at least $C^3$-boundary and bounded curvature, where $k$ is a constant
-related to the maximal curvature of the shape, they have:
-%
-\begin{align}
-\forall 0 < h \le h_0,\,\, &\forall \vx \in \Bd{\Shape},\,\,
-\forall \vxH \in \Bd{\Body{\DSh}{h}} \text{~with~} \| \vxH -\vx\|_\infty \le h, \nonumber \\
-&\CurvH{R}(\DSh, \vxH, h) = \Curv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,,\\
-&\MeanCurvH{R}(\DSh, \vxH, h) = \MeanCurv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,.
-\end{align}
+%Setting $R = kh^\frac{1}{3}$ on convex shapes
+%with at least $C^3$-boundary and bounded curvature, where $k$ is a constant
+%related to the maximal curvature of the shape, they have:
+%%
+%\begin{align}
+%\forall 0 < h \le h_0,\,\, &\forall \vx \in \Bd{\Shape},\,\,
+%\forall \vxH \in \Bd{\Body{\DSh}{h}} \text{~with~} \| \vxH -\vx\|_\infty \le h, \nonumber \\
+%&\CurvH{R}(\DSh, \vxH, h) = \Curv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,,\\
+%&\MeanCurvH{R}(\DSh, \vxH, h) = \MeanCurv(\Shape, \vx) + O\left(h^{\frac{1}{3}}\right)\,.
+%\end{align}
 
@@
 % Equation~20 of \cite{CVIU2014} for more details).
-These estimators are proven convergent when setting the ball
+\color{blue}
+These estimators are proven convergent in $O\left(h^{\frac{1}{3}}\right)$ when setting the ball
 radius $h$ in $R = kh^\frac{1}{3}$, where $k$ is a constant related to the
 maximal curvature of the shape, on convex shapes with at least $C^3$-boundary
-and bounded curvature \cite{CVIU2014}. More formally, it leads to:
-%
-\begin{align}
-  \forall 0 < h \le h_0,\,\, &\forall \vx \in \Bd{\Shape},\,\,
-  \forall \vxH \in \Bd{\Body{\DSh}{h}} \text{~with~} \| \vxH -\vx\|_\infty \le h, \nonumber \\
-  &\PrincCurvH{1}{R}(\DigF{\Shape}{h},\vxH, h) = \PrincCurv{1}(\Shape,\vx) + O\left(h^{\frac{1}{3}}\right) \,,\\
-  &\PrincCurvH{2}{R}(\DigF{\Shape}{h},\vxH, h) = \PrincCurv{2}(\Shape,\vx) + O\left(h^{\frac{1}{3}}\right) \,.
-\end{align}
+and bounded curvature \cite{CVIU2014}.
+\normalcolor 
+%More formally, it leads to:
+%%
+%\begin{align}
+%  \forall 0 < h \le h_0,\,\, &\forall \vx \in \Bd{\Shape},\,\,
+%  \forall \vxH \in \Bd{\Body{\DSh}{h}} \text{~with~} \| \vxH -\vx\|_\infty \le h, \nonumber \\
+%  &\PrincCurvH{1}{R}(\DigF{\Shape}{h},\vxH, h) = \PrincCurv{1}(\Shape,\vx) + O\left(h^{\frac{1}{3}}\right) \,,\\
+%  &\PrincCurvH{2}{R}(\DigF{\Shape}{h},\vxH, h) = \PrincCurv{2}(\Shape,\vx) + O\left(h^{\frac{1}{3}}\right) \,.
+%\end{align}
 
@@
 present our approaches.
-
-\subsection{Design principles}
-
+%\subsection{Design principles}
 The general idea is to perform an Integral Invariant computation on
-GPU at each vertex of the generated triangulated mesh. First note that
+GPU at each vertex of the generated triangulated mesh.
+\color{blue}
+Since GPU's are massively parallel, we can do all those computations in parallel 
+to get a very efficient implementation. Please note that
+\normalcolor
 when the LoD criterion is removed, each MC vertex is exactly centered at
@@
 
-To implement the integration on $\Ball{R}{\vx} \cap \Shape$
-(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all digital
-points inside such domain (Fig.~\ref{fig:approx}-$b$) and then to estimate the
+\color{blue}
+To implement the integration on $\Ball{R}{\vx} \cap \Shape$ (Fig.~\ref{fig:approx}-$a$), we tried several approaches.
+
+\subsection{Per Vertex Real-time Computation on GPU}
+\label{sec:hierarchical}
+
+\paragraph{Naive Approach.}
+A first simple solution , consists in scanning all digital
+\normalcolor
+points inside the integration domain (Fig.~\ref{fig:approx}-$b$) and then to estimate the
 geometrical moment as the sum of the geometrical moments of each elementary
-cubes lying in the intersection. On GPU, \emph{mipmap} textures are used to
-obtain a multi-resolution information: if the input binary object is stored in a
-3D texture, GPU hardware can construct a multi-resolution pyramid such that 8
+cubes lying in the intersection. 
+\color{blue}
+This is exactly similar to what is done on the CPU, but on the GPU, we can
+exploit \emph{mipmap} textures to obtain a multi-resolution information.
+\normalcolor
+If the input binary object is stored in a
+3D texture, GPU hardware constructs a multi-resolution pyramid (mipmap) such that 8
 neighboring voxel intensities at level $l$ are averaged to define the voxel
 value at level $l+1$. If the level 0 corresponds to the binary input object, at
-a given level $l$, a voxel $(x,y,z)$ contains the fraction of $\DSh$ belonging
+\color{blue}
+a given level $l$, a texture probe returns a voxel $(x,y,z)$, containing the fraction of $\DSh$ belonging
+\normalcolor
 to the cube of center $(x,y,z)$ and edge length $2^l$. As a consequence, we can
 approximate the volume of $\Ball{R}{\vx}\cap\Shape$ by considering mipmap values
-at a given resolution $l$ (Fig.~\ref{fig:approx}-$c$). In this case, errors only
+at a given resolution $l$ (Fig.~\ref{fig:approx}-$c,d$). In this case, errors only
 occurs for cells lying inside $\Shape$ (with density 1) not entirely covered by
@@
     {\includegraphics[width=4.0cm]{figs/approx-reg-2}}
+    %TODO image Mipmap 3eme Niveau
   \end{center}
   \vspace{-0.35cm}
-  \caption{Integral computation with an area estimation (\emph{left}) from pixel
-    counting (\emph{middle}) or from densities (represented by different
-    gray values) in a mipmap approximation of $\Shape$ (\emph{right}).}
+  \caption{Integral computation with an area estimation (\emph{left}) 
+  \color{blue}
+  	from mipmaps at level $l=0$ (note that this is the same as pixel counting) \emph{middle-left}
+  	from mipmaps at level $l=1$ \emph{middle-right}
+  	from mipmaps at level $l=2$ \emph{right}
+  	We can note that the higher the mipmap level, the more we approximate our integrand, and the less texture probe we need to do.
+    \normalcolor}
   \label{fig:approx}
@@
 
+\begin{figure}
+  \vspace{-0.35cm}
+  \begin{center}
+    {\includegraphics[width=4cm]{figs/approx-bh}}
+    %{\includegraphics[width=4cm]{figs/approx-ada}}
+    %TODO Image alignement cellules mipmaps
+  \end{center}
+  \vspace{-0.35cm}
+  \caption{Adaptive approximation of the integration using a
+    hierarchical decomposition of the ball $\Ball{R}{\vx}$ }
+    %(\emph{left}), or a decomposition of $\Ball{R}{\vx}\cap\Shape$ (\emph{right}).}
+  \label{fig:approx2}
+  \vspace{-0.35cm}
+\end{figure}
+
+We describe here two different visualization pipeline on GPU that will
+be evaluated in the next section.
+
+\paragraph{Hierarchical Decomposition.}  
+\color{blue}
 Using the hierarchical nature of the mipmap texture, we could also
-consider hierarchical decompositions of either $\Ball{R}{\vx}$
-(Fig.~\ref{fig:approx2}-$a$) or $\Ball{R}{\vx}\cap\Shape$
-(Fig.~\ref{fig:approx2}-$b$). The idea would be to decompose the
+consider hierarchical decompositions of $\Ball{R}{\vx}$
+(Fig.~\ref{fig:approx2}-$a$) 
+%or $\Ball{R}{\vx}\cap\Shape$
+%(Fig.~\ref{fig:approx2}-$b$). 
+The idea would be to decompose the
 regions into mipmap cells of different resolution in order to limit
 the number of texture access (important bottleneck on GPU hardwares)
-and to get better approximated quantities. Note that the scenario in
-Fig.~\ref{fig:approx2}-$b$ is clearly the best approach: the
-volume is exact  (\wrt the regular grid case) since geometrical moments
-are additive quantities, and the number of texture fetches is  optimal
-at this point.
-
-\begin{figure}
-  \vspace{-0.35cm}
-  \begin{center}
-    {\includegraphics[width=4cm]{figs/approx-bh}}
-    {\includegraphics[width=4cm]{figs/approx-ada}}
-  \end{center}
-  \vspace{-0.35cm}
-  \caption{Adaptive approximation of the integration using a
-    hierarchical decomposition of the ball $\Ball{R}{\vx}$ (\emph{left}), or a decomposition of $\Ball{R}{\vx}\cap\Shape$ (\emph{right}).}
-  \label{fig:approx2}
-  \vspace{-0.35cm}
-\end{figure}
-
-\subsection{Per Vertex Real-time Computation on GPU}
-\label{sec:hierarchical}
-
-We describe here two different visualization pipeline on GPU that will
-be evaluated in the next section.
-
-\paragraph{Hierarchical Decomposition.}  As discussed above, best
-results in terms of texture fetch can be obtained by the approach
-presented in Fig.~\ref{fig:approx2}-$b$. At each vertex, the
-computation algorithm would consist in a recursive decomposition of
-the domain such that a cell is subdivided if it does not belong to
-$\Ball{R}{\vx}\cap\Shape$. However, on the GPU %hardware,
-this approach is
-highly inefficient since the hardware optimizes the parallelism only
-when the micro-program described in the shader has a predictive
-execution flow. Hence, implementing the recursive algorithm (or its
-de-recursified version) requires a lot of branches (conditional
-\emph{if} tests) in the flow. Instead of implementing this approach,
-we have considered a fast hierarchical approximation following
+and to get better approximated quantities. 
+%Note that the scenario in
+%Fig.~\ref{fig:approx2}-$b$ is clearly the best approach: the
+%volume is exact  (\wrt the regular grid case) since geometrical moments
+%are additive quantities, and the number of texture fetches is  optimal
+%at this point.
+%As discussed above, best
+%results in terms of texture fetch can be obtained by the approach
+%presented in Fig.~\ref{fig:approx2}-$b$. 
+%At each vertex, the
+%computation algorithm would consist in a recursive decomposition of
+%the domain such that a cell is subdivided if it does not belong to
+%$\Ball{R}{\vx}\cap\Shape$. However, on the GPU %hardware,
+%this approach is
+%highly inefficient since the hardware optimizes the parallelism only
+%when the micro-program described in the shader has a predictive
+%execution flow. Hence, implementing the recursive algorithm (or its
+%de-recursified version) requires a lot of branches (conditional
+%\emph{if} tests) in the flow. 
+We have thus considered a fast multi-resolution approximation as
 Fig.~\ref{fig:approx2}-$a$: for a given radius $R$, we precompute a
@@
 material (see Section \ref{sec:discussion}).
-
-\paragraph{Dynamic Refinement.} In this approach, we want to optimize
+Still, this method is not fully exploiting the GPU parallelism. 
+The hardware optimizes the parallelism only
+when the micro-program described in the shader has a predictive
+execution flow. Hence, implementing this recursive algorithm (or its
+de-recursified version) requires a lot of branches (conditional
+\emph{if} tests) in the flow. 
+\normalcolor
+
+\paragraph{Dynamic Refinement.} In this last approach, we want to optimize
 the interactivity and the execution flow or parallelism on GPU. The
@@
   % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
-  \emph{Second row:} Mean curvature computed in real-time on a dynamic object.}
+  \emph{Second row:} Mean curvature computed in real-time (around 20 FPS) on a dynamic object.}
   \label{fig:full}

### 2016-01-19 latex/article.tex
minor edits

@@
 \color{blue}
-Here, we focus on curvature tensor estimators.
-Most of them require a parameter fixing the scale
+Here, we focus on curvature tensor estimation (mean/Gaussian curvature, principal curvatures
+directions, \ldots). Most curvature estimators require a parameter fixing the scale
 at which the computation is performed. For short, such parameter
 (integration radius, convolution kernel size, \ldots) specifies a scale for analyzing the object surface, 
-and is naturally related to the amount of perturbation on input data. As a consequence, when using
-such tensors, exploring different values of this parameter is mandatory.
+and is naturally related to the amount of perturbation on input
+data\todo{DC: ``related to a expected signal/noise ratio?''}. As a consequence, when using
+such estimators, exploring different values of this parameter is mandatory.
 However, this is usually an offline process, due to the amount of computations that
-needs to be done.
+needs\todo{DC: needs->need?} to be done.
 \normalcolor
@@
 
-\vspace{0.2cm}
-\color{blue}
-In this paper, we will first present the previous works on
-curvature tensor estimation. Then, we will see how we can
-efficiently extract a triangulation of an object on the GPU
-and finally, we will present how we can evaluate the curvature tensor in
-real time and discuss on the several approaches that we tried.
+\vspace{0.2cm} \color{blue} In this paper, we first present the
+previous works on curvature tensor estimation. Then, we propose na
+efficient GPU approach to extract a triangulated isosurface from a
+digital object. Finally, we propose a fully-parallel  GPU pipeline to compute
+curvature tensor in real time and discuss on experiments. \todo{DC:
+  bof le discuss}
 \normalcolor
@@
 associated one on $\Bd{\Shape}$ in $O\left(h^{\frac{1}{3}}\right)$ for
-convex shapes with at least $C^3$-boundary and bounded curvature.
+convex shapes with at least $C^3$-boundary and bounded curvature
+(setting $R\EqDef kh^\frac{1}{3}$ for some $k\in\R$).
 \normalcolor
@@
 To implement the integration on $\Ball{R}{\vx} \cap \Shape$ (Fig.~\ref{fig:approx}-$a$), we tried several approaches.
+\normalcolor
 
@@
 \paragraph{Naive Approach.}
-A first simple solution , consists in scanning all digital
-\normalcolor
-points inside the integration domain (Fig.~\ref{fig:approx}-$b$) and then to estimate the
+\txtblue{A first simple solution  consists in scanning all digital
+points, at a given resolution, lying inside the integration domain}
+(Fig.~\ref{fig:approx}-$b$) and then \txtblue{estimating} the
 geometrical moment as the sum of the geometrical moments of each elementary
-cubes lying in the intersection. 
+cubes lying in the intersection (see
+Eq.~(\ref{eq:dig-curvature-estimator-k}) to (\ref{eq:dig-curvature-estimator-k2})). 
 \color{blue}
-This is exactly similar to what is done on the CPU, but on the GPU, we can
+This is exactly similar to what is done on the CPU. On  the GPU, we can
 exploit \emph{mipmap} textures to obtain a multi-resolution information.
@@
    \begin{center}
-   	 {\includegraphics[width=0.4\textwidth]{figs/snow_r8}}
-   	 {\includegraphics[width=0.4\textwidth]{figs/xyzrgb_dragon-510_R8_mean}}
-
-     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_min}}
-	 {\includegraphics[width=0.4\textwidth]{figs/dragon_r8}}
-
-     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_max}}
-	 {\includegraphics[width=0.4\textwidth]{figs/dragon_r8_max}}
-
-     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_normales}}
-     {\includegraphics[width=0.4\textwidth]{figs/dragon_r8_normales}}
+   	 {\includegraphics[width=0.45\textwidth]{figs/snow_r8}}
+   	 {\includegraphics[width=0.45\textwidth]{figs/xyzrgb_dragon-510_R8_mean}}
+
+     {\includegraphics[width=0.45\textwidth]{figs/snow_r8_min}}
+	 {\includegraphics[width=0.45\textwidth]{figs/dragon_r8}}
+
+     {\includegraphics[width=0.45\textwidth]{figs/snow_r8_max}}
+	 {\includegraphics[width=0.45\textwidth]{figs/dragon_r8_max}}
+
+     {\includegraphics[width=0.45\textwidth]{figs/snow_r8_normales}}
+     {\includegraphics[width=0.45\textwidth]{figs/dragon_r8_normales}}
 

### 2016-01-19 latex/article.tex
minor edits
ok

@@
 \usepackage{pgfplots}
+\usepackage[normalem]{ulem}
 
@@
 \color{blue}
-Since GPU's are massively parallel, we can do all those computations in parallel 
-to get a very efficient implementation. Please note that
+Since GPU have massively parallel architectures, we can do all those computations in parallel 
+to obtain a very efficient implementation. Please note that
 \normalcolor
@@
 
-\color{blue}
-To implement the integration on $\Ball{R}{\vx} \cap \Shape$ (Fig.~\ref{fig:approx}-$a$), we tried several approaches.
-\normalcolor
+\txtblue{To implement the integration on $\Ball{R}{\vx} \cap \Shape$
+  (Fig.~\ref{fig:approx}-$a$), several strategies have been evaluated.}
 
@@
 This is exactly similar to what is done on the CPU. On  the GPU, we can
-exploit \emph{mipmap} textures to obtain a multi-resolution information.
+exploit \emph{mipmap} textures to obtain  multi-resolution information.
 \normalcolor
@@
 \color{blue}
-a given level $l$, a texture probe returns a voxel $(x,y,z)$, containing the fraction of $\DSh$ belonging
+a given level $l$, a texture probe at  a point $(x,y,z)$ returns the fraction of $\DSh$ belonging
 \normalcolor
@@
 
-We describe here two different visualization pipeline on GPU that will
-be evaluated in the next section.
+\txtblue{\sout{We describe here two different visualization pipeline on GPU that will
+be evaluated in the next section.}}
 
@@
 %(Fig.~\ref{fig:approx2}-$b$). 
-The idea would be to decompose the
-regions into mipmap cells of different resolution in order to limit
+The idea is to decompose the
+ball into mipmap cells of different resolution in order to limit
 the number of texture access (important bottleneck on GPU hardwares)
@@
 %the domain such that a cell is subdivided if it does not belong to
-%$\Ball{R}{\vx}\cap\Shape$. However, on the GPU %hardware,
-%this approach is
-%highly inefficient since the hardware optimizes the parallelism only
-%when the micro-program described in the shader has a predictive
-%execution flow. Hence, implementing the recursive algorithm (or its
-%de-recursified version) requires a lot of branches (conditional
-%\emph{if} tests) in the flow. 
-We have thus considered a fast multi-resolution approximation as
-Fig.~\ref{fig:approx2}-$a$: for a given radius $R$, we precompute a
-hierarchical decomposition of $B_R$. Such decomposition is made of
-octree cells at different resolutions. At a given MC vertex $\vx$, the
-algorithm becomes simple since we just scan the ball cells and
-estimate the area (or other moments) from the mipmap values associated
-to this cell. Note that cells in the $B_R$ decomposition may not be
-aligned with mipmap cells. However, we can use GPU %mipmap
-functionalities which interpolates mipmap values if we probe at
-non-discrete positions. For a given radius $R$, the expected number of
-cells in $B_R$ is in $O(\log{R})$. Implementation details on the
-hierarchical octree representation can be found in the supplementary
-material (see Section \ref{sec:discussion}).
-Still, this method is not fully exploiting the GPU parallelism. 
-The hardware optimizes the parallelism only
-when the micro-program described in the shader has a predictive
-execution flow. Hence, implementing this recursive algorithm (or its
-de-recursified version) requires a lot of branches (conditional
-\emph{if} tests) in the flow. 
-\normalcolor
+%$\Ball{R}{\vx}\cap\Shape$.
+\txtred{On the GPU, computing a hierarchical decomposition of
+  $B_R(\vx)$ at each point $\vx$ is highly inefficient since the
+  hardware optimizes the parallelism only when the micro-program
+  described in the shader has a predictive execution flow. Hence,
+  implementing the recursive algorithm (or its de-recursified version)
+  requires a lot of branches (conditional \emph{if} tests) in the
+  flow.}  We have thus considered a fast multi-resolution
+approximation as illustrated in Fig.~\ref{fig:approx2}-$a$: for a
+given radius $R$, we precompute a hierarchical decomposition of
+$B_R$. Such decomposition is made of octree cells at different
+resolutions. At a given MC vertex $\vx$, the algorithm becomes simple
+since we just scan the ball cells and estimate the area (or other
+moments) from the mipmap values associated to this cell. Note that
+these \txtred{precomputed} cells in the $B_R$ decomposition may not be aligned
+with mipmap cells. However, we can use GPU %mipmap functionalities
+which interpolates mipmap values if we probe at non-discrete
+positions. For a given radius $R$, the expected number of cells in
+$B_R$ is in $O(\log{R})$. Implementation details on the hierarchical
+octree representation can be found in the supplementary material (see
+Section \ref{sec:discussion}). \sout{ Still, this method is not fully
+exploiting the GPU parallelism.  The hardware optimizes the
+parallelism only when the micro-program described in the shader has a
+predictive execution flow. Hence, implementing this recursive
+algorithm (or its de-recursified version) requires a lot of branches
+(conditional \emph{if} tests) in the flow.}\todo{la discussion vient apres}  \normalcolor
 

### 2016-01-20 latex/article.tex
Added figures

@@
 However, this is usually an offline process, due to the amount of computations that
-needs\todo{DC: needs->need?} to be done.
+need to be done.
 \normalcolor
@@
 digital object. Finally, we propose a fully-parallel  GPU pipeline to compute
-curvature tensor in real time and discuss on experiments. \todo{DC:
-  bof le discuss}
+curvature tensor in real time and present our results.
 \normalcolor
@@
 \txtblue{To implement the integration on $\Ball{R}{\vx} \cap \Shape$
-  (Fig.~\ref{fig:approx}-$a$), several strategies have been evaluated.}
+  (Fig.~\ref{fig:notations}), several strategies have been evaluated.}
 
@@
 points, at a given resolution, lying inside the integration domain}
-(Fig.~\ref{fig:approx}-$b$) and then \txtblue{estimating} the
+(Fig.~\ref{fig:approx}-$left$) and then \txtblue{estimating} the
 geometrical moment as the sum of the geometrical moments of each elementary
@@
 approximate the volume of $\Ball{R}{\vx}\cap\Shape$ by considering mipmap values
-at a given resolution $l$ (Fig.~\ref{fig:approx}-$c,d$). In this case, errors only
+at a given resolution $l$ (Fig.~\ref{fig:approx}-$right$). In this case, errors only
 occurs for cells lying inside $\Shape$ (with density 1) not entirely covered by
@@
   \begin{center}
-    {\includegraphics[width=4.0cm]{figs/approx1}}
-    {\includegraphics[width=4.0cm]{figs/approx-reg-1}}
-    {\includegraphics[width=4.0cm]{figs/approx-reg-2}}
-    %TODO image Mipmap 3eme Niveau
+    {\includegraphics[width=4.0cm]{figs/approx-naive}}
+    {\includegraphics[width=4.0cm]{figs/approx-hierarchical}}
+    {\includegraphics[width=4.0cm]{figs/approx-dynamic}}
   \end{center}
   \vspace{-0.35cm}
-  \caption{Integral computation with an area estimation (\emph{left}) 
-  \color{blue}
-  	from mipmaps at level $l=0$ (note that this is the same as pixel counting) \emph{middle-left}
-  	from mipmaps at level $l=1$ \emph{middle-right}
-  	from mipmaps at level $l=2$ \emph{right}
-  	We can note that the higher the mipmap level, the more we approximate our integrand, and the less texture probe we need to do.
-    \normalcolor}
+  \caption{\txtblue{
+  	Here are the three approaches we used to evaluate the integrand.
+  	(\emph{left}) is the naive approach, where we sum all the digital points that are inside the integrand domain
+  	(\emph{middle}) shows the hierarchical decomposition of the ball, thus limiting the number of texture probes to do.
+  	(\emph{right}) illustrates the dynamic approach, we probe the textures at a higher resolution and we refine it at each frame until we reach the finer level.
+    }}
   \label{fig:approx}
@@
 
-\begin{figure}
-  \vspace{-0.35cm}
-  \begin{center}
-    {\includegraphics[width=4cm]{figs/approx-bh}}
-    %{\includegraphics[width=4cm]{figs/approx-ada}}
-    %TODO Image alignement cellules mipmaps
-  \end{center}
-  \vspace{-0.35cm}
-  \caption{Adaptive approximation of the integration using a
-    hierarchical decomposition of the ball $\Ball{R}{\vx}$ }
-    %(\emph{left}), or a decomposition of $\Ball{R}{\vx}\cap\Shape$ (\emph{right}).}
-  \label{fig:approx2}
-  \vspace{-0.35cm}
-\end{figure}
+%\begin{figure}
+%  \vspace{-0.35cm}
+%  \begin{center}
+%    {\includegraphics[width=4cm]{figs/approx-bh}}
+%    %{\includegraphics[width=4cm]{figs/approx-ada}}
+%  \end{center}
+%  \vspace{-0.35cm}
+%  \caption{Adaptive approximation of the integration using a
+%    hierarchical decomposition of the ball $\Ball{R}{\vx}$ }
+%    %(\emph{left}), or a decomposition of $\Ball{R}{\vx}\cap\Shape$ (\emph{right}).}
+%  \label{fig:approx2}
+%  \vspace{-0.35cm}
+%\end{figure}
 
@@
 Using the hierarchical nature of the mipmap texture, we could also
-consider hierarchical decompositions of $\Ball{R}{\vx}$
-(Fig.~\ref{fig:approx2}-$a$) 
+consider hierarchical decompositions of $\Ball{R}{\vx}$.
+%(Fig.~\ref{fig:approx}-$middle$) 
 %or $\Ball{R}{\vx}\cap\Shape$
@@
   flow.}  We have thus considered a fast multi-resolution
-approximation as illustrated in Fig.~\ref{fig:approx2}-$a$: for a
+approximation as illustrated in Fig.~\ref{fig:approx}-$middle$: for a
 given radius $R$, we precompute a hierarchical decomposition of
@@
 integration is simply computed using a regular grid at different
-resolution $l$ (Fig. \ref{fig:approx}-$b$ and $c$). The shader code
+resolution $l$ (Fig. \ref{fig:approx}-$right$). The shader code
 becomes trivial (simple triple loop) and a lot of texture fetches are

### 2016-01-24 latex/article.tex
minor fix + adding macro for blue text => easier to remove after

@@
 settings of the geometry processing tool.
-\color{blue}
+\txtblue{
 Here, we focus on curvature tensor estimation (mean/Gaussian curvature, principal curvatures
@@
 However, this is usually an offline process, due to the amount of computations that
-need to be done.
-\normalcolor
+need to be done.}
 %In this work, we present an interactive visualization of volumetric data isosurfaces combined with
@@
 
-\vspace{0.2cm} \color{blue} In this paper, we first present the
-previous works on curvature tensor estimation. Then, we propose na
+\vspace{0.2cm} \txtblue{In this paper, we first present the
+previous works on curvature tensor estimation. Then, we propose an
 efficient GPU approach to extract a triangulated isosurface from a
 digital object. Finally, we propose a fully-parallel  GPU pipeline to compute
-curvature tensor in real time and present our results.
-\normalcolor
+curvature tensor in real time and present our results.}
 
@@
 on $\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to the
-\color{blue}
+\txtblue{
 associated one on $\Bd{\Shape}$ in $O\left(h^{\frac{1}{3}}\right)$ for
 convex shapes with at least $C^3$-boundary and bounded curvature
-(setting $R\EqDef kh^\frac{1}{3}$ for some $k\in\R$).
-\normalcolor
+(setting $R\EqDef kh^\frac{1}{3}$ for some $k\in\R$).}
 %
@@
 % Equation~20 of \cite{CVIU2014} for more details).
-\color{blue}
+\txtblue{
 These estimators are proven convergent in $O\left(h^{\frac{1}{3}}\right)$ when setting the ball
@@
 maximal curvature of the shape, on convex shapes with at least $C^3$-boundary
-and bounded curvature \cite{CVIU2014}.
-\normalcolor 
+and bounded curvature \cite{CVIU2014}.}
 %More formally, it leads to:
@@
 GPU at each vertex of the generated triangulated mesh.
-\color{blue}
+\txtblue{
 Since GPU have massively parallel architectures, we can do all those computations in parallel
-to obtain a very efficient implementation. Please note that
-\normalcolor
+to obtain a very efficient implementation. Please note that}
 when the LoD criterion is removed, each MC vertex is exactly centered at
@@
 Eq.~(\ref{eq:dig-curvature-estimator-k}) to (\ref{eq:dig-curvature-estimator-k2})).
-\color{blue}
+\txtblue{
 This is exactly similar to what is done on the CPU. On  the GPU, we can
-exploit \emph{mipmap} textures to obtain  multi-resolution information.
-\normalcolor
+exploit \emph{mipmap} textures to obtain  multi-resolution information.}
 If the input binary object is stored in a
@@
 value at level $l+1$. If the level 0 corresponds to the binary input object, at
-\color{blue}
-a given level $l$, a texture probe at  a point $(x,y,z)$ returns the fraction of $\DSh$ belonging
-\normalcolor
+\txtblue{
+a given level $l$, a texture probe at  a point $(x,y,z)$ returns the fraction of $\DSh$ belonging}
 to the cube of center $(x,y,z)$ and edge length $2^l$. As a consequence, we can
@@
 \paragraph{Hierarchical Decomposition.}
-\color{blue}
+\txtblue{
 Using the hierarchical nature of the mipmap texture, we could also
@@
 algorithm (or its de-recursified version) requires a lot of branches
-(conditional \emph{if} tests) in the flow.}\todo{la discussion vient apres}  \normalcolor
+(conditional \emph{if} tests) in the flow.}\todo{la discussion vient apres}}
 

### 2016-01-24 latex/article.tex
minor fix

@@
 Curvature estimation on discrete or digital surface has also been
-widely investigated. In \cite{CVIU2014}, authors propose digital
+widely investigated. In~\cite{CVIU2014}, authors propose digital
 versions of Integral Invariant estimators
@@
 digital object. Finally, we propose a fully-parallel  GPU pipeline to compute
-curvature tensor in real time and present our results.}
+curvature tensor in real-time and present our results.}
 
@@
 and boundaries of digital shapes $\DigBoundary{Z}$. We denote by $\DSh$ the
-Gauss digitization of $\Shape$ in a $d-$dimensional grid with grid step $h$,
+Gauss digitization of \comJeremy{a shape $\Shape \subset \R^d$ } in a $d-$dimensional grid with grid step $h$,
 \emph{i.e.}  $\DSh \EqDef \{ \vz \in \Z^d,\, h\cdot\vz\in\Shape\}$. For such
@@
 $\partial\Body{Z}{h}$ are topological boundaries of objects lying in the same
-space (see Fig. \ref{fig:notations}-b). Note that the combinatorial digital
+space (see Fig.~\ref{fig:notations}-b). Note that the combinatorial digital
 boundary $\DigBoundary{Z}$ of $Z$ made of cells in a cellular Cartesian complex
@@
           \put(1.5,10){$\partial \Shape$}
-          \put(15,7){$\partial \Body{\DSh}{h}$}
+          \put(15,7){$\partial \Body{Z}{h}$}
       \end{overpic}}
@@
     \end{center}}
-    \caption{Integral invariant computation (\emph{left}) and
-      notations (\emph{right}) in dimension 2 \cite{CVIU2014}.\label{fig:notations}}
+    %
+    \caption{Integral invariant computation (\emph{left}) and notations
+    (\emph{right}) in dimension 2~\cite{CVIU2014}.\label{fig:notations}}
+    %
     \vspace{-0.35cm}
@@
 
-In \cite{DGCI2013}, estimators are defined based on the 2D digital curvature estimator
-$\CurvH{R}$ and the 3D digital mean curvature estimator $\MeanCurvH{R}$ based on
-the digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ (we denote such
-quantity $\AreaC(Y,h)$ in dimension 2):
+In~\cite{DGCI2013}, \comJeremy{the 2D digital curvature estimator $\CurvH{R}$
+and the 3D digital mean curvature estimator $\MeanCurvH{R}$ are based on the
+digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ (we denote such
+quantity $\AreaC(Y,h)$ in dimension 2):}
 %% Redite
@@
   Given the Gauss digitization $Z\EqDef\DSh$ of a shape $\Shape \subset \R^2$
-  (or $\R^3$ for the 3D mean curvature estimator), {\em digital curvature
+  (or $\R^3$ for the 3D mean curvature estimator), \emph{digital curvature
   estimators} are defined for any point $\vx \in \R^2$ (or $\R^3$) as:
+  %
+  \vspace{-0.05cm}
   %
@@
 %
-Estimators of both 2D curvature and 3D mean curvature on digital
-objects with volumetric integral information are proved to be multigrid convergent
-property \cite{DGCI2013}. For short, when the digital object becomes finer and
-finer, \ie when the digitization step $h$ tends to zero, the estimated quantity
-on $\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to the
-\txtblue{
-associated one on $\Bd{\Shape}$ in $O\left(h^{\frac{1}{3}}\right)$ for
-convex shapes with at least $C^3$-boundary and bounded curvature
-(setting $R\EqDef kh^\frac{1}{3}$ for some $k\in\R$).}
+\comJeremy{Estimators of both 2D curvature and 3D mean curvature on digital
+objects with volumetric integral information are proved to be multigrid
+convergent~\cite{DGCI2013}.}
+%
+For short, when the digital object becomes finer and finer, \ie when the
+digitization step $h$ tends to zero, the estimated quantity on
+$\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to the
+\txtblue{ associated one on $\Bd{\Shape}$ in $O\left(h^{\frac{1}{3}}\right)$ for
+convex shapes with at least $C^3$-boundary and bounded curvature (setting
+$R\EqDef kh^\frac{1}{3}$ for some $k\in\R$).}
 %
@@
 
-In \cite{CVIU2014}, authors have also defined 3D digital principal curvature
+In~\cite{CVIU2014}, authors have also defined 3D digital principal curvature
 estimators $\PrincCurvH{1}{R}$ and $\PrincCurvH{2}{R}$ on $Z\subset\Z^3$ based
@@
   Given the Gauss digitization $Z \EqDef \DSh$ of a shape $\Shape \subset \R^3$,
-  {\em 3D digital principal curvature estimators} are defined for any point $\vx
+  \emph{3D digital principal curvature estimators} are defined for any point $\vx
   \in \R^3$ as:
@@
   where $\hat{\lambda}_1$ and $\hat{\lambda}_2$ are the two greatest eigenvalues
-  of the covariance matrix of the intersection between the digital shape
-  $\DigShape$ and a ball of digital radius $R/h$ centered on digital point
-  $\vx/h$.
+  of the covariance matrix of \comJeremy{$\Ball{R/h}{\vx/h} \cap Z$.}
+  % the intersection between the digital shape
+  % $\DigShape$ and a ball of digital radius $R/h$ centered on digital point
+  % $\vx/h$.
   %
@@
 %
-The covariance matrix needs to compute digital moments of order $0$, order $1$
-and order $2$ (see Equation~20 of \cite{CVIU2014} for more details).
+The covariance matrix needs to compute digital moments of order $0$, $1$
+and $2$ (see Equation~20 of~\cite{CVIU2014} for more details).
 % ($\DMom{000}{h}$), of order $1$ ($\DMom{100}{h}$, $\DMom{010}{h}$ and
@@
 maximal curvature of the shape, on convex shapes with at least $C^3$-boundary
-and bounded curvature \cite{CVIU2014}.}
+and bounded curvature~\cite{CVIU2014}.}
 %More formally, it leads to:
@@
 direction $\NormalDirH{R}$ at $\vx$. Convergence results can be found
-in \cite{ChapterIICurvature}.
+in~\cite{ChapterIICurvature}.
 %%% Changer avec le chapitre de Jaco à un moment
@@
 It has been shown that the radius of the ball depends on the geometry of the
-underlying shape. In \cite{DGCI2014}, a proposal was made for a parameter-free
+underlying shape. In~\cite{DGCI2014}, a proposal was made for a parameter-free
 estimation of the radius of the ball by analyzing the shape \wrt the local shape
-geometry using maximal digital straight segments of the digital boundary. In
-\cite{SMI2015}, these estimators have been analyzed in scale-space (for a range of radii)  for a given digital shape. This allows to detect features of the
-shape thanks to the behavior of estimators on singularities.
+geometry using maximal digital straight segments of the digital boundary.
+In~\cite{SMI2015}, these estimators have been analyzed in scale-space (for a
+range of radii) for a given digital shape. This allows to detect features of
+the shape thanks to the behavior of estimators on singularities.
 
@@
 consider different ball radius which could be time consuming when implemented on
-CPU. We propose here a fully parallel implementation on GPU allowing us to
+CPU\@. We propose here a fully parallel implementation on GPU allowing us to
 change the radius and thus update the estimated quantities in real-time.
@@
 %from a Marching Cubes approach \cite{lorensen1987marching} (MC for short): the
-using Marching Cubes \cite{lorensen1987marching} (MC for short): the
+using Marching Cubes~\cite{lorensen1987marching} (MC for short): the
 triangulation is generated from local triangle patches computed on
@@
 %Since triangle patches are locally computed,
-Such approach is fully parallel and easy to implement on the GPU.
+Such approach is fully parallel and easy to implement on the GPU\@.
 However, since adjacent cells may not have the same depth
@@
   %Based on LoD criterion evaluation, the cell buffer is updated between each frame \emph{(right)}.
-  }
-  \label{fig_lod_octree}
+  }\label{fig_lod_octree}
 \end{figure}
@@
     represented in green and computations in red. Each computation
-    retrieves data from a buffer and fills a new one. }
-  \label{fig_pipeline}
+    retrieves data from a buffer and fills a new one.}\label{fig_pipeline}
 \end{figure}
@@
 \txtblue{
-This is exactly similar to what is done on the CPU. On  the GPU, we can
+This is exactly similar to what is done on the CPU\@. On  the GPU, we can
 exploit \emph{mipmap} textures to obtain  multi-resolution information.}
@@
   	(\emph{right}) illustrates the dynamic approach, we probe the textures at a higher resolution and we refine it at each frame until we reach the finer level.
-    }}
-  \label{fig:approx}
+    }}\label{fig:approx}
   \vspace{-0.35cm}
@@
 octree representation can be found in the supplementary material (see
-Section \ref{sec:discussion}). \sout{ Still, this method is not fully
+Section~\ref{sec:discussion}). \sout{ Still, this method is not fully
 exploiting the GPU parallelism.  The hardware optimizes the
@@
 \paragraph{Dynamic Refinement.} In this last approach, we want to optimize
-the interactivity and the execution flow or parallelism on GPU. The
+the interactivity and the execution flow or parallelism on GPU\@. The
 integration is simply computed using a regular grid at different
-resolution $l$ (Fig. \ref{fig:approx}-$right$). The shader code
+resolution $l$ (Fig.~\ref{fig:approx}-$right$). The shader code
 becomes trivial (simple triple loop) and a lot of texture fetches are
@@
 \item When the surface geometry has been computed, we set the current
-  level $l$ at an high level $l\EqDef l_{max}$ of the mipmap
+  level $l$ at an high level $l\EqDef l_{\max}$ of the mipmap
   pyramid.
@@
 refines the estimation. Even if step 2 is quite expensive, in
-$O\left(\left(\frac{R}{2^l}\right)^3\right)$, the interactive control
+$O\left(\left({\frac{R}{2^l}}\right)^3\right)$, the interactive control
 in step 3 considerably improves the interactive exploration of the
@@
   % \emph{Second row:} (Zoom of) First and second principal directions estimation on an OctaFlower.
-  \emph{Second row:} Mean curvature computed in real-time (around 20 FPS) on a dynamic object.}
-  \label{fig:full}
+  \emph{Second row:} Mean curvature computed in real-time (around 20 FPS) on a dynamic object.}\label{fig:full}
   \vspace{-0.35cm}
@@
   l_0$ approximation algorithms. The object is triangulated at full resolution
-  with a regular grid and contains 282,396 vertices.
-  %
-  \label{tab:full-res-stat}}
+  with a regular grid and contains 282,396 vertices.\label{tab:full-res-stat}}
   %
@@
   \vspace{-0.35cm}
-  \caption{Illustration of mean curvature computation on ``OctaFlower'' (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
+  \caption{Illustration of mean curvature computation on ``OctaFlower'' (digital domain of $130^3$) using mipmap approximation with different levels: $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
   %
   %For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}
-  }
-  \label{fig:refine}
+  }\label{fig:refine}
   \vspace{-0.35cm}
@@
   \caption{Timings in milliseconds (in logscale) obtained while visualizing an adaptive
-  triangulation on three objects -- ``OctaFlower'' (digital domain of $130^3$ ), ``Snow microstructures'' ($233^3$) and ``XYZ-Dragon'' ($510^3$) --  by computing the
+  triangulation on three objects -- ``OctaFlower'' (digital domain of $130^3$), ``Snow microstructures'' ($233^3$) and ``XYZ-Dragon'' ($510^3$) --  by computing the
   curvature with a regular grid (\emph{left}) and with hierarchical
@@
   %
-  Timings are given using a NVIDIA GeForce GTX 850M GPU.
-  }
-  %
-  \label{fig:timings}
+  Timings are given using a NVIDIA GeForce GTX 850M GPU\@.
+  }\label{fig:timings}
   \vspace{-0.35cm}
@@
   and $R=8$). Normal vectors are colored with a mapping of their
-  component to RGB color space.}
-   \label{fig:adaptive}
+  component to RGB color space.}\label{fig:adaptive}
    \vspace{-0.35cm}
@@
 on both a linear octree representation with Morton codes and an
-efficient integral computation on GPU. The source code and additional
+efficient integral computation on GPU\@. The source code and additional
 material (video, \ldots) are available on the project website

### 2016-01-24 latex/article.tex
minor edit

@@
 
-\newcommand{\ie}{\emph{i.e.} }
-\newcommand{\eg}{\emph{e.g.} }
-\newcommand{\wrt}{\emph{w.r.t.} }
-\newcommand{\wnlog}{w.l.o.g. }
+\newcommand{\ie}{\emph{i.e.}\xspace}
+\newcommand{\eg}{\emph{e.g.}\xspace}
+\newcommand{\wrt}{\emph{w.r.t.}\xspace}
+\newcommand{\wnlog}{w.l.o.g.\xspace}
 \newcommand{\Zr}{\ensuremath{\mathbb{Z}[\rho]}}
@@
 cells have a visibility ratio greater than  constant $k$\,;
-  \item $c$ and its sibling cells are merged if their parent cell $c'$ has a visibility ratio lower than $k$\;
+  \item $c$ and its sibling cells are merged if their parent cell $c'$ has a visibility ratio lower than $k$\,;
   \item otherwise, the cell $c$ stays for the next frame.
@@
 refines the estimation. Even if step 2 is quite expensive, in
-$O\left(\left({\frac{R}{2^l}}\right)^3\right)$, the interactive control
+$O\left({\left({\frac{R}{2^l}}\right)}^3\right)$, the interactive control
 in step 3 considerably improves the interactive exploration of the

### 2016-01-25 latex/article.tex
Aucun souvenir de ce que j'ai fait (probablement juste ouvert le fichier)

--- 2016-01-24 latex/article.tex
@@
 settings of the geometry processing tool.
-\txtblue{
+\color{blue}
 Here, we focus on curvature tensor estimation (mean/Gaussian curvature, principal curvatures
@@
 However, this is usually an offline process, due to the amount of computations that
-need to be done.}
+need to be done.
+\normalcolor
 %In this work, we present an interactive visualization of volumetric data isosurfaces combined with
@@
 
-\vspace{0.2cm} \txtblue{In this paper, we first present the
-previous works on curvature tensor estimation. Then, we propose an
+\vspace{0.2cm} \color{blue} In this paper, we first present the
+previous works on curvature tensor estimation. Then, we propose na
 efficient GPU approach to extract a triangulated isosurface from a
 digital object. Finally, we propose a fully-parallel  GPU pipeline to compute
-curvature tensor in real time and present our results.}
+curvature tensor in real time and present our results.
+\normalcolor
 
@@
 on $\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to the
-\txtblue{
+\color{blue}
 associated one on $\Bd{\Shape}$ in $O\left(h^{\frac{1}{3}}\right)$ for
 convex shapes with at least $C^3$-boundary and bounded curvature
-(setting $R\EqDef kh^\frac{1}{3}$ for some $k\in\R$).}
+(setting $R\EqDef kh^\frac{1}{3}$ for some $k\in\R$).
+\normalcolor
 %
@@
 % Equation~20 of \cite{CVIU2014} for more details).
-\txtblue{
+\color{blue}
 These estimators are proven convergent in $O\left(h^{\frac{1}{3}}\right)$ when setting the ball
@@
 maximal curvature of the shape, on convex shapes with at least $C^3$-boundary
-and bounded curvature \cite{CVIU2014}.}
+and bounded curvature \cite{CVIU2014}.
+\normalcolor 
 %More formally, it leads to:
@@
 GPU at each vertex of the generated triangulated mesh.
-\txtblue{
+\color{blue}
 Since GPU have massively parallel architectures, we can do all those computations in parallel 
-to obtain a very efficient implementation. Please note that}
+to obtain a very efficient implementation. Please note that
+\normalcolor
 when the LoD criterion is removed, each MC vertex is exactly centered at
@@
 Eq.~(\ref{eq:dig-curvature-estimator-k}) to (\ref{eq:dig-curvature-estimator-k2})). 
-\txtblue{
+\color{blue}
 This is exactly similar to what is done on the CPU. On  the GPU, we can
-exploit \emph{mipmap} textures to obtain  multi-resolution information.}
+exploit \emph{mipmap} textures to obtain  multi-resolution information.
+\normalcolor
 If the input binary object is stored in a
@@
 value at level $l+1$. If the level 0 corresponds to the binary input object, at
-\txtblue{
-a given level $l$, a texture probe at  a point $(x,y,z)$ returns the fraction of $\DSh$ belonging}
+\color{blue}
+a given level $l$, a texture probe at  a point $(x,y,z)$ returns the fraction of $\DSh$ belonging
+\normalcolor
 to the cube of center $(x,y,z)$ and edge length $2^l$. As a consequence, we can
@@
   \begin{center}
-    {\includegraphics[width=4.0cm]{figs/approx-naive}}
-    {\includegraphics[width=4.0cm]{figs/approx-hierarchical}}
-    {\includegraphics[width=4.0cm]{figs/approx-dynamic}}
+    \raisebox{-0.5\height}{\includegraphics[width=4.0cm]{figs/approx-naive}}
+    \raisebox{-0.5\height}{\includegraphics[width=4.0cm]{figs/approx-hierarchical}}
+    \raisebox{-0.5\height}{\includegraphics[width=4.0cm]{figs/approx-dynamic}}
   \end{center}
@@
 \paragraph{Hierarchical Decomposition.}  
-\txtblue{
+\color{blue}
 Using the hierarchical nature of the mipmap texture, we could also
@@
 algorithm (or its de-recursified version) requires a lot of branches
-(conditional \emph{if} tests) in the flow.}\todo{la discussion vient apres}}
+(conditional \emph{if} tests) in the flow.}\todo{la discussion vient apres}  \normalcolor
 

### 2016-01-25 latex/article.tex
added raisebox and "..." to figure 5

--- 2016-01-24 latex/article.tex
@@
   \begin{center}
-    {\includegraphics[width=4.0cm]{figs/approx-naive}}
-    {\includegraphics[width=4.0cm]{figs/approx-hierarchical}}
-    {\includegraphics[width=4.0cm]{figs/approx-dynamic}}
+    \raisebox{60pt}{\includegraphics[width=3.7cm]{figs/approx-naive}}
+    \hfill
+    \raisebox{60pt}{\includegraphics[width=3.7cm]{figs/approx-hierarchical}}
+    \hfill
+    \includegraphics[width=3.7cm]{figs/approx-dynamic}
   \end{center}

### 2016-01-26 latex/article.tex
ok

@@
 (integration radius, convolution kernel size, \ldots) specifies a scale for analyzing the object surface,
-and is naturally related to the amount of perturbation on input
-data\todo{DC: ``related to a expected signal/noise ratio?''}. As a consequence, when using
+and is naturally related to the amount allowed perturbations on input
+data. As a consequence, when using
 such estimators, exploring different values of this parameter is mandatory.
@@
 %exploring 3D structures in Material Sciences \todo{REF}.
-
-\vspace{0.2cm}
 
@@
 invariant curvature estimators.
-
-\vspace{0.2cm}
 
@@
 
-\vspace{0.2cm} \txtblue{In this paper, we first present the
+\txtblue{In this paper, we first present the
 previous works on curvature tensor estimation. Then, we propose an
@@
 
-In~\cite{DGCI2013}, \comJeremy{the 2D digital curvature estimator $\CurvH{R}$
-and the 3D digital mean curvature estimator $\MeanCurvH{R}$ are based on the
-digital volumetric integral $\VolC(Y,h) \EqDef h^d \MCard(Y)$ (we denote such
-quantity $\AreaC(Y,h)$ in dimension 2):}
+In~\cite{DGCI2013}, \comJeremy{authors define a  2D digital curvature estimator $\CurvH{R}$
+and a 3D digital mean curvature estimator $\MeanCurvH{R}$  based on the
+digital volume estimator $\VolC(Y,h) \EqDef h^d \MCard(Y)$ (area estimator $\AreaC(Y,h)$ in dimension 2):}
 %% Redite
@@
 %
-\comJeremy{Estimators of both 2D curvature and 3D mean curvature on digital
-objects with volumetric integral information are proved to be multigrid
-convergent~\cite{DGCI2013}.}
-%
-For short, when the digital object becomes finer and finer, \ie when the
-digitization step $h$ tends to zero, the estimated quantity on
-$\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to the
-\txtblue{ associated one on $\Bd{\Shape}$ in $O\left(h^{\frac{1}{3}}\right)$ for
-convex shapes with at least $C^3$-boundary and bounded curvature (setting
-$R\EqDef kh^\frac{1}{3}$ for some $k\in\R$).}
+\comJeremy{Such curvature estimators have multigrid convergence
+  properties~\cite{DGCI2013}:} For short, when
+the digital object becomes finer and finer, \ie when the digitization
+step $h$ tends to zero, the estimated quantity on
+$\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to
+the \txtblue{ associated one on $\Bd{\Shape}$ in
+  $O\left(h^{\frac{1}{3}}\right)$ for convex shapes with at least
+  $C^3$-boundary and bounded curvature (setting $R\EqDef
+  kh^\frac{1}{3}$ for some $k\in\R$).}
 %
@@
 %\end{align}
-
 Additionally, eigenvectors associated to $\hat{\lambda}_1$ and
@@
 
-\txtblue{\sout{We describe here two different visualization pipeline on GPU that will
-be evaluated in the next section.}}
+%\txtblue{\sout{We describe here two different visualization pipeline on GPU that will
+ %   be evaluated in the next section.}}
 
@@
 octree representation can be found in the supplementary material (see
-Section~\ref{sec:discussion}). \sout{ Still, this method is not fully
-exploiting the GPU parallelism.  The hardware optimizes the
-parallelism only when the micro-program described in the shader has a
-predictive execution flow. Hence, implementing this recursive
-algorithm (or its de-recursified version) requires a lot of branches
-(conditional \emph{if} tests) in the flow.}\todo{la discussion vient apres}}
+Section~\ref{sec:discussion}).}
+%\sout{ Still, this method is not fully
+%exploiting the GPU parallelism.  The hardware optimizes the
+%parallelism only when the micro-program described in the shader has a
+%predictive execution flow. Hence, implementing this recursive
+%algorithm (or its de-recursified version) requires a lot of branches
+%(conditional \emph{if} tests) in the flow.}\todo{la discussion vient apres}}
 
@@
    \begin{center}
-   	 {\includegraphics[width=0.45\textwidth]{figs/snow_r8}}
-   	 {\includegraphics[width=0.45\textwidth]{figs/xyzrgb_dragon-510_R8_mean}}
-
-     {\includegraphics[width=0.45\textwidth]{figs/snow_r8_min}}
-	 {\includegraphics[width=0.45\textwidth]{figs/dragon_r8}}
-
-     {\includegraphics[width=0.45\textwidth]{figs/snow_r8_max}}
-	 {\includegraphics[width=0.45\textwidth]{figs/dragon_r8_max}}
-
-     {\includegraphics[width=0.45\textwidth]{figs/snow_r8_normales}}
-     {\includegraphics[width=0.45\textwidth]{figs/dragon_r8_normales}}
+   	 {\includegraphics[width=0.4\textwidth]{figs/snow_r8}}
+   	 {\includegraphics[width=0.4\textwidth]{figs/xyzrgb_dragon-510_R8_mean}}
+
+     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_min}}
+	 {\includegraphics[width=0.4\textwidth]{figs/dragon_r8}}
+
+     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_max}}
+	 {\includegraphics[width=0.4\textwidth]{figs/dragon_r8_max}}
+
+     {\includegraphics[width=0.4\textwidth]{figs/snow_r8_normales}}
+     {\includegraphics[width=0.4\textwidth]{figs/dragon_r8_normales}}
 

### 2016-01-26 latex/article.tex
ok

@@
 \comJeremy{Such curvature estimators have multigrid convergence
-  properties~\cite{DGCI2013}:} For short, when
-the digital object becomes finer and finer, \ie when the digitization
-step $h$ tends to zero, the estimated quantity on
-$\Bd{\Body{\DSh}{h}}$ converges (theoretically and experimentally) to
-the \txtblue{ associated one on $\Bd{\Shape}$ in
-  $O\left(h^{\frac{1}{3}}\right)$ for convex shapes with at least
+  properties~\cite{DGCI2013}:} when the digital object becomes finer
+and finer, \ie when the digitization step $h$ tends to zero, the
+estimated quantities on $\Bd{\Body{\DSh}{h}}$ converges (theoretically
+and experimentally) to the \txtblue{ associated one on $\Bd{\Shape}$
+  in $O\left(h^{\frac{1}{3}}\right)$ for convex shapes with at least
   $C^3$-boundary and bounded curvature (setting $R\EqDef

### 2016-01-26 latex/article.tex
minor

@@
 Here, we focus on curvature tensor estimation (mean/Gaussian curvature, principal curvatures
-directions, \ldots). Most curvature estimators require a parameter fixing the scale
+directions\ldots). Most curvature estimators require a parameter fixing the scale
 at which the computation is performed. For short, such parameter
-(integration radius, convolution kernel size, \ldots) specifies a scale for analyzing the object surface,
+(integration radius, convolution kernel size\ldots) specifies a scale for analyzing the object surface,
 and is naturally related to the amount allowed perturbations on input

### 2016-01-27 latex/article.tex
moved fig 7 to the bottom of the page 10
final

@@
 the shape thanks to the behavior of estimators on singularities.
-
 As a consequence, for all these integral invariant based approaches, we need to
 consider different ball radius which could be time consuming when implemented on
-CPU\@. We propose here a fully parallel implementation on GPU allowing us to
+CPU. We propose here a fully parallel implementation on GPU allowing us to
 change the radius and thus update the estimated quantities in real-time.
@@
 such a data parallel component is unable to handle recursivity.
-
 %since the GPU
@@
 %to huge payload from cache misses.
-
 Efficient spatial tree encoding can be
@@
 Table~\ref{tab:full-res-stat}) that needs to be considered.
-
+%
+%
 \begin{table}
@@
 \end{table}
-
+%
 \begin{figure}[!htbp]
@@
 \end{figure}
-
+%
 \begin{figure}[!htbp]
@@
 \end{figure}
-
+%
  \begin{figure}[h!]
@@
  \end{figure}
-
  Figure~\ref{fig:adaptive} shows curvature computation and exploration in
